### 2018-12-06 data-analysis/EAll-update.Rmd
add first draft

---
title: "SharedContexts"
output: html_document
---

### Less than 0% accuracy on counting task excluded
### Less than 75% accuracy on flanker task excluded

```{r,include=FALSE,echo=FALSE}
pack<-c("dplyr","ggplot2","pander","knitr","xtable","car","Crump","lsr","afex","stringr","tidyr")
lapply(pack, require, character.only = TRUE)

vjoutNR <- function(x,n) {
  xm <- mean(x)
  xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
             25, 30, 35, 50, 80)
  stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
            2.45, 2.48, 2.5)
  stdindex <- length(xsize[xsize <= length(x)])
  removed <- x[x < xm+sd(x)*stds[stdindex]]
  removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
  proportionRemoved <- length(removed)/length(x)
  finaldata<-c(mean(removed),1-proportionRemoved)
  return(finaldata[[n]])
}
```

```{r}
minACC<- 0.75
minQACC<- 0
RTMax<- 3000
RTMin<- 250
```

```{r, include=FALSE}

## LOAD DATA FROM E1 and E2 ###
load("EAll.Rda")
load("EAllq.Rda")

### ANALYZE QUIZ DATA ###
quizAnalysis <-tbl_df(data)
quizAnalysis <- quizAnalysis %>%
  filter(trialColor == "quiz")

quizAnalysis <- quizAnalysis[,-10:-17]
colnames(quizAnalysis)<- c("subID","trial","trialType","correctResponse","time1","time2","response","ACC","unknown","Subject","block","subBlock","subBlockB","newACC","preCon","preTrialProp", "order")

quizAnalysis <- quizAnalysis %>%
  filter(is.na(response) == FALSE)

quizAnalysis$response<-as.numeric(as.character(quizAnalysis$response))
quizAnalysis$correctResponse<-as.numeric(as.character(quizAnalysis$correctResponse))
quizAnalysis$ACC<-as.numeric(as.character(quizAnalysis$ACC))
quizAnalysis$fineACC<-abs(quizAnalysis$response - quizAnalysis$correctResponse)

quiz.Sum<- quizAnalysis %>%
  group_by(Subject) %>%
  filter(!is.na(fineACC),Subject != 4, Subject != 29) %>%
  summarise(ACC = mean(ACC), fineACC = mean(fineACC))

quiz.Sum

lowQuizACC <- quiz.Sum %>%
  filter(ACC < minQACC) %>%
  .$Subject
### END QUIZ DATA ###

### GET QUESTIONNAIRE DATA ###
questData$expTime<-((as.numeric(as.character(questData$completeTime)) -as.numeric(as.character(questData$startTime)))/1000)/60
questData$Exp<-NA
questData[questData$subnum < 51,]$Exp <- "E1"
questData[questData$subnum > 51,]$Exp <- "E2"
questData <- questData %>%
  select(Exp,subnum,expTime,country,gender,age,handedness,vision,english,browser,count1_Cat,count1_Feat,count1_Prop,count2_Cat,count2_Feat,count2_Prop)

questData_12<-questData

### CLEAN UP DATAFRAME ###
dataAnalysis <- tbl_df(data)
dataAnalysis$Exp<-NA
dataAnalysis[dataAnalysis$Subject < 51,]$Exp <- "E1"
dataAnalysis[dataAnalysis$Subject > 51,]$Exp <- "E2"

dataAnalysis[dataAnalysis$subBlock == 1 | dataAnalysis$subBlock == 3,]$subBlock <- "B1"
dataAnalysis[dataAnalysis$subBlock == 2 | dataAnalysis$subBlock == 4,]$subBlock <- "B2"

dataAnalysis <- dataAnalysis %>%
  filter(trialColor != "quiz",
         Subject != 109)

dataAnalysis <- as.data.frame(lapply(dataAnalysis, function (x) if (is.factor(x)) factor(x) else x))

dataAnalysis$time1<-as.numeric(as.character(dataAnalysis$time1))
dataAnalysis$time2<-as.numeric(as.character(dataAnalysis$time2))

dataAnalysis$ACC<-as.numeric(as.character(dataAnalysis$ACC))
dataAnalysis$RT <- dataAnalysis$time2 - dataAnalysis$time1

dataAnalysis$trialProp<-factor(dataAnalysis$trialProp)
levels(dataAnalysis$trialProp)<-c("biased","biased","unbiased")
dataAnalysis$trialProp <- factor(dataAnalysis$trialProp)

levels(dataAnalysis$countProp) <- c("0% Con", "100% Con")
dataAnalysis$countProp <- factor(dataAnalysis$countProp, levels = c("100% Con","0% Con"))

### Identify subjects with Low ACC ###
ExploreDF <- dataAnalysis %>%
  group_by(Subject,Exp,countProp,trialProp,trialCongruency) %>%
  filter(!is.na(ACC))%>%
  summarise(meanRT = mean(RT), 
            meanAccuracy = mean(ACC), 
            TrialsCompleted = length(RT),
            maxRT = max(RT),
            vjoutRT = mean(vjoutNR(RT,1)),
            removed = vjoutNR(RT,2))

LowACC <- ExploreDF %>%
  filter(meanAccuracy < minACC) %>%
  .$Subject

#### END LOW ACC ###

### SAVE DATAFRAME ###
E12<-dataAnalysis %>%
  select(Exp,Subject,order,block,subBlock,trial,countProp,trialProp,trialCongruency,ACC,RT)

```

```{r, echo=FALSE}
### PRINT ACC STATS ##
print(paste("AVG Quiz ACC in E1 & E2 = ",round(mean(quiz.Sum$ACC), digits=2)))
#print(paste("Subjects with low ACC = ",sort(unique(LowACC))))
print(paste("# of Subjects in E1 & E2 with low ACC = ",length(sort(unique(LowACC)))))

### SAVE LOW ACC IDs ###
LowACC <-c(LowACC,lowQuizACC)
tempLowACC<-LowACC

print(sort(unique(LowACC)))
```

```{r,include=FALSE}
### LOAD DATA ###
load("E3.Rda")
load("E3quiz.Rda")
load("E3q.Rda")

### IDENTIFY REPEAT SUBJECTS ###
load("E3ids.Rda")
ids<-gsub("[^[:alnum:][:blank:]+?&/\\-]", "", ids)
E3ids<-ids
load("E12ids.Rda")
ids<-gsub("[^[:alnum:][:blank:]+?&/\\-]", "", ids)
E12ids<-ids
repeatSub<-intersect(E3ids,E12ids)
#repeatSub<-repeatSub[-11]
### END REPEAT SUBJECTS ###

### GET QUESTIONNAIRE DATA ###
questData$expTime<- ((as.numeric(as.character(questData$completeTime)) - as.numeric(as.character(questData$startTime)))/1000)/60
questData$Exp<- "E3"
questData <- questData %>%
  select(Exp,subnum,expTime,country,gender,age,handedness,vision,english,browser,count1_Cat,count1_Feat,count1_Prop,count2_Cat,count2_Feat,count2_Prop)
questData$subnum = questData$subnum + 110

questData<-rbind(questData_12,questData)
save(questData,file="questDataAll.Rda")
### END QUESTIONNAIRE DATA ####

### ANALYZE QUIZ DATA ###
quizAnalysis <-tbl_df(quizData)
quizAnalysis$Subject<-quizAnalysis$Subject +110
quizAnalysis$response<-as.numeric(as.character(quizAnalysis$response))
quizAnalysis$cResponse<-as.numeric(as.character(quizAnalysis$cResponse))
quizAnalysis$ACC<-as.numeric(as.character(quizAnalysis$ACC))
quizAnalysis$fineACC<-abs(quizAnalysis$response - quizAnalysis$cResponse)

quiz.Sum<- quizAnalysis %>%
  group_by(Subject) %>%
  filter(!is.na(fineACC)) %>%
  summarise(ACC = mean(ACC), fineACC = mean(fineACC))

quiz.Sum

lowQuizACC <- quiz.Sum %>%
  filter(ACC < 0) %>%
  .$Subject
#### END QUIZ DATA ###

### CLEAN UP DATAFRAME ###
dataAnalysis <- tbl_df(data)
dataAnalysis$Exp<-"E3"
dataAnalysis$Subject<-dataAnalysis$Subject + 110

dataAnalysis[dataAnalysis$subBlock == 1 | dataAnalysis$subBlock == 3,]$subBlock <- "B1"
dataAnalysis[dataAnalysis$subBlock == 2 | dataAnalysis$subBlock == 4,]$subBlock <- "B2"

dataAnalysis <- dataAnalysis %>%
  filter(trialGender != "quiz",
         ID%in%repeatSub == FALSE,
         Subject != 139)

dataAnalysis <- as.data.frame(lapply(dataAnalysis, function (x) if (is.factor(x)) factor(x) else x))

dataAnalysis$time1<-as.numeric(as.character(dataAnalysis$time1))
dataAnalysis$time2<-as.numeric(as.character(dataAnalysis$time2))

dataAnalysis$ACC<-as.numeric(as.character(dataAnalysis$ACC))
dataAnalysis$RT <- dataAnalysis$time2 - dataAnalysis$time1

dataAnalysis <- dataAnalysis %>%
  filter(RT < RTMax, RT > RTMin)

dataAnalysis$trialProp<-factor(dataAnalysis$trialProp)
levels(dataAnalysis$trialProp)<-c("biased","biased","unbiased")
dataAnalysis$trialProp <- factor(dataAnalysis$trialProp)

levels(dataAnalysis$countProp) <- c("0% Con", "100% Con")
dataAnalysis$countProp <- factor(dataAnalysis$countProp, levels = c("100% Con","0% Con"))

### Identify subjects with LOW ACC ###
ExploreDF <- dataAnalysis %>%
  group_by(Subject,Exp,countProp,trialProp,trialCongruency) %>%
  summarise(meanRT = mean(RT), 
            meanAccuracy = mean(ACC), 
            TrialsCompleted = length(RT),
            maxRT = max(RT),
            vjoutRT = mean(vjoutNR(RT,1)),
            removed = vjoutNR(RT,2))

LowACC <- ExploreDF %>%
  filter(meanAccuracy < minACC) %>%
  .$Subject

### SAVE AND BIND DATAFRAMES ###
dataAnalysis$Exp<-"E3"

E3<- dataAnalysis %>%
  select(Exp,Subject,order,block,subBlock,trial,countProp,trialProp,trialCongruency,ACC,RT)

dataAnalysis<-rbind(E12,E3)

dataAnalysis[is.na(dataAnalysis$ACC),]$ACC<-0
dataAnalysis$trial<-as.numeric(as.character(dataAnalysis$trial))
```

```{r, echo=FALSE}

print(paste("AVG Quiz ACC in E3 = ",round(mean(quiz.Sum$ACC), digits=2)))
#print(paste("Subjects with low ACC = ",sort(unique(LowACC))))
print(paste("# of Subjects in E3 with low ACC = ",length(sort(unique(LowACC)))))

LowACC <-c(LowACC,lowQuizACC,tempLowACC)
print(paste("Total # of Subjects with low ACC = ",length(sort(unique(LowACC)))))
print(sort(unique(LowACC)))
```

```{r}
#### GRAPH ACC ####
ExploreDF <- dataAnalysis %>%
  filter(Subject != 157, RT > RTMin, RT < RTMax) %>%
  group_by(Subject,Exp,subBlock,countProp,trialProp,trialCongruency) %>%
  summarise(N = n(),
            meanRT = mean(RT), 
            meanAccuracy = mean(ACC), 
            TrialsCompleted = length(RT),
            maxRT = max(RT),
            vjoutRT = mean(vjoutNR(RT,1)),
            removed = vjoutNR(RT,2))

CleanDF<-ExploreDF %>% filter(Subject%in%LowACC == FALSE)

ggplot(CleanDF,aes(x=vjoutRT, y=meanAccuracy,color=Exp))+
  geom_point(show.legend = FALSE)+
  theme_classic(base_size=15)+
  ylab("Proportion Correct")+
  xlab("Mean Reaction Time (ms)")+
  ylim(0,1)+
  theme(legend.position="top",
    legend.direction="horizontal",
    legend.title = element_blank())+
  ggtitle("RT x ACC")

############ TAG OUTLIERS BY VJOUT FOR PROBE TRIALS #################

      xsize <- c(1.3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
                 25, 30, 35, 50, 80)
      stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
                2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
                2.45, 2.48, 2.5)

      #maxRT<- xm+sd(x)*stds[length(xsize[xsize <= length(x)])]
      #minRT<- xm-sd(x)*stds[length(xsize[xsize <= length(x)])]

      temp.data<-dataAnalysis

      minMax <- temp.data %>%
        filter(
          RT < RTMax,
          RT > RTMin,
          ACC == TRUE,
          Subject%in%LowACC == FALSE
        ) %>%
        group_by(Exp,Subject,subBlock,trialProp,countProp,trialCongruency) %>%
        summarize (
          Ntrials = n(),
          cutoff = stds[length(xsize[xsize <= length(RT)])],
          min = mean(RT) - sd(RT)*stds[length(xsize[xsize <= length(RT)])],
          max = mean(RT) + sd(RT)*stds[length(xsize[xsize <= length(RT)])]
        )

    new.data<-merge(dataAnalysis,minMax)
    new.data$outlier<- new.data$RT < new.data$min | new.data$RT > new.data$max

##### CREATE CLEAN DF #####

clean.DF<- new.data %>%
  filter(
         Subject%in%LowACC == FALSE,
         Subject != 157 #INCOMPLETE
         ) %>%
  select(Exp,Subject,order,block,subBlock,trial,trialProp,countProp,trialCongruency,RT,ACC,outlier)

clean.DF<-clean.DF[with(clean.DF, order(Exp, Subject, trial, block, subBlock)), ]

### AVERAGE REMOVED ###
print(paste("E1 removed", round(1 - nrow(clean.DF %>% filter(RT < RTMax, RT > RTMin,Exp == "E1", ACC == TRUE, outlier == FALSE))/nrow(clean.DF %>% filter(RT < RTMax, RT > RTMin, Exp == "E1",ACC == TRUE)),digits=4)
            )
      )

print(paste("E2 removed", round(1 - nrow(clean.DF %>% filter(RT < RTMax, RT > RTMin, Exp == "E2", ACC == TRUE, outlier == FALSE))/nrow(clean.DF %>% filter(RT < RTMax, RT > RTMin, Exp == "E2",ACC == TRUE)),digits=4)
            )
      )

print(paste("E3 removed", round(1 - nrow(clean.DF %>% filter(RT < RTMax, RT > RTMin, Exp == "E3", ACC == TRUE, outlier == FALSE))/nrow(clean.DF %>% filter(RT < RTMax, RT > RTMin, Exp == "E3",ACC == TRUE)),digits=4)
            )
      )

######### CLEAN AND SAVE ##########

clean.DF <- clean.DF %>%
  filter(
    outlier == FALSE
  ) %>%
  select(Exp,Subject,order,block,subBlock,trial,trialProp,countProp,trialCongruency,RT,ACC)

save(clean.DF,file="cleanDF.Rda")
```

## RT Analysis: Exp x count proportion x trial congruency

```{r}

RT.DF<- clean.DF %>%
  filter(
    RT < RTMax,
    RT > RTMin,
    ACC == TRUE,
    trialProp == "unbiased"
  ) %>%
  group_by(Subject,Exp,order,subBlock,countProp,trialCongruency) %>%
  summarise(vjoutRT = mean(RT))

####### GRAPH FLANKER EFFECTS #########
RT.Diff<-RT.DF %>%
  group_by(Exp,Subject,countProp,trialCongruency) %>%
  summarise(
    RT = mean(vjoutRT)
    ) %>%
  spread(trialCongruency,RT) %>%
  mutate(Diff = inc - con) %>%
  select(-con:-inc)%>%
  group_by(Exp,countProp) %>%
  summarise(
    N = n_distinct(Subject), 
    Flanker = mean(Diff), 
    sd = sd(Diff), 
    SE = sd/sqrt(N)
    )

RT.Diff

limits <- aes(ymax = Flanker + SE, ymin = Flanker - SE)
ggplot(RT.Diff,aes(x=Exp, y=Flanker,fill=countProp))+
  geom_bar(stat="identity", position=position_dodge(width=0.9), colour = "black") + 
  scale_fill_manual(values=c("#454545", "white"))+
  geom_errorbar(limits, width = .2, position=position_dodge(width=0.9))+
  coord_cartesian(ylim = c(0,120))+
  scale_y_continuous(breaks=seq(0, 120, 10))+
  theme_classic(base_size=12)+
  labs(title="")+
  ylab("Congruency Effect (ms)")+
  theme(legend.position="top",legend.direction="horizontal",legend.title = element_blank())+
  ggtitle("All Exp's")

RT.analysis<- clean.DF %>%
  filter(
    RT < RTMax,
    RT > RTMin,
    ACC == TRUE,
    trialProp == "unbiased"
  ) %>%
  group_by(Subject,Exp,countProp,trialCongruency) %>%
  summarise(vjoutRT = mean(RT))

aov.out <- aov_car(vjoutRT ~ Exp*countProp*trialCongruency + Error(Subject/countProp*trialCongruency), data = RT.analysis)

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

aov.out <- aov_car(vjoutRT ~  countProp*trialCongruency + Error(Subject/countProp*trialCongruency), data = RT.analysis[RT.analysis$Exp == "E1",])

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

aov.out <- aov_car(vjoutRT ~  countProp*trialCongruency + Error(Subject/countProp*trialCongruency), data = RT.analysis[RT.analysis$Exp == "E2",])

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

aov.out <- aov_car(vjoutRT ~  countProp*trialCongruency + Error(Subject/countProp*trialCongruency), data = RT.analysis[RT.analysis$Exp == "E3",])

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

########### COLLAPSE OVER EXPERIMENT #################

####### GRAPH FLANKER EFFECTS #########
RT.Diff<-RT.DF %>%
  group_by(Exp,Subject,countProp,trialCongruency) %>%
  summarise(
    RT = mean(vjoutRT)
    ) %>%
  spread(trialCongruency,RT) %>%
  mutate(Diff = inc - con) %>%
  select(-con:-inc)%>%
  group_by(countProp) %>%
  summarise(
    N = n_distinct(Subject), 
    Flanker = mean(Diff), 
    sd = sd(Diff), 
    SE = sd/sqrt(N)
    )

RT.Diff

limits <- aes(ymax = Flanker + SE, ymin = Flanker - SE)
ggplot(RT.Diff,aes(x=countProp, y=Flanker,fill=countProp, width=1))+
  geom_bar(stat="identity", position=position_dodge(width=0.5), colour = "black") + 
  scale_fill_manual(values=c("#454545", "white"))+
  geom_errorbar(limits, width = .2, position=position_dodge(width=0.5))+
  coord_cartesian(ylim = c(0,120))+
  scale_y_continuous(breaks=seq(0, 120, 10))+
  theme_classic(base_size=12)+
  labs(title="")+
  ylab("Congruency Effect (ms)")+
  theme(legend.position="top",legend.direction="horizontal",legend.title = element_blank())+
  ggtitle("Collapsed over Exp")

########### COLLAPSE OVER EXPERIMENT #################

####### GRAPH FLANKER EFFECTS BY BLOCK #########
RT.Diff<-RT.DF %>%
  group_by(Exp,Subject,subBlock,countProp,trialCongruency) %>%
  summarise(
    RT = mean(vjoutRT)
    ) %>%
  spread(trialCongruency,RT) %>%
  mutate(Diff = inc - con) %>%
  select(-con:-inc)

aov.out <- aov_car(Diff~ subBlock*countProp + Error(Subject/subBlock*countProp), data = RT.Diff)

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

RT.Diff <- RT.Diff %>%
  group_by(subBlock,countProp) %>%
  summarise(
    N = n_distinct(Subject), 
    Flanker = mean(Diff), 
    sd = sd(Diff), 
    SE = sd/sqrt(N)
    )

RT.Diff

limits <- aes(ymax = Flanker + SE, ymin = Flanker - SE)
ggplot(RT.Diff,aes(x=subBlock, y=Flanker,fill=countProp, width=.75))+
  geom_bar(stat="identity", position=position_dodge(width=.75), colour = "black") + 
  scale_fill_manual(values=c("#454545", "white"))+
  geom_errorbar(limits, width = .2, position=position_dodge(width=0.75))+
  coord_cartesian(ylim = c(0,120))+
  scale_y_continuous(breaks=seq(0, 120, 10))+
  theme_classic(base_size=12)+
  labs(title="")+
  ylab("Congruency Effect (ms)")+
  theme(legend.position="top",legend.direction="horizontal",legend.title = element_blank())+
  ggtitle("By Block")

########### COLLAPSE OVER EXPERIMENT #################

####### GRAPH FLANKER EFFECTS BY ORDER #########
RT.Diff<-RT.DF %>%
  group_by(Exp,Subject,order,countProp,trialCongruency) %>%
  summarise(
    RT = mean(vjoutRT)
    ) %>%
  spread(trialCongruency,RT) %>%
  mutate(Diff = inc - con) %>%
  select(-con:-inc)

aov.out <- aov_car(Diff~ order*countProp + Error(Subject/countProp), data = RT.Diff)

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

aov.out <- aov_car(Diff~ countProp + Error(Subject/countProp), data = RT.Diff[RT.Diff$order == "B1 0",])

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

aov.out <- aov_car(Diff~ countProp + Error(Subject/countProp), data = RT.Diff[RT.Diff$order == "B1 100",])

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

RT.Diff <-  RT.Diff %>%
  group_by(order,countProp) %>%
  summarise(
    N = n_distinct(Subject), 
    Flanker = mean(Diff), 
    sd = sd(Diff), 
    SE = sd/sqrt(N)
    )

RT.Diff

limits <- aes(ymax = Flanker + SE, ymin = Flanker - SE)
ggplot(RT.Diff,aes(x=order, y=Flanker,fill=countProp, width=.75))+
  geom_bar(stat="identity", position=position_dodge(width=.75), colour = "black") + 
  scale_fill_manual(values=c("#454545", "white"))+
  geom_errorbar(limits, width = .2, position=position_dodge(width=0.75))+
  coord_cartesian(ylim = c(0,120))+
  scale_y_continuous(breaks=seq(0, 120, 10))+
  theme_classic(base_size=12)+
  labs(title="")+
  ylab("Congruency Effect (ms)")+
  theme(legend.position="top",legend.direction="horizontal",legend.title = element_blank())+
  ggtitle("By Order")

```

## ACC analysis: Exp x count proportion x trial congruency

```{r}

RT.DF<- dataAnalysis %>%
  filter(
         Subject%in%LowACC == FALSE,
         trialProp != "biased",
         Subject != 157
         ) %>%
  group_by(Subject,Exp,order,subBlock,countProp,trialProp,trialCongruency) %>%
  summarise(ACC = mean(ACC))

RT.DF$ACC = (1-RT.DF$ACC)*100

####### GRAPH FLANKER EFFECTS #########
RT.Diff<-RT.DF %>%
  group_by(Exp,Subject,countProp,trialCongruency) %>%
  summarise(
    RT = mean(ACC)
    ) %>%
  spread(trialCongruency,RT) %>%
  mutate(Diff = inc - con) %>%
  select(-con:-inc)%>%
  group_by(Exp,countProp) %>%
  summarise(
    N = n_distinct(Subject), 
    Flanker = mean(Diff), 
    sd = sd(Diff), 
    SE = sd/sqrt(N)
    )

RT.Diff

limits <- aes(ymax = Flanker + SE, ymin = Flanker - SE)
ggplot(RT.Diff,aes(x=Exp, y=Flanker,fill=countProp))+
  geom_bar(stat="identity", position=position_dodge(width=0.9), colour = "black") + 
  scale_fill_manual(values=c("#454545", "white"))+
  geom_errorbar(limits, width = .2, position=position_dodge(width=0.9))+
  coord_cartesian(ylim = c(0,10))+
  scale_y_continuous(breaks=seq(0, 10, 1))+
  theme_classic(base_size=12)+
  labs(title="")+
  ylab("Congruency Effect (Error %)")+
  theme(legend.position="top",legend.direction="horizontal",legend.title = element_blank())+
  ggtitle("All Exp's")

ACC.analysis<- dataAnalysis %>%
  filter(
         Subject%in%LowACC == FALSE,
         trialProp != "biased",
         Subject != 157
         ) %>%
  group_by(Subject,Exp,countProp,trialCongruency) %>%
  summarise(ACC = mean(ACC)*100)

aov.out <- aov_car(ACC ~ Exp*countProp*trialCongruency + Error(Subject/countProp*trialCongruency), data = ACC.analysis)

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

aov.out <- aov_car(ACC ~  countProp*trialCongruency + Error(Subject/countProp*trialCongruency), data = ACC.analysis[ACC.analysis$Exp == "E1",])

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

aov.out <- aov_car(ACC ~  countProp*trialCongruency + Error(Subject/countProp*trialCongruency), data = ACC.analysis[ACC.analysis$Exp == "E2",])

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

aov.out <- aov_car(ACC ~  countProp*trialCongruency + Error(Subject/countProp*trialCongruency), data = ACC.analysis[ACC.analysis$Exp == "E3",])

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

########### COLLAPSE OVER EXPERIMENT #################

####### GRAPH FLANKER EFFECTS #########
RT.Diff<-RT.DF %>%
  group_by(Exp,Subject,countProp,trialCongruency) %>%
  summarise(
    RT = mean(ACC)
    ) %>%
  spread(trialCongruency,RT) %>%
  mutate(Diff = inc - con) %>%
  select(-con:-inc)%>%
  group_by(countProp) %>%
  summarise(
    N = n_distinct(Subject), 
    Flanker = mean(Diff), 
    sd = sd(Diff), 
    SE = sd/sqrt(N)
    )

RT.Diff

limits <- aes(ymax = Flanker + SE, ymin = Flanker - SE)
ggplot(RT.Diff,aes(x=countProp, y=Flanker,fill=countProp, width=1))+
  geom_bar(stat="identity", position=position_dodge(width=0.5), colour = "black") + 
  scale_fill_manual(values=c("#454545", "white"))+
  geom_errorbar(limits, width = .2, position=position_dodge(width=0.5))+
  coord_cartesian(ylim = c(0,10))+
  scale_y_continuous(breaks=seq(0, 10, 1))+
  theme_classic(base_size=12)+
  labs(title="")+
  ylab("Congruency Effect (Error %)")+
  theme(legend.position="top",legend.direction="horizontal",legend.title = element_blank())+
  ggtitle("Collapsed over Exp")

########### COLLAPSE OVER EXPERIMENT #################

####### GRAPH FLANKER EFFECTS BY BLOCK #########
RT.Diff<-RT.DF %>%
  group_by(Exp,Subject,subBlock,countProp,trialCongruency) %>%
  summarise(
    RT = mean(ACC)*100
    ) %>%
  spread(trialCongruency,RT) %>%
  mutate(Diff = inc - con) %>%
  select(-con:-inc)%>%
  group_by(subBlock,countProp) %>%
  summarise(
    N = n_distinct(Subject), 
    Flanker = mean(Diff), 
    sd = sd(Diff), 
    SE = sd/sqrt(N)
    )

RT.Diff

limits <- aes(ymax = Flanker + SE, ymin = Flanker - SE)
ggplot(RT.Diff,aes(x=subBlock, y=Flanker,fill=countProp, width=.75))+
  geom_bar(stat="identity", position=position_dodge(width=.75), colour = "black") + 
  scale_fill_manual(values=c("#454545", "white"))+
  geom_errorbar(limits, width = .2, position=position_dodge(width=0.75))+
  coord_cartesian(ylim = c(0,10))+
  scale_y_continuous(breaks=seq(0, 10, 1))+
  theme_classic(base_size=12)+
  labs(title="")+
  ylab("Congruency Effect (Error %)")+
  theme(legend.position="top",legend.direction="horizontal",legend.title = element_blank())+
  ggtitle("By Block")

########### COLLAPSE OVER EXPERIMENT #################

####### GRAPH FLANKER EFFECTS BY ORDER #########
RT.Diff<-RT.DF %>%
  group_by(Exp,Subject,order,countProp,trialCongruency) %>%
  summarise(
    RT = mean(ACC)
    ) %>%
  spread(trialCongruency,RT) %>%
  mutate(Diff = inc - con) %>%
  select(-con:-inc)

aov.out <- aov_car(Diff~ order*countProp + Error(Subject/countProp), data = RT.Diff)

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

aov.out <- aov_car(Diff~ countProp + Error(Subject/countProp), data = RT.Diff[RT.Diff$order == "B1 0",])

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

aov.out <- aov_car(Diff~ countProp + Error(Subject/countProp), data = RT.Diff[RT.Diff$order == "B1 100",])

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

RT.Diff <-  RT.Diff %>%
  group_by(order,countProp) %>%
  summarise(
    N = n_distinct(Subject), 
    Flanker = mean(Diff), 
    sd = sd(Diff), 
    SE = sd/sqrt(N)
    )

RT.Diff

limits <- aes(ymax = Flanker + SE, ymin = Flanker - SE)
ggplot(RT.Diff,aes(x=order, y=Flanker,fill=countProp, width=.75))+
  geom_bar(stat="identity", position=position_dodge(width=.75), colour = "black") + 
  scale_fill_manual(values=c("#454545", "white"))+
  geom_errorbar(limits, width = .2, position=position_dodge(width=0.75))+
  coord_cartesian(ylim = c(0,10))+
  scale_y_continuous(breaks=seq(0, 10, 1))+
  theme_classic(base_size=12)+
  labs(title="")+
  ylab("Congruency Effect (Error %)")+
  theme(legend.position="top",legend.direction="horizontal",legend.title = element_blank())+
  ggtitle("By Order")

```

#Alternate ACC graphs

```{r}

RT.DF<- dataAnalysis %>%
  filter(
         Subject%in%LowACC == FALSE,
         trialProp != "biased",
         Subject != 157
         ) %>%
  group_by(Subject,Exp,order,subBlock,countProp,trialProp,trialCongruency) %>%
  summarise(ACC = mean(ACC))

RT.DF$ACC = (1-RT.DF$ACC)*100

RT.Sum <- RT.DF %>%
  group_by(Exp,countProp,trialProp,trialCongruency) %>%
  summarise(
    N = n_distinct(Subject), 
    mACC = round(mean(ACC),digits=2), 
    sd = round(sd(ACC),digits=2), 
    SE = round(sd/sqrt(N),digits=2),
    upper = mACC + qnorm(0.975)*sd/sqrt(N),
    lower = mACC - qnorm(0.975)*sd/sqrt(N)
  )

RT.Sum

RT.Diff<-RT.DF %>%
  group_by(Exp,countProp,trialCongruency) %>%
  summarise(
    mACC = mean(ACC)
    ) %>%
  spread(trialCongruency,mACC) %>%
  mutate(Diff = inc - con) %>%
  select(-con:-inc) %>%
  summarise(
    Diff = round(Diff,digits=2)
  )

RT.Diff

limits <- aes(ymax = mACC + SE, ymin = mACC - SE)
ggplot(RT.Sum,aes(x=countProp, y=mACC,fill=trialCongruency))+
  geom_bar(stat="identity", position=position_dodge(width=0.9)) + 
  scale_fill_manual(values=c("#56B4E9", "#009E73"))+
  geom_errorbar(limits, width = .2, position=position_dodge(width=0.9))+
  #coord_cartesian(ylim = c(.8, 1))+
  theme_classic(base_size=15)+
  labs(title="Overall")+
  ylab("Error Rates (%)")+
  xlab("")+
  theme(legend.position="top",legend.direction="horizontal",legend.title = element_blank())+
  facet_wrap(~Exp)

aov.out <- aov_car(ACC ~ Exp*countProp*trialCongruency + Error(Subject/countProp*trialCongruency), data = RT.DF)

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

aov.out <- aov_car(ACC ~  countProp*trialCongruency + Error(Subject/countProp*trialCongruency), data = RT.DF[RT.DF$Exp == "E1",])

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

aov.out <- aov_car(ACC ~  countProp*trialCongruency + Error(Subject/countProp*trialCongruency), data = RT.DF[RT.DF$Exp == "E2",])

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

aov.out <- aov_car(ACC ~  countProp*trialCongruency + Error(Subject/countProp*trialCongruency), data = RT.DF[RT.DF$Exp == "E3",])

nice(aov.out, es = "pes", observed = NULL,
    correction = c("none"), MSE = TRUE,
    sig.symbols = c(" +", " *", " **", " ***"))

### AGGREGATE OVER EXP ###
RT.Sum <- RT.DF %>%
  group_by(countProp,trialProp,trialCongruency) %>%
  summarise(
    N = n_distinct(Subject), 
    mACC = round(mean(ACC),digits=2), 
    sd = round(sd(ACC),digits=2), 
    SE = round(sd/sqrt(N),digits=2)
  )

RT.Sum

RT.Diff<-RT.DF %>%
  group_by(countProp,trialCongruency) %>%
  summarise(
    mACC = mean(ACC)
    ) %>%
  spread(trialCongruency,mACC) %>%
  mutate(Diff = inc - con) %>%
  select(-con:-inc)%>%
  summarise(
    Diff = round(Diff,digits=2)
  )

RT.Diff

limits <- aes(ymax = mACC + SE, ymin = mACC - SE)
ggplot(RT.Sum,aes(x=countProp, y=mACC,fill=trialCongruency))+
  geom_bar(stat="identity", position=position_dodge(width=0.9)) + 
  scale_fill_manual(values=c("#56B4E9", "#009E73"))+
  geom_errorbar(limits, width = .2, position=position_dodge(width=0.9))+
  #coord_cartesian(ylim = c(.8, 1))+
  theme_classic(base_size=15)+
  labs(title="Overall")+
  ylab("Error Rates (%)")+
  xlab("")+
  theme(legend.position="top",legend.direction="horizontal",legend.title = element_blank())

```

### 2018-12-06 v1-task-relevance-cspc.Rmd
add first draft

---
title             : "Contextual recruitment of selective attention can be updated via changes in task-relevance"
shorttitle        : "Contextual recruitment of selective attention"

author: 
  - name          : "Nicholaus P. Brosowsky"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "The Graduate Center, CUNY, 365 5th Ave, New York, NY 10016"
    email         : "nbrosowsky@gradcenter.cuny.edu"
  - name          : "Matthew J. C. Crump"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "The Graduate Center of the City University of New York"
  - id            : "2"
    institution   : "Brooklyn College of the City University of New York"

abstract: |
  Evidence across a wide variety of attention paradigms shows that environmental cues can trigger adjustments to ongoing priorities for attending to relevant and irrelevant information. This context-specific control over attention suggests that cognitive control can be both automatic and flexible. For instance, in selective attention tasks, congruency effects are larger for items that appear in a context associated with infrequent conflict than in a context associated with frequent conflict. Since the to-be-presented context cannot be predicted or prepared for in advance, attention is assumed to be rapidly updated on-the-fly, triggered by the currently presented context. Context-specific control exemplifies how learning and memory processes can influence attention to enable cognitive flexibility. However, what determines the use of previously learned associations still remains unclear. In the current study, we examined whether task-relevance would influence the learning and use of context cues in a flanker task. Using a secondary counting task, context dimensions associated with differing levels of conflict were made task-relevant or -irrelevant across the experiment. In short, we found that making new contextual information task-relevant caused participants to ignore a previously learned context-attention association and adopt a new context-specific control strategy; all without changing the experimental stimuli. This result suggests that task-relevance is a key determinant of context-specific control.

keywords          : "Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance"
wordcount         : "5946"

bibliography      : ["task-relevance-cspc.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no

#class             : doc
lang              : english

class             : "man"
output:
 bookdown::html_document2:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 2
    code_folding: hide
#    css: webpaper.css

header-includes:
  - \usepackage{setspace}
  - \AtBeginEnvironment{tabular}{\onehalfspacing}
  - \AtBeginEnvironment{lltable}{\onehalfspacing}
  - \captionsetup[table]{font={stretch=1.5}}
  - \captionsetup[figure]{font={stretch=1}}
  - \setlength{\skip\footins}{1cm}
  - \setlength{\footnotesep}{0.5cm}

#output:
#  papaja::apa6_pdf
---

```{r setup, include=FALSE, eval=TRUE,echo=FALSE}
#options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache = FALSE)
```

#Introduction

Selective attention processes are commonly investigated using interference paradigms such as the Stroop [-@stroop_studies_1935] and flanker [@eriksen_effects_1974] tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor. Performance is typically better on congruent versus incongruent trials and the difference-the congruency effect-taken as an index of attentional priorities. Large congruency effects are thought to reflect ineffective filtering of the distracting stimuli whereas small congruency effects are thought to reflect effective filtering. By probing factors that systematically alter congruency effects, we can then make inferences about processes that control attentional filtering. For example, manipulating the frequency of conflict via the proportion of congruent versus incongruent trials has shown to influence the size of the congruency effect. Typically, a high proportion congruent experiment produces large congruency effects, whereas a low proportion congruent experiment produces small congruency effects [@logan_when_1979; @lowe_selective_1982; @west_effects_1998]. This result is usually  explained as strategic control, where participants increase attentional control under high-conflict demands and relax attentional control under low-conflict demands [@logan_attention_1980; @logan_strategies_1984; @logan_when_1979; @lowe_selective_1982]. Recent work however, has demonstrated that attentional control is not only adjusted by top-down regulation, but can also be triggered automatically by environmental cues [@brosowsky_memory-guided_2018; @bugg_support_2012; @egner_creatures_2014; @fischer_predicting_2015; @king_priming_2012; @mayr_outsourcing_2007].

For example, Crump, Gong, and Milliken [@crump_context-specific_2006; see also, @corballis_independent_2003] presented Stroop stimuli in one of two randomly chosen locations and manipulated the frequency of conflict associated with each location. One location was associated with a high frequency of conflict (25% congruent trials) and the other with a low frequency of conflict (75% congruent trials). Overall, the proportion of congruent trials was 50% and randomized such that the upcoming location could not be predicted. Even so, congruency effects were shown to be smaller for trials where the stimulus appeared in the high conflict location as compared to the low conflict location. This effect, known now as the context-specific proportion congruent effect (CSPC), has now been replicated in a number of different selective attention paradigms [e.g., @alards-tomalin_auditory_2017; @blais_trial-by-trial_2015; @bugg_conflict-triggered_2014; @crump_context-dependent_2018; @crump_learning_2016; @fischer_context-sensitive_2014; @hubner_location-specific_2016].

Critical evidence however, that CSPC effects reflect context-specific control rather than other non-control learning processes [e.g., @schmidt_stroop_2008], comes from work showing that CSPC effects can transfer to frequency unbiased items [@brosowsky_context-specific_2016; @crump_flexibility_2009; @weidler_attentional_2018; @weidler_transfer_2016; though, see @hutcheon_limits_2017]. Crump and Milliken (2009), for example, divided Stroop items into two mutually exclusive sets (e.g., RED/GREEN and BLUE/YELLOW). One set was defined as the frequency biased set, and presented with 75% congruency in one location, and 25% congruency in the other. The second set however, was presented with 50% congruency in both locations. Nevertheless, they found smaller congruency effects for unbiased items presented in the high conflict location as compared to the low conflict location.

One explanation for CSPC effects is that the repeated application of attentional priorities in a particular context creates an associative link in episodic memory between the attentional control procedures and the contextual information [@abrahamse_grounding_2016; @brosowsky_memory-guided_2018; @crump_learning_2016; @egner_creatures_2014]. Once the associative link is established, processing the context is assumed to trigger the retrieval of previous experiences, automatically reinstating the associated attentional priorities. Although this explanation seems plausible, it remains largely unclear how such associations are established and perhaps more importantly, it remains unclear what determines which learned associations will be used to guide attention at any given moment.

The importance of the latter issue becomes increasingly clear if we speculate about context-specificity in more complex, real-world environments. Consider myself, right now, writing this article in a coffee shop. The coffee shop is a complex environment that contains a multitude of contextual cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which I have had many different experiences applying attentional control. Although my laptop might cue attentional processing helpful for finishing this article, other features of the coffee shop might cue other, unhelpful attentional processing related to other experiences like socializing and people-watching. This is all to say that our environments, and experiences within them, afford many different associative relationships between cognitive processing and environmental cues. What then determines which associative relationships will be used to guide attention (or even if such associative relationships are used at all)?

Task-relevance might be one factor that is important for establishing and using context-attention associations. This proposal might seem counter-intuitive as it is typically assumed that the context, within selective attention tasks at least, is completely irrelevant to the task. In fact, referring to such stimulus dimensions as the "context" carries with it an implication that the feature is background information, irrelevant to the task-at-hand, and should be ignored by the participant. A closer look at CSPC designs however, suggests that the context cues may not be as irrelevant as implied. For example, the most commonly used context cue is location [@brosowsky_context-specific_2016; @corballis_independent_2003; @crump_context-specific_2006; @crump_context-specific_2008; @crump_learning_2016; @weidler_attentional_2018; @weidler_transfer_2016]. Although in some sense, the location is irrelevant for identifying the color of a word, it seems disingenuous to consider it completely task-irrelevant. In order to identify the target, the participant must first identify and orient to its location on the screen. In this is sense, it is relevant to their ability to complete the task and furthermore, location information may receive priority during encoding [@logan_what_1998; @mayr_spatial_1996]. Similar arguments could be made about other context features that are inherent to processing the target stimulus, like font-type [@bugg_multiple_2008] and color [@vietze_context_2009].

To date, we are aware of only one study that has looked at task-relevance within the CSPC literature. Crump, Vaquero, & Milliken [-@crump_context-specific_2008] used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe. Critically, they used the shape of the color patch probe, either a square or a circle, as the contextual dimension; one associated with a high frequency of conflict, the other with a low frequency. In one experiment participants were made aware of the shape-proportion contingencies but given no additional instructions. In the second, participants were given a secondary task to count the number of trials that contained a square. The first experiment failed to find evidence for context-specificity, whereas the second did. Although not testing task-relevance directly, Cañadas, Rodríguez-Bailón, Milliken, & Lupiáñez [-@canadas_social_2013]) found similar effects. In this study they used images of male and female faces as context cues in a flanker task. When given instructions to think of the faces as members of the gender categories they found CSPC effects, but when given instructions to think of the faces as individuals they did not. These results suggest that making a context dimension relevant to the on-going task is important for producing CSPC effects.

#The Current Study

Some prior suggests that the task-relevance of contextual information is important for establishing new associations between context cues and attentional priorities. Simply put, CSPC effects emerge when context cues are somehow made relevant to the task, but do not when made irrelevant [@canadas_social_2013; @crump_context-specific_2006; @crump_context-specific_2008]. However, it still remains unclear how task-relevance may or may not inform the use of previously learned associations. In the current study, we examined whether manipulating task-relevance would cause participants to ignore a previously learned association and adopt a new context-specific control strategy.

A flanker task was used to measure attentional control in an adapted CSPC design [@crump_flexibility_2009; @crump_reproducing_2017]. Similar to previous studies, flanker stimuli were presented in contexts associated with differing levels of conflict (0%, 50%, or 100% congruent). However, unlike previous CSPC designs where contexts were defined by a single discriminating feature (e.g., upper vs. lower screen locations), contexts were defined by two feature dimensions (see Figure 1A). In one condition, for example, contexts were defined by object identity (hat or chair) and color (blue or green). Only three out of the four possible feature combinations were presented, each associated with a different proportion of congruent trials (0%, 50%, or 100% congruent). Critically, the frequency unbiased context (50% congruent) always shared a feature with each of the frequency-biased contexts (0% and 100% congruent). The frequency biased contexts (0% and 100% congruent) however, did not share any features (see Figure 1C for an example).

A secondary counting task was used to manipulate the task-relevance of the context dimensions [@crump_flexibility_2009] which critically, switched halfway through the experiment. Participants were instructed to keep a running count of one of the overlapping features (e.g., "count whenever a hat is presented") which was associated with either a high or low frequency of conflict. Halfway through the experiment they received new instructions to count the other overlapping feature (e.g., "count whenever a green item is presented"). Critically, the set of context images remained the same throughout the experiment (see Figure 1C for an example) and the task-relevance of the context dimensions was the only aspect of the experiment that changed from the first to second phases.

The critical measure of interest is the congruency effect produced in the frequency unbiased context. If, on the one hand, task-relevance has no impact on the use of context-attention associations we would expect no differences between the congruency effects when the high-conflict context dimension is made task-relevant or the low-conflict context dimension is made task-relevant. This could occur because all three contexts are treated as individual contexts throughout the whole experiment [e.g., @canadas_social_2013]. Or it could occur because associations formed in the first block interfere with learning new associations in the second [e.g., @brosowsky_context-specific_2016]. On other hand, task-relevance might not only dictate how associations are formed, but also whether learned associations are used. In this case, we would expect that there will be smaller congruency effects when the high-conflict context dimension is made task-relevant as compared to when the low-conflict context dimension is made task-relevant. This would demonstrate that participants were able to ignore a previously learned association and adopt a new context-specific control strategy.

A secondary goal was to conceptually replicate previous findings and test the generalizability of any task-relevance effects. Therefore, we included three conditions that differed only in the kinds of stimuli used to create context cues. In one condition we used face images where context dimensions were defined by social categories, similar to Cañadas et al.,  [-@canadas_social_2013]. However, they found that social categorization occurred spontaneously and it was unclear what impact that would have on the current results. Therefore, we included another condition that used images of simple objects where context dimensions were defined by object features. Finally, Cañadas et al.[-@canadas_social_2013] also found that context effects generalized to novel face images. In our third condition we used non-repeating face exemplars to examine whether any task-relevance effects would also generalize in our design or if learning would be image-specific.

#Methods

(ref:figure1)
Illustration of the stimuli and trial construction. Figure 1A shows the feature dimensions for each of the conditions. Figure 1B shows an example trial stimulus containing both the context and flanker images. Figure 1C shows an example of how feature dimensions could have been assigned to each proportion congruency (PC) condition, and an example of the secondary task assignments. The secondary task order, as well as the feature and congruency assignments were all randomized for each participant.

```{r figure1, echo=FALSE, fig.cap="A caption", out.width = "75%", fig.align="center"}
knitr::include_graphics("images/Task.jpg")
```

##Participants

All participants were recruited from Amazon Mechanical Turk (AMT) and compensated $2.00 for participating. The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by $6.00 per hour. For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study. Participants were included in the study if they completed all trials. We posted 150 HITs and 145 participants completed all trials.

##Apparatus & Stimuli

The experiments were programmed using JavaScript, CSS and HTML. The program allowed participants to complete task only if they were running Safari, Google Chrome, or Firefox web browsers. Flanker stimuli consisted of images of five arrows pointed left or right presented at 250 x 50 pixels (each arrow was 50 x 50 pixels). Context stimuli were constructed using images selected from @brady_visual_2013 color-rotated to blue and green, and face images from the Chicago Face Database [@ma_chicago_2015], supplemented with the NimStim Set of Facial Expressions [@tottenham_nimstim_2009]. The object images were displayed at 250 x 250 pixels, while the face images were displayed at 250 x 313 pixels. The experiment ran as a pop-up window that filled the entire screen. The background was white, and stimuli were presented in the center of the screen.

Design. Experiment 1 used a 2x2x3 mixed design with task-relevant context (0% and 100%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
All three conditions were constructed using the same general method. The experiment was divided into two phases. Each phase consisted of 144 flanker trials (48 trials per context), and 13 count response trials for a total of 314 trials. On the count response trials, participants indicated how many trials they had counted until that point. The count response trials occurred once for every 12 flanker trials and was randomly inserted between trial 6 and 12 of each 12-trial block. Each phase ended with one additional count response trial.

On every flanker trial, participants were presented with flanker stimuli paired with one of three contexts. Each context was associated with a different proportion congruency such that two cues were associated with a biased frequency (0% and 100% proportion congruency), while one was associated with an unbiased frequency (50% proportion congruency). The feature dimensions and corresponding context images assigned to each of the biased and unbiased item sets were randomly determined for each participant. However, context images used for the frequency biased trials never shared features, while the frequency unbiased context image always shared a feature with each of the frequency biased context images (see Figure 1). Additionally, the feature assignments remained the same throughout phases 1 and 2, and critically, the only change to the task was which feature the participant was instructed to count (see Figure 1C for an example).

All critical aspects of the task were randomized between participants. This includes the three chosen context images, the features assigned to proportion levels, the features assigned to each counting condition, the secondary task order, and the order of trials.

##Procedure

All participants were AMT workers who found the experiment using the AMT system. The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board. Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form. Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window. Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing 'z' if the arrow pointed left, and 'm' if the arrow pointed right. Additionally, they were instructed to silently keep count of the number of trials that contained a feature. In the object context condition, they were asked to count trials that contained a certain color (blue or green) or object-identity (hat or chair) and in the social context conditions they were asked to count the number of trials that contained appeared a certain gender (male or female) or race (black or white). Periodically throughout the experiment, participants were asked to report how many trials they had counted until that point and to restart their count from 0. Halfway through the experiment participants received new instructions about which feature to count (see Figure 1C).
Each trial began with a blank inter-stimulus interval (ISI) of 400 ms, followed by a fixation cross presented in the center of the screen for 200 ms, then a second blank ISI of 400 ms. Next, the flanker and context stimuli appeared in the center of screen (the flanker above the context image; see Figure 1B) and remained on screen until a response was made. Following a response, accuracy feedback was presented for 1000 ms. A response automatically triggered the next trial. 
Halfway through the experiment (157 trials), participants received new instructions about which feature to count and to press the button on-screen when they were ready to continue.

#Results

(ref:figure2)
Results from experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent).

```{r figure2, echo=FALSE, fig.cap="A caption", out.width = "75%", fig.align="center"}
knitr::include_graphics("images/E1_bar.jpg")
```

Participants with mean error rates greater than 25% were excluded from the analyses, eliminating fourteen participants. For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure. The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms [@van_selst_solution_1994]. This procedure removed 3.76% of the total observations.
The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1). To that end, mean correct RTs and mean error rates from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0% and 100% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.

The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, F(1,128) = 8.76, *MSE* = 1672.8, *p* = .004, η~p~2 = .06, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant. Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, F(2,128) = .01, *MSE* = 1672.8, *p* = .99, η~p~2 < .0001, showing no evidence for differences between the CSPC effects across context-type manipulations.

Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, F(1,128) = 6.57, *MSE*  = 13.98, *p* = .01, η~p~2 = .05, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, F(2,128) = .9, *MSE* = 13.98, *p* = .41, η~p~2 = .01. Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.

#General Discussion

The aim of the current study was to investigate whether task-relevance plays a role in the contextual recruitment of selective attention. Specifically, we tested whether manipulating the relative task-relevance of context cues could cause participants to ignore a previously learned context-association and apply a new association. We created a frequency unbiased context cue that shared features with two frequency biased contexts and included a feature-counting task to manipulate the task-relevance of context dimensions across two blocks of trials. Critically, halfway through the experiment participants received new instructions changing the task-relevant feature from one frequency biased cue to the other.

The key finding was that the congruency effects for the frequency unbiased items were significantly larger when the low-conflict context was made task-relevant as compared to when the high-conflict context was made task-relevant. This result is consistent with prior CSPC effects and, like the previous work, suggests that the context cues triggered rapid adjustments to attentional control [@crump_flexibility_2009]. However, unlike prior studies, we were able to experimentally manipulate the CSPC effect across blocks of trials without changing any of the physical properties of the stimuli. This novel finding demonstrates that participants were able to learn and apply one context-attention association in the first phase, and subsequently ignore that association to learn a new association in the second phase.

This result implicates an important role for task-relevance in producing CSPC phenomena. @crump_context-specific_2008 used shapes as context cues in a prime-probe Stroop task and did not find CSPC effects until the context cues were made task-relevant. Similarly, @canadas_social_2013 eliminated the CSPC effect by making the contextual cue effectively unrelated to the task. These studies suggest that task-relevance plays an important role in establishing associations between contextual information and attentional priorities to produce CSPC effects. Our finding extends this work in two important ways. First, we show that changing the task-relevance of the presented cues corresponded with a change in attentional control in the predicted direction. This demonstrates that task-relevance is also a key determinant of whether a previously learned attention-context association will be used or ignored in favor of a new association. Second, we show that task-relevance allowed participants resolve competition between two competing contextual cues, responding on the basis of one at the expense of the other. To our knowledge, this is the first demonstration that CSPC effects can be produced when there are multiple, overlapping contextual cues available.

In light of prior work, we take this as evidence that the contextual recruitment of selective attention, although likely implicit, is not obligatory [e.g., @brosowsky_context-specific_2016], requiring that environmental information be incorporated into the task representation. Similarly, there appears to be flexibility in which environmental features are selected and used to guide attention, which can be rapidly updated depending on the task-relevance of those features. Such a result lends some insight into how context-specific control might operate in more complex, real-world environments, where there is an over-abundance of environmental features that afford many different learned associations. From a theoretical perspective, this result is consistent memory-based accounts of CSPC phenomena [@brosowsky_memory-guided_2018; @bugg_converging_2013; @crump_context-dependent_2018; @crump_flexibility_2009; @crump_reproducing_2017]. Under this view, a memory process encodes attentional priorities in the representation of individual experiences and, as a result, become associated with the environment where they were used. The subsequent reoccurrence of a prior context triggers the retrieval and reinstatement of those attentional priorities. Our results show however, that all the features of the environment may not be treated equally and that only task-relevant features are used to probe memory and guide attention.

Another key result of this study concerned the different stimuli used as context cues. Across the three conditions, we varied the type of context image and dimensions. We manipulated the type of image presented, including both objects (identity and color dimensions) and faces (gender and racial dimensions). We also manipulated whether a single set of three repeating images were presented (object and social) or a set of non-repeating images were presented (social/non-repeating). Across all three conditions, we found no evidence that using different stimuli had an influence on the size or direction of the CSPC demonstrating generalizability of this phenomenon. Furthermore, CSPC effects were present even when using non-repeating images which suggests that context-dependency did rely on image-specific associations but higher-order, learned categorical information.

Traditional models of person perception posit that social categories are automatically activated in the presence of social stimuli  [e.g., @brewer_dual_1988; @devine_stereotypes_1989; @fiske_continuum_1990]. @canadas_social_2013 however, found that directing participants to think about faces in terms of individual features eliminated context-specific attention effect and suggested that momentary motivations may influence the automaticity of social categorization. Our results add to this literature by observing the influence of momentary motivations (i.e., task-relevance) when there is competition between two salient social categories. Specifically, we found that participants could categorize on the basis of one social cue at the expense of the other, and subsequently switch between them. These findings may speak to issues of automaticity in social categorization [@macrae_social_2001] as well as understanding how the situational context can prime one social identity over another [@crisp_multiple_2007]. Furthermore, we found no evidence for differences between the social and object conditions. This suggests that categorization within the CSPC task is quickly and easily learned when the task supports such learning and is non-unique to social stimuli.

In sum, our results provide new evidence that changes in task-relevance can update the contextual recruitment of selective attention in a CSPC flanker task. Importantly, we show that making one feature task-relevant produced a CSPC effect, even in the presence of a competing contextual cue. Moreover, changing the task-relevant context-cue midway through the experiment was accompanied by predictable changes in the congruency effects. This effect was found to be generalizable across two different kinds of stimuli and occurred even when using non-repeating images. These results implicate an important role for task-relevance in producing context-dependency and are consistent with memory-based accounts of CSPC phenomena.

#References

### 2018-12-07 v1-task-relevance-cspc.Rmd
in progress

@@
 class             : "man"
-output:
- bookdown::html_document2:
-    toc: true
-    toc_float: true
-    collapsed: false
-    number_sections: false
-    toc_depth: 2
-    code_folding: hide
+# output:
+#  bookdown::html_document2:
+#     toc: true
+#     toc_float: true
+#     collapsed: false
+#     number_sections: false
+#     toc_depth: 2
+#     code_folding: hide
 #     css: webpaper.css
 
-header-includes:
-  - \usepackage{setspace}
-  - \AtBeginEnvironment{tabular}{\onehalfspacing}
-  - \AtBeginEnvironment{lltable}{\onehalfspacing}
-  - \captionsetup[table]{font={stretch=1.5}}
-  - \captionsetup[figure]{font={stretch=1}}
-  - \setlength{\skip\footins}{1cm}
-  - \setlength{\footnotesep}{0.5cm}
-
-#output:
-#  papaja::apa6_pdf
+output:
+ papaja::apa6_pdf
 ---
@@
 ```{r setup, include=FALSE, eval=TRUE,echo=FALSE}
-#options(htmltools.dir.version = FALSE)
+# options(htmltools.dir.version = FALSE)
 knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache = FALSE)
+
+library("dplyr")
+library("afex")
+library("papaja")
 ```
 
-#Introduction
+#  Introduction
 
@@
 The first experiment failed to find evidence for context-specificity, whereas the second did.
-Although not testing task-relevance directly, Cañadas, Rodríguez-Bailón, Milliken, & Lupiáñez [-@canadas_social_2013]) found similar effects.
+Although not testing task-relevance directly, [-@canadas_social_2013]) found similar effects.
 In this study they used images of male and female faces as context cues in a flanker task.
@@
 
-#The Current Study
+# The Current Study
 
@@
 
-#Methods
+# Methods
 
@@
 
-```{r figure1, echo=FALSE, fig.cap="A caption", out.width = "75%", fig.align="center"}
+```{r figure1, echo=FALSE, fig.cap='(ref:figure1)', out.width = "75%", fig.align="center"}
 knitr::include_graphics("images/Task.jpg")
@@
 
-##Participants
+## Participants
 
@@
 
-##Apparatus & Stimuli
+## Apparatus & Stimuli
 
@@
 
-##Procedure
+## Procedure
 
@@
 
-#Results
+# Results
+
+```{r analysis}
+source("data-analysis/analysis.R")
+
+```
 
@@
 
-```{r figure2, echo=FALSE, fig.cap="A caption", out.width = "75%", fig.align="center"}
+```{r figure2, echo=FALSE, fig.cap='(ref:figure2)', out.width = "75%", fig.align="center"}
 knitr::include_graphics("images/E1_bar.jpg")
@@
 
-Participants with mean error rates greater than 25% were excluded from the analyses, eliminating fourteen participants.
+Participants with mean error rates greater than 25% were excluded from the analyses, eliminating `r N_subjects_removed` participants.
 For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure.
 The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms [@van_selst_solution_1994].
-This procedure removed 3.76% of the total observations.
+This procedure removed `r round(percent_removed*100,digits = 2)`% of the total observations.
+
 The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1).
@@
 
-The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, F(1,128) = 8.76, *MSE* = 1672.8, *p* = .004, η~p~2 = .06, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
-Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, F(2,128) = .01, *MSE* = 1672.8, *p* = .99, η~p~2 < .0001, showing no evidence for differences between the CSPC effects across context-type manipulations.
+The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, `r RT_ANOVA$countProp_trialCongruency`, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
+Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant,  showing no evidence for differences between the CSPC effects across context-type manipulations.
 
-Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, F(1,128) = 6.57, *MSE*  = 13.98, *p* = .01, η~p~2 = .05, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, F(2,128) = .9, *MSE* = 13.98, *p* = .41, η~p~2 = .01.
+Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, F(1,128) = 6.57, *MSE*  = 13.98, *p* = .01, $\eta$~p~2 = .05, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, F(2,128) = .9, *MSE* = 13.98, *p* = .41, $\eta$~p~2 = .01.
 Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.
 
-#General Discussion
+# General Discussion
 
@@
 
-#References
+\newpage
+
+# References
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id = "refs"></div>
+\endgroup

### 2018-12-07 data-analysis/analysis.R

@@ -1,0 +1,91 @@
+load("data-analysis/raw_data.Rda")
+
+vjoutNR <- function(x,n) {
+  xm <- mean(x)
+  xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
+             25, 30, 35, 50, 80)
+  stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
+            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
+            2.45, 2.48, 2.5)
+  stdindex <- length(xsize[xsize <= length(x)])
+  removed <- x[x < xm+sd(x)*stds[stdindex]]
+  removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
+  proportionRemoved <- length(removed)/length(x)
+  finaldata<-c(mean(removed),1-proportionRemoved)
+  return(finaldata[[n]])
+}
+
+labelDataset <- function(data) {
+  correctLabel <- function(x) {
+    
+    if(!is.null(attributes(x)$labels)) {
+      class(attributes(x)$labels) <- typeof(x)
+    }
+    return(x)
+  }
+  for(i in colnames(data)) {
+    data[, i] <- correctLabel(data[, i])
+  }
+  return(data)
+}
+
+# Find subs with < 75% accuracy
+low_acc <- raw_data %>%
+  group_by(Subject,Exp,countProp,trialProp,trialCongruency) %>%
+  summarise(meanAccuracy = mean(ACC)) %>%
+  filter(meanAccuracy < .75) %>%
+  .$Subject
+
+N_subjects_removed<-length(unique(low_acc))
+
+## Summarize by subject
+RT.DF <- raw_data %>%
+  filter(
+    RT < 3000,
+    RT > 0,
+    ACC == TRUE,
+    Subject%in%low_acc == FALSE
+  ) %>%
+  group_by(Exp,Subject,order,block,trialProp,countProp,trialCongruency)%>%
+  summarize(vjoutRT = vjoutNR(RT,1))
+
+## Find percentage of trials removed 
+percent_removed <- raw_data %>%
+  filter(
+    RT < 3000,
+    RT > 0,
+    ACC == TRUE,
+    Subject%in%low_acc == FALSE
+  ) %>%
+  group_by(Exp,Subject,order,block,trialProp,countProp,trialCongruency)%>%
[…]

### 2018-12-07 data-analysis/combineData.R

@@ -1,0 +1,206 @@
+pack<-c("dplyr","ggplot2","pander","knitr","xtable","car","Crump","lsr","afex","stringr","tidyr")
+lapply(pack, require, character.only = TRUE)
+
+
+## LOAD DATA FROM E1 and E2 ###
+load("EAll.Rda")
+load("EAllq.Rda")
+
+### ANALYZE QUIZ DATA ###
+quizAnalysis <-tbl_df(data)
+quizAnalysis <- quizAnalysis %>%
+  filter(trialColor == "quiz")
+
+quizAnalysis <- quizAnalysis[,-10:-17]
+colnames(quizAnalysis)<- c("subID","trial","trialType","correctResponse","time1","time2","response","ACC","unknown","Subject","block","subBlock","subBlockB","newACC","preCon","preTrialProp", "order")
+
+quizAnalysis <- quizAnalysis %>%
+  filter(is.na(response) == FALSE)
+
+quizAnalysis$response<-as.numeric(as.character(quizAnalysis$response))
+quizAnalysis$correctResponse<-as.numeric(as.character(quizAnalysis$correctResponse))
+quizAnalysis$ACC<-as.numeric(as.character(quizAnalysis$ACC))
+quizAnalysis$fineACC<-abs(quizAnalysis$response - quizAnalysis$correctResponse)
+quizAnalysis$Exp <- NA
+quizAnalysis[quizAnalysis$Subject < 51,]$Exp <- "E1"
+quizAnalysis[quizAnalysis$Subject > 51,]$Exp <- "E2"
+
+
+quiz.Sum<- quizAnalysis %>%
+  group_by(Subject) %>%
+  filter(!is.na(fineACC),Subject != 4, Subject != 29) %>%
+  summarise(ACC = mean(ACC), fineACC = mean(fineACC)) 
+
+quiz.Sum
+### END QUIZ DATA ###
+
+### GET QUESTIONNAIRE DATA ###
+questData$expTime<-((as.numeric(as.character(questData$completeTime)) -as.numeric(as.character(questData$startTime)))/1000)/60
+questData$Exp<-NA
+questData[questData$subnum < 51,]$Exp <- "E1"
+questData[questData$subnum > 51,]$Exp <- "E2"
+questData <- questData %>%
[…]

### 2018-12-07 v1-task-relevance-cspc.Rmd
First Draft

@@
 
-```{r figure1, echo=FALSE, fig.cap='(ref:figure1)', out.width = "75%", fig.align="center"}
+```{r figure1, echo=FALSE, fig.cap="(ref:figure1)", fig.width=6.7,fig.height=4.51}
 knitr::include_graphics("images/Task.jpg")
@@
 
-```{r figure2, echo=FALSE, fig.cap='(ref:figure2)', out.width = "75%", fig.align="center"}
-knitr::include_graphics("images/E1_bar.jpg")
+```{r figure2, echo=FALSE, fig.cap="(ref:figure2)", fig.width=6.875, fig.height= 4}
+figure2
 ```
@@
 
-The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, `r RT_ANOVA$countProp_trialCongruency`, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
-Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant,  showing no evidence for differences between the CSPC effects across context-type manipulations.
+The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, `r RT_ANOVA$Task_Relevant_Context_Congruency`, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
+Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, `r RT_ANOVA$Condition_Task_Relevant_Context_Congruency`, showing no evidence for differences between the CSPC effects across context-type manipulations.
 
-Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, F(1,128) = 6.57, *MSE*  = 13.98, *p* = .01, $\eta$~p~2 = .05, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, F(2,128) = .9, *MSE* = 13.98, *p* = .41, $\eta$~p~2 = .01.
+Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, `r RT_ANOVA$Task_Relevant_Context_Congruency`, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, `r RT_ANOVA$Condition_Task_Relevant_Context_Congruency`.
 Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.

### 2018-12-07 v1-task-relevance-cspc.tex
First Draft

\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Contextual recruitment of selective attention can be updated via changes in task-relevance},
            pdfauthor={Nicholaus P. Brosowsky~\& Matthew J. C. Crump},
            pdfkeywords={Attention, Memory, Cognitive Control, Conflict Adaptation,
Context-specific, Task Relevance},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Contextual recruitment of selective attention can be updated via changes
in task-relevance}
    \author{Nicholaus P. Brosowsky\textsuperscript{1}~\& Matthew J. C.
Crump\textsuperscript{2}}
    \date{}

\shorttitle{Contextual recruitment of selective attention}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} The Graduate Center of the City University of New York\\\textsuperscript{2} Brooklyn College of the City University of New York}
\keywords{Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance\newline\indent Word count: 5946}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\authornote{

Correspondence concerning this article should be addressed to Nicholaus
P. Brosowsky, The Graduate Center, CUNY, 365 5th Ave, New York, NY
10016. E-mail:
\href{mailto:nbrosowsky@gradcenter.cuny.edu}{\nolinkurl{nbrosowsky@gradcenter.cuny.edu}}}

\abstract{
Evidence across a wide variety of attention paradigms shows that
environmental cues can trigger adjustments to ongoing priorities for
attending to relevant and irrelevant information. This context-specific
control over attention suggests that cognitive control can be both
automatic and flexible. For instance, in selective attention tasks,
congruency effects are larger for items that appear in a context
associated with infrequent conflict than in a context associated with
frequent conflict. Since the to-be-presented context cannot be predicted
or prepared for in advance, attention is assumed to be rapidly updated
on-the-fly, triggered by the currently presented context.
Context-specific control exemplifies how learning and memory processes
can influence attention to enable cognitive flexibility. However, what
determines the use of previously learned associations still remains
unclear. In the current study, we examined whether task-relevance would
influence the learning and use of context cues in a flanker task. Using
a secondary counting task, context dimensions associated with differing
levels of conflict were made task-relevant or -irrelevant across the
experiment. In short, we found that making new contextual information
task-relevant caused participants to ignore a previously learned
context-attention association and adopt a new context-specific control
strategy; all without changing the experimental stimuli. This result
suggests that task-relevance is a key determinant of context-specific
control.

}

\begin{document}
\maketitle

\section{Introduction}\label{introduction}

Selective attention processes are commonly investigated using
interference paradigms such as the Stroop (1935) and flanker (B. A.
Eriksen \& Eriksen, 1974) tasks, where participants identify a target
while ignoring a response-congruent or -incongruent distractor.
Performance is typically better on congruent versus incongruent trials
and the difference-the congruency effect-taken as an index of
attentional priorities. Large congruency effects are thought to reflect
ineffective filtering of the distracting stimuli whereas small
congruency effects are thought to reflect effective filtering. By
probing factors that systematically alter congruency effects, we can
then make inferences about processes that control attentional filtering.
For example, manipulating the frequency of conflict via the proportion
of congruent versus incongruent trials has shown to influence the size
of the congruency effect. Typically, a high proportion congruent
experiment produces large congruency effects, whereas a low proportion
congruent experiment produces small congruency effects (Logan \&
Zbrodoff, 1979; Lowe \& Mitterer, 1982; West \& Baylis, 1998). This
result is usually explained as strategic control, where participants
increase attentional control under high-conflict demands and relax
attentional control under low-conflict demands (Logan, 1980; Logan \&
Zbrodoff, 1979; Logan, Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer,
1982). Recent work however, has demonstrated that attentional control is
not only adjusted by top-down regulation, but can also be triggered
automatically by environmental cues (Brosowsky \& Crump, 2018; J. Bugg
\& Crump, 2012; Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \&
Egner, 2012; Mayr \& Bryck, 2007).

For example, Crump, Gong, and Milliken (see also, Corballis \& Gratton,
2003; Crump, Gong, \& Milliken, 2006) presented Stroop stimuli in one of
two randomly chosen locations and manipulated the frequency of conflict
associated with each location. One location was associated with a high
frequency of conflict (25\% congruent trials) and the other with a low
frequency of conflict (75\% congruent trials). Overall, the proportion
of congruent trials was 50\% and randomized such that the upcoming
location could not be predicted. Even so, congruency effects were shown
to be smaller for trials where the stimulus appeared in the high
conflict location as compared to the low conflict location. This effect,
known now as the context-specific proportion congruent effect (CSPC),
has now been replicated in a number of different selective attention
paradigms (e.g., Alards-Tomalin, Brosowsky, \& Mondor, 2017; Blais,
Harris, Sinanian, \& Bunge, 2015; J. Bugg, 2014; Crump, 2016; Crump,
Milliken, Leboe-McGowan, Leboe-McGowan, \& Gao, 2018; Fischer,
Gottschalk, \& Dreisbach, 2014; Hübner \& Mishra, 2016).

Critical evidence however, that CSPC effects reflect context-specific
control rather than other non-control learning processes (e.g., Schmidt
\& Besner, 2008), comes from work showing that CSPC effects can transfer
to frequency unbiased items (Brosowsky \& Crump, 2016; Crump \&
Milliken, 2009; though, see Hutcheon \& Spieler, 2017; Weidler \& Bugg,
2016; Weidler, Dey, \& Bugg, 2018). Crump and Milliken (2009), for
example, divided Stroop items into two mutually exclusive sets (e.g.,
RED/GREEN and BLUE/YELLOW). One set was defined as the frequency biased
set, and presented with 75\% congruency in one location, and 25\%
congruency in the other. The second set however, was presented with 50\%
congruency in both locations. Nevertheless, they found smaller
congruency effects for unbiased items presented in the high conflict
location as compared to the low conflict location.

One explanation for CSPC effects is that the repeated application of
attentional priorities in a particular context creates an associative
link in episodic memory between the attentional control procedures and
the contextual information (Abrahamse, Braem, Notebaert, \& Verguts,
2016; Brosowsky \& Crump, 2018; Crump, 2016; Egner, 2014). Once the
associative link is established, processing the context is assumed to
trigger the retrieval of previous experiences, automatically reinstating
the associated attentional priorities. Although this explanation seems
plausible, it remains largely unclear how such associations are
established and perhaps more importantly, it remains unclear what
determines which learned associations will be used to guide attention at
any given moment.

The importance of the latter issue becomes increasingly clear if we
speculate about context-specificity in more complex, real-world
environments. Consider myself, right now, writing this article in a
coffee shop. The coffee shop is a complex environment that contains a
multitude of contextual cues (e.g., pictures on the wall, chairs,
coffee, laptop), each of which I have had many different experiences
applying attentional control. Although my laptop might cue attentional
processing helpful for finishing this article, other features of the
coffee shop might cue other, unhelpful attentional processing related to
other experiences like socializing and people-watching. This is all to
say that our environments, and experiences within them, afford many
different associative relationships between cognitive processing and
environmental cues. What then determines which associative relationships
will be used to guide attention (or even if such associative
relationships are used at all)?

Task-relevance might be one factor that is important for establishing
and using context-attention associations. This proposal might seem
counter-intuitive as it is typically assumed that the context, within
selective attention tasks at least, is completely irrelevant to the
task. In fact, referring to such stimulus dimensions as the
\enquote{context} carries with it an implication that the feature is
background information, irrelevant to the task-at-hand, and should be
ignored by the participant. A closer look at CSPC designs however,
suggests that the context cues may not be as irrelevant as implied. For
example, the most commonly used context cue is location (Brosowsky \&
Crump, 2016; Corballis \& Gratton, 2003; Crump, 2016; Crump et al.,
2006; Crump, Vaquero, \& Milliken, 2008; Weidler \& Bugg, 2016; Weidler
et al., 2018). Although in some sense, the location is irrelevant for
identifying the color of a word, it seems disingenuous to consider it
completely task-irrelevant. In order to identify the target, the
participant must first identify and orient to its location on the
screen. In this is sense, it is relevant to their ability to complete
the task and furthermore, location information may receive priority
during encoding (Logan, 1998; Mayr, 1996). Similar arguments could be
made about other context features that are inherent to processing the
target stimulus, like font-type (J. Bugg, Jacoby, \& Toth, 2008) and
color (Vietze \& Wendt, 2009).

To date, we are aware of only one study that has looked at
task-relevance within the CSPC literature. Crump, Vaquero, \& Milliken
(2008) used a Stroop prime-probe task where the distractor word is
presented first followed by a color patch probe. Critically, they used
the shape of the color patch probe, either a square or a circle, as the
contextual dimension; one associated with a high frequency of conflict,
the other with a low frequency. In one experiment participants were made
aware of the shape-proportion contingencies but given no additional
instructions. In the second, participants were given a secondary task to
count the number of trials that contained a square. The first experiment
failed to find evidence for context-specificity, whereas the second did.
Although not testing task-relevance directly, (2013)) found similar
effects. In this study they used images of male and female faces as
context cues in a flanker task. When given instructions to think of the
faces as members of the gender categories they found CSPC effects, but
when given instructions to think of the faces as individuals they did
not. These results suggest that making a context dimension relevant to
the on-going task is important for producing CSPC effects.

\section{The Current Study}\label{the-current-study}

Some prior suggests that the task-relevance of contextual information is
important for establishing new associations between context cues and
attentional priorities. Simply put, CSPC effects emerge when context
cues are somehow made relevant to the task, but do not when made
irrelevant (Cañadas et al., 2013; Crump et al., 2006, 2008). However, it
still remains unclear how task-relevance may or may not inform the use
of previously learned associations. In the current study, we examined
whether manipulating task-relevance would cause participants to ignore a
previously learned association and adopt a new context-specific control
strategy.

A flanker task was used to measure attentional control in an adapted
CSPC design (Crump \& Milliken, 2009; Crump, Brosowsky, \& Milliken,
2017). Similar to previous studies, flanker stimuli were presented in
contexts associated with differing levels of conflict (0\%, 50\%, or
100\% congruent). However, unlike previous CSPC designs where contexts
were defined by a single discriminating feature (e.g., upper vs.~lower
screen locations), contexts were defined by two feature dimensions (see
Figure 1A). In one condition, for example, contexts were defined by
object identity (hat or chair) and color (blue or green). Only three out
of the four possible feature combinations were presented, each
associated with a different proportion of congruent trials (0\%, 50\%,
or 100\% congruent). Critically, the frequency unbiased context (50\%
congruent) always shared a feature with each of the frequency-biased
contexts (0\% and 100\% congruent). The frequency biased contexts (0\%
and 100\% congruent) however, did not share any features (see Figure 1C
for an example).

A secondary counting task was used to manipulate the task-relevance of
the context dimensions (Crump \& Milliken, 2009) which critically,
switched halfway through the experiment. Participants were instructed to
keep a running count of one of the overlapping features (e.g.,
\enquote{count whenever a hat is presented}) which was associated with
either a high or low frequency of conflict. Halfway through the
experiment they received new instructions to count the other overlapping
feature (e.g., \enquote{count whenever a green item is presented}).
Critically, the set of context images remained the same throughout the
experiment (see Figure 1C for an example) and the task-relevance of the
context dimensions was the only aspect of the experiment that changed
from the first to second phases.

The critical measure of interest is the congruency effect produced in
the frequency unbiased context. If, on the one hand, task-relevance has
no impact on the use of context-attention associations we would expect
no differences between the congruency effects when the high-conflict
context dimension is made task-relevant or the low-conflict context
dimension is made task-relevant. This could occur because all three
contexts are treated as individual contexts throughout the whole
experiment (e.g., Cañadas et al., 2013). Or it could occur because
associations formed in the first block interfere with learning new
associations in the second (e.g., Brosowsky \& Crump, 2016). On other
hand, task-relevance might not only dictate how associations are formed,
but also whether learned associations are used. In this case, we would
expect that there will be smaller congruency effects when the
high-conflict context dimension is made task-relevant as compared to
when the low-conflict context dimension is made task-relevant. This
would demonstrate that participants were able to ignore a previously
learned association and adopt a new context-specific control strategy.

A secondary goal was to conceptually replicate previous findings and
test the generalizability of any task-relevance effects. Therefore, we
included three conditions that differed only in the kinds of stimuli
used to create context cues. In one condition we used face images where
context dimensions were defined by social categories, similar to Cañadas
et al., (2013). However, they found that social categorization occurred
spontaneously and it was unclear what impact that would have on the
current results. Therefore, we included another condition that used
images of simple objects where context dimensions were defined by object
features. Finally, Cañadas et al.(2013) also found that context effects
generalized to novel face images. In our third condition we used
non-repeating face exemplars to examine whether any task-relevance
effects would also generalize in our design or if learning would be
image-specific.

\section{Methods}\label{methods}

\begin{figure}
\centering
\includegraphics{images/Task.jpg}
\caption{\label{fig:figure1}Illustration of the stimuli and trial construction. Figure
1A shows the feature dimensions for each of the conditions. Figure 1B
shows an example trial stimulus containing both the context and flanker
images. Figure 1C shows an example of how feature dimensions could have
been assigned to each proportion congruency (PC) condition, and an
example of the secondary task assignments. The secondary task order, as
well as the feature and congruency assignments were all randomized for
each participant.}
\end{figure}

\subsection{Participants}\label{participants}

All participants were recruited from Amazon Mechanical Turk (AMT) and
compensated \$2.00 for participating. The amount compensated was
calculated by estimating the maximum amount of time required to complete
each experiment and multiplying by \$6.00 per hour. For each experiment
the number of HITs (Human intelligence tasks, an Amazon term for a
work-unit) refers to the number of participants who initiated the study.
Participants were included in the study if they completed all trials. We
posted 150 HITs and 145 participants completed all trials.

\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli}

The experiments were programmed using JavaScript, CSS and HTML. The
program allowed participants to complete task only if they were running
Safari, Google Chrome, or Firefox web browsers. Flanker stimuli
consisted of images of five arrows pointed left or right presented at
250 x 50 pixels (each arrow was 50 x 50 pixels). Context stimuli were
constructed using images selected from Brady, Konkle, Gill, Oliva, and
Alvarez (2013) color-rotated to blue and green, and face images from the
Chicago Face Database (Ma, Correll, \& Wittenbrink, 2015), supplemented
with the NimStim Set of Facial Expressions (Tottenham et al., 2009). The
object images were displayed at 250 x 250 pixels, while the face images
were displayed at 250 x 313 pixels. The experiment ran as a pop-up
window that filled the entire screen. The background was white, and
stimuli were presented in the center of the screen.

Design. Experiment 1 used a 2x2x3 mixed design with task-relevant
context (0\% and 100\%) and unbiased-item congruency (congruent and
incongruent) as within-subject factors, and context-type (object,
social, and social/non-repeating) as the between-subjects factor. All
three conditions were constructed using the same general method. The
experiment was divided into two phases. Each phase consisted of 144
flanker trials (48 trials per context), and 13 count response trials for
a total of 314 trials. On the count response trials, participants
indicated how many trials they had counted until that point. The count
response trials occurred once for every 12 flanker trials and was
randomly inserted between trial 6 and 12 of each 12-trial block. Each
phase ended with one additional count response trial.

On every flanker trial, participants were presented with flanker stimuli
paired with one of three contexts. Each context was associated with a
different proportion congruency such that two cues were associated with
a biased frequency (0\% and 100\% proportion congruency), while one was
associated with an unbiased frequency (50\% proportion congruency). The
feature dimensions and corresponding context images assigned to each of
the biased and unbiased item sets were randomly determined for each
participant. However, context images used for the frequency biased
trials never shared features, while the frequency unbiased context image
always shared a feature with each of the frequency biased context images
(see Figure 1). Additionally, the feature assignments remained the same
throughout phases 1 and 2, and critically, the only change to the task
was which feature the participant was instructed to count (see Figure 1C
for an example).

All critical aspects of the task were randomized between participants.
This includes the three chosen context images, the features assigned to
proportion levels, the features assigned to each counting condition, the
secondary task order, and the order of trials.

\subsection{Procedure}\label{procedure}

All participants were AMT workers who found the experiment using the AMT
system. The participant recruitment procedure and tasks were approved by
the Brooklyn College Institutional Review Board. Each participant read a
short description of the task and gave consent by pressing a button
acknowledging they had read the displayed consent form. Participants
then completed a short demographic survey, and proceeded to the main
task, which was displayed as a pop-up window. Participants were
instructed to identify the direction of the center arrow on each trial
as quickly and accurately as possible by pressing \enquote{z} if the
arrow pointed left, and \enquote{m} if the arrow pointed right.
Additionally, they were instructed to silently keep count of the number
of trials that contained a feature. In the object context condition,
they were asked to count trials that contained a certain color (blue or
green) or object-identity (hat or chair) and in the social context
conditions they were asked to count the number of trials that contained
appeared a certain gender (male or female) or race (black or white).
Periodically throughout the experiment, participants were asked to
report how many trials they had counted until that point and to restart
their count from 0. Halfway through the experiment participants received
new instructions about which feature to count (see Figure 1C). Each
trial began with a blank inter-stimulus interval (ISI) of 400 ms,
followed by a fixation cross presented in the center of the screen for
200 ms, then a second blank ISI of 400 ms. Next, the flanker and context
stimuli appeared in the center of screen (the flanker above the context
image; see Figure 1B) and remained on screen until a response was made.
Following a response, accuracy feedback was presented for 1000 ms. A
response automatically triggered the next trial. Halfway through the
experiment (157 trials), participants received new instructions about
which feature to count and to press the button on-screen when they were
ready to continue.

\section{Results}\label{results}

\begin{figure}
\centering
\includegraphics{v1-task-relevance-cspc_files/figure-latex/figure2-1.pdf}
\caption{\label{fig:figure2}Results from experiment 1 showing congruency effects
(incongruent - congruent) for frequency unbiased items in reaction times
(left) and error rates (right) as a function of the task-relevant
context (100\% proportion congruent versus 0\% proportion congruent).}
\end{figure}

Participants with mean error rates greater than 25\% were excluded from
the analyses, eliminating 13 participants. For all remaining
participants, the correct RTs from frequency unbiased trials in each
condition were submitted to an outlier removal procedure. The
non-recursive Van Selst and Jolicoeur outlier removal procedure was
applied after removing response times greater than 3000 ms (Van Selst \&
Jolicoeur, 1994). This procedure removed 3.39\% of the total
observations.

The primary question of interest was whether the task-relevance of
context features associated with different levels of conflict would
influence the size of the congruency effect for frequency unbiased items
(see Table 1). To that end, mean correct RTs and mean error rates from
frequency unbiased trials were submitted to a mixed analysis of variance
(ANOVA) with task-relevant context (0\% and 100\% PC) and unbiased-item
congruency (congruent and incongruent) as within-subject factors, and
context-type (object, social, and social/non-repeating) as the
between-subjects factor.

The results of the RT analysis revealed the critical, two-way
interaction between task-relevant context and unbiased-item congruency
to be significant, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 1,608.54\),
\(p = .005\), \(\hat{\eta}^2_p = .061\), demonstrating smaller
congruency effects when the context dimension associated with high
conflict was made task-relevant. Additionally, the three-way interaction
between the task-relevant context, unbiased-item congruency, and
context-type was non-significant, \(F(2, 128) = 0.00\),
\(\mathit{MSE} = 1,608.54\), \(p = .996\), \(\hat{\eta}^2_p = .000\),
showing no evidence for differences between the CSPC effects across
context-type manipulations.

Similarly, the corresponding error analysis also resulted in a
significant two-way interaction between the task-relevant context and
unbiased-item congruency, \(F(1, 128) = 8.30\),
\(\mathit{MSE} = 1,608.54\), \(p = .005\), \(\hat{\eta}^2_p = .061\),
and a non-significant three-way interaction between task-relevant
context, unbiased-item congruency, and context-type,
\(F(2, 128) = 0.00\), \(\mathit{MSE} = 1,608.54\), \(p = .996\),
\(\hat{\eta}^2_p = .000\). Therefore, the congruency effects in error
rates were also smaller when the context dimension associated with high
conflict was made task-relevant, corroborating the results of the
reaction time analysis.

\section{General Discussion}\label{general-discussion}

The aim of the current study was to investigate whether task-relevance
plays a role in the contextual recruitment of selective attention.
Specifically, we tested whether manipulating the relative task-relevance
of context cues could cause participants to ignore a previously learned
context-association and apply a new association. We created a frequency
unbiased context cue that shared features with two frequency biased
contexts and included a feature-counting task to manipulate the
task-relevance of context dimensions across two blocks of trials.
Critically, halfway through the experiment participants received new
instructions changing the task-relevant feature from one frequency
biased cue to the other.

The key finding was that the congruency effects for the frequency
unbiased items were significantly larger when the low-conflict context
was made task-relevant as compared to when the high-conflict context was
made task-relevant. This result is consistent with prior CSPC effects
and, like the previous work, suggests that the context cues triggered
rapid adjustments to attentional control (Crump \& Milliken, 2009).
However, unlike prior studies, we were able to experimentally manipulate
the CSPC effect across blocks of trials without changing any of the
physical properties of the stimuli. This novel finding demonstrates that
participants were able to learn and apply one context-attention
association in the first phase, and subsequently ignore that association
to learn a new association in the second phase.

This result implicates an important role for task-relevance in producing
CSPC phenomena. Crump et al. (2008) used shapes as context cues in a
prime-probe Stroop task and did not find CSPC effects until the context
cues were made task-relevant. Similarly, Cañadas et al. (2013)
eliminated the CSPC effect by making the contextual cue effectively
unrelated to the task. These studies suggest that task-relevance plays
an important role in establishing associations between contextual
information and attentional priorities to produce CSPC effects. Our
finding extends this work in two important ways. First, we show that
changing the task-relevance of the presented cues corresponded with a
change in attentional control in the predicted direction. This
demonstrates that task-relevance is also a key determinant of whether a
previously learned attention-context association will be used or ignored
in favor of a new association. Second, we show that task-relevance
allowed participants resolve competition between two competing
contextual cues, responding on the basis of one at the expense of the
other. To our knowledge, this is the first demonstration that CSPC
effects can be produced when there are multiple, overlapping contextual
cues available.

In light of prior work, we take this as evidence that the contextual
recruitment of selective attention, although likely implicit, is not
obligatory (e.g., Brosowsky \& Crump, 2016), requiring that
environmental information be incorporated into the task representation.
Similarly, there appears to be flexibility in which environmental
features are selected and used to guide attention, which can be rapidly
updated depending on the task-relevance of those features. Such a result
lends some insight into how context-specific control might operate in
more complex, real-world environments, where there is an over-abundance
of environmental features that afford many different learned
associations. From a theoretical perspective, this result is consistent
memory-based accounts of CSPC phenomena (Brosowsky \& Crump, 2018; J.
Bugg \& Hutchison, 2013; Crump \& Milliken, 2009; Crump et al., 2018,
2017). Under this view, a memory process encodes attentional priorities
in the representation of individual experiences and, as a result, become
associated with the environment where they were used. The subsequent
reoccurrence of a prior context triggers the retrieval and reinstatement
of those attentional priorities. Our results show however, that all the
features of the environment may not be treated equally and that only
task-relevant features are used to probe memory and guide attention.

Another key result of this study concerned the different stimuli used as
context cues. Across the three conditions, we varied the type of context
image and dimensions. We manipulated the type of image presented,
including both objects (identity and color dimensions) and faces (gender
and racial dimensions). We also manipulated whether a single set of
three repeating images were presented (object and social) or a set of
non-repeating images were presented (social/non-repeating). Across all
three conditions, we found no evidence that using different stimuli had
an influence on the size or direction of the CSPC demonstrating
generalizability of this phenomenon. Furthermore, CSPC effects were
present even when using non-repeating images which suggests that
context-dependency did rely on image-specific associations but
higher-order, learned categorical information.

Traditional models of person perception posit that social categories are
automatically activated in the presence of social stimuli (e.g., Brewer,
1988; Devine, 1989; Fiske \& Neuberg, 1990). Cañadas et al. (2013)
however, found that directing participants to think about faces in terms
of individual features eliminated context-specific attention effect and
suggested that momentary motivations may influence the automaticity of
social categorization. Our results add to this literature by observing
the influence of momentary motivations (i.e., task-relevance) when there
is competition between two salient social categories. Specifically, we
found that participants could categorize on the basis of one social cue
at the expense of the other, and subsequently switch between them. These
findings may speak to issues of automaticity in social categorization
(Macrae \& Bodenhausen, 2001) as well as understanding how the
situational context can prime one social identity over another (Crisp \&
Hewstone, 2007). Furthermore, we found no evidence for differences
between the social and object conditions. This suggests that
categorization within the CSPC task is quickly and easily learned when
the task supports such learning and is non-unique to social stimuli.

In sum, our results provide new evidence that changes in task-relevance
can update the contextual recruitment of selective attention in a CSPC
flanker task. Importantly, we show that making one feature task-relevant
produced a CSPC effect, even in the presence of a competing contextual
cue. Moreover, changing the task-relevant context-cue midway through the
experiment was accompanied by predictable changes in the congruency
effects. This effect was found to be generalizable across two different
kinds of stimuli and occurred even when using non-repeating images.
These results implicate an important role for task-relevance in
producing context-dependency and are consistent with memory-based
accounts of CSPC phenomena.

\newpage

\section{References}\label{references}

\begingroup
\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\hypertarget{ref-abrahamse_grounding_2016}{}
Abrahamse, E., Braem, S., Notebaert, W., \& Verguts, T. (2016).
Grounding cognitive control in associative learning. \emph{Psychological
Bulletin}, \emph{142}, 693--728.
doi:\href{https://doi.org/10.1037/bul0000047}{10.1037/bul0000047}

\hypertarget{ref-alards-tomalin_auditory_2017}{}
Alards-Tomalin, D., Brosowsky, N. P., \& Mondor, T. A. (2017). Auditory
statistical learning: Predictive frequency information affects the
deployment of contextually mediated attentional resources on perceptual
tasks. \emph{Journal of Cognitive Psychology}, \emph{0}(0), 1--11.
doi:\href{https://doi.org/10.1080/20445911.2017.1353518}{10.1080/20445911.2017.1353518}

\hypertarget{ref-blais_trial-by-trial_2015}{}
Blais, C., Harris, M. B., Sinanian, M. H., \& Bunge, S. A. (2015).
Trial-by-trial adjustments in control triggered by incidentally encoded
semantic cues. \emph{The Quarterly Journal of Experimental Psychology},
\emph{68}, 1920--1930.
doi:\href{https://doi.org/10.1080/17470218.2014.1000346}{10.1080/17470218.2014.1000346}

\hypertarget{ref-brady_visual_2013}{}
Brady, T. F., Konkle, T., Gill, J., Oliva, A., \& Alvarez, G. A. (2013).
Visual long-term memory has the same limit on fidelity as visual working
memory. \emph{Psychological Science}, \emph{24}, 981--990.
doi:\href{https://doi.org/10.1177/0956797612465439}{10.1177/0956797612465439}

\hypertarget{ref-brewer_dual_1988}{}
Brewer, M. B. (1988). A dual process model of impression formation. In
R. S. Wyer Jr \& T. K. Srull (Eds.), \emph{A dual-process model of
impression formation: Advances in social cognition} (Vol. 1, pp. 1--36).
Hillsdale, NJ: Erlbaum.

\hypertarget{ref-brosowsky_context-specific_2016}{}
Brosowsky, N. P., \& Crump, M. J. (2016). Context-specific attentional
sampling: Intentional control as a pre-requisite for contextual control.
\emph{Consciousness and Cognition}, \emph{44}, 146--160.
doi:\href{https://doi.org/10.1016/j.concog.2016.07.001}{10.1016/j.concog.2016.07.001}

\hypertarget{ref-brosowsky_memory-guided_2018}{}
Brosowsky, N. P., \& Crump, M. J. C. (2018). Memory-guided selective
attention: Single experiences with conflict have long-lasting effects on
cognitive control. \emph{Journal of Experimental Psychology: General}.
doi:\href{https://doi.org/10.1037/xge0000431}{10.1037/xge0000431}

\hypertarget{ref-bugg_conflict-triggered_2014}{}
Bugg, J. (2014). Conflict-triggered top-down control: Default mode, last
resort, or no such thing? \emph{Journal of Experimental Psychology:
Learning, Memory, and Cognition}, \emph{40}(2), 567.

\hypertarget{ref-bugg_support_2012}{}
Bugg, J., \& Crump, M. J. (2012). In support of a distinction between
voluntary and stimulus-driven control: A review of the literature on
proportion congruent effects. \emph{Frontiers in Psychology}, \emph{3},
367.
doi:\href{https://doi.org/10.3389/fpsyg.2012.00367}{10.3389/fpsyg.2012.00367}

\hypertarget{ref-bugg_converging_2013}{}
Bugg, J., \& Hutchison, K. A. (2013). Converging evidence for control of
color--word Stroop interference at the item level. \emph{Journal of
Experimental Psychology: Human Perception and Performance},
\emph{39}(2), 433.

\hypertarget{ref-bugg_multiple_2008}{}
Bugg, J., Jacoby, L. L., \& Toth, J. P. (2008). Multiple levels of
control in the Stroop task. \emph{Memory \& Cognition}, \emph{36},
1484--1494.
doi:\href{https://doi.org/10.3758/MC.36.8.1484}{10.3758/MC.36.8.1484}

\hypertarget{ref-canadas_social_2013}{}
Cañadas, E., Rodríguez-Bailón, R., Milliken, B., \& Lupiáñez, J. (2013).
Social categories as a context for the allocation of attentional
control. \emph{Journal of Experimental Psychology: General}, \emph{142},
934--943. doi:\href{https://doi.org/10.1037/a0029794}{10.1037/a0029794}

\hypertarget{ref-corballis_independent_2003}{}
Corballis, P. M., \& Gratton, G. (2003). Independent control of
processing strategies for different locations in the visual field.
\emph{Biological Psychology}, \emph{64}, 191--209.
doi:\href{https://doi.org/10.1016/S0301-0511(03)00109-1}{10.1016/S0301-0511(03)00109-1}

\hypertarget{ref-crisp_multiple_2007}{}
Crisp, R. J., \& Hewstone, M. (2007). Multiple social categorization.
\emph{Advances in Experimental Social Psychology}, \emph{39}, 163--254.

\hypertarget{ref-crump_learning_2016}{}
Crump, M. J. (2016). Learning to selectively attend from
context-specific attentional histories: A demonstration and some
constraints. \emph{Canadian Journal of Experimental Psychology/Revue
Canadienne de Psychologie Expérimentale}, \emph{70}, 59--77.
doi:\href{https://doi.org/10.1037/cep0000066}{10.1037/cep0000066}

\hypertarget{ref-crump_flexibility_2009}{}
Crump, M. J. C., \& Milliken, B. (2009). The flexibility of
context-specific control: Evidence for context-driven generalization of
item-specific control settings. \emph{The Quarterly Journal of
Experimental Psychology}, \emph{62}, 1523--1532.
doi:\href{https://doi.org/10.1080/17470210902752096}{10.1080/17470210902752096}

\hypertarget{ref-crump_context-dependent_2018}{}
Crump, M. J. C., Milliken, B., Leboe-McGowan, J., Leboe-McGowan, L., \&
Gao, X. (2018). Context-Dependent Control of Attention Capture: Evidence
From Proportion Congruent Effects. \emph{Canadian Journal of
Experimental Psychology= Revue Canadienne de Psychologie Experimentale}.

\hypertarget{ref-crump_reproducing_2017}{}
Crump, M. J., Brosowsky, N. P., \& Milliken, B. (2017). Reproducing the
location-based context-specific proportion congruent effect for
frequency unbiased items: A reply to Hutcheon and Spieler (2016).
\emph{The Quarterly Journal of Experimental Psychology}, \emph{70},
1792--1807.
doi:\href{https://doi.org/10.1080/17470218.2016.1206130}{10.1080/17470218.2016.1206130}

\hypertarget{ref-crump_context-specific_2006}{}
Crump, M. J., Gong, Z., \& Milliken, B. (2006). The context-specific
proportion congruent Stroop effect: Location as a contextual cue.
\emph{Psychonomic Bulletin \& Review}, \emph{13}, 316--321.
doi:\href{https://doi.org/10.3758/BF03193850}{10.3758/BF03193850}

\hypertarget{ref-crump_context-specific_2008}{}
Crump, M. J., Vaquero, J. M., \& Milliken, B. (2008). Context-specific
learning and control: The roles of awareness, task relevance, and
relative salience. \emph{Consciousness and Cognition}, \emph{17},
22--36.
doi:\href{https://doi.org/10.1016/j.concog.2007.01.004}{10.1016/j.concog.2007.01.004}

\hypertarget{ref-devine_stereotypes_1989}{}
Devine, P. G. (1989). Stereotypes and prejudice: Their automatic and
controlled components. \emph{Journal of Personality and Social
Psychology}, \emph{56}(1), 5.

\hypertarget{ref-egner_creatures_2014}{}
Egner, T. (2014). Creatures of habit (and control): A multi-level
learning perspective on the modulation of congruency effects.
\emph{Frontiers in Psychology}, \emph{5}, 1247.
doi:\href{https://doi.org/10.3389/fpsyg.2014.01247}{10.3389/fpsyg.2014.01247}

\hypertarget{ref-eriksen_effects_1974}{}
Eriksen, B. A., \& Eriksen, C. W. (1974). Effects of noise letters upon
the identification of a target letter in a nonsearch task.
\emph{Perception \& Psychophysics}, \emph{16}, 143--149.
doi:\href{https://doi.org/10.3758/BF03203267}{10.3758/BF03203267}

\hypertarget{ref-fischer_predicting_2015}{}
Fischer, R., \& Dreisbach, G. (2015). Predicting high levels of
multitasking reduces between-tasks interactions. Retrieved from
\url{http://psycnet.apa.org/psycinfo/2015-47211-001/}

\hypertarget{ref-fischer_context-sensitive_2014}{}
Fischer, R., Gottschalk, C., \& Dreisbach, G. (2014). Context-sensitive
adjustment of cognitive control in dual-task performance. \emph{Journal
of Experimental Psychology: Learning, Memory, and Cognition},
\emph{40}(2), 399.

\hypertarget{ref-fiske_continuum_1990}{}
Fiske, S. T., \& Neuberg, S. L. (1990). A continuum of impression
formation, from category-based to individuating processes: Influences of
information and motivation on attention and interpretation. In
\emph{Advances in experimental social psychology} (Vol. 23, pp. 1--74).
Elsevier.

\hypertarget{ref-hutcheon_limits_2017}{}
Hutcheon, T. G., \& Spieler, D. H. (2017). Limits on the
generalizability of context-driven control. \emph{Quarterly Journal of
Experimental Psychology}, \emph{70}(7), 1292--1304.
doi:\href{https://doi.org/10.1080/17470218.2016.1182193}{10.1080/17470218.2016.1182193}

\hypertarget{ref-hubner_location-specific_2016}{}
Hübner, R., \& Mishra, S. (2016). Location-specific attentional control
is also possible in the Simon task. \emph{Psychonomic Bulletin \&
Review}, \emph{23}, 1867--1872.
doi:\href{https://doi.org/10.3758/s13423-016-1057-y}{10.3758/s13423-016-1057-y}

\hypertarget{ref-king_priming_2012}{}
King, J. A., Korb, F. M., \& Egner, T. (2012). Priming of control:
Implicit contextual cuing of top-down attentional set. \emph{The Journal
of Neuroscience}, \emph{32}, 8192--8200.
doi:\href{https://doi.org/10.1523/JNEUROSCI.0934-12.2012}{10.1523/JNEUROSCI.0934-12.2012}

\hypertarget{ref-logan_attention_1980}{}
Logan, G. D. (1980). Attention and automaticity in Stroop and priming
tasks: Theory and data. \emph{Cognitive Psychology}, \emph{12}(4),
523--553.

\hypertarget{ref-logan_what_1998}{}
Logan, G. D. (1998). What is learned during automatization? II.
obligatory encoding of spatial location. \emph{Journal of Experimental
Psychology: Human Perception and Performance}, \emph{24}(6), 1720.

\hypertarget{ref-logan_when_1979}{}
Logan, G. D., \& Zbrodoff, N. J. (1979). When it helps to be misled:
Facilitative effects of increasing the frequency of conflicting stimuli
in a Stroop-like task. \emph{Memory \& Cognition}, \emph{7}, 166--174.
doi:\href{https://doi.org/10.3758/BF03197535}{10.3758/BF03197535}

\hypertarget{ref-logan_strategies_1984}{}
Logan, G. D., Zbrodoff, N. J., \& Williamson, J. (1984). Strategies in
the color-word Stroop task. \emph{Bulletin of the Psychonomic Society},
\emph{22}(2), 135--138.

\hypertarget{ref-lowe_selective_1982}{}
Lowe, D. G., \& Mitterer, J. O. (1982). Selective and divided Attention
in a Stroop task. \emph{Canadian Journal of Psychology/Revue Canadienne
de Psychologie}, \emph{36}(4), 684.

\hypertarget{ref-ma_chicago_2015}{}
Ma, D. S., Correll, J., \& Wittenbrink, B. (2015). The Chicago face
database: A free stimulus set of faces and norming data. \emph{Behavior
Research Methods}, \emph{47}(4), 1122--1135.
doi:\href{https://doi.org/10.3758/s13428-014-0532-5}{10.3758/s13428-014-0532-5}

\hypertarget{ref-macrae_social_2001}{}
Macrae, C. N., \& Bodenhausen, G. V. (2001). Social cognition:
Categorical person perception. \emph{British Journal of Psychology},
\emph{92}(1), 239--255.

\hypertarget{ref-mayr_spatial_1996}{}
Mayr, U. (1996). Spatial attention and implicit sequence learning:
Evidence for independent learning of spatial and nonspatial sequences.
\emph{Journal of Experimental Psychology: Learning, Memory, and
Cognition}, \emph{22}(2), 350.

\hypertarget{ref-mayr_outsourcing_2007}{}
Mayr, U., \& Bryck, R. L. (2007). Outsourcing control to the
environment: Effects of stimulus/response locations on task selection.
\emph{Psychological Research}, \emph{71}(1), 107--116.
doi:\href{https://doi.org/10.1007/s00426-005-0039-x}{10.1007/s00426-005-0039-x}

\hypertarget{ref-schmidt_stroop_2008}{}
Schmidt, J. R., \& Besner, D. (2008). The Stroop effect: Why proportion
congruent has nothing to do with congruency and everything to do with
contingency. \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{34}, 514--523.
doi:\href{https://doi.org/10.1037/0278-7393.34.3.514}{10.1037/0278-7393.34.3.514}

\hypertarget{ref-stroop_studies_1935}{}
Stroop, J. R. (1935). Studies of interference in serial verbal
reactions. \emph{Journal of Experimental Psychology}, \emph{18}, 643.
doi:\href{https://doi.org/10.1037/h0054651}{10.1037/h0054651}

\hypertarget{ref-tottenham_nimstim_2009}{}
Tottenham, N., Tanaka, J. W., Leon, A. C., McCarry, T., Nurse, M., Hare,
T. A., \ldots{} Nelson, C. (2009). The NimStim set of facial
expressions: Judgments from untrained research participants.
\emph{Psychiatry Research}, \emph{168}(3), 242--249.
doi:\href{https://doi.org/10.1016/j.psychres.2008.05.006}{10.1016/j.psychres.2008.05.006}

\hypertarget{ref-van_selst_solution_1994}{}
Van Selst, M., \& Jolicoeur, P. (1994). A solution to the effect of
sample size on outlier elimination. \emph{The Quarterly Journal of
Experimental Psychology Section A}, \emph{47}, 631--650.
doi:\href{https://doi.org/10.1080/14640749408401131}{10.1080/14640749408401131}

\hypertarget{ref-vietze_context_2009}{}
Vietze, I., \& Wendt, M. (2009). Context specificity of conflict
frequency-dependent control. \emph{The Quarterly Journal of Experimental
Psychology}, \emph{62}, 1391--1400.
doi:\href{https://doi.org/10.1080/17470210802426908}{10.1080/17470210802426908}

\hypertarget{ref-weidler_transfer_2016}{}
Weidler, B. J., \& Bugg, J. (2016). Transfer of location-specific
control to untrained locations. \emph{The Quarterly Journal of
Experimental Psychology}, \emph{69}, 2202--2217.
doi:\href{https://doi.org/10.1080/17470218.2015.1111396}{10.1080/17470218.2015.1111396}

\hypertarget{ref-weidler_attentional_2018}{}
Weidler, B. J., Dey, A., \& Bugg, J. M. (2018). Attentional control
transfers beyond the reference frame. \emph{Psychological Research},
1--14.

\hypertarget{ref-west_effects_1998}{}
West, R., \& Baylis, G. C. (1998). Effects of increased response
dominance and contextual disintegration on the Stroop interference
effect in older adults. \emph{Psychology and Aging}, \emph{13}(2), 206.

\endgroup

\end{document}

### 2018-12-07 data-analysis/analysis.R

@@ -1,3 +1,12 @@
+library(dplyr)
+library(tidyr)
+library(afex)
+library(ggplot2)
+library(cowplot)
+#As of 2018/12/07 apa_print() requires development version of Papaja
+#devtools::install_github("crsh/papaja")
+library(papaja)
+
 load("data-analysis/raw_data.Rda")
 
 vjoutNR <- function(x,n) {
@@ -15,23 +24,10 @@ vjoutNR <- function(x,n) {
   return(finaldata[[n]])
 }
 
-labelDataset <- function(data) {
-  correctLabel <- function(x) {
-    
-    if(!is.null(attributes(x)$labels)) {
-      class(attributes(x)$labels) <- typeof(x)
-    }
-    return(x)
-  }
-  for(i in colnames(data)) {
-    data[, i] <- correctLabel(data[, i])
-  }
-  return(data)
-}
 
 # Find subs with < 75% accuracy
 low_acc <- raw_data %>%
-  group_by(Subject,Exp,countProp,trialProp,trialCongruency) %>%
+  group_by(Subject,Condition,Task_Relevant_Context,Frequency,Congruency) %>%
   summarise(meanAccuracy = mean(ACC)) %>%
   filter(meanAccuracy < .75) %>%
   .$Subject
@@ -46,7 +42,7 @@ RT.DF <- raw_data %>%
     ACC == TRUE,
     Subject%in%low_acc == FALSE
   ) %>%
-  group_by(Exp,Subject,order,block,trialProp,countProp,trialCongruency)%>%
+  group_by(Condition,Subject,Order,Phase,Block,Frequency,Task_Relevant_Context,Congruency)%>%
   summarize(vjoutRT = vjoutNR(RT,1))
 
 ## Find percentage of trials removed 
@@ -57,7 +53,7 @@ percent_removed <- raw_data %>%
     ACC == TRUE,
     Subject%in%low_acc == FALSE
   ) %>%
-  group_by(Exp,Subject,order,block,trialProp,countProp,trialCongruency)%>%
+  group_by(Condition,Subject,Order,Phase,Frequency,Task_Relevant_Context,Congruency)%>%
   summarize(percent_removed = vjoutNR(RT,2)) %>%
   ungroup() %>%
   summarize(avg_removed = mean(percent_removed)) %>%
@@ -66,26 +62,139 @@ percent_removed <- raw_data %>%
 ## Analyze RTs for frequency unbiased items
[…]

### 2018-12-07 data-analysis/combineData.R

@@ -1,206 +1,0 @@
-pack<-c("dplyr","ggplot2","pander","knitr","xtable","car","Crump","lsr","afex","stringr","tidyr")
-lapply(pack, require, character.only = TRUE)
-
-
-## LOAD DATA FROM E1 and E2 ###
-load("EAll.Rda")
-load("EAllq.Rda")
-
-### ANALYZE QUIZ DATA ###
-quizAnalysis <-tbl_df(data)
-quizAnalysis <- quizAnalysis %>%
-  filter(trialColor == "quiz")
-
-quizAnalysis <- quizAnalysis[,-10:-17]
-colnames(quizAnalysis)<- c("subID","trial","trialType","correctResponse","time1","time2","response","ACC","unknown","Subject","block","subBlock","subBlockB","newACC","preCon","preTrialProp", "order")
-
-quizAnalysis <- quizAnalysis %>%
-  filter(is.na(response) == FALSE)
-
-quizAnalysis$response<-as.numeric(as.character(quizAnalysis$response))
-quizAnalysis$correctResponse<-as.numeric(as.character(quizAnalysis$correctResponse))
-quizAnalysis$ACC<-as.numeric(as.character(quizAnalysis$ACC))
-quizAnalysis$fineACC<-abs(quizAnalysis$response - quizAnalysis$correctResponse)
-quizAnalysis$Exp <- NA
-quizAnalysis[quizAnalysis$Subject < 51,]$Exp <- "E1"
-quizAnalysis[quizAnalysis$Subject > 51,]$Exp <- "E2"
-
-
-quiz.Sum<- quizAnalysis %>%
-  group_by(Subject) %>%
-  filter(!is.na(fineACC),Subject != 4, Subject != 29) %>%
-  summarise(ACC = mean(ACC), fineACC = mean(fineACC)) 
-
-quiz.Sum
-### END QUIZ DATA ###
-
-### GET QUESTIONNAIRE DATA ###
-questData$expTime<-((as.numeric(as.character(questData$completeTime)) -as.numeric(as.character(questData$startTime)))/1000)/60
-questData$Exp<-NA
-questData[questData$subnum < 51,]$Exp <- "E1"
-questData[questData$subnum > 51,]$Exp <- "E2"
-questData <- questData %>%
[…]

### 2018-12-09 manuscript.Rmd
first draft

--- 2018-12-07 v1-task-relevance-cspc.Rmd
@@
 keywords          : "Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance"
-wordcount         : "5946"
+wordcount         : "4402"
 
@@
 
+#output: 
+#  word_document
+
 output:
- papaja::apa6_pdf
+ # papaja::apa6_word: default
+  papaja::apa6_pdf: default
+  #redoc::rdocx_reversible
+
+knit: (function(inputFile, encoding) {
+  rmarkdown::render(inputFile, encoding = encoding,
+  output_format = "all") })
+
+header-includes:
+  - \usepackage{float}
+  - \usepackage{booktabs}
+  - \usepackage{longtable}
+  - \usepackage{array}
+  - \usepackage{multirow}
+  - \usepackage[table]{xcolor}
+  - \usepackage{wrapfig}
+  - \usepackage{colortbl}
+  - \usepackage{pdflscape}
+  - \usepackage{tabu}
+  - \usepackage{threeparttable}
+  - \usepackage{threeparttablex}
+  - \usepackage[normalem]{ulem}
+  - \usepackage{makecell}
+  - \usepackage{setspace}\singlespacing 
+  - \newenvironment{zeroindent}
+     {\par\setlength{\parindent}{0pt}}
+     {\par}  
+  - \setlength{\parskip}{0.25cm plus4mm minus3mm}
+
 ---
-
 ```{r setup, include=FALSE, eval=TRUE,echo=FALSE}
-# options(htmltools.dir.version = FALSE)
-knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache = FALSE)
-
 library("dplyr")
@@
 library("papaja")
+library("magrittr")
+library("kableExtra")
+
+#As of 2018/12/07 apa_print() requires development version of Papaja
+#devtools::install_github("crsh/papaja")
+library(papaja)
 ```
 
-#  Introduction
-
-Selective attention processes are commonly investigated using interference paradigms such as the Stroop [-@stroop_studies_1935] and flanker [@eriksen_effects_1974] tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor.
+Selective attention is commonly investigated using interference paradigms such as the Stroop [-@stroop_studies_1935] and flanker [@eriksen_effects_1974] tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor.
 Performance is typically better on congruent versus incongruent trials and the difference-the congruency effect-taken as an index of attentional priorities.
@@
 The first experiment failed to find evidence for context-specificity, whereas the second did.
-Although not testing task-relevance directly, [-@canadas_social_2013]) found similar effects.
+Although not testing task-relevance directly, @canadas_social_2013] found similar effects.
 In this study they used images of male and female faces as context cues in a flanker task.
@@
 
-Some prior suggests that the task-relevance of contextual information is important for establishing new associations between context cues and attentional priorities.
+Prior work suggests that the task-relevance of contextual information is important for establishing new associations between context cues and attentional priorities.
 Simply put, CSPC effects emerge when context cues are somehow made relevant to the task, but do not when made irrelevant [@canadas_social_2013; @crump_context-specific_2006; @crump_context-specific_2008].
@@
 On other hand, task-relevance might not only dictate how associations are formed, but also whether learned associations are used.
-In this case, we would expect that there will be smaller congruency effects when the high-conflict context dimension is made task-relevant as compared to when the low-conflict context dimension is made task-relevant.
+In this case, we would expect smaller congruency effects when the high-conflict context dimension is made task-relevant as compared to when the low-conflict context dimension is made task-relevant.
 This would demonstrate that participants were able to ignore a previously learned association and adopt a new context-specific control strategy.
@@
 Therefore, we included three conditions that differed only in the kinds of stimuli used to create context cues.
-In one condition we used face images where context dimensions were defined by social categories, similar to Cañadas et al.,  [-@canadas_social_2013].
+In one condition we used face images where context dimensions were defined by social categories, similar to @canadas_social_2013.
 However, they found that social categorization occurred spontaneously and it was unclear what impact that would have on the current results.
 Therefore, we included another condition that used images of simple objects where context dimensions were defined by object features.
-Finally, Cañadas et al.[-@canadas_social_2013] also found that context effects generalized to novel face images.
+Finally, @canadas_social_2013 also found that context effects generalized to novel face images.
 In our third condition we used non-repeating face exemplars to examine whether any task-relevance effects would also generalize in our design or if learning would be image-specific.
@@
 
-(ref:figure1)
-Illustration of the stimuli and trial construction.
+(ref:figure1) Illustration of the stimuli and trial construction.
 Figure 1A shows the feature dimensions for each of the conditions.
@@
 
-```{r figure1, echo=FALSE, fig.cap="(ref:figure1)", fig.width=6.7,fig.height=4.51}
+```{r figure1, echo=FALSE, fig.width=6.7,fig.height=4.51, fig.cap='(ref:figure1)'}
 knitr::include_graphics("images/Task.jpg")
@@
 Participants were included in the study if they completed all trials.
-We posted 150 HITs and 145 participants completed all trials.
+We posted 150 HITs and 144 participants completed all trials.
 
@@
 
-# Results
-
 ```{r analysis}
 source("data-analysis/analysis.R")
-
 ```
 
-(ref:figure2)
-Results from experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent).
+(ref:figure2) Results from experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent).
 
-```{r figure2, echo=FALSE, fig.cap="(ref:figure2)", fig.width=6.875, fig.height= 4}
+```{r figure2, echo=FALSE,fig.width=6.875, fig.height= 4, fig.cap='(ref:figure2)'}
 figure2
 ```
+
+# Results
 
@@
 
-Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, `r RT_ANOVA$Task_Relevant_Context_Congruency`, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, `r RT_ANOVA$Condition_Task_Relevant_Context_Congruency`.
+Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA$Task_Relevant_Context_Congruency`, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, `r ACC_ANOVA$Condition_Task_Relevant_Context_Congruency`.
 Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.
+
+\begingroup
+\setlength{\parindent}{0in}
+\vspace{2.5mm}
+\textbf{Table 1. \\ \textit{Reaction times and error rates from Experiment 1.}}
+
+![ ](images/table1.pdf) 
+\endgroup
 
@@
 
-The aim of the current study was to investigate whether task-relevance plays a role in the contextual recruitment of selective attention.
+The aim of the current study was to determine whether task-relevance plays a role in the contextual recruitment of selective attention.
 Specifically, we tested whether manipulating the relative task-relevance of context cues could cause participants to ignore a previously learned context-association and apply a new association.
-We created a frequency unbiased context cue that shared features with two frequency biased contexts and included a feature-counting task to manipulate the task-relevance of context dimensions across two blocks of trials.
+We created a frequency unbiased context cue that shared features with two frequency biased contexts and used a feature-counting task to manipulate the task-relevance of context dimensions across two blocks of trials.
 Critically, halfway through the experiment participants received new instructions changing the task-relevant feature from one frequency biased cue to the other.
@@
 In sum, our results provide new evidence that changes in task-relevance can update the contextual recruitment of selective attention in a CSPC flanker task.
-Importantly, we show that making one feature task-relevant produced a CSPC effect, even in the presence of a competing contextual cue.
-Moreover, changing the task-relevant context-cue midway through the experiment was accompanied by predictable changes in the congruency effects.
-This effect was found to be generalizable across two different kinds of stimuli and occurred even when using non-repeating images.
-These results implicate an important role for task-relevance in producing context-dependency and are consistent with memory-based accounts of CSPC phenomena.
+We demonstrated that making one context cue task-relevant produced a CSPC effect, even in the presence of a competing contextual cue.
+More important however, we found that changing the task-relevance of the contextual cues across blocks of trials was accompanied by predictable changes in the congruency effects.
+These effects were found to be generalizable across two different kinds of stimuli and occurred even when using non-repeating images, and implicate an important role for task-relevance in producing context-dependency and are consistent with memory-based accounts of CSPC phenomena.
 
@@
 \endgroup
+
+\newpage
+
+```{r tableLatex}
+#if (knitr::opts_knit$get("rmarkdown.pandoc.to")== "latex"){
+#source("data-analysis/table1.R")
+#latexTable1
+#}
+```

### 2018-12-09 manuscript.tex
first draft

--- 2018-12-07 v1-task-relevance-cspc.tex
@@
             pdfauthor={Nicholaus P. Brosowsky~\& Matthew J. C. Crump},
-            pdfkeywords={Attention, Memory, Cognitive Control, Conflict Adaptation,
-Context-specific, Task Relevance},
+            pdfkeywords={Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance},
             pdfborder={0 0 0},
@@
 
-  \title{Contextual recruitment of selective attention can be updated via changes
-in task-relevance}
-    \author{Nicholaus P. Brosowsky\textsuperscript{1}~\& Matthew J. C.
-Crump\textsuperscript{2}}
+  \title{Contextual recruitment of selective attention can be updated via changes in task-relevance}
+    \author{Nicholaus P. Brosowsky\textsuperscript{1}~\& Matthew J. C. Crump\textsuperscript{2}}
     \date{}
@@
 \textsuperscript{1} The Graduate Center of the City University of New York\\\textsuperscript{2} Brooklyn College of the City University of New York}
-\keywords{Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance\newline\indent Word count: 5946}
+\keywords{Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance\newline\indent Word count: 4402}
 \usepackage{csquotes}
@@
 \newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+\usepackage{float}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage[table]{xcolor}
+\usepackage{wrapfig}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{setspace}\singlespacing
+\newenvironment{zeroindent} {\par\setlength{\parindent}{0pt}} {\par}
+\setlength{\parskip}{0.25cm plus4mm minus3mm}
 
@@
 
-Correspondence concerning this article should be addressed to Nicholaus
-P. Brosowsky, The Graduate Center, CUNY, 365 5th Ave, New York, NY
-10016. E-mail:
-\href{mailto:nbrosowsky@gradcenter.cuny.edu}{\nolinkurl{nbrosowsky@gradcenter.cuny.edu}}}
+Correspondence concerning this article should be addressed to Nicholaus P.
+Brosowsky, The Graduate Center, CUNY, 365 5th Ave, New York, NY 10016.
+E-mail: \href{mailto:nbrosowsky@gradcenter.cuny.edu}{\nolinkurl{nbrosowsky@gradcenter.cuny.edu}}}
 
 \abstract{
-Evidence across a wide variety of attention paradigms shows that
-environmental cues can trigger adjustments to ongoing priorities for
-attending to relevant and irrelevant information. This context-specific
-control over attention suggests that cognitive control can be both
-automatic and flexible. For instance, in selective attention tasks,
-congruency effects are larger for items that appear in a context
-associated with infrequent conflict than in a context associated with
-frequent conflict. Since the to-be-presented context cannot be predicted
-or prepared for in advance, attention is assumed to be rapidly updated
-on-the-fly, triggered by the currently presented context.
-Context-specific control exemplifies how learning and memory processes
-can influence attention to enable cognitive flexibility. However, what
-determines the use of previously learned associations still remains
-unclear. In the current study, we examined whether task-relevance would
-influence the learning and use of context cues in a flanker task. Using
-a secondary counting task, context dimensions associated with differing
-levels of conflict were made task-relevant or -irrelevant across the
-experiment. In short, we found that making new contextual information
-task-relevant caused participants to ignore a previously learned
-context-attention association and adopt a new context-specific control
-strategy; all without changing the experimental stimuli. This result
-suggests that task-relevance is a key determinant of context-specific
-control.
+Evidence across a wide variety of attention paradigms shows that environmental cues can trigger adjustments to ongoing priorities for attending to relevant and irrelevant information.
+This context-specific control over attention suggests that cognitive control can be both automatic and flexible.
+For instance, in selective attention tasks, congruency effects are larger for items that appear in a context associated with infrequent conflict than in a context associated with frequent conflict.
+Since the to-be-presented context cannot be predicted or prepared for in advance, attention is assumed to be rapidly updated on-the-fly, triggered by the currently presented context.
+Context-specific control exemplifies how learning and memory processes can influence attention to enable cognitive flexibility.
+However, what determines the use of previously learned associations still remains unclear.
+In the current study, we examined whether task-relevance would influence the learning and use of context cues in a flanker task.
+Using a secondary counting task, context dimensions associated with differing levels of conflict were made task-relevant or -irrelevant across the experiment.
+In short, we found that making new contextual information task-relevant caused participants to ignore a previously learned context-attention association and adopt a new context-specific control strategy; all without changing the experimental stimuli.
+This result suggests that task-relevance is a key determinant of context-specific control.
 
@@
 
-\section{Introduction}\label{introduction}
+Selective attention is commonly investigated using interference paradigms such as the Stroop (1935) and flanker (Eriksen \& Eriksen, 1974) tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor.
+Performance is typically better on congruent versus incongruent trials and the difference-the congruency effect-taken as an index of attentional priorities.
+Large congruency effects are thought to reflect ineffective filtering of the distracting stimuli whereas small congruency effects are thought to reflect effective filtering.
+By probing factors that systematically alter congruency effects, we can then make inferences about processes that control attentional filtering.
+For example, manipulating the frequency of conflict via the proportion of congruent versus incongruent trials has shown to influence the size of the congruency effect.
+Typically, a high proportion congruent experiment produces large congruency effects, whereas a low proportion congruent experiment produces small congruency effects (Logan \& Zbrodoff, 1979; Lowe \& Mitterer, 1982; West \& Baylis, 1998).
+This result is usually explained as strategic control, where participants increase attentional control under high-conflict demands and relax attentional control under low-conflict demands (Logan, 1980; Logan \& Zbrodoff, 1979; Logan, Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer, 1982).
+Recent work however, has demonstrated that attentional control is not only adjusted by top-down regulation, but can also be triggered automatically by environmental cues (Brosowsky \& Crump, 2018; Bugg \& Crump, 2012; Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \& Egner, 2012; Mayr \& Bryck, 2007).
 
-Selective attention processes are commonly investigated using
-interference paradigms such as the Stroop (1935) and flanker (B. A.
-Eriksen \& Eriksen, 1974) tasks, where participants identify a target
-while ignoring a response-congruent or -incongruent distractor.
-Performance is typically better on congruent versus incongruent trials
-and the difference-the congruency effect-taken as an index of
-attentional priorities. Large congruency effects are thought to reflect
-ineffective filtering of the distracting stimuli whereas small
-congruency effects are thought to reflect effective filtering. By
-probing factors that systematically alter congruency effects, we can
-then make inferences about processes that control attentional filtering.
-For example, manipulating the frequency of conflict via the proportion
-of congruent versus incongruent trials has shown to influence the size
-of the congruency effect. Typically, a high proportion congruent
-experiment produces large congruency effects, whereas a low proportion
-congruent experiment produces small congruency effects (Logan \&
-Zbrodoff, 1979; Lowe \& Mitterer, 1982; West \& Baylis, 1998). This
-result is usually explained as strategic control, where participants
-increase attentional control under high-conflict demands and relax
-attentional control under low-conflict demands (Logan, 1980; Logan \&
-Zbrodoff, 1979; Logan, Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer,
-1982). Recent work however, has demonstrated that attentional control is
-not only adjusted by top-down regulation, but can also be triggered
-automatically by environmental cues (Brosowsky \& Crump, 2018; J. Bugg
-\& Crump, 2012; Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \&
-Egner, 2012; Mayr \& Bryck, 2007).
+For example, Crump, Gong, and Milliken (Crump, Gong, \& Milliken, 2006; see also, Corballis \& Gratton, 2003) presented Stroop stimuli in one of two randomly chosen locations and manipulated the frequency of conflict associated with each location.
+One location was associated with a high frequency of conflict (25\% congruent trials) and the other with a low frequency of conflict (75\% congruent trials).
+Overall, the proportion of congruent trials was 50\% and randomized such that the upcoming location could not be predicted.
+Even so, congruency effects were shown to be smaller for trials where the stimulus appeared in the high conflict location as compared to the low conflict location.
+This effect, known now as the context-specific proportion congruent effect (CSPC), has now been replicated in a number of different selective attention paradigms (e.g., Alards-Tomalin, Brosowsky, \& Mondor, 2017; Blais, Harris, Sinanian, \& Bunge, 2015; Bugg, 2014; Crump, 2016; Crump, Milliken, Leboe-McGowan, Leboe-McGowan, \& Gao, 2018; Fischer, Gottschalk, \& Dreisbach, 2014; Hübner \& Mishra, 2016).
 
-For example, Crump, Gong, and Milliken (see also, Corballis \& Gratton,
-2003; Crump, Gong, \& Milliken, 2006) presented Stroop stimuli in one of
-two randomly chosen locations and manipulated the frequency of conflict
-associated with each location. One location was associated with a high
-frequency of conflict (25\% congruent trials) and the other with a low
-frequency of conflict (75\% congruent trials). Overall, the proportion
-of congruent trials was 50\% and randomized such that the upcoming
-location could not be predicted. Even so, congruency effects were shown
-to be smaller for trials where the stimulus appeared in the high
-conflict location as compared to the low conflict location. This effect,
-known now as the context-specific proportion congruent effect (CSPC),
-has now been replicated in a number of different selective attention
-paradigms (e.g., Alards-Tomalin, Brosowsky, \& Mondor, 2017; Blais,
-Harris, Sinanian, \& Bunge, 2015; J. Bugg, 2014; Crump, 2016; Crump,
-Milliken, Leboe-McGowan, Leboe-McGowan, \& Gao, 2018; Fischer,
-Gottschalk, \& Dreisbach, 2014; Hübner \& Mishra, 2016).
+Critical evidence however, that CSPC effects reflect context-specific control rather than other non-control learning processes (e.g., Schmidt \& Besner, 2008), comes from work showing that CSPC effects can transfer to frequency unbiased items (Brosowsky \& Crump, 2016; Crump \& Milliken, 2009; Weidler \& Bugg, 2016; Weidler, Dey, \& Bugg, 2018; though, see Hutcheon \& Spieler, 2017).
+Crump and Milliken (2009), for example, divided Stroop items into two mutually exclusive sets (e.g., RED/GREEN and BLUE/YELLOW).
+One set was defined as the frequency biased set, and presented with 75\% congruency in one location, and 25\% congruency in the other.
+The second set however, was presented with 50\% congruency in both locations.
+Nevertheless, they found smaller congruency effects for unbiased items presented in the high conflict location as compared to the low conflict location.
 
-Critical evidence however, that CSPC effects reflect context-specific
-control rather than other non-control learning processes (e.g., Schmidt
-\& Besner, 2008), comes from work showing that CSPC effects can transfer
-to frequency unbiased items (Brosowsky \& Crump, 2016; Crump \&
-Milliken, 2009; though, see Hutcheon \& Spieler, 2017; Weidler \& Bugg,
-2016; Weidler, Dey, \& Bugg, 2018). Crump and Milliken (2009), for
-example, divided Stroop items into two mutually exclusive sets (e.g.,
-RED/GREEN and BLUE/YELLOW). One set was defined as the frequency biased
-set, and presented with 75\% congruency in one location, and 25\%
-congruency in the other. The second set however, was presented with 50\%
-congruency in both locations. Nevertheless, they found smaller
-congruency effects for unbiased items presented in the high conflict
-location as compared to the low conflict location.
+One explanation for CSPC effects is that the repeated application of attentional priorities in a particular context creates an associative link in episodic memory between the attentional control procedures and the contextual information (Abrahamse, Braem, Notebaert, \& Verguts, 2016; Brosowsky \& Crump, 2018; Crump, 2016; Egner, 2014).
+Once the associative link is established, processing the context is assumed to trigger the retrieval of previous experiences, automatically reinstating the associated attentional priorities.
+Although this explanation seems plausible, it remains largely unclear how such associations are established and perhaps more importantly, it remains unclear what determines which learned associations will be used to guide attention at any given moment.
 
-One explanation for CSPC effects is that the repeated application of
-attentional priorities in a particular context creates an associative
-link in episodic memory between the attentional control procedures and
-the contextual information (Abrahamse, Braem, Notebaert, \& Verguts,
-2016; Brosowsky \& Crump, 2018; Crump, 2016; Egner, 2014). Once the
-associative link is established, processing the context is assumed to
-trigger the retrieval of previous experiences, automatically reinstating
-the associated attentional priorities. Although this explanation seems
-plausible, it remains largely unclear how such associations are
-established and perhaps more importantly, it remains unclear what
-determines which learned associations will be used to guide attention at
-any given moment.
+The importance of the latter issue becomes increasingly clear if we speculate about context-specificity in more complex, real-world environments.
+Consider myself, right now, writing this article in a coffee shop.
+The coffee shop is a complex environment that contains a multitude of contextual cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which I have had many different experiences applying attentional control.
+Although my laptop might cue attentional processing helpful for finishing this article, other features of the coffee shop might cue other, unhelpful attentional processing related to other experiences like socializing and people-watching.
+This is all to say that our environments, and experiences within them, afford many different associative relationships between cognitive processing and environmental cues.
+What then determines which associative relationships will be used to guide attention (or even if such associative relationships are used at all)?
 
-The importance of the latter issue becomes increasingly clear if we
-speculate about context-specificity in more complex, real-world
-environments. Consider myself, right now, writing this article in a
-coffee shop. The coffee shop is a complex environment that contains a
-multitude of contextual cues (e.g., pictures on the wall, chairs,
-coffee, laptop), each of which I have had many different experiences
-applying attentional control. Although my laptop might cue attentional
-processing helpful for finishing this article, other features of the
-coffee shop might cue other, unhelpful attentional processing related to
-other experiences like socializing and people-watching. This is all to
-say that our environments, and experiences within them, afford many
-different associative relationships between cognitive processing and
-environmental cues. What then determines which associative relationships
-will be used to guide attention (or even if such associative
-relationships are used at all)?
+Task-relevance might be one factor that is important for establishing and using context-attention associations.
+This proposal might seem counter-intuitive as it is typically assumed that the context, within selective attention tasks at least, is completely irrelevant to the task.
+In fact, referring to such stimulus dimensions as the \enquote{context} carries with it an implication that the feature is background information, irrelevant to the task-at-hand, and should be ignored by the participant.
+A closer look at CSPC designs however, suggests that the context cues may not be as irrelevant as implied.
+For example, the most commonly used context cue is location (Brosowsky \& Crump, 2016; Corballis \& Gratton, 2003; Crump, 2016; Crump et al., 2006; Crump, Vaquero, \& Milliken, 2008; Weidler \& Bugg, 2016; Weidler et al., 2018).
+Although in some sense, the location is irrelevant for identifying the color of a word, it seems disingenuous to consider it completely task-irrelevant.
+In order to identify the target, the participant must first identify and orient to its location on the screen.
+In this is sense, it is relevant to their ability to complete the task and furthermore, location information may receive priority during encoding (Logan, 1998; Mayr, 1996).
+Similar arguments could be made about other context features that are inherent to processing the target stimulus, like font-type (Bugg, Jacoby, \& Toth, 2008) and color (Vietze \& Wendt, 2009).
 
-Task-relevance might be one factor that is important for establishing
-and using context-attention associations. This proposal might seem
-counter-intuitive as it is typically assumed that the context, within
-selective attention tasks at least, is completely irrelevant to the
-task. In fact, referring to such stimulus dimensions as the
-\enquote{context} carries with it an implication that the feature is
-background information, irrelevant to the task-at-hand, and should be
-ignored by the participant. A closer look at CSPC designs however,
-suggests that the context cues may not be as irrelevant as implied. For
-example, the most commonly used context cue is location (Brosowsky \&
-Crump, 2016; Corballis \& Gratton, 2003; Crump, 2016; Crump et al.,
-2006; Crump, Vaquero, \& Milliken, 2008; Weidler \& Bugg, 2016; Weidler
-et al., 2018). Although in some sense, the location is irrelevant for
-identifying the color of a word, it seems disingenuous to consider it
-completely task-irrelevant. In order to identify the target, the
-participant must first identify and orient to its location on the
-screen. In this is sense, it is relevant to their ability to complete
-the task and furthermore, location information may receive priority
-during encoding (Logan, 1998; Mayr, 1996). Similar arguments could be
-made about other context features that are inherent to processing the
-target stimulus, like font-type (J. Bugg, Jacoby, \& Toth, 2008) and
-color (Vietze \& Wendt, 2009).
+To date, we are aware of only one study that has looked at task-relevance within the CSPC literature.
+Crump, Vaquero, \& Milliken (2008) used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe.
+Critically, they used the shape of the color patch probe, either a square or a circle, as the contextual dimension; one associated with a high frequency of conflict, the other with a low frequency.
+In one experiment participants were made aware of the shape-proportion contingencies but given no additional instructions.
+In the second, participants were given a secondary task to count the number of trials that contained a square.
+The first experiment failed to find evidence for context-specificity, whereas the second did.
+Although not testing task-relevance directly, Cañadas, Rodríguez-Bailón, Milliken, and Lupiáñez (2013){]} found similar effects.
+In this study they used images of male and female faces as context cues in a flanker task.
+When given instructions to think of the faces as members of the gender categories they found CSPC effects, but when given instructions to think of the faces as individuals they did not.
+These results suggest that making a context dimension relevant to the on-going task is important for producing CSPC effects.
 
-To date, we are aware of only one study that has looked at
-task-relevance within the CSPC literature. Crump, Vaquero, \& Milliken
-(2008) used a Stroop prime-probe task where the distractor word is
-presented first followed by a color patch probe. Critically, they used
-the shape of the color patch probe, either a square or a circle, as the
-contextual dimension; one associated with a high frequency of conflict,
-the other with a low frequency. In one experiment participants were made
-aware of the shape-proportion contingencies but given no additional
-instructions. In the second, participants were given a secondary task to
-count the number of trials that contained a square. The first experiment
-failed to find evidence for context-specificity, whereas the second did.
-Although not testing task-relevance directly, (2013)) found similar
-effects. In this study they used images of male and female faces as
-context cues in a flanker task. When given instructions to think of the
-faces as members of the gender categories they found CSPC effects, but
-when given instructions to think of the faces as individuals they did
-not. These results suggest that making a context dimension relevant to
-the on-going task is important for producing CSPC effects.
+\hypertarget{the-current-study}{%
+\section{The Current Study}\label{the-current-study}}
 
-\section{The Current Study}\label{the-current-study}
+Prior work suggests that the task-relevance of contextual information is important for establishing new associations between context cues and attentional priorities.
+Simply put, CSPC effects emerge when context cues are somehow made relevant to the task, but do not when made irrelevant (Cañadas et al., 2013; Crump et al., 2006, 2008).
+However, it still remains unclear how task-relevance may or may not inform the use of previously learned associations.
+In the current study, we examined whether manipulating task-relevance would cause participants to ignore a previously learned association and adopt a new context-specific control strategy.
 
-Some prior suggests that the task-relevance of contextual information is
-important for establishing new associations between context cues and
-attentional priorities. Simply put, CSPC effects emerge when context
-cues are somehow made relevant to the task, but do not when made
-irrelevant (Cañadas et al., 2013; Crump et al., 2006, 2008). However, it
-still remains unclear how task-relevance may or may not inform the use
-of previously learned associations. In the current study, we examined
-whether manipulating task-relevance would cause participants to ignore a
-previously learned association and adopt a new context-specific control
-strategy.
+A flanker task was used to measure attentional control in an adapted CSPC design (Crump, Brosowsky, \& Milliken, 2017; Crump \& Milliken, 2009).
+Similar to previous studies, flanker stimuli were presented in contexts associated with differing levels of conflict (0\%, 50\%, or 100\% congruent).
+However, unlike previous CSPC designs where contexts were defined by a single discriminating feature (e.g., upper vs.~lower screen locations), contexts were defined by two feature dimensions (see Figure 1A).
+In one condition, for example, contexts were defined by object identity (hat or chair) and color (blue or green).
+Only three out of the four possible feature combinations were presented, each associated with a different proportion of congruent trials (0\%, 50\%, or 100\% congruent).
+Critically, the frequency unbiased context (50\% congruent) always shared a feature with each of the frequency-biased contexts (0\% and 100\% congruent).
+The frequency biased contexts (0\% and 100\% congruent) however, did not share any features (see Figure 1C for an example).
 
-A flanker task was used to measure attentional control in an adapted
-CSPC design (Crump \& Milliken, 2009; Crump, Brosowsky, \& Milliken,
-2017). Similar to previous studies, flanker stimuli were presented in
-contexts associated with differing levels of conflict (0\%, 50\%, or
-100\% congruent). However, unlike previous CSPC designs where contexts
-were defined by a single discriminating feature (e.g., upper vs.~lower
-screen locations), contexts were defined by two feature dimensions (see
-Figure 1A). In one condition, for example, contexts were defined by
-object identity (hat or chair) and color (blue or green). Only three out
-of the four possible feature combinations were presented, each
-associated with a different proportion of congruent trials (0\%, 50\%,
-or 100\% congruent). Critically, the frequency unbiased context (50\%
-congruent) always shared a feature with each of the frequency-biased
-contexts (0\% and 100\% congruent). The frequency biased contexts (0\%
-and 100\% congruent) however, did not share any features (see Figure 1C
-for an example).
+A secondary counting task was used to manipulate the task-relevance of the context dimensions (Crump \& Milliken, 2009) which critically, switched halfway through the experiment.
+Participants were instructed to keep a running count of one of the overlapping features (e.g., \enquote{count whenever a hat is presented}) which was associated with either a high or low frequency of conflict.
+Halfway through the experiment they received new instructions to count the other overlapping feature (e.g., \enquote{count whenever a green item is presented}).
+Critically, the set of context images remained the same throughout the experiment (see Figure 1C for an example) and the task-relevance of the context dimensions was the only aspect of the experiment that changed from the first to second phases.
 
-A secondary counting task was used to manipulate the task-relevance of
-the context dimensions (Crump \& Milliken, 2009) which critically,
-switched halfway through the experiment. Participants were instructed to
-keep a running count of one of the overlapping features (e.g.,
-\enquote{count whenever a hat is presented}) which was associated with
-either a high or low frequency of conflict. Halfway through the
-experiment they received new instructions to count the other overlapping
-feature (e.g., \enquote{count whenever a green item is presented}).
-Critically, the set of context images remained the same throughout the
-experiment (see Figure 1C for an example) and the task-relevance of the
-context dimensions was the only aspect of the experiment that changed
-from the first to second phases.
+The critical measure of interest is the congruency effect produced in the frequency unbiased context.
+If, on the one hand, task-relevance has no impact on the use of context-attention associations we would expect no differences between the congruency effects when the high-conflict context dimension is made task-relevant or the low-conflict context dimension is made task-relevant.
+This could occur because all three contexts are treated as individual contexts throughout the whole experiment (e.g., Cañadas et al., 2013).
+Or it could occur because associations formed in the first block interfere with learning new associations in the second (e.g., Brosowsky \& Crump, 2016).
+On other hand, task-relevance might not only dictate how associations are formed, but also whether learned associations are used.
+In this case, we would expect smaller congruency effects when the high-conflict context dimension is made task-relevant as compared to when the low-conflict context dimension is made task-relevant.
+This would demonstrate that participants were able to ignore a previously learned association and adopt a new context-specific control strategy.
 
-The critical measure of interest is the congruency effect produced in
-the frequency unbiased context. If, on the one hand, task-relevance has
-no impact on the use of context-attention associations we would expect
-no differences between the congruency effects when the high-conflict
-context dimension is made task-relevant or the low-conflict context
-dimension is made task-relevant. This could occur because all three
-contexts are treated as individual contexts throughout the whole
-experiment (e.g., Cañadas et al., 2013). Or it could occur because
-associations formed in the first block interfere with learning new
-associations in the second (e.g., Brosowsky \& Crump, 2016). On other
-hand, task-relevance might not only dictate how associations are formed,
-but also whether learned associations are used. In this case, we would
-expect that there will be smaller congruency effects when the
-high-conflict context dimension is made task-relevant as compared to
-when the low-conflict context dimension is made task-relevant. This
-would demonstrate that participants were able to ignore a previously
-learned association and adopt a new context-specific control strategy.
+A secondary goal was to conceptually replicate previous findings and test the generalizability of any task-relevance effects.
+Therefore, we included three conditions that differed only in the kinds of stimuli used to create context cues.
+In one condition we used face images where context dimensions were defined by social categories, similar to Cañadas et al.
+(2013).
+However, they found that social categorization occurred spontaneously and it was unclear what impact that would have on the current results.
+Therefore, we included another condition that used images of simple objects where context dimensions were defined by object features.
+Finally, Cañadas et al.
+(2013) also found that context effects generalized to novel face images.
+In our third condition we used non-repeating face exemplars to examine whether any task-relevance effects would also generalize in our design or if learning would be image-specific.
 
-A secondary goal was to conceptually replicate previous findings and
-test the generalizability of any task-relevance effects. Therefore, we
-included three conditions that differed only in the kinds of stimuli
-used to create context cues. In one condition we used face images where
-context dimensions were defined by social categories, similar to Cañadas
-et al., (2013). However, they found that social categorization occurred
-spontaneously and it was unclear what impact that would have on the
-current results. Therefore, we included another condition that used
-images of simple objects where context dimensions were defined by object
-features. Finally, Cañadas et al.(2013) also found that context effects
-generalized to novel face images. In our third condition we used
-non-repeating face exemplars to examine whether any task-relevance
-effects would also generalize in our design or if learning would be
-image-specific.
-
-\section{Methods}\label{methods}
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
@@
 \includegraphics{images/Task.jpg}
-\caption{\label{fig:figure1}Illustration of the stimuli and trial construction. Figure
-1A shows the feature dimensions for each of the conditions. Figure 1B
-shows an example trial stimulus containing both the context and flanker
-images. Figure 1C shows an example of how feature dimensions could have
-been assigned to each proportion congruency (PC) condition, and an
-example of the secondary task assignments. The secondary task order, as
-well as the feature and congruency assignments were all randomized for
-each participant.}
+\caption{\label{fig:figure1}Illustration of the stimuli and trial construction.
+Figure 1A shows the feature dimensions for each of the conditions.
+Figure 1B shows an example trial stimulus containing both the context and flanker images.
+Figure 1C shows an example of how feature dimensions could have been assigned to each proportion congruency (PC) condition, and an example of the secondary task assignments.
+The secondary task order, as well as the feature and congruency assignments were all randomized for each participant.}
 \end{figure}
 
-\subsection{Participants}\label{participants}
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
-All participants were recruited from Amazon Mechanical Turk (AMT) and
-compensated \$2.00 for participating. The amount compensated was
-calculated by estimating the maximum amount of time required to complete
-each experiment and multiplying by \$6.00 per hour. For each experiment
-the number of HITs (Human intelligence tasks, an Amazon term for a
-work-unit) refers to the number of participants who initiated the study.
-Participants were included in the study if they completed all trials. We
-posted 150 HITs and 145 participants completed all trials.
+All participants were recruited from Amazon Mechanical Turk (AMT) and compensated \$2.00 for participating.
+The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by \$6.00 per hour.
+For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study.
+Participants were included in the study if they completed all trials.
+We posted 150 HITs and 144 participants completed all trials.
 
-\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli}
+\hypertarget{apparatus-stimuli}{%
+\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli}}
 
-The experiments were programmed using JavaScript, CSS and HTML. The
-program allowed participants to complete task only if they were running
-Safari, Google Chrome, or Firefox web browsers. Flanker stimuli
-consisted of images of five arrows pointed left or right presented at
-250 x 50 pixels (each arrow was 50 x 50 pixels). Context stimuli were
-constructed using images selected from Brady, Konkle, Gill, Oliva, and
-Alvarez (2013) color-rotated to blue and green, and face images from the
-Chicago Face Database (Ma, Correll, \& Wittenbrink, 2015), supplemented
-with the NimStim Set of Facial Expressions (Tottenham et al., 2009). The
-object images were displayed at 250 x 250 pixels, while the face images
-were displayed at 250 x 313 pixels. The experiment ran as a pop-up
-window that filled the entire screen. The background was white, and
-stimuli were presented in the center of the screen.
+The experiments were programmed using JavaScript, CSS and HTML.
+The program allowed participants to complete task only if they were running Safari, Google Chrome, or Firefox web browsers.
+Flanker stimuli consisted of images of five arrows pointed left or right presented at 250 x 50 pixels (each arrow was 50 x 50 pixels).
+Context stimuli were constructed using images selected from Brady, Konkle, Gill, Oliva, and Alvarez (2013) color-rotated to blue and green, and face images from the Chicago Face Database (Ma, Correll, \& Wittenbrink, 2015), supplemented with the NimStim Set of Facial Expressions (Tottenham et al., 2009).
+The object images were displayed at 250 x 250 pixels, while the face images were displayed at 250 x 313 pixels.
+The experiment ran as a pop-up window that filled the entire screen.
+The background was white, and stimuli were presented in the center of the screen.
 
-Design. Experiment 1 used a 2x2x3 mixed design with task-relevant
-context (0\% and 100\%) and unbiased-item congruency (congruent and
-incongruent) as within-subject factors, and context-type (object,
-social, and social/non-repeating) as the between-subjects factor. All
-three conditions were constructed using the same general method. The
-experiment was divided into two phases. Each phase consisted of 144
-flanker trials (48 trials per context), and 13 count response trials for
-a total of 314 trials. On the count response trials, participants
-indicated how many trials they had counted until that point. The count
-response trials occurred once for every 12 flanker trials and was
-randomly inserted between trial 6 and 12 of each 12-trial block. Each
-phase ended with one additional count response trial.
+Design.
+Experiment 1 used a 2x2x3 mixed design with task-relevant context (0\% and 100\%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+All three conditions were constructed using the same general method.
+The experiment was divided into two phases.
+Each phase consisted of 144 flanker trials (48 trials per context), and 13 count response trials for a total of 314 trials.
+On the count response trials, participants indicated how many trials they had counted until that point.
+The count response trials occurred once for every 12 flanker trials and was randomly inserted between trial 6 and 12 of each 12-trial block.
+Each phase ended with one additional count response trial.
 
-On every flanker trial, participants were presented with flanker stimuli
-paired with one of three contexts. Each context was associated with a
-different proportion congruency such that two cues were associated with
-a biased frequency (0\% and 100\% proportion congruency), while one was
-associated with an unbiased frequency (50\% proportion congruency). The
-feature dimensions and corresponding context images assigned to each of
-the biased and unbiased item sets were randomly determined for each
-participant. However, context images used for the frequency biased
-trials never shared features, while the frequency unbiased context image
-always shared a feature with each of the frequency biased context images
-(see Figure 1). Additionally, the feature assignments remained the same
-throughout phases 1 and 2, and critically, the only change to the task
-was which feature the participant was instructed to count (see Figure 1C
-for an example).
+On every flanker trial, participants were presented with flanker stimuli paired with one of three contexts.
+Each context was associated with a different proportion congruency such that two cues were associated with a biased frequency (0\% and 100\% proportion congruency), while one was associated with an unbiased frequency (50\% proportion congruency).
+The feature dimensions and corresponding context images assigned to each of the biased and unbiased item sets were randomly determined for each participant.
+However, context images used for the frequency biased trials never shared features, while the frequency unbiased context image always shared a feature with each of the frequency biased context images (see Figure 1).
+Additionally, the feature assignments remained the same throughout phases 1 and 2, and critically, the only change to the task was which feature the participant was instructed to count (see Figure 1C for an example).
 
 All critical aspects of the task were randomized between participants.
-This includes the three chosen context images, the features assigned to
-proportion levels, the features assigned to each counting condition, the
-secondary task order, and the order of trials.
+This includes the three chosen context images, the features assigned to proportion levels, the features assigned to each counting condition, the secondary task order, and the order of trials.
 
-\subsection{Procedure}\label{procedure}
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
-All participants were AMT workers who found the experiment using the AMT
-system. The participant recruitment procedure and tasks were approved by
-the Brooklyn College Institutional Review Board. Each participant read a
-short description of the task and gave consent by pressing a button
-acknowledging they had read the displayed consent form. Participants
-then completed a short demographic survey, and proceeded to the main
-task, which was displayed as a pop-up window. Participants were
-instructed to identify the direction of the center arrow on each trial
-as quickly and accurately as possible by pressing \enquote{z} if the
-arrow pointed left, and \enquote{m} if the arrow pointed right.
-Additionally, they were instructed to silently keep count of the number
-of trials that contained a feature. In the object context condition,
-they were asked to count trials that contained a certain color (blue or
-green) or object-identity (hat or chair) and in the social context
-conditions they were asked to count the number of trials that contained
-appeared a certain gender (male or female) or race (black or white).
-Periodically throughout the experiment, participants were asked to
-report how many trials they had counted until that point and to restart
-their count from 0. Halfway through the experiment participants received
-new instructions about which feature to count (see Figure 1C). Each
-trial began with a blank inter-stimulus interval (ISI) of 400 ms,
-followed by a fixation cross presented in the center of the screen for
-200 ms, then a second blank ISI of 400 ms. Next, the flanker and context
-stimuli appeared in the center of screen (the flanker above the context
-image; see Figure 1B) and remained on screen until a response was made.
-Following a response, accuracy feedback was presented for 1000 ms. A
-response automatically triggered the next trial. Halfway through the
-experiment (157 trials), participants received new instructions about
-which feature to count and to press the button on-screen when they were
-ready to continue.
-
-\section{Results}\label{results}
+All participants were AMT workers who found the experiment using the AMT system.
+The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board.
+Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form.
+Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window.
+Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing \enquote{z} if the arrow pointed left, and \enquote{m} if the arrow pointed right.
+Additionally, they were instructed to silently keep count of the number of trials that contained a feature.
+In the object context condition, they were asked to count trials that contained a certain color (blue or green) or object-identity (hat or chair) and in the social context conditions they were asked to count the number of trials that contained appeared a certain gender (male or female) or race (black or white).
+Periodically throughout the experiment, participants were asked to report how many trials they had counted until that point and to restart their count from 0.
+Halfway through the experiment participants received new instructions about which feature to count (see Figure 1C).
+Each trial began with a blank inter-stimulus interval (ISI) of 400 ms, followed by a fixation cross presented in the center of the screen for 200 ms, then a second blank ISI of 400 ms.
+Next, the flanker and context stimuli appeared in the center of screen (the flanker above the context image; see Figure 1B) and remained on screen until a response was made.
+Following a response, accuracy feedback was presented for 1000 ms.
+A response automatically triggered the next trial.
+Halfway through the experiment (157 trials), participants received new instructions about which feature to count and to press the button on-screen when they were ready to continue.
 
@@
 \centering
-\includegraphics{v1-task-relevance-cspc_files/figure-latex/figure2-1.pdf}
-\caption{\label{fig:figure2}Results from experiment 1 showing congruency effects
-(incongruent - congruent) for frequency unbiased items in reaction times
-(left) and error rates (right) as a function of the task-relevant
-context (100\% proportion congruent versus 0\% proportion congruent).}
+\includegraphics{manuscript_files/figure-latex/figure2-1.pdf}
+\caption{\label{fig:figure2}Results from experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent).}
 \end{figure}
 
-Participants with mean error rates greater than 25\% were excluded from
-the analyses, eliminating 13 participants. For all remaining
-participants, the correct RTs from frequency unbiased trials in each
-condition were submitted to an outlier removal procedure. The
-non-recursive Van Selst and Jolicoeur outlier removal procedure was
-applied after removing response times greater than 3000 ms (Van Selst \&
-Jolicoeur, 1994). This procedure removed 3.39\% of the total
-observations.
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
-The primary question of interest was whether the task-relevance of
-context features associated with different levels of conflict would
-influence the size of the congruency effect for frequency unbiased items
-(see Table 1). To that end, mean correct RTs and mean error rates from
-frequency unbiased trials were submitted to a mixed analysis of variance
-(ANOVA) with task-relevant context (0\% and 100\% PC) and unbiased-item
-congruency (congruent and incongruent) as within-subject factors, and
-context-type (object, social, and social/non-repeating) as the
-between-subjects factor.
+Participants with mean error rates greater than 25\% were excluded from the analyses, eliminating 13 participants.
+For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure.
+The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms (Van Selst \& Jolicoeur, 1994).
+This procedure removed 3.39\% of the total observations.
 
-The results of the RT analysis revealed the critical, two-way
-interaction between task-relevant context and unbiased-item congruency
-to be significant, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 1,608.54\),
-\(p = .005\), \(\hat{\eta}^2_p = .061\), demonstrating smaller
-congruency effects when the context dimension associated with high
-conflict was made task-relevant. Additionally, the three-way interaction
-between the task-relevant context, unbiased-item congruency, and
-context-type was non-significant, \(F(2, 128) = 0.00\),
-\(\mathit{MSE} = 1,608.54\), \(p = .996\), \(\hat{\eta}^2_p = .000\),
-showing no evidence for differences between the CSPC effects across
-context-type manipulations.
+The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1).
+To that end, mean correct RTs and mean error rates from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
 
-Similarly, the corresponding error analysis also resulted in a
-significant two-way interaction between the task-relevant context and
-unbiased-item congruency, \(F(1, 128) = 8.30\),
-\(\mathit{MSE} = 1,608.54\), \(p = .005\), \(\hat{\eta}^2_p = .061\),
-and a non-significant three-way interaction between task-relevant
-context, unbiased-item congruency, and context-type,
-\(F(2, 128) = 0.00\), \(\mathit{MSE} = 1,608.54\), \(p = .996\),
-\(\hat{\eta}^2_p = .000\). Therefore, the congruency effects in error
-rates were also smaller when the context dimension associated with high
-conflict was made task-relevant, corroborating the results of the
-reaction time analysis.
+The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 1,608.54\), \(p = .005\), \(\hat{\eta}^2_p = .061\), demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
+Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, \(F(2, 128) = 0.00\), \(\mathit{MSE} = 1,608.54\), \(p = .996\), \(\hat{\eta}^2_p = .000\), showing no evidence for differences between the CSPC effects across context-type manipulations.
 
-\section{General Discussion}\label{general-discussion}
+Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 128) = 6.72\), \(\mathit{MSE} = 13.93\), \(p = .011\), \(\hat{\eta}^2_p = .050\), and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, \(F(2, 128) = 0.92\), \(\mathit{MSE} = 13.93\), \(p = .400\), \(\hat{\eta}^2_p = .014\).
+Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.
 
-The aim of the current study was to investigate whether task-relevance
-plays a role in the contextual recruitment of selective attention.
-Specifically, we tested whether manipulating the relative task-relevance
-of context cues could cause participants to ignore a previously learned
-context-association and apply a new association. We created a frequency
-unbiased context cue that shared features with two frequency biased
-contexts and included a feature-counting task to manipulate the
-task-relevance of context dimensions across two blocks of trials.
-Critically, halfway through the experiment participants received new
-instructions changing the task-relevant feature from one frequency
-biased cue to the other.
+\begingroup
+\setlength{\parindent}{0in}
+\vspace{2.5mm}
 
-The key finding was that the congruency effects for the frequency
-unbiased items were significantly larger when the low-conflict context
-was made task-relevant as compared to when the high-conflict context was
-made task-relevant. This result is consistent with prior CSPC effects
-and, like the previous work, suggests that the context cues triggered
-rapid adjustments to attentional control (Crump \& Milliken, 2009).
-However, unlike prior studies, we were able to experimentally manipulate
-the CSPC effect across blocks of trials without changing any of the
-physical properties of the stimuli. This novel finding demonstrates that
-participants were able to learn and apply one context-attention
-association in the first phase, and subsequently ignore that association
-to learn a new association in the second phase.
+\textbf{Table 1. \\ \textit{Reaction times and error rates from Experiment 1.}}
 
-This result implicates an important role for task-relevance in producing
-CSPC phenomena. Crump et al. (2008) used shapes as context cues in a
-prime-probe Stroop task and did not find CSPC effects until the context
-cues were made task-relevant. Similarly, Cañadas et al. (2013)
-eliminated the CSPC effect by making the contextual cue effectively
-unrelated to the task. These studies suggest that task-relevance plays
-an important role in establishing associations between contextual
-information and attentional priorities to produce CSPC effects. Our
-finding extends this work in two important ways. First, we show that
-changing the task-relevance of the presented cues corresponded with a
-change in attentional control in the predicted direction. This
-demonstrates that task-relevance is also a key determinant of whether a
-previously learned attention-context association will be used or ignored
-in favor of a new association. Second, we show that task-relevance
-allowed participants resolve competition between two competing
-contextual cues, responding on the basis of one at the expense of the
-other. To our knowledge, this is the first demonstration that CSPC
-effects can be produced when there are multiple, overlapping contextual
-cues available.
+\includegraphics{images/table1.pdf}
+\endgroup
 
-In light of prior work, we take this as evidence that the contextual
-recruitment of selective attention, although likely implicit, is not
-obligatory (e.g., Brosowsky \& Crump, 2016), requiring that
-environmental information be incorporated into the task representation.
-Similarly, there appears to be flexibility in which environmental
-features are selected and used to guide attention, which can be rapidly
-updated depending on the task-relevance of those features. Such a result
-lends some insight into how context-specific control might operate in
-more complex, real-world environments, where there is an over-abundance
-of environmental features that afford many different learned
-associations. From a theoretical perspective, this result is consistent
-memory-based accounts of CSPC phenomena (Brosowsky \& Crump, 2018; J.
-Bugg \& Hutchison, 2013; Crump \& Milliken, 2009; Crump et al., 2018,
-2017). Under this view, a memory process encodes attentional priorities
-in the representation of individual experiences and, as a result, become
-associated with the environment where they were used. The subsequent
-reoccurrence of a prior context triggers the retrieval and reinstatement
-of those attentional priorities. Our results show however, that all the
-features of the environment may not be treated equally and that only
-task-relevant features are used to probe memory and guide attention.
+\hypertarget{general-discussion}{%
+\section{General Discussion}\label{general-discussion}}
 
-Another key result of this study concerned the different stimuli used as
-context cues. Across the three conditions, we varied the type of context
-image and dimensions. We manipulated the type of image presented,
-including both objects (identity and color dimensions) and faces (gender
-and racial dimensions). We also manipulated whether a single set of
-three repeating images were presented (object and social) or a set of
-non-repeating images were presented (social/non-repeating). Across all
-three conditions, we found no evidence that using different stimuli had
-an influence on the size or direction of the CSPC demonstrating
-generalizability of this phenomenon. Furthermore, CSPC effects were
-present even when using non-repeating images which suggests that
-context-dependency did rely on image-specific associations but
-higher-order, learned categorical information.
+The aim of the current study was to determine whether task-relevance plays a role in the contextual recruitment of selective attention.
+Specifically, we tested whether manipulating the relative task-relevance of context cues could cause participants to ignore a previously learned context-association and apply a new association.
+We created a frequency unbiased context cue that shared features with two frequency biased contexts and used a feature-counting task to manipulate the task-relevance of context dimensions across two blocks of trials.
+Critically, halfway through the experiment participants received new instructions changing the task-relevant feature from one frequency biased cue to the other.
 
-Traditional models of person perception posit that social categories are
-automatically activated in the presence of social stimuli (e.g., Brewer,
-1988; Devine, 1989; Fiske \& Neuberg, 1990). Cañadas et al. (2013)
-however, found that directing participants to think about faces in terms
-of individual features eliminated context-specific attention effect and
-suggested that momentary motivations may influence the automaticity of
-social categorization. Our results add to this literature by observing
-the influence of momentary motivations (i.e., task-relevance) when there
-is competition between two salient social categories. Specifically, we
-found that participants could categorize on the basis of one social cue
-at the expense of the other, and subsequently switch between them. These
-findings may speak to issues of automaticity in social categorization
-(Macrae \& Bodenhausen, 2001) as well as understanding how the
-situational context can prime one social identity over another (Crisp \&
-Hewstone, 2007). Furthermore, we found no evidence for differences
-between the social and object conditions. This suggests that
-categorization within the CSPC task is quickly and easily learned when
-the task supports such learning and is non-unique to social stimuli.
+The key finding was that the congruency effects for the frequency unbiased items were significantly larger when the low-conflict context was made task-relevant as compared to when the high-conflict context was made task-relevant.
+This result is consistent with prior CSPC effects and, like the previous work, suggests that the context cues triggered rapid adjustments to attentional control (Crump \& Milliken, 2009).
+However, unlike prior studies, we were able to experimentally manipulate the CSPC effect across blocks of trials without changing any of the physical properties of the stimuli.
+This novel finding demonstrates that participants were able to learn and apply one context-attention association in the first phase, and subsequently ignore that association to learn a new association in the second phase.
 
-In sum, our results provide new evidence that changes in task-relevance
-can update the contextual recruitment of selective attention in a CSPC
-flanker task. Importantly, we show that making one feature task-relevant
-produced a CSPC effect, even in the presence of a competing contextual
-cue. Moreover, changing the task-relevant context-cue midway through the
-experiment was accompanied by predictable changes in the congruency
-effects. This effect was found to be generalizable across two different
-kinds of stimuli and occurred even when using non-repeating images.
-These results implicate an important role for task-relevance in
-producing context-dependency and are consistent with memory-based
-accounts of CSPC phenomena.
+This result implicates an important role for task-relevance in producing CSPC phenomena.
+Crump et al.
+(2008) used shapes as context cues in a prime-probe Stroop task and did not find CSPC effects until the context cues were made task-relevant.
+Similarly, Cañadas et al.
+(2013) eliminated the CSPC effect by making the contextual cue effectively unrelated to the task.
+These studies suggest that task-relevance plays an important role in establishing associations between contextual information and attentional priorities to produce CSPC effects.
+Our finding extends this work in two important ways.
+First, we show that changing the task-relevance of the presented cues corresponded with a change in attentional control in the predicted direction.
+This demonstrates that task-relevance is also a key determinant of whether a previously learned attention-context association will be used or ignored in favor of a new association.
+Second, we show that task-relevance allowed participants resolve competition between two competing contextual cues, responding on the basis of one at the expense of the other.
+To our knowledge, this is the first demonstration that CSPC effects can be produced when there are multiple, overlapping contextual cues available.
+
+In light of prior work, we take this as evidence that the contextual recruitment of selective attention, although likely implicit, is not obligatory (e.g., Brosowsky \& Crump, 2016), requiring that environmental information be incorporated into the task representation.
+Similarly, there appears to be flexibility in which environmental features are selected and used to guide attention, which can be rapidly updated depending on the task-relevance of those features.
+Such a result lends some insight into how context-specific control might operate in more complex, real-world environments, where there is an over-abundance of environmental features that afford many different learned associations.
+From a theoretical perspective, this result is consistent memory-based accounts of CSPC phenomena (Brosowsky \& Crump, 2018; Bugg \& Hutchison, 2013; Crump et al., 2017, 2018; Crump \& Milliken, 2009).
+Under this view, a memory process encodes attentional priorities in the representation of individual experiences and, as a result, become associated with the environment where they were used.
+The subsequent reoccurrence of a prior context triggers the retrieval and reinstatement of those attentional priorities.
+Our results show however, that all the features of the environment may not be treated equally and that only task-relevant features are used to probe memory and guide attention.
+
+Another key result of this study concerned the different stimuli used as context cues.
+Across the three conditions, we varied the type of context image and dimensions.
+We manipulated the type of image presented, including both objects (identity and color dimensions) and faces (gender and racial dimensions).
+We also manipulated whether a single set of three repeating images were presented (object and social) or a set of non-repeating images were presented (social/non-repeating).
+Across all three conditions, we found no evidence that using different stimuli had an influence on the size or direction of the CSPC demonstrating generalizability of this phenomenon.
+Furthermore, CSPC effects were present even when using non-repeating images which suggests that context-dependency did rely on image-specific associations but higher-order, learned categorical information.
+
+Traditional models of person perception posit that social categories are automatically activated in the presence of social stimuli (e.g., Brewer, 1988; Devine, 1989; Fiske \& Neuberg, 1990).
+Cañadas et al.
+(2013) however, found that directing participants to think about faces in terms of individual features eliminated context-specific attention effect and suggested that momentary motivations may influence the automaticity of social categorization.
+Our results add to this literature by observing the influence of momentary motivations (i.e., task-relevance) when there is competition between two salient social categories.
+Specifically, we found that participants could categorize on the basis of one social cue at the expense of the other, and subsequently switch between them.
+These findings may speak to issues of automaticity in social categorization (Macrae \& Bodenhausen, 2001) as well as understanding how the situational context can prime one social identity over another (Crisp \& Hewstone, 2007).
+Furthermore, we found no evidence for differences between the social and object conditions.
+This suggests that categorization within the CSPC task is quickly and easily learned when the task supports such learning and is non-unique to social stimuli.
+
+In sum, our results provide new evidence that changes in task-relevance can update the contextual recruitment of selective attention in a CSPC flanker task.
+We demonstrated that making one context cue task-relevant produced a CSPC effect, even in the presence of a competing contextual cue.
+More important however, we found that changing the task-relevance of the contextual cues across blocks of trials was accompanied by predictable changes in the congruency effects.
+These effects were found to be generalizable across two different kinds of stimuli and occurred even when using non-repeating images, and implicate an important role for task-relevance in producing context-dependency and are consistent with memory-based accounts of CSPC phenomena.
 
@@
 
-\section{References}\label{references}
+\hypertarget{references}{%
+\section{References}\label{references}}
 
 \begingroup
-\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\hypertarget{ref-abrahamse_grounding_2016}{}
-Abrahamse, E., Braem, S., Notebaert, W., \& Verguts, T. (2016).
-Grounding cognitive control in associative learning. \emph{Psychological
-Bulletin}, \emph{142}, 693--728.
+\leavevmode\hypertarget{ref-abrahamse_grounding_2016}{}%
+Abrahamse, E., Braem, S., Notebaert, W., \& Verguts, T.
+(2016).
+Grounding cognitive control in associative learning.
+\emph{Psychological Bulletin}, \emph{142}, 693--728.
 doi:\href{https://doi.org/10.1037/bul0000047}{10.1037/bul0000047}
 
-\hypertarget{ref-alards-tomalin_auditory_2017}{}
-Alards-Tomalin, D., Brosowsky, N. P., \& Mondor, T. A. (2017). Auditory
-statistical learning: Predictive frequency information affects the
-deployment of contextually mediated attentional resources on perceptual
-tasks. \emph{Journal of Cognitive Psychology}, \emph{0}(0), 1--11.
+\leavevmode\hypertarget{ref-alards-tomalin_auditory_2017}{}%
+Alards-Tomalin, D., Brosowsky, N.
+P., \& Mondor, T.
+A.
+(2017).
+Auditory statistical learning: Predictive frequency information affects the deployment of contextually mediated attentional resources on perceptual tasks.
+\emph{Journal of Cognitive Psychology}, \emph{0}(0), 1--11.
 doi:\href{https://doi.org/10.1080/20445911.2017.1353518}{10.1080/20445911.2017.1353518}
 
-\hypertarget{ref-blais_trial-by-trial_2015}{}
-Blais, C., Harris, M. B., Sinanian, M. H., \& Bunge, S. A. (2015).
-Trial-by-trial adjustments in control triggered by incidentally encoded
-semantic cues. \emph{The Quarterly Journal of Experimental Psychology},
-\emph{68}, 1920--1930.
+\leavevmode\hypertarget{ref-blais_trial-by-trial_2015}{}%
+Blais, C., Harris, M.
+B., Sinanian, M.
+H., \& Bunge, S.
+A.
+(2015).
+Trial-by-trial adjustments in control triggered by incidentally encoded semantic cues.
+\emph{The Quarterly Journal of Experimental Psychology}, \emph{68}, 1920--1930.
 doi:\href{https://doi.org/10.1080/17470218.2014.1000346}{10.1080/17470218.2014.1000346}
 
-\hypertarget{ref-brady_visual_2013}{}
-Brady, T. F., Konkle, T., Gill, J., Oliva, A., \& Alvarez, G. A. (2013).
-Visual long-term memory has the same limit on fidelity as visual working
-memory. \emph{Psychological Science}, \emph{24}, 981--990.
+\leavevmode\hypertarget{ref-brady_visual_2013}{}%
+Brady, T.
+F., Konkle, T., Gill, J., Oliva, A., \& Alvarez, G.
+A.
+(2013).
+Visual long-term memory has the same limit on fidelity as visual working memory.
+\emph{Psychological Science}, \emph{24}, 981--990.
 doi:\href{https://doi.org/10.1177/0956797612465439}{10.1177/0956797612465439}
 
-\hypertarget{ref-brewer_dual_1988}{}
-Brewer, M. B. (1988). A dual process model of impression formation. In
-R. S. Wyer Jr \& T. K. Srull (Eds.), \emph{A dual-process model of
-impression formation: Advances in social cognition} (Vol. 1, pp. 1--36).
+\leavevmode\hypertarget{ref-brewer_dual_1988}{}%
+Brewer, M.
+B.
+(1988).
+A dual process model of impression formation.
+In R.
+S.
+Wyer Jr \& T.
+K.
+Srull (Eds.), \emph{A dual-process model of impression formation: Advances in social cognition} (Vol.
+1, pp.
+1--36).
 Hillsdale, NJ: Erlbaum.
 
-\hypertarget{ref-brosowsky_context-specific_2016}{}
-Brosowsky, N. P., \& Crump, M. J. (2016). Context-specific attentional
-sampling: Intentional control as a pre-requisite for contextual control.
+\leavevmode\hypertarget{ref-brosowsky_context-specific_2016}{}%
+Brosowsky, N.
+P., \& Crump, M.
+J.
+(2016).
+Context-specific attentional sampling: Intentional control as a pre-requisite for contextual control.
 \emph{Consciousness and Cognition}, \emph{44}, 146--160.
@@
 
-\hypertarget{ref-brosowsky_memory-guided_2018}{}
-Brosowsky, N. P., \& Crump, M. J. C. (2018). Memory-guided selective
-attention: Single experiences with conflict have long-lasting effects on
-cognitive control. \emph{Journal of Experimental Psychology: General}.
+\leavevmode\hypertarget{ref-brosowsky_memory-guided_2018}{}%
+Brosowsky, N.
+P., \& Crump, M.
+J.
+C.
+(2018).
+Memory-guided selective attention: Single experiences with conflict have long-lasting effects on cognitive control.
+\emph{Journal of Experimental Psychology: General}.
 doi:\href{https://doi.org/10.1037/xge0000431}{10.1037/xge0000431}
 
-\hypertarget{ref-bugg_conflict-triggered_2014}{}
-Bugg, J. (2014). Conflict-triggered top-down control: Default mode, last
-resort, or no such thing? \emph{Journal of Experimental Psychology:
-Learning, Memory, and Cognition}, \emph{40}(2), 567.
+\leavevmode\hypertarget{ref-bugg_conflict-triggered_2014}{}%
+Bugg, J. (2014). Conflict-triggered top-down control: Default mode, last resort, or no such thing? \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}(2), 567.
 
-\hypertarget{ref-bugg_support_2012}{}
-Bugg, J., \& Crump, M. J. (2012). In support of a distinction between
-voluntary and stimulus-driven control: A review of the literature on
-proportion congruent effects. \emph{Frontiers in Psychology}, \emph{3},
-367.
+\leavevmode\hypertarget{ref-bugg_support_2012}{}%
+Bugg, J., \& Crump, M.
+J.
+(2012).
+In support of a distinction between voluntary and stimulus-driven control: A review of the literature on proportion congruent effects.
+\emph{Frontiers in Psychology}, \emph{3}, 367.
 doi:\href{https://doi.org/10.3389/fpsyg.2012.00367}{10.3389/fpsyg.2012.00367}
 
-\hypertarget{ref-bugg_converging_2013}{}
-Bugg, J., \& Hutchison, K. A. (2013). Converging evidence for control of
-color--word Stroop interference at the item level. \emph{Journal of
-Experimental Psychology: Human Perception and Performance},
-\emph{39}(2), 433.
+\leavevmode\hypertarget{ref-bugg_converging_2013}{}%
+Bugg, J., \& Hutchison, K.
+A.
+(2013).
+Converging evidence for control of color--word Stroop interference at the item level.
+\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{39}(2), 433.
 
-\hypertarget{ref-bugg_multiple_2008}{}
-Bugg, J., Jacoby, L. L., \& Toth, J. P. (2008). Multiple levels of
-control in the Stroop task. \emph{Memory \& Cognition}, \emph{36},
-1484--1494.
+\leavevmode\hypertarget{ref-bugg_multiple_2008}{}%
+Bugg, J., Jacoby, L.
+L., \& Toth, J.
+P.
+(2008).
+Multiple levels of control in the Stroop task.
+\emph{Memory \& Cognition}, \emph{36}, 1484--1494.
 doi:\href{https://doi.org/10.3758/MC.36.8.1484}{10.3758/MC.36.8.1484}
 
-\hypertarget{ref-canadas_social_2013}{}
-Cañadas, E., Rodríguez-Bailón, R., Milliken, B., \& Lupiáñez, J. (2013).
-Social categories as a context for the allocation of attentional
-control. \emph{Journal of Experimental Psychology: General}, \emph{142},
-934--943. doi:\href{https://doi.org/10.1037/a0029794}{10.1037/a0029794}
+\leavevmode\hypertarget{ref-canadas_social_2013}{}%
+Cañadas, E., Rodríguez-Bailón, R., Milliken, B., \& Lupiáñez, J.
+(2013).
+Social categories as a context for the allocation of attentional control.
+\emph{Journal of Experimental Psychology: General}, \emph{142}, 934--943.
+doi:\href{https://doi.org/10.1037/a0029794}{10.1037/a0029794}
 
-\hypertarget{ref-corballis_independent_2003}{}
-Corballis, P. M., \& Gratton, G. (2003). Independent control of
-processing strategies for different locations in the visual field.
+\leavevmode\hypertarget{ref-corballis_independent_2003}{}%
+Corballis, P.
+M., \& Gratton, G.
+(2003).
+Independent control of processing strategies for different locations in the visual field.
 \emph{Biological Psychology}, \emph{64}, 191--209.
@@
 
-\hypertarget{ref-crisp_multiple_2007}{}
-Crisp, R. J., \& Hewstone, M. (2007). Multiple social categorization.
-\emph{Advances in Experimental Social Psychology}, \emph{39}, 163--254.
+\leavevmode\hypertarget{ref-crisp_multiple_2007}{}%
+Crisp, R. J., \& Hewstone, M. (2007). Multiple social categorization. \emph{Advances in Experimental Social Psychology}, \emph{39}, 163--254.
 
-\hypertarget{ref-crump_learning_2016}{}
-Crump, M. J. (2016). Learning to selectively attend from
-context-specific attentional histories: A demonstration and some
-constraints. \emph{Canadian Journal of Experimental Psychology/Revue
-Canadienne de Psychologie Expérimentale}, \emph{70}, 59--77.
+\leavevmode\hypertarget{ref-crump_learning_2016}{}%
+Crump, M.
+J.
+(2016).
+Learning to selectively attend from context-specific attentional histories: A demonstration and some constraints.
+\emph{Canadian Journal of Experimental Psychology/Revue Canadienne de Psychologie Expérimentale}, \emph{70}, 59--77.
 doi:\href{https://doi.org/10.1037/cep0000066}{10.1037/cep0000066}
 
-\hypertarget{ref-crump_flexibility_2009}{}
-Crump, M. J. C., \& Milliken, B. (2009). The flexibility of
-context-specific control: Evidence for context-driven generalization of
-item-specific control settings. \emph{The Quarterly Journal of
-Experimental Psychology}, \emph{62}, 1523--1532.
+\leavevmode\hypertarget{ref-crump_reproducing_2017}{}%
+Crump, M.
+J., Brosowsky, N.
+P., \& Milliken, B.
+(2017).
+Reproducing the location-based context-specific proportion congruent effect for frequency unbiased items: A reply to Hutcheon and Spieler (2016).
+\emph{The Quarterly Journal of Experimental Psychology}, \emph{70}, 1792--1807.
+doi:\href{https://doi.org/10.1080/17470218.2016.1206130}{10.1080/17470218.2016.1206130}
+
+\leavevmode\hypertarget{ref-crump_flexibility_2009}{}%
+Crump, M.
+J.
+C., \& Milliken, B.
+(2009).
+The flexibility of context-specific control: Evidence for context-driven generalization of item-specific control settings.
+\emph{The Quarterly Journal of Experimental Psychology}, \emph{62}, 1523--1532.
 doi:\href{https://doi.org/10.1080/17470210902752096}{10.1080/17470210902752096}
 
-\hypertarget{ref-crump_context-dependent_2018}{}
-Crump, M. J. C., Milliken, B., Leboe-McGowan, J., Leboe-McGowan, L., \&
-Gao, X. (2018). Context-Dependent Control of Attention Capture: Evidence
-From Proportion Congruent Effects. \emph{Canadian Journal of
-Experimental Psychology= Revue Canadienne de Psychologie Experimentale}.
+\leavevmode\hypertarget{ref-crump_context-dependent_2018}{}%
+Crump, M.
+J.
+C., Milliken, B., Leboe-McGowan, J., Leboe-McGowan, L., \& Gao, X.
+(2018).
+Context-Dependent Control of Attention Capture: Evidence From Proportion Congruent Effects.
+\emph{Canadian Journal of Experimental Psychology= Revue Canadienne de Psychologie Experimentale}.
 
-\hypertarget{ref-crump_reproducing_2017}{}
-Crump, M. J., Brosowsky, N. P., \& Milliken, B. (2017). Reproducing the
-location-based context-specific proportion congruent effect for
-frequency unbiased items: A reply to Hutcheon and Spieler (2016).
-\emph{The Quarterly Journal of Experimental Psychology}, \emph{70},
-1792--1807.
-doi:\href{https://doi.org/10.1080/17470218.2016.1206130}{10.1080/17470218.2016.1206130}
-
-\hypertarget{ref-crump_context-specific_2006}{}
-Crump, M. J., Gong, Z., \& Milliken, B. (2006). The context-specific
-proportion congruent Stroop effect: Location as a contextual cue.
+\leavevmode\hypertarget{ref-crump_context-specific_2006}{}%
+Crump, M.
+J., Gong, Z., \& Milliken, B.
+(2006).
+The context-specific proportion congruent Stroop effect: Location as a contextual cue.
 \emph{Psychonomic Bulletin \& Review}, \emph{13}, 316--321.
@@
 
-\hypertarget{ref-crump_context-specific_2008}{}
-Crump, M. J., Vaquero, J. M., \& Milliken, B. (2008). Context-specific
-learning and control: The roles of awareness, task relevance, and
-relative salience. \emph{Consciousness and Cognition}, \emph{17},
-22--36.
+\leavevmode\hypertarget{ref-crump_context-specific_2008}{}%
+Crump, M.
+J., Vaquero, J.
+M., \& Milliken, B.
+(2008).
+Context-specific learning and control: The roles of awareness, task relevance, and relative salience.
+\emph{Consciousness and Cognition}, \emph{17}, 22--36.
 doi:\href{https://doi.org/10.1016/j.concog.2007.01.004}{10.1016/j.concog.2007.01.004}
 
-\hypertarget{ref-devine_stereotypes_1989}{}
-Devine, P. G. (1989). Stereotypes and prejudice: Their automatic and
-controlled components. \emph{Journal of Personality and Social
-Psychology}, \emph{56}(1), 5.
+\leavevmode\hypertarget{ref-devine_stereotypes_1989}{}%
+Devine, P. G. (1989). Stereotypes and prejudice: Their automatic and controlled components. \emph{Journal of Personality and Social Psychology}, \emph{56}(1), 5.
 
-\hypertarget{ref-egner_creatures_2014}{}
-Egner, T. (2014). Creatures of habit (and control): A multi-level
-learning perspective on the modulation of congruency effects.
+\leavevmode\hypertarget{ref-egner_creatures_2014}{}%
+Egner, T.
+(2014).
+Creatures of habit (and control): A multi-level learning perspective on the modulation of congruency effects.
 \emph{Frontiers in Psychology}, \emph{5}, 1247.
@@
 
-\hypertarget{ref-eriksen_effects_1974}{}
-Eriksen, B. A., \& Eriksen, C. W. (1974). Effects of noise letters upon
-the identification of a target letter in a nonsearch task.
+\leavevmode\hypertarget{ref-eriksen_effects_1974}{}%
+Eriksen, B.
+A., \& Eriksen, C.
+W.
+(1974).
+Effects of noise letters upon the identification of a target letter in a nonsearch task.
 \emph{Perception \& Psychophysics}, \emph{16}, 143--149.
@@
 
-\hypertarget{ref-fischer_predicting_2015}{}
-Fischer, R., \& Dreisbach, G. (2015). Predicting high levels of
-multitasking reduces between-tasks interactions. Retrieved from
-\url{http://psycnet.apa.org/psycinfo/2015-47211-001/}
+\leavevmode\hypertarget{ref-fischer_predicting_2015}{}%
+Fischer, R., \& Dreisbach, G. (2015). Predicting high levels of multitasking reduces between-tasks interactions. Retrieved from \url{http://psycnet.apa.org/psycinfo/2015-47211-001/}
 
-\hypertarget{ref-fischer_context-sensitive_2014}{}
-Fischer, R., Gottschalk, C., \& Dreisbach, G. (2014). Context-sensitive
-adjustment of cognitive control in dual-task performance. \emph{Journal
-of Experimental Psychology: Learning, Memory, and Cognition},
-\emph{40}(2), 399.
+\leavevmode\hypertarget{ref-fischer_context-sensitive_2014}{}%
+Fischer, R., Gottschalk, C., \& Dreisbach, G.
+(2014).
+Context-sensitive adjustment of cognitive control in dual-task performance.
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}(2), 399.
 
-\hypertarget{ref-fiske_continuum_1990}{}
-Fiske, S. T., \& Neuberg, S. L. (1990). A continuum of impression
-formation, from category-based to individuating processes: Influences of
-information and motivation on attention and interpretation. In
-\emph{Advances in experimental social psychology} (Vol. 23, pp. 1--74).
+\leavevmode\hypertarget{ref-fiske_continuum_1990}{}%
+Fiske, S.
+T., \& Neuberg, S.
+L.
+(1990).
+A continuum of impression formation, from category-based to individuating processes: Influences of information and motivation on attention and interpretation.
+In \emph{Advances in experimental social psychology} (Vol.
+23, pp.
+1--74).
 Elsevier.
 
-\hypertarget{ref-hutcheon_limits_2017}{}
-Hutcheon, T. G., \& Spieler, D. H. (2017). Limits on the
-generalizability of context-driven control. \emph{Quarterly Journal of
-Experimental Psychology}, \emph{70}(7), 1292--1304.
+\leavevmode\hypertarget{ref-hutcheon_limits_2017}{}%
+Hutcheon, T.
+G., \& Spieler, D.
+H.
+(2017).
+Limits on the generalizability of context-driven control.
+\emph{Quarterly Journal of Experimental Psychology}, \emph{70}(7), 1292--1304.
 doi:\href{https://doi.org/10.1080/17470218.2016.1182193}{10.1080/17470218.2016.1182193}
 
-\hypertarget{ref-hubner_location-specific_2016}{}
-Hübner, R., \& Mishra, S. (2016). Location-specific attentional control
-is also possible in the Simon task. \emph{Psychonomic Bulletin \&
-Review}, \emph{23}, 1867--1872.
+\leavevmode\hypertarget{ref-hubner_location-specific_2016}{}%
+Hübner, R., \& Mishra, S.
+(2016).
+Location-specific attentional control is also possible in the Simon task.
+\emph{Psychonomic Bulletin \& Review}, \emph{23}, 1867--1872.
 doi:\href{https://doi.org/10.3758/s13423-016-1057-y}{10.3758/s13423-016-1057-y}
 
-\hypertarget{ref-king_priming_2012}{}
-King, J. A., Korb, F. M., \& Egner, T. (2012). Priming of control:
-Implicit contextual cuing of top-down attentional set. \emph{The Journal
-of Neuroscience}, \emph{32}, 8192--8200.
+\leavevmode\hypertarget{ref-king_priming_2012}{}%
+King, J.
+A., Korb, F.
+M., \& Egner, T.
+(2012).
+Priming of control: Implicit contextual cuing of top-down attentional set.
+\emph{The Journal of Neuroscience}, \emph{32}, 8192--8200.
 doi:\href{https://doi.org/10.1523/JNEUROSCI.0934-12.2012}{10.1523/JNEUROSCI.0934-12.2012}
 
-\hypertarget{ref-logan_attention_1980}{}
-Logan, G. D. (1980). Attention and automaticity in Stroop and priming
-tasks: Theory and data. \emph{Cognitive Psychology}, \emph{12}(4),
-523--553.
+\leavevmode\hypertarget{ref-logan_attention_1980}{}%
+Logan, G. D. (1980). Attention and automaticity in Stroop and priming tasks: Theory and data. \emph{Cognitive Psychology}, \emph{12}(4), 523--553.
 
-\hypertarget{ref-logan_what_1998}{}
-Logan, G. D. (1998). What is learned during automatization? II.
-obligatory encoding of spatial location. \emph{Journal of Experimental
-Psychology: Human Perception and Performance}, \emph{24}(6), 1720.
+\leavevmode\hypertarget{ref-logan_what_1998}{}%
+Logan, G.
+D.
+(1998).
+What is learned during automatization?
+II.
+Obligatory encoding of spatial location.
+\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{24}(6), 1720.
 
-\hypertarget{ref-logan_when_1979}{}
-Logan, G. D., \& Zbrodoff, N. J. (1979). When it helps to be misled:
-Facilitative effects of increasing the frequency of conflicting stimuli
-in a Stroop-like task. \emph{Memory \& Cognition}, \emph{7}, 166--174.
+\leavevmode\hypertarget{ref-logan_when_1979}{}%
+Logan, G.
+D., \& Zbrodoff, N.
+J.
+(1979).
+When it helps to be misled: Facilitative effects of increasing the frequency of conflicting stimuli in a Stroop-like task.
+\emph{Memory \& Cognition}, \emph{7}, 166--174.
 doi:\href{https://doi.org/10.3758/BF03197535}{10.3758/BF03197535}
 
-\hypertarget{ref-logan_strategies_1984}{}
-Logan, G. D., Zbrodoff, N. J., \& Williamson, J. (1984). Strategies in
-the color-word Stroop task. \emph{Bulletin of the Psychonomic Society},
-\emph{22}(2), 135--138.
+\leavevmode\hypertarget{ref-logan_strategies_1984}{}%
+Logan, G. D., Zbrodoff, N. J., \& Williamson, J. (1984). Strategies in the color-word Stroop task. \emph{Bulletin of the Psychonomic Society}, \emph{22}(2), 135--138.
 
-\hypertarget{ref-lowe_selective_1982}{}
-Lowe, D. G., \& Mitterer, J. O. (1982). Selective and divided Attention
-in a Stroop task. \emph{Canadian Journal of Psychology/Revue Canadienne
-de Psychologie}, \emph{36}(4), 684.
+\leavevmode\hypertarget{ref-lowe_selective_1982}{}%
+Lowe, D. G., \& Mitterer, J. O. (1982). Selective and divided Attention in a Stroop task. \emph{Canadian Journal of Psychology/Revue Canadienne de Psychologie}, \emph{36}(4), 684.
 
-\hypertarget{ref-ma_chicago_2015}{}
-Ma, D. S., Correll, J., \& Wittenbrink, B. (2015). The Chicago face
-database: A free stimulus set of faces and norming data. \emph{Behavior
-Research Methods}, \emph{47}(4), 1122--1135.
+\leavevmode\hypertarget{ref-ma_chicago_2015}{}%
+Ma, D.
+S., Correll, J., \& Wittenbrink, B.
+(2015).
+The Chicago face database: A free stimulus set of faces and norming data.
+\emph{Behavior Research Methods}, \emph{47}(4), 1122--1135.
 doi:\href{https://doi.org/10.3758/s13428-014-0532-5}{10.3758/s13428-014-0532-5}
 
-\hypertarget{ref-macrae_social_2001}{}
-Macrae, C. N., \& Bodenhausen, G. V. (2001). Social cognition:
-Categorical person perception. \emph{British Journal of Psychology},
-\emph{92}(1), 239--255.
+\leavevmode\hypertarget{ref-macrae_social_2001}{}%
+Macrae, C. N., \& Bodenhausen, G. V. (2001). Social cognition: Categorical person perception. \emph{British Journal of Psychology}, \emph{92}(1), 239--255.
 
-\hypertarget{ref-mayr_spatial_1996}{}
-Mayr, U. (1996). Spatial attention and implicit sequence learning:
-Evidence for independent learning of spatial and nonspatial sequences.
-\emph{Journal of Experimental Psychology: Learning, Memory, and
-Cognition}, \emph{22}(2), 350.
+\leavevmode\hypertarget{ref-mayr_spatial_1996}{}%
+Mayr, U.
+(1996).
+Spatial attention and implicit sequence learning: Evidence for independent learning of spatial and nonspatial sequences.
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{22}(2), 350.
 
-\hypertarget{ref-mayr_outsourcing_2007}{}
-Mayr, U., \& Bryck, R. L. (2007). Outsourcing control to the
-environment: Effects of stimulus/response locations on task selection.
+\leavevmode\hypertarget{ref-mayr_outsourcing_2007}{}%
+Mayr, U., \& Bryck, R.
+L.
+(2007).
+Outsourcing control to the environment: Effects of stimulus/response locations on task selection.
 \emph{Psychological Research}, \emph{71}(1), 107--116.
@@
 
-\hypertarget{ref-schmidt_stroop_2008}{}
-Schmidt, J. R., \& Besner, D. (2008). The Stroop effect: Why proportion
-congruent has nothing to do with congruency and everything to do with
-contingency. \emph{Journal of Experimental Psychology: Learning, Memory,
-and Cognition}, \emph{34}, 514--523.
+\leavevmode\hypertarget{ref-schmidt_stroop_2008}{}%
+Schmidt, J.
+R., \& Besner, D.
+(2008).
+The Stroop effect: Why proportion congruent has nothing to do with congruency and everything to do with contingency.
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{34}, 514--523.
 doi:\href{https://doi.org/10.1037/0278-7393.34.3.514}{10.1037/0278-7393.34.3.514}
 
-\hypertarget{ref-stroop_studies_1935}{}
-Stroop, J. R. (1935). Studies of interference in serial verbal
-reactions. \emph{Journal of Experimental Psychology}, \emph{18}, 643.
-doi:\href{https://doi.org/10.1037/h0054651}{10.1037/h0054651}
+\leavevmode\hypertarget{ref-stroop_studies_1935}{}%
+Stroop, J. R. (1935). Studies of interference in serial verbal reactions. \emph{Journal of Experimental Psychology}, \emph{18}, 643. doi:\href{https://doi.org/10.1037/h0054651}{10.1037/h0054651}
 
-\hypertarget{ref-tottenham_nimstim_2009}{}
-Tottenham, N., Tanaka, J. W., Leon, A. C., McCarry, T., Nurse, M., Hare,
-T. A., \ldots{} Nelson, C. (2009). The NimStim set of facial
-expressions: Judgments from untrained research participants.
+\leavevmode\hypertarget{ref-tottenham_nimstim_2009}{}%
+Tottenham, N., Tanaka, J.
+W., Leon, A.
+C., McCarry, T., Nurse, M., Hare, T.
+A., \ldots{} Nelson, C.
+(2009).
+The NimStim set of facial expressions: Judgments from untrained research participants.
 \emph{Psychiatry Research}, \emph{168}(3), 242--249.
@@
 
-\hypertarget{ref-van_selst_solution_1994}{}
-Van Selst, M., \& Jolicoeur, P. (1994). A solution to the effect of
-sample size on outlier elimination. \emph{The Quarterly Journal of
-Experimental Psychology Section A}, \emph{47}, 631--650.
+\leavevmode\hypertarget{ref-van_selst_solution_1994}{}%
+Van Selst, M., \& Jolicoeur, P.
+(1994).
+A solution to the effect of sample size on outlier elimination.
+\emph{The Quarterly Journal of Experimental Psychology Section A}, \emph{47}, 631--650.
 doi:\href{https://doi.org/10.1080/14640749408401131}{10.1080/14640749408401131}
 
-\hypertarget{ref-vietze_context_2009}{}
-Vietze, I., \& Wendt, M. (2009). Context specificity of conflict
-frequency-dependent control. \emph{The Quarterly Journal of Experimental
-Psychology}, \emph{62}, 1391--1400.
+\leavevmode\hypertarget{ref-vietze_context_2009}{}%
+Vietze, I., \& Wendt, M.
+(2009).
+Context specificity of conflict frequency-dependent control.
+\emph{The Quarterly Journal of Experimental Psychology}, \emph{62}, 1391--1400.
 doi:\href{https://doi.org/10.1080/17470210802426908}{10.1080/17470210802426908}
 
-\hypertarget{ref-weidler_transfer_2016}{}
-Weidler, B. J., \& Bugg, J. (2016). Transfer of location-specific
-control to untrained locations. \emph{The Quarterly Journal of
-Experimental Psychology}, \emph{69}, 2202--2217.
+\leavevmode\hypertarget{ref-weidler_transfer_2016}{}%
+Weidler, B.
+J., \& Bugg, J.
+(2016).
+Transfer of location-specific control to untrained locations.
+\emph{The Quarterly Journal of Experimental Psychology}, \emph{69}, 2202--2217.
 doi:\href{https://doi.org/10.1080/17470218.2015.1111396}{10.1080/17470218.2015.1111396}
 
-\hypertarget{ref-weidler_attentional_2018}{}
-Weidler, B. J., Dey, A., \& Bugg, J. M. (2018). Attentional control
-transfers beyond the reference frame. \emph{Psychological Research},
-1--14.
+\leavevmode\hypertarget{ref-weidler_attentional_2018}{}%
+Weidler, B. J., Dey, A., \& Bugg, J. M. (2018). Attentional control transfers beyond the reference frame. \emph{Psychological Research}, 1--14.
 
-\hypertarget{ref-west_effects_1998}{}
-West, R., \& Baylis, G. C. (1998). Effects of increased response
-dominance and contextual disintegration on the Stroop interference
-effect in older adults. \emph{Psychology and Aging}, \emph{13}(2), 206.
+\leavevmode\hypertarget{ref-west_effects_1998}{}%
+West, R., \& Baylis, G.
+C.
+(1998).
+Effects of increased response dominance and contextual disintegration on the Stroop interference effect in older adults.
+\emph{Psychology and Aging}, \emph{13}(2), 206.
 
@@
 
+\newpage
+
 \end{document}

### 2018-12-09 redoc_manuscript.Rmd
first draft

--- 2018-12-07 v1-task-relevance-cspc.Rmd
@@
 
+#output: 
+#  word_document
+
 output:
- papaja::apa6_pdf
+#  papaja::apa6_word: default
+#  papaja::apa6_pdf: default
+   redoc::rdocx_reversible
+
+knit: (function(inputFile, encoding) {
+  rmarkdown::render(inputFile, encoding = encoding,
+  output_format = "all") })
+
+header-includes:
+  - \usepackage{setspace}\singlespacing 
+  - \AtBeginEnvironment{tabular}{\onehalfspacing}
+  - \AtBeginEnvironment{lltable}{\onehalfspacing}
+  - \captionsetup[table]{font={stretch=1.5}}
+  - \captionsetup[figure]{font={stretch=1}}
+  - \setlength{\skip\footins}{1cm}
+  - \setlength{\footnotesep}{0.5cm}
+  - \usepackage{float}
+  - \usepackage{booktabs}
+  - \usepackage{longtable}
+  - \usepackage{array}
+  - \usepackage{multirow}
+  - \usepackage[table]{xcolor}
+  - \usepackage{wrapfig}
+  - \usepackage{colortbl}
+  - \usepackage{pdflscape}
+  - \usepackage{tabu}
+  - \usepackage{threeparttable}
+  - \usepackage{threeparttablex}
+  - \usepackage[normalem]{ulem}
+  - \usepackage{makecell}
+  - \usepackage{setspace}\singlespacing 
+  - \AtBeginEnvironment{tabular}{\onehalfspacing}
+  - \AtBeginEnvironment{lltable}{\onehalfspacing}
+  - \newenvironment{zeroindent}
+     {\par\setlength{\parindent}{0pt}}
+     {\par}
+
 ---
@@
 ```{r setup, include=FALSE, eval=TRUE,echo=FALSE}
-# options(htmltools.dir.version = FALSE)
-knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache = FALSE)
-
 library("dplyr")
@@
 library("papaja")
+library("magrittr")
+library("kableExtra")
+#As of 2018/12/07 apa_print() requires development version of Papaja
+#devtools::install_github("crsh/papaja")
+library(papaja)
 ```
 
-#  Introduction
+Selective attention is commonly investigated using interference paradigms such
+as the Stroop (1935) and flanker (Eriksen and Eriksen 1974) tasks, where
+participants identify a target while ignoring a response-congruent or
+-incongruent distractor. {++ Typically, p ++}{-- P --}erformance is
+{-- typically --} better {++ (quicker reaction times and higher accuracy) ++} on
+congruent versus incongruent trials and the difference-the congruency
+effect-taken as an index of attentional priorities. Large congruency effects are
+thought to reflect ineffective filtering of the distracting stimuli whereas
+small congruency effects are thought to reflect effective filtering. By probing
+factors that systematically alter congruency effects, we can then make
+inferences about processes that control attentional filtering. For example,
+manipulating the frequency of conflict via the proportion of congruent versus
+incongruent trials has shown to influence the size of the congruency effect.
+Typically, a high proportion congruent experiment produces large congruency
+effects, whereas a low proportion congruent experiment produces small congruency
+effects (Logan and Zbrodoff 1979; Lowe and Mitterer 1982; West and Baylis 1998).
+This result is usually explained as strategic control, where participants
+increase attentional control under high-conflict demands and relax attentional
+control under low-conflict demands (Logan 1980; Logan, Zbrodoff, and Williamson
+1984; Logan and Zbrodoff 1979; Lowe and Mitterer 1982). Recent work however, has
+demonstrated that attentional control is not only adjusted by top-down
+regulation, but can also be triggered automatically by environmental cues
+(Brosowsky and Crump 2018; Bugg and Crump 2012; Egner 2014; Fischer and
+Dreisbach 2015; King, Korb, and Egner 2012; Mayr and Bryck 2007).
 
-Selective attention processes are commonly investigated using interference paradigms such as the Stroop [-@stroop_studies_1935] and flanker [@eriksen_effects_1974] tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor.
-Performance is typically better on congruent versus incongruent trials and the difference-the congruency effect-taken as an index of attentional priorities.
-Large congruency effects are thought to reflect ineffective filtering of the distracting stimuli whereas small congruency effects are thought to reflect effective filtering.
-By probing factors that systematically alter congruency effects, we can then make inferences about processes that control attentional filtering.
-For example, manipulating the frequency of conflict via the proportion of congruent versus incongruent trials has shown to influence the size of the congruency effect.
-Typically, a high proportion congruent experiment produces large congruency effects, whereas a low proportion congruent experiment produces small congruency effects [@logan_when_1979; @lowe_selective_1982; @west_effects_1998].
-This result is usually  explained as strategic control, where participants increase attentional control under high-conflict demands and relax attentional control under low-conflict demands [@logan_attention_1980; @logan_strategies_1984; @logan_when_1979; @lowe_selective_1982].
-Recent work however, has demonstrated that attentional control is not only adjusted by top-down regulation, but can also be triggered automatically by environmental cues [@brosowsky_memory-guided_2018; @bugg_support_2012; @egner_creatures_2014; @fischer_predicting_2015; @king_priming_2012; @mayr_outsourcing_2007].
+For example, Crump, Gong, and Milliken (Crump, Gong, and Milliken 2006; see
+also, Corballis and Gratton 2003) presented Stroop stimuli in one of two
+randomly chosen locations and manipulated the frequency of conflict associated
+with each location. One location was associated with a high frequency of
+conflict (25% congruent trials) and the other with a low frequency of conflict
+(75% congruent trials). Overall, the proportion of congruent trials was 50% and
+randomized such that the upcoming location could not be predicted. Even so,
+congruency effects were shown to be smaller for trials where the stimulus
+appeared in the high conflict location as compared to the low conflict location.
+This effect, known now as the context-specific proportion congruent effect
+(CSPC), has now been replicated in a number of different selective attention
+paradigms (e.g., Alards-Tomalin, Brosowsky, and Mondor 2017; Blais et al. 2015;
+Bugg 2014; Crump et al. 2018; Crump 2016; Fischer, Gottschalk, and Dreisbach
+2014; Hübner and Mishra 2016).
 
-For example, Crump, Gong, and Milliken [@crump_context-specific_2006; see also, @corballis_independent_2003] presented Stroop stimuli in one of two randomly chosen locations and manipulated the frequency of conflict associated with each location.
-One location was associated with a high frequency of conflict (25% congruent trials) and the other with a low frequency of conflict (75% congruent trials).
-Overall, the proportion of congruent trials was 50% and randomized such that the upcoming location could not be predicted.
-Even so, congruency effects were shown to be smaller for trials where the stimulus appeared in the high conflict location as compared to the low conflict location.
-This effect, known now as the context-specific proportion congruent effect (CSPC), has now been replicated in a number of different selective attention paradigms [e.g., @alards-tomalin_auditory_2017; @blais_trial-by-trial_2015; @bugg_conflict-triggered_2014; @crump_context-dependent_2018; @crump_learning_2016; @fischer_context-sensitive_2014; @hubner_location-specific_2016].
+Critical evidence however, that CSPC effects reflect context-specific control
+rather than other non-control learning processes (e.g., Schmidt and Besner
+2008), comes from work showing that CSPC effects can transfer to frequency
+unbiased items (Brosowsky and Crump 2016; Crump and Milliken 2009; Weidler, Dey,
+and Bugg 2018; Weidler and Bugg 2016; though, see Hutcheon and Spieler 2017).
+Crump and Milliken (2009), for example, divided Stroop items into two mutually
+exclusive sets (e.g., RED/GREEN and BLUE/YELLOW). One set was defined as the
+frequency biased set, and presented with 75% congruency in one location, and 25%
+congruency in the other. The second set however, was presented with 50%
+congruency in both locations. Nevertheless, they found smaller congruency
+effects for unbiased items presented in the high conflict location as compared
+to the low conflict location.
 
-Critical evidence however, that CSPC effects reflect context-specific control rather than other non-control learning processes [e.g., @schmidt_stroop_2008], comes from work showing that CSPC effects can transfer to frequency unbiased items [@brosowsky_context-specific_2016; @crump_flexibility_2009; @weidler_attentional_2018; @weidler_transfer_2016; though, see @hutcheon_limits_2017].
-Crump and Milliken (2009), for example, divided Stroop items into two mutually exclusive sets (e.g., RED/GREEN and BLUE/YELLOW).
-One set was defined as the frequency biased set, and presented with 75% congruency in one location, and 25% congruency in the other.
-The second set however, was presented with 50% congruency in both locations.
-Nevertheless, they found smaller congruency effects for unbiased items presented in the high conflict location as compared to the low conflict location.
+One explanation for CSPC effects is that the repeated application of attentional
+priorities in a particular context creates an associative link in episodic
+memory between the attentional control procedures and the contextual information
+(Abrahamse et al. 2016; Brosowsky and Crump 2018; Crump 2016; Egner 2014). Once
+the associative link is established, processing the context is assumed to
+trigger the retrieval of previous experiences, automatically reinstating the
+associated attentional priorities. Although this explanation seems plausible, it
+remains largely unclear how such associations are established and perhaps more
+importantly, it remains unclear what determines which learned associations will
+be used to guide attention at any given moment.
 
-One explanation for CSPC effects is that the repeated application of attentional priorities in a particular context creates an associative link in episodic memory between the attentional control procedures and the contextual information [@abrahamse_grounding_2016; @brosowsky_memory-guided_2018; @crump_learning_2016; @egner_creatures_2014].
-Once the associative link is established, processing the context is assumed to trigger the retrieval of previous experiences, automatically reinstating the associated attentional priorities.
-Although this explanation seems plausible, it remains largely unclear how such associations are established and perhaps more importantly, it remains unclear what determines which learned associations will be used to guide attention at any given moment.
+The importance of the latter issue becomes increasingly clear if we speculate
+about context-specificity in more complex, real-world environments. Consider
+myself, right now, writing this article in a coffee shop. The coffee shop is a
+complex environment that contains a multitude of contextual cues (e.g., pictures
+on the wall, chairs, coffee, laptop), each of which I have had many different
+experiences applying attentional control. Although my laptop might cue
+attentional processing helpful for finishing this article, other features of the
+coffee shop might cue other, unhelpful attentional processing related to other
+experiences like socializing and people-watching. This is all to say that our
+environments, and experiences within them, afford many different associative
+relationships between cognitive processing and environmental cues. What then
+determines which associative relationships will be used to guide attention (or
+even if such associative relationships are used at all)?
 
-The importance of the latter issue becomes increasingly clear if we speculate about context-specificity in more complex, real-world environments.
-Consider myself, right now, writing this article in a coffee shop.
-The coffee shop is a complex environment that contains a multitude of contextual cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which I have had many different experiences applying attentional control.
-Although my laptop might cue attentional processing helpful for finishing this article, other features of the coffee shop might cue other, unhelpful attentional processing related to other experiences like socializing and people-watching.
-This is all to say that our environments, and experiences within them, afford many different associative relationships between cognitive processing and environmental cues.
-What then determines which associative relationships will be used to guide attention (or even if such associative relationships are used at all)?
+Task-relevance might be one factor that is important for establishing and using
+context-attention associations. This proposal might seem counter-intuitive as it
+is typically assumed that the context, within selective attention tasks at
+least, is completely irrelevant to the task. In fact, referring to such stimulus
+dimensions as the "context" carries with it an implication that the feature is
+background information, irrelevant to the task-at-hand, and should be ignored by
+the participant. A closer look at CSPC designs however, suggests that the
+context cues may not be as irrelevant as implied. For example, the most commonly
+used context cue is location (Brosowsky and Crump 2016; Corballis and Gratton
+2003; Crump, Gong, and Milliken 2006; Crump, Vaquero, and Milliken 2008; Crump
+2016; Weidler, Dey, and Bugg 2018; Weidler and Bugg 2016). Although in some
+sense, the location is irrelevant for identifying the color of a word, it seems
+disingenuous to consider it completely task-irrelevant. In order to identify the
+target, the participant must first identify and orient to its location on the
+screen. In this is sense, it is relevant to their ability to complete the task
+and furthermore, location information may receive priority during encoding
+(Logan 1998; Mayr 1996). Similar arguments could be made about other context
+features that are inherent to processing the target stimulus, like font-type
+(Bugg, Jacoby, and Toth 2008) and color (Vietze and Wendt 2009).
 
-Task-relevance might be one factor that is important for establishing and using context-attention associations.
-This proposal might seem counter-intuitive as it is typically assumed that the context, within selective attention tasks at least, is completely irrelevant to the task.
-In fact, referring to such stimulus dimensions as the "context" carries with it an implication that the feature is background information, irrelevant to the task-at-hand, and should be ignored by the participant.
-A closer look at CSPC designs however, suggests that the context cues may not be as irrelevant as implied.
-For example, the most commonly used context cue is location [@brosowsky_context-specific_2016; @corballis_independent_2003; @crump_context-specific_2006; @crump_context-specific_2008; @crump_learning_2016; @weidler_attentional_2018; @weidler_transfer_2016].
-Although in some sense, the location is irrelevant for identifying the color of a word, it seems disingenuous to consider it completely task-irrelevant.
-In order to identify the target, the participant must first identify and orient to its location on the screen.
-In this is sense, it is relevant to their ability to complete the task and furthermore, location information may receive priority during encoding [@logan_what_1998; @mayr_spatial_1996].
-Similar arguments could be made about other context features that are inherent to processing the target stimulus, like font-type [@bugg_multiple_2008] and color [@vietze_context_2009].
+To date, we are aware of only one study that has looked at task-relevance within
+the CSPC literature. Crump, Vaquero, & Milliken (2008) used a Stroop prime-probe
+task where the distractor word is presented first followed by a color patch
+probe. Critically, they used the shape of the color patch probe, either a square
+or a circle, as the contextual dimension; one associated with a high frequency
+of conflict, the other with a low frequency. In one experiment participants were
+made aware of the shape-proportion contingencies but given no additional
+instructions. In the second, participants were given a secondary task to count
+the number of trials that contained a square. The first experiment failed to
+find evidence for context-specificity, whereas the second did. Although not
+testing task-relevance directly, Cañadas et al. (2013)\] found similar effects.
+In this study they used images of male and female faces as context cues in a
+flanker task. When given instructions to think of the faces as members of the
+gender categories they found CSPC effects, but when given instructions to think
+of the faces as individuals they did not. These results suggest that making a
+context dimension relevant to the on-going task is important for producing CSPC
+effects.
 
-To date, we are aware of only one study that has looked at task-relevance within the CSPC literature.
-Crump, Vaquero, & Milliken [-@crump_context-specific_2008] used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe.
-Critically, they used the shape of the color patch probe, either a square or a circle, as the contextual dimension; one associated with a high frequency of conflict, the other with a low frequency.
-In one experiment participants were made aware of the shape-proportion contingencies but given no additional instructions.
-In the second, participants were given a secondary task to count the number of trials that contained a square.
-The first experiment failed to find evidence for context-specificity, whereas the second did.
-Although not testing task-relevance directly, [-@canadas_social_2013]) found similar effects.
-In this study they used images of male and female faces as context cues in a flanker task.
-When given instructions to think of the faces as members of the gender categories they found CSPC effects, but when given instructions to think of the faces as individuals they did not.
-These results suggest that making a context dimension relevant to the on-going task is important for producing CSPC effects.
+The Current Study
+=================
 
-# The Current Study
+Prior work suggests that the task-relevance of contextual information is
+important for establishing new associations between context cues and attentional
+priorities. Simply put, CSPC effects emerge when context cues are somehow made
+relevant to the task, but do not when made irrelevant (Cañadas et al. 2013;
+Crump, Gong, and Milliken 2006; Crump, Vaquero, and Milliken 2008). However, it
+still remains unclear how task-relevance may or may not inform the use of
+previously learned associations. In the current study, we examined whether
+manipulating task-relevance would cause participants to ignore a previously
+learned association and adopt a new context-specific control strategy.
 
-Some prior suggests that the task-relevance of contextual information is important for establishing new associations between context cues and attentional priorities.
-Simply put, CSPC effects emerge when context cues are somehow made relevant to the task, but do not when made irrelevant [@canadas_social_2013; @crump_context-specific_2006; @crump_context-specific_2008].
-However, it still remains unclear how task-relevance may or may not inform the use of previously learned associations.
-In the current study, we examined whether manipulating task-relevance would cause participants to ignore a previously learned association and adopt a new context-specific control strategy.
+A flanker task was used to measure attentional control in an adapted CSPC design
+(Crump and Milliken 2009; Crump, Brosowsky, and Milliken 2017). Similar to
+previous studies, flanker stimuli were presented in contexts associated with
+differing levels of conflict (0%, 50%, or 100% congruent). However, unlike
+previous CSPC designs where contexts were defined by a single discriminating
+feature (e.g., upper vs. lower screen locations), contexts were defined by two
+feature dimensions (see Figure 1A). In one condition, for example, contexts were
+defined by object identity (hat or chair) and color (blue or green). Only three
+out of the four possible feature combinations were presented, each associated
+with a different proportion of congruent trials (0%, 50%, or 100% congruent).
+Critically, the frequency unbiased context (50% congruent) always shared a
+feature with each of the frequency-biased contexts (0% and 100% congruent). The
+frequency biased contexts (0% and 100% congruent) however, did not share any
+features (see Figure 1C for an example).
 
-A flanker task was used to measure attentional control in an adapted CSPC design [@crump_flexibility_2009; @crump_reproducing_2017].
-Similar to previous studies, flanker stimuli were presented in contexts associated with differing levels of conflict (0%, 50%, or 100% congruent).
-However, unlike previous CSPC designs where contexts were defined by a single discriminating feature (e.g., upper vs.
-lower screen locations), contexts were defined by two feature dimensions (see Figure 1A).
-In one condition, for example, contexts were defined by object identity (hat or chair) and color (blue or green).
-Only three out of the four possible feature combinations were presented, each associated with a different proportion of congruent trials (0%, 50%, or 100% congruent).
-Critically, the frequency unbiased context (50% congruent) always shared a feature with each of the frequency-biased contexts (0% and 100% congruent).
-The frequency biased contexts (0% and 100% congruent) however, did not share any features (see Figure 1C for an example).
+A secondary counting task was used to manipulate the task-relevance of the
+context dimensions (Crump and Milliken 2009) which critically, switched halfway
+through the experiment. Participants were instructed to keep a running count of
+one of the overlapping features (e.g., "count whenever a hat is presented")
+which was associated with either a high or low frequency of conflict. Halfway
+through the experiment they received new instructions to count the other
+overlapping feature (e.g., "count whenever a green item is presented").
+Critically, the set of context images remained the same throughout the
+experiment (see Figure 1C for an example) and the task-relevance of the context
+dimensions was the only aspect of the experiment that changed from the first to
+second phases.
 
-A secondary counting task was used to manipulate the task-relevance of the context dimensions [@crump_flexibility_2009] which critically, switched halfway through the experiment.
-Participants were instructed to keep a running count of one of the overlapping features (e.g., "count whenever a hat is presented") which was associated with either a high or low frequency of conflict.
-Halfway through the experiment they received new instructions to count the other overlapping feature (e.g., "count whenever a green item is presented").
-Critically, the set of context images remained the same throughout the experiment (see Figure 1C for an example) and the task-relevance of the context dimensions was the only aspect of the experiment that changed from the first to second phases.
+The critical measure of interest is the congruency effect produced in the
+frequency unbiased context. If, on the one hand, task-relevance has no impact on
+the use of context-attention associations we would expect no differences between
+the congruency effects when the high-conflict context dimension is made
+task-relevant or the low-conflict context dimension is made task-relevant. This
+could occur because all three contexts are treated as individual contexts
+throughout the whole experiment (e.g., Cañadas et al. 2013). Or it could occur
+because associations formed in the first block interfere with learning new
+associations in the second (e.g., Brosowsky and Crump 2016). On other hand,
+task-relevance might not only dictate how associations are formed, but also
+whether learned associations are used. In this case, we would expect smaller
+congruency effects when the high-conflict context dimension is made
+task-relevant as compared to when the low-conflict context dimension is made
+task-relevant. This would demonstrate that participants were able to ignore a
+previously learned association and adopt a new context-specific control
+strategy.
 
-The critical measure of interest is the congruency effect produced in the frequency unbiased context.
-If, on the one hand, task-relevance has no impact on the use of context-attention associations we would expect no differences between the congruency effects when the high-conflict context dimension is made task-relevant or the low-conflict context dimension is made task-relevant.
-This could occur because all three contexts are treated as individual contexts throughout the whole experiment [e.g., @canadas_social_2013].
-Or it could occur because associations formed in the first block interfere with learning new associations in the second [e.g., @brosowsky_context-specific_2016].
-On other hand, task-relevance might not only dictate how associations are formed, but also whether learned associations are used.
-In this case, we would expect that there will be smaller congruency effects when the high-conflict context dimension is made task-relevant as compared to when the low-conflict context dimension is made task-relevant.
-This would demonstrate that participants were able to ignore a previously learned association and adopt a new context-specific control strategy.
+A secondary goal was to conceptually replicate previous findings and test the
+generalizability of any task-relevance effects. Therefore, we included three
+conditions that differed only in the kinds of stimuli used to create context
+cues. In one condition we used face images where context dimensions were defined
+by social categories, similar to Cañadas et al. (2013). However, they found that
+social categorization occurred spontaneously and it was unclear what impact that
+would have on the current results. Therefore, we included another condition that
+used images of simple objects where context dimensions were defined by object
+features. Finally, Cañadas et al. (2013) also found that context effects
+generalized to novel face images. In our third condition we used non-repeating
+face exemplars to examine whether any task-relevance effects would also
+generalize in our design or if learning would be image-specific.
 
-A secondary goal was to conceptually replicate previous findings and test the generalizability of any task-relevance effects.
-Therefore, we included three conditions that differed only in the kinds of stimuli used to create context cues.
-In one condition we used face images where context dimensions were defined by social categories, similar to Cañadas et al.,  [-@canadas_social_2013].
-However, they found that social categorization occurred spontaneously and it was unclear what impact that would have on the current results.
-Therefore, we included another condition that used images of simple objects where context dimensions were defined by object features.
-Finally, Cañadas et al.[-@canadas_social_2013] also found that context effects generalized to novel face images.
-In our third condition we used non-repeating face exemplars to examine whether any task-relevance effects would also generalize in our design or if learning would be image-specific.
+Methods
+=======
 
-# Methods
+(ref:figure1) Illustration of the stimuli and trial construction. Figure 1A
+shows the feature dimensions for each of the conditions. Figure 1B shows an
+example trial stimulus containing both the context and flanker images. Figure 1C
+shows an example of how feature dimensions could have been assigned to each
+proportion congruency (PC) condition, and an example of the secondary task
+assignments. The secondary task order, as well as the feature and congruency
+assignments were all randomized for each participant.
 
-(ref:figure1)
-Illustration of the stimuli and trial construction.
-Figure 1A shows the feature dimensions for each of the conditions.
-Figure 1B shows an example trial stimulus containing both the context and flanker images.
-Figure 1C shows an example of how feature dimensions could have been assigned to each proportion congruency (PC) condition, and an example of the secondary task assignments.
-The secondary task order, as well as the feature and congruency assignments were all randomized for each participant.
-
-```{r figure1, echo=FALSE, fig.cap="(ref:figure1)", fig.width=6.7,fig.height=4.51}
+```{r figure1, echo=FALSE, fig.width=6.7,fig.height=4.51, fig.cap='(ref:figure1)'}
 knitr::include_graphics("images/Task.jpg")
@@
 
-## Participants
+Participants
+------------
 
-All participants were recruited from Amazon Mechanical Turk (AMT) and compensated $2.00 for participating.
-The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by $6.00 per hour.
-For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study.
-Participants were included in the study if they completed all trials.
-We posted 150 HITs and 145 participants completed all trials.
+All participants were recruited from Amazon Mechanical Turk (AMT) and
+compensated \$2.00 for participating. The amount compensated was calculated by
+estimating the maximum amount of time required to complete each experiment and
+multiplying by \$6.00 per hour. For each experiment the number of HITs (Human
+intelligence tasks, an Amazon term for a work-unit) refers to the number of
+participants who initiated the study. Participants were included in the study if
+they completed all trials. We posted 150 HITs and 144 participants completed all
+trials.
 
-## Apparatus & Stimuli
+Apparatus & Stimuli
+-------------------
 
-The experiments were programmed using JavaScript, CSS and HTML.
-The program allowed participants to complete task only if they were running Safari, Google Chrome, or Firefox web browsers.
-Flanker stimuli consisted of images of five arrows pointed left or right presented at 250 x 50 pixels (each arrow was 50 x 50 pixels).
-Context stimuli were constructed using images selected from @brady_visual_2013 color-rotated to blue and green, and face images from the Chicago Face Database [@ma_chicago_2015], supplemented with the NimStim Set of Facial Expressions [@tottenham_nimstim_2009].
-The object images were displayed at 250 x 250 pixels, while the face images were displayed at 250 x 313 pixels.
-The experiment ran as a pop-up window that filled the entire screen.
-The background was white, and stimuli were presented in the center of the screen.
+The experiments were programmed using JavaScript, CSS and HTML. The program
+allowed participants to complete task only if they were running Safari, Google
+Chrome, or Firefox web browsers. Flanker stimuli consisted of images of five
+arrows pointed left or right presented at 250 x 50 pixels (each arrow was 50 x
+50 pixels). Context stimuli were constructed using images selected from Brady et
+al. (2013) color-rotated to blue and green, and face images from the Chicago
+Face Database (Ma, Correll, and Wittenbrink 2015), supplemented with the NimStim
+Set of Facial Expressions (Tottenham et al. 2009). The object images were
+displayed at 250 x 250 pixels, while the face images were displayed at 250 x 313
+pixels. The experiment ran as a pop-up window that filled the entire screen. The
+background was white, and stimuli were presented in the center of the screen.
 
-Design.
-Experiment 1 used a 2x2x3 mixed design with task-relevant context (0% and 100%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
-All three conditions were constructed using the same general method.
-The experiment was divided into two phases.
-Each phase consisted of 144 flanker trials (48 trials per context), and 13 count response trials for a total of 314 trials.
-On the count response trials, participants indicated how many trials they had counted until that point.
-The count response trials occurred once for every 12 flanker trials and was randomly inserted between trial 6 and 12 of each 12-trial block.
-Each phase ended with one additional count response trial.
+Design. Experiment 1 used a 2x2x3 mixed design with task-relevant context (0%
+and 100%) and unbiased-item congruency (congruent and incongruent) as
+within-subject factors, and context-type (object, social, and
+social/non-repeating) as the between-subjects factor. All three conditions were
+constructed using the same general method. The experiment was divided into two
+phases. Each phase consisted of 144 flanker trials (48 trials per context), and
+13 count response trials for a total of 314 trials. On the count response
+trials, participants indicated how many trials they had counted until that
+point. The count response trials occurred once for every 12 flanker trials and
+was randomly inserted between trial 6 and 12 of each 12-trial block. Each phase
+ended with one additional count response trial.
 
-On every flanker trial, participants were presented with flanker stimuli paired with one of three contexts.
-Each context was associated with a different proportion congruency such that two cues were associated with a biased frequency (0% and 100% proportion congruency), while one was associated with an unbiased frequency (50% proportion congruency).
-The feature dimensions and corresponding context images assigned to each of the biased and unbiased item sets were randomly determined for each participant.
-However, context images used for the frequency biased trials never shared features, while the frequency unbiased context image always shared a feature with each of the frequency biased context images (see Figure 1).
-Additionally, the feature assignments remained the same throughout phases 1 and 2, and critically, the only change to the task was which feature the participant was instructed to count (see Figure 1C for an example).
+On every flanker trial, participants were presented with flanker stimuli paired
+with one of three contexts. Each context was associated with a different
+proportion congruency such that two cues were associated with a biased frequency
+(0% and 100% proportion congruency), while one was associated with an unbiased
+frequency (50% proportion congruency). The feature dimensions and corresponding
+context images assigned to each of the biased and unbiased item sets were
+randomly determined for each participant. However, context images used for the
+frequency biased trials never shared features, while the frequency unbiased
+context image always shared a feature with each of the frequency biased context
+images (see Figure 1). Additionally, the feature assignments remained the same
+throughout phases 1 and 2, and critically, the only change to the task was which
+feature the participant was instructed to count (see Figure 1C for an example).
 
-All critical aspects of the task were randomized between participants.
-This includes the three chosen context images, the features assigned to proportion levels, the features assigned to each counting condition, the secondary task order, and the order of trials.
+All critical aspects of the task were randomized between participants. This
+includes the three chosen context images, the features assigned to proportion
+levels, the features assigned to each counting condition, the secondary task
+order, and the order of trials.
 
-## Procedure
+Procedure
+---------
 
 All participants were AMT workers who found the experiment using the AMT system.
-The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board.
-Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form.
-Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window.
-Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing 'z' if the arrow pointed left, and 'm' if the arrow pointed right.
-Additionally, they were instructed to silently keep count of the number of trials that contained a feature.
-In the object context condition, they were asked to count trials that contained a certain color (blue or green) or object-identity (hat or chair) and in the social context conditions they were asked to count the number of trials that contained appeared a certain gender (male or female) or race (black or white).
-Periodically throughout the experiment, participants were asked to report how many trials they had counted until that point and to restart their count from 0.
-Halfway through the experiment participants received new instructions about which feature to count (see Figure 1C).
-Each trial began with a blank inter-stimulus interval (ISI) of 400 ms, followed by a fixation cross presented in the center of the screen for 200 ms, then a second blank ISI of 400 ms.
-Next, the flanker and context stimuli appeared in the center of screen (the flanker above the context image; see Figure 1B) and remained on screen until a response was made.
-Following a response, accuracy feedback was presented for 1000 ms.
-A response automatically triggered the next trial.
-Halfway through the experiment (157 trials), participants received new instructions about which feature to count and to press the button on-screen when they were ready to continue.
+The participant recruitment procedure and tasks were approved by the Brooklyn
+College Institutional Review Board. Each participant read a short description of
+the task and gave consent by pressing a button acknowledging they had read the
+displayed consent form. Participants then completed a short demographic survey,
+and proceeded to the main task, which was displayed as a pop-up window.
+Participants were instructed to identify the direction of the center arrow on
+each trial as quickly and accurately as possible by pressing 'z' if the arrow
+pointed left, and 'm' if the arrow pointed right. Additionally, they were
+instructed to silently keep count of the number of trials that contained a
+feature. In the object context condition, they were asked to count trials that
+contained a certain color (blue or green) or object-identity (hat or chair) and
+in the social context conditions they were asked to count the number of trials
+that contained appeared a certain gender (male or female) or race (black or
+white). Periodically throughout the experiment, participants were asked to
+report how many trials they had counted until that point and to restart their
+count from 0. Halfway through the experiment participants received new
+instructions about which feature to count (see Figure 1C). Each trial began with
+a blank inter-stimulus interval (ISI) of 400 ms, followed by a fixation cross
+presented in the center of the screen for 200 ms, then a second blank ISI of 400
+ms. Next, the flanker and context stimuli appeared in the center of screen (the
+flanker above the context image; see Figure 1B) and remained on screen until a
+response was made. Following a response, accuracy feedback was presented for
+1000 ms. A response automatically triggered the next trial. Halfway through the
+experiment (157 trials), participants received new instructions about which
+feature to count and to press the button on-screen when they were ready to
+continue.
 
-# Results
+Results
+=======
 
@@
 source("data-analysis/analysis.R")
-
 ```
 
-(ref:figure2)
-Results from experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent).
+(ref:figure2) Results from experiment 1 showing congruency effects (incongruent
+- congruent) for frequency unbiased items in reaction times (left) and error
+rates (right) as a function of the task-relevant context (100% proportion
+congruent versus 0% proportion congruent).
 
-```{r figure2, echo=FALSE, fig.cap="(ref:figure2)", fig.width=6.875, fig.height= 4}
+```{r figure2, echo=FALSE,fig.width=6.875, fig.height= 4, fig.cap='(ref:figure2)'}
 figure2
@@
 
-Participants with mean error rates greater than 25% were excluded from the analyses, eliminating `r N_subjects_removed` participants.
-For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure.
-The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms [@van_selst_solution_1994].
-This procedure removed `r round(percent_removed*100,digits = 2)`% of the total observations.
+Participants with mean error rates greater than 25% were excluded from the
+analyses, eliminating `r N_subjects_removed` participants. For all remaining participants,
+the correct RTs from frequency unbiased trials in each condition were submitted
+to an outlier removal procedure. The non-recursive Van Selst and Jolicoeur
+outlier removal procedure was applied after removing response times greater than
+3000 ms (Van Selst and Jolicoeur 1994). This procedure removed `r round(percent_removed*100,digits = 2)`% of
+the total observations.
 
-The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1).
-To that end, mean correct RTs and mean error rates from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0% and 100% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+The primary question of interest was whether the task-relevance of context
+features associated with different levels of conflict would influence the size
+of the congruency effect for frequency unbiased items (see Table 1). To that
+end, mean correct RTs and mean error rates from frequency unbiased trials were
+submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0%
+and 100% PC) and unbiased-item congruency (congruent and incongruent) as
+within-subject factors, and context-type (object, social, and
+social/non-repeating) as the between-subjects factor.
 
-The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, `r RT_ANOVA$Task_Relevant_Context_Congruency`, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
-Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, `r RT_ANOVA$Condition_Task_Relevant_Context_Congruency`, showing no evidence for differences between the CSPC effects across context-type manipulations.
+The results of the RT analysis revealed the critical, two-way interaction
+between task-relevant context and unbiased-item congruency to be significant,
+$F(1,128) = 8.30$`r RT_ANOVA$Task_Relevant_Context_Congruency` $\text{MSE} = 1,608.54$`r RT_ANOVA$Task_Relevant_Context_Congruency`
+$p = .005$`r RT_ANOVA$Task_Relevant_Context_Congruency` ${\widehat{\eta}}_{p}^{2} = .061$, demonstrating smaller
+congruency effects when the context dimension associated with high conflict was
+made task-relevant. Additionally, the three-way interaction between the
+task-relevant context, unbiased-item congruency, and context-type was
+non-significant, $F(2,128) = 0.00$`r RT_ANOVA$Condition_Task_Relevant_Context_Congruency`
+$\text{MSE} = 1,608.54$`r RT_ANOVA$Condition_Task_Relevant_Context_Congruency` $p = .996$`r RT_ANOVA$Condition_Task_Relevant_Context_Congruency`
+${\widehat{\eta}}_{p}^{2} = .000$, showing no evidence for differences between
+the CSPC effects across context-type manipulations.
 
-Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, `r RT_ANOVA$Task_Relevant_Context_Congruency`, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, `r RT_ANOVA$Condition_Task_Relevant_Context_Congruency`.
-Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.
+Similarly, the corresponding error analysis also resulted in a significant
+two-way interaction between the task-relevant context and unbiased-item
+congruency, $F(1,128) = 6.72$`r ACC_ANOVA$Task_Relevant_Context_Congruency` $\text{MSE} = 13.93$`r ACC_ANOVA$Task_Relevant_Context_Congruency`
+$p = .011$`r ACC_ANOVA$Task_Relevant_Context_Congruency` ${\widehat{\eta}}_{p}^{2} = .050$, and a non-significant
+three-way interaction between task-relevant context, unbiased-item congruency,
+and context-type, $F(2,128) = 0.92$`r ACC_ANOVA$Condition_Task_Relevant_Context_Congruency` $\text{MSE} = 13.93$`r ACC_ANOVA$Condition_Task_Relevant_Context_Congruency`
+$p = .400$`r ACC_ANOVA$Condition_Task_Relevant_Context_Congruency` ${\widehat{\eta}}_{p}^{2} = .014$. Therefore, the
+congruency effects in error rates were also smaller when the context dimension
+associated with high conflict was made task-relevant, corroborating the results
+of the reaction time analysis.
 
-# General Discussion
+General Discussion
+==================
 
-The aim of the current study was to investigate whether task-relevance plays a role in the contextual recruitment of selective attention.
-Specifically, we tested whether manipulating the relative task-relevance of context cues could cause participants to ignore a previously learned context-association and apply a new association.
-We created a frequency unbiased context cue that shared features with two frequency biased contexts and included a feature-counting task to manipulate the task-relevance of context dimensions across two blocks of trials.
-Critically, halfway through the experiment participants received new instructions changing the task-relevant feature from one frequency biased cue to the other.
+The aim of the current study was to investigate whether task-relevance plays a
+role in the contextual recruitment of selective attention. Specifically, we
+tested whether manipulating the relative task-relevance of context cues could
+cause participants to ignore a previously learned context-association and apply
+a new association. We created a frequency unbiased context cue that shared
+features with two frequency biased contexts and included a feature-counting task
+to manipulate the task-relevance of context dimensions across two blocks of
+trials. Critically, halfway through the experiment participants received new
+instructions changing the task-relevant feature from one frequency biased cue to
+the other.
 
-The key finding was that the congruency effects for the frequency unbiased items were significantly larger when the low-conflict context was made task-relevant as compared to when the high-conflict context was made task-relevant.
-This result is consistent with prior CSPC effects and, like the previous work, suggests that the context cues triggered rapid adjustments to attentional control [@crump_flexibility_2009].
-However, unlike prior studies, we were able to experimentally manipulate the CSPC effect across blocks of trials without changing any of the physical properties of the stimuli.
-This novel finding demonstrates that participants were able to learn and apply one context-attention association in the first phase, and subsequently ignore that association to learn a new association in the second phase.
+The key finding was that the congruency effects for the frequency unbiased items
+were significantly larger when the low-conflict context was made task-relevant
+as compared to when the high-conflict context was made task-relevant. This
+result is consistent with prior CSPC effects and, like the previous work,
+suggests that the context cues triggered rapid adjustments to attentional
+control (Crump and Milliken 2009). However, unlike prior studies, we were able
+to experimentally manipulate the CSPC effect across blocks of trials without
+changing any of the physical properties of the stimuli. This novel finding
+demonstrates that participants were able to learn and apply one
+context-attention association in the first phase, and subsequently ignore that
+association to learn a new association in the second phase.
 
-This result implicates an important role for task-relevance in producing CSPC phenomena.
-@crump_context-specific_2008 used shapes as context cues in a prime-probe Stroop task and did not find CSPC effects until the context cues were made task-relevant.
-Similarly, @canadas_social_2013 eliminated the CSPC effect by making the contextual cue effectively unrelated to the task.
-These studies suggest that task-relevance plays an important role in establishing associations between contextual information and attentional priorities to produce CSPC effects.
-Our finding extends this work in two important ways.
-First, we show that changing the task-relevance of the presented cues corresponded with a change in attentional control in the predicted direction.
-This demonstrates that task-relevance is also a key determinant of whether a previously learned attention-context association will be used or ignored in favor of a new association.
-Second, we show that task-relevance allowed participants resolve competition between two competing contextual cues, responding on the basis of one at the expense of the other.
-To our knowledge, this is the first demonstration that CSPC effects can be produced when there are multiple, overlapping contextual cues available.
+This result implicates an important role for task-relevance in producing CSPC
+phenomena. Crump, Vaquero, and Milliken (2008) used shapes as context cues in a
+prime-probe Stroop task and did not find CSPC effects until the context cues
+were made task-relevant. Similarly, Cañadas et al. (2013) eliminated the CSPC
+effect by making the contextual cue effectively unrelated to the task. These
+studies suggest that task-relevance plays an important role in establishing
+associations between contextual information and attentional priorities to
+produce CSPC effects. Our finding extends this work in two important ways.
+First, we show that changing the task-relevance of the presented cues
+corresponded with a change in attentional control in the predicted direction.
+This demonstrates that task-relevance is also a key determinant of whether a
+previously learned attention-context association will be used or ignored in
+favor of a new association. Second, we show that task-relevance allowed
+participants resolve competition between two competing contextual cues,
+responding on the basis of one at the expense of the other. To our knowledge,
+this is the first demonstration that CSPC effects can be produced when there are
+multiple, overlapping contextual cues available.
 
-In light of prior work, we take this as evidence that the contextual recruitment of selective attention, although likely implicit, is not obligatory [e.g., @brosowsky_context-specific_2016], requiring that environmental information be incorporated into the task representation.
-Similarly, there appears to be flexibility in which environmental features are selected and used to guide attention, which can be rapidly updated depending on the task-relevance of those features.
-Such a result lends some insight into how context-specific control might operate in more complex, real-world environments, where there is an over-abundance of environmental features that afford many different learned associations.
-From a theoretical perspective, this result is consistent memory-based accounts of CSPC phenomena [@brosowsky_memory-guided_2018; @bugg_converging_2013; @crump_context-dependent_2018; @crump_flexibility_2009; @crump_reproducing_2017].
-Under this view, a memory process encodes attentional priorities in the representation of individual experiences and, as a result, become associated with the environment where they were used.
-The subsequent reoccurrence of a prior context triggers the retrieval and reinstatement of those attentional priorities.
-Our results show however, that all the features of the environment may not be treated equally and that only task-relevant features are used to probe memory and guide attention.
+In light of prior work, we take this as evidence that the contextual recruitment
+of selective attention, although likely implicit, is not obligatory (e.g.,
+Brosowsky and Crump 2016), requiring that environmental information be
+incorporated into the task representation. Similarly, there appears to be
+flexibility in which environmental features are selected and used to guide
+attention, which can be rapidly updated depending on the task-relevance of those
+features. Such a result lends some insight into how context-specific control
+might operate in more complex, real-world environments, where there is an
+over-abundance of environmental features that afford many different learned
+associations. From a theoretical perspective, this result is consistent
+memory-based accounts of CSPC phenomena (Brosowsky and Crump 2018; Bugg and
+Hutchison 2013; Crump et al. 2018; Crump and Milliken 2009; Crump, Brosowsky,
+and Milliken 2017). Under this view, a memory process encodes attentional
+priorities in the representation of individual experiences and, as a result,
+become associated with the environment where they were used. The subsequent
+reoccurrence of a prior context triggers the retrieval and reinstatement of
+those attentional priorities. Our results show however, that all the features of
+the environment may not be treated equally and that only task-relevant features
+are used to probe memory and guide attention.
 
-Another key result of this study concerned the different stimuli used as context cues.
-Across the three conditions, we varied the type of context image and dimensions.
-We manipulated the type of image presented, including both objects (identity and color dimensions) and faces (gender and racial dimensions).
-We also manipulated whether a single set of three repeating images were presented (object and social) or a set of non-repeating images were presented (social/non-repeating).
-Across all three conditions, we found no evidence that using different stimuli had an influence on the size or direction of the CSPC demonstrating generalizability of this phenomenon.
-Furthermore, CSPC effects were present even when using non-repeating images which suggests that context-dependency did rely on image-specific associations but higher-order, learned categorical information.
+Another key result of this study concerned the different stimuli used as context
+cues. Across the three conditions, we varied the type of context image and
+dimensions. We manipulated the type of image presented, including both objects
+(identity and color dimensions) and faces (gender and racial dimensions). We
+also manipulated whether a single set of three repeating images were presented
+(object and social) or a set of non-repeating images were presented
+(social/non-repeating). Across all three conditions, we found no evidence that
+using different stimuli had an influence on the size or direction of the CSPC
+demonstrating generalizability of this phenomenon. Furthermore, CSPC effects
+were present even when using non-repeating images which suggests that
+context-dependency did rely on image-specific associations but higher-order,
+learned categorical information.
 
-Traditional models of person perception posit that social categories are automatically activated in the presence of social stimuli  [e.g., @brewer_dual_1988; @devine_stereotypes_1989; @fiske_continuum_1990].
-@canadas_social_2013 however, found that directing participants to think about faces in terms of individual features eliminated context-specific attention effect and suggested that momentary motivations may influence the automaticity of social categorization.
-Our results add to this literature by observing the influence of momentary motivations (i.e., task-relevance) when there is competition between two salient social categories.
-Specifically, we found that participants could categorize on the basis of one social cue at the expense of the other, and subsequently switch between them.
-These findings may speak to issues of automaticity in social categorization [@macrae_social_2001] as well as understanding how the situational context can prime one social identity over another [@crisp_multiple_2007].
-Furthermore, we found no evidence for differences between the social and object conditions.
-This suggests that categorization within the CSPC task is quickly and easily learned when the task supports such learning and is non-unique to social stimuli.
+Traditional models of person perception posit that social categories are
+automatically activated in the presence of social stimuli (e.g., Brewer 1988;
+Devine 1989; Fiske and Neuberg 1990). Cañadas et al. (2013) however, found that
+directing participants to think about faces in terms of individual features
+eliminated context-specific attention effect and suggested that momentary
+motivations may influence the automaticity of social categorization. Our results
+add to this literature by observing the influence of momentary motivations
+(i.e., task-relevance) when there is competition between two salient social
+categories. Specifically, we found that participants could categorize on the
+basis of one social cue at the expense of the other, and subsequently switch
+between them. These findings may speak to issues of automaticity in social
+categorization (Macrae and Bodenhausen 2001) as well as understanding how the
+situational context can prime one social identity over another (Crisp and
+Hewstone 2007). Furthermore, we found no evidence for differences between the
+social and object conditions. This suggests that categorization within the CSPC
+task is quickly and easily learned when the task supports such learning and is
+non-unique to social stimuli.
 
-In sum, our results provide new evidence that changes in task-relevance can update the contextual recruitment of selective attention in a CSPC flanker task.
-Importantly, we show that making one feature task-relevant produced a CSPC effect, even in the presence of a competing contextual cue.
-Moreover, changing the task-relevant context-cue midway through the experiment was accompanied by predictable changes in the congruency effects.
-This effect was found to be generalizable across two different kinds of stimuli and occurred even when using non-repeating images.
-These results implicate an important role for task-relevance in producing context-dependency and are consistent with memory-based accounts of CSPC phenomena.
+In sum, our results provide new evidence that changes in task-relevance can
+update the contextual recruitment of selective attention in a CSPC flanker task.
+Importantly, we show that making one feature task-relevant produced a CSPC
+effect, even in the presence of a competing contextual cue. Moreover, changing
+the task-relevant context-cue midway through the experiment was accompanied by
+predictable changes in the congruency effects. This effect was found to be
+generalizable across two different kinds of stimuli and occurred even when using
+non-repeating images. These results implicate an important role for
+task-relevance in producing context-dependency and are consistent with
+memory-based accounts of CSPC phenomena.
 
-\newpage
+References
+==========
 
-# References
+Abrahamse, Elger, Senne Braem, Wim Notebaert, and Tom Verguts. 2016. "Grounding
+Cognitive Control in Associative Learning." *Psychological Bulletin* 142:
+693--728. <https://doi.org/10.1037/bul0000047>.
 
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
+Alards-Tomalin, Doug, Nicholaus P. Brosowsky, and Todd A. Mondor. 2017.
+"Auditory Statistical Learning: Predictive Frequency Information Affects the
+Deployment of Contextually Mediated Attentional Resources on Perceptual Tasks."
+*Journal of Cognitive Psychology* 0 (0): 1--11.
+<https://doi.org/10.1080/20445911.2017.1353518>.
 
-<div id = "refs"></div>
-\endgroup
+Blais, Chris, Michael B. Harris, Michael H. Sinanian, and Silvia A. Bunge. 2015.
+"Trial-by-Trial Adjustments in Control Triggered by Incidentally Encoded
+Semantic Cues." *The Quarterly Journal of Experimental Psychology* 68: 1920--30.
+<https://doi.org/10.1080/17470218.2014.1000346>.
+
+Brady, Timothy F., Talia Konkle, Jonathan Gill, Aude Oliva, and George A.
+Alvarez. 2013. "Visual Long-Term Memory Has the Same Limit on Fidelity as Visual
+Working Memory." *Psychological Science* 24: 981--90.
+<https://doi.org/10.1177/0956797612465439>.
+
+Brewer, M. B. 1988. "A Dual Process Model of Impression Formation." In *A
+Dual-Process Model of Impression Formation: Advances in Social Cognition*,
+edited by Robert S. Wyer Jr and Thomas K. Srull, 1:1--36. Hillsdale, NJ:
+Erlbaum.
+
+Brosowsky, Nicholaus P., and Matthew J. C. Crump. 2018. "Memory-Guided Selective
+Attention: Single Experiences with Conflict Have Long-Lasting Effects on
+Cognitive Control." *Journal of Experimental Psychology: General*.
+<https://doi.org/10.1037/xge0000431>.
+
+Brosowsky, Nicholaus P., and Matthew J.C. Crump. 2016. "Context-Specific
+Attentional Sampling: Intentional Control as a Pre-Requisite for Contextual
+Control." *Consciousness and Cognition* 44: 146--60.
+<https://doi.org/10.1016/j.concog.2016.07.001>.
+
+Bugg, J.M. 2014. "Conflict-Triggered Top-down Control: Default Mode, Last
+Resort, or No Such Thing?" *Journal of Experimental Psychology: Learning,
+Memory, and Cognition* 40 (2): 567.
+
+Bugg, J.M., and Matthew J.C. Crump. 2012. "In Support of a Distinction Between
+Voluntary and Stimulus-Driven Control: A Review of the Literature on Proportion
+Congruent Effects." *Frontiers in Psychology* 3: 367.
+<https://doi.org/10.3389/fpsyg.2012.00367>.
+
+Bugg, J.M., and Keith A. Hutchison. 2013. "Converging Evidence for Control of
+Color--Word Stroop Interference at the Item Level." *Journal of Experimental
+Psychology: Human Perception and Performance* 39 (2): 433.
+
+Bugg, J.M., Larry L. Jacoby, and Jeffrey P. Toth. 2008. "Multiple Levels of
+Control in the Stroop Task." *Memory & Cognition* 36: 1484--94.
+<https://doi.org/10.3758/MC.36.8.1484>.
+
+Cañadas, Elena, Rosa Rodríguez-Bailón, Bruce Milliken, and Juan Lupiáñez. 2013.
+"Social Categories as a Context for the Allocation of Attentional Control."
+*Journal of Experimental Psychology: General* 142: 934--43.
+<https://doi.org/10.1037/a0029794>.
+
+Corballis, Paul M., and Gabriele Gratton. 2003. "Independent Control of
+Processing Strategies for Different Locations in the Visual Field." *Biological
+Psychology* 64: 191--209. <https://doi.org/10.1016/S0301-0511(03)00109-1>.
+
+Crisp, Richard J., and Miles Hewstone. 2007. "Multiple Social Categorization."
+*Advances in Experimental Social Psychology* 39: 163--254.
+
+Crump, Matthew J.C. 2016. "Learning to Selectively Attend from Context-Specific
+Attentional Histories: A Demonstration and Some Constraints." *Canadian Journal
+of Experimental Psychology/Revue Canadienne de Psychologie Expérimentale* 70:
+59--77. <https://doi.org/10.1037/cep0000066>.
+
+Crump, Matthew J.C., Nicholaus P. Brosowsky, and Bruce Milliken. 2017.
+"Reproducing the Location-Based Context-Specific Proportion Congruent Effect for
+Frequency Unbiased Items: A Reply to Hutcheon and Spieler (2016)." *The
+Quarterly Journal of Experimental Psychology* 70: 1792--1807.
+<https://doi.org/10.1080/17470218.2016.1206130>.
+
+Crump, Matthew J.C., Zhiyu Gong, and Bruce Milliken. 2006. "The Context-Specific
+Proportion Congruent Stroop Effect: Location as a Contextual Cue." *Psychonomic
+Bulletin & Review* 13: 316--21. <https://doi.org/10.3758/BF03193850>.
+
+Crump, Matthew J. C., B. Milliken, J. Leboe-McGowan, L. Leboe-McGowan, and X.
+Gao. 2018. "Context-Dependent Control of Attention Capture: Evidence from
+Proportion Congruent Effects." *Canadian Journal of Experimental Psychology=
+Revue Canadienne de Psychologie Experimentale*.
+
+Crump, Matthew J. C., and Bruce Milliken. 2009. "The Flexibility of
+Context-Specific Control: Evidence for Context-Driven Generalization of
+Item-Specific Control Settings." *The Quarterly Journal of Experimental
+Psychology* 62: 1523--32. <https://doi.org/10.1080/17470210902752096>.
+
+Crump, Matthew J.C., Joaquín M.M. Vaquero, and Bruce Milliken. 2008.
+"Context-Specific Learning and Control: The Roles of Awareness, Task Relevance,
+and Relative Salience." *Consciousness and Cognition* 17: 22--36.
+<https://doi.org/10.1016/j.concog.2007.01.004>.
+
+Devine, Patricia G. 1989. "Stereotypes and Prejudice: Their Automatic and
+Controlled Components." *Journal of Personality and Social Psychology* 56 (1):
+5.
+
+Egner, Tobias. 2014. "Creatures of Habit (and Control): A Multi-Level Learning
+Perspective on the Modulation of Congruency Effects." *Frontiers in Psychology*
+5: 1247. <https://doi.org/10.3389/fpsyg.2014.01247>.
+
+Eriksen, Barbara A., and Charles W. Eriksen. 1974. "Effects of Noise Letters
+Upon the Identification of a Target Letter in a Nonsearch Task." *Perception &
+Psychophysics* 16: 143--49. <https://doi.org/10.3758/BF03203267>.
+
+Fischer, Rico, and Gesine Dreisbach. 2015. "Predicting High Levels of
+Multitasking Reduces Between-Tasks Interactions."
+<http://psycnet.apa.org/psycinfo/2015-47211-001/>.
+
+Fischer, Rico, Caroline Gottschalk, and Gesine Dreisbach. 2014.
+"Context-Sensitive Adjustment of Cognitive Control in Dual-Task Performance."
+*Journal of Experimental Psychology: Learning, Memory, and Cognition* 40 (2):
+399.
+
+Fiske, Susan T., and Steven L. Neuberg. 1990. "A Continuum of Impression
+Formation, from Category-Based to Individuating Processes: Influences of
+Information and Motivation on Attention and Interpretation." In *Advances in
+Experimental Social Psychology*, 23:1--74. Elsevier.
+
+Hutcheon, Thomas G., and Daniel H. Spieler. 2017. "Limits on the
+Generalizability of Context-Driven Control." *Quarterly Journal of Experimental
+Psychology* 70 (7): 1292--1304. <https://doi.org/10.1080/17470218.2016.1182193>.
+
+Hübner, Ronald, and Shreyasi Mishra. 2016. "Location-Specific Attentional
+Control Is Also Possible in the Simon Task." *Psychonomic Bulletin & Review* 23:
+1867--72. <https://doi.org/10.3758/s13423-016-1057-y>.
+
+King, Joseph A., Franziska M. Korb, and Tobias Egner. 2012. "Priming of Control:
+Implicit Contextual Cuing of Top-down Attentional Set." *The Journal of
+Neuroscience* 32: 8192--8200. <https://doi.org/10.1523/JNEUROSCI.0934-12.2012>.
+
+Logan, Gordon D. 1980. "Attention and Automaticity in Stroop and Priming Tasks:
+Theory and Data." *Cognitive Psychology* 12 (4): 523--53.
+
+---------. 1998. "What Is Learned During Automatization? II. Obligatory Encoding
+of Spatial Location." *Journal of Experimental Psychology: Human Perception and
+Performance* 24 (6): 1720.
+
+Logan, Gordon D., and N. Jane Zbrodoff. 1979. "When It Helps to Be Misled:
+Facilitative Effects of Increasing the Frequency of Conflicting Stimuli in a
+Stroop-Like Task." *Memory & Cognition* 7: 166--74.
+<https://doi.org/10.3758/BF03197535>.
+
+Logan, Gordon D., N. Jane Zbrodoff, and James Williamson. 1984. "Strategies in
+the Color-Word Stroop Task." *Bulletin of the Psychonomic Society* 22 (2):
+135--38.
+
+Lowe, Douglas G., and John O. Mitterer. 1982. "Selective and Divided Attention
+in a Stroop Task." *Canadian Journal of Psychology/Revue Canadienne de
+Psychologie* 36 (4): 684.
+
+Ma, Debbie S., Joshua Correll, and Bernd Wittenbrink. 2015. "The Chicago Face
+Database: A Free Stimulus Set of Faces and Norming Data." *Behavior Research
+Methods* 47 (4): 1122--35. <https://doi.org/10.3758/s13428-014-0532-5>.
+
+Macrae, C. Neil, and Galen V. Bodenhausen. 2001. "Social Cognition: Categorical
+Person Perception." *British Journal of Psychology* 92 (1): 239--55.
+
+Mayr, Ulrich. 1996. "Spatial Attention and Implicit Sequence Learning: Evidence
+for Independent Learning of Spatial and Nonspatial Sequences." *Journal of
+Experimental Psychology: Learning, Memory, and Cognition* 22 (2): 350.
+
+Mayr, Ulrich, and Richard L. Bryck. 2007. "Outsourcing Control to the
+Environment: Effects of Stimulus/Response Locations on Task Selection."
+*Psychological Research* 71 (1): 107--16.
+<https://doi.org/10.1007/s00426-005-0039-x>.
+
+Schmidt, James R., and Derek Besner. 2008. "The Stroop Effect: Why Proportion
+Congruent Has Nothing to Do with Congruency and Everything to Do with
+Contingency." *Journal of Experimental Psychology: Learning, Memory, and
+Cognition* 34: 514--23. <https://doi.org/10.1037/0278-7393.34.3.514>.
+
+Stroop, J. Ridley. 1935. "Studies of Interference in Serial Verbal Reactions."
+*Journal of Experimental Psychology* 18: 643.
+<https://doi.org/10.1037/h0054651>.
+
+Tottenham, Nim, James W. Tanaka, Andrew C. Leon, Thomas McCarry, Marcella Nurse,
+Todd A. Hare, David J. Marcus, Alissa Westerlund, BJ Casey, and Charles Nelson.
+2009. "The NimStim Set of Facial Expressions: Judgments from Untrained Research
+Participants." *Psychiatry Research* 168 (3): 242--49.
+<https://doi.org/10.1016/j.psychres.2008.05.006>.
+
+Van Selst, Mark, and Pierre Jolicoeur. 1994. "A Solution to the Effect of Sample
+Size on Outlier Elimination." *The Quarterly Journal of Experimental Psychology
+Section A* 47: 631--50. <https://doi.org/10.1080/14640749408401131>.
+
+Vietze, Ina, and Mike Wendt. 2009. "Context Specificity of Conflict
+Frequency-Dependent Control." *The Quarterly Journal of Experimental Psychology*
+62: 1391--1400. <https://doi.org/10.1080/17470210802426908>.
+
+Weidler, Blaire J., and J.M. Bugg. 2016. "Transfer of Location-Specific Control
+to Untrained Locations." *The Quarterly Journal of Experimental Psychology* 69:
+2202--17. <https://doi.org/10.1080/17470218.2015.1111396>.
+
+Weidler, Blaire J., Abhishek Dey, and Julie M. Bugg. 2018. "Attentional Control
+Transfers Beyond the Reference Frame." *Psychological Research*, 1--14.
+
+West, Robert, and Gordon C. Baylis. 1998. "Effects of Increased Response
+Dominance and Contextual Disintegration on the Stroop Interference Effect in
+Older Adults." *Psychology and Aging* 13 (2): 206.
+
+Table 1
+-------
+
+### Reaction times and error rates from Experiment 1.
+
+\\begin{zeroindent}
+
+```{r tableLatex}
+
+if (knitr::opts_knit$get("rmarkdown.pandoc.to")== "latex"){
+source("data-analysis/table1.R")
+latexTable1
+
+}
+```
+
+\\end{zeroindent}
+
+```{r tableWord, echo=FALSE, out.width = '100%'}
+if (knitr::opts_knit$get("rmarkdown.pandoc.to")== "docx"){
+  knitr::include_graphics("data-analysis/table1.png")
+}
+
+```

### 2018-12-09 data-analysis/analysis.R

@@ -1,13 +1,25 @@
+
 library(dplyr)
 library(tidyr)
 library(afex)
 library(ggplot2)
 library(cowplot)
+library(tables)
+library(magrittr)
+library(kableExtra)
 #As of 2018/12/07 apa_print() requires development version of Papaja
 #devtools::install_github("crsh/papaja")
 library(papaja)
 
-load("data-analysis/raw_data.Rda")
+
+folderName <- function(){
+  wd<-getwd()
+  wd<-strsplit(wd,"/")
+  wd<-wd[[1]][length(wd[[1]])]
+  
+  return(wd)
+}
+
 
 vjoutNR <- function(x,n) {
   xm <- mean(x)
@@ -25,6 +37,10 @@ vjoutNR <- function(x,n) {
 }
 
 
+
+load("data-analysis/raw_data.Rda")
+
+
 # Find subs with < 75% accuracy
 low_acc <- raw_data %>%
   group_by(Subject,Condition,Task_Relevant_Context,Frequency,Congruency) %>%
@@ -34,7 +50,7 @@ low_acc <- raw_data %>%
 
 N_subjects_removed<-length(unique(low_acc))
 
-## Summarize by subject
+## summarise by subject
 RT.DF <- raw_data %>%
   filter(
     RT < 3000,
@@ -43,7 +59,7 @@ RT.DF <- raw_data %>%
     Subject%in%low_acc == FALSE
   ) %>%
   group_by(Condition,Subject,Order,Phase,Block,Frequency,Task_Relevant_Context,Congruency)%>%
-  summarize(vjoutRT = vjoutNR(RT,1))
+  summarise(vjoutRT = vjoutNR(RT,1))
 
 ## Find percentage of trials removed 
 percent_removed <- raw_data %>%
@@ -54,9 +70,9 @@ percent_removed <- raw_data %>%
     Subject%in%low_acc == FALSE
   ) %>%
   group_by(Condition,Subject,Order,Phase,Frequency,Task_Relevant_Context,Congruency)%>%
-  summarize(percent_removed = vjoutNR(RT,2)) %>%
+  summarise(percent_removed = vjoutNR(RT,2)) %>%
   ungroup() %>%
-  summarize(avg_removed = mean(percent_removed)) %>%
+  summarise(avg_removed = mean(percent_removed)) %>%
   .$avg_removed
 
 ## Analyze RTs for frequency unbiased items
[…]

### 2018-12-09 data-analysis/table1.R

@@ -1,0 +1,202 @@
+library(dplyr)
+library(tidyr)
+library(afex)
+library(ggplot2)
+library(cowplot)
+#library(tables)
+library(magrittr)
+library(kableExtra)
+#As of 2018/12/07 apa_print() requires development version of Papaja
+#devtools::install_github("crsh/papaja")
+library(papaja)
+
+
+folderName <- function(){
+  wd<-getwd()
+  wd<-strsplit(wd,"/")
+  wd<-wd[[1]][length(wd[[1]])]
+  
+  return(wd)
+}
+
+
+vjoutNR <- function(x,n) {
+  xm <- mean(x)
+  xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
+             25, 30, 35, 50, 80)
+  stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
+            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
+            2.45, 2.48, 2.5)
+  stdindex <- length(xsize[xsize <= length(x)])
+  removed <- x[x < xm+sd(x)*stds[stdindex]]
+  removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
+  proportionRemoved <- length(removed)/length(x)
+  finaldata<-c(mean(removed),1-proportionRemoved)
+  return(finaldata[[n]])
+}
+
+
+## manuscript.Rmd is called from parent
+load("data-analysis/raw_data.Rda")
+
+
+
+
+# Find subs with < 75% accuracy
+low_acc <- raw_data %>%
+  group_by(Subject,Condition,Task_Relevant_Context,Frequency,Congruency) %>%
+  summarise(meanAccuracy = mean(ACC)) %>%
+  filter(meanAccuracy < .75) %>%
+  .$Subject
+
+########## Create table
+
+
+## summarise by subject
+RT.DF <- raw_data %>%
+  filter(
+    RT < 3000,
+    RT > 0,
+    ACC == TRUE,
+    Subject%in%low_acc == FALSE
+  ) %>%
+  group_by(Condition,Subject,Frequency,Order,Phase,Block,Frequency,Task_Relevant_Context,Congruency)%>%
+  summarise(vjoutRT = vjoutNR(RT,1)) %>%
[…]

### 2018-12-09 manuscript.Rmd
first draft

@@
 Selective attention is commonly investigated using interference paradigms such as the Stroop [-@stroop_studies_1935] and flanker [@eriksen_effects_1974] tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor.
-Performance is typically better on congruent versus incongruent trials and the difference-the congruency effect-taken as an index of attentional priorities.
+Performance is typically better on congruent versus incongruent trials and the difference---the congruency effect---taken as an index of attentional priorities.
 Large congruency effects are thought to reflect ineffective filtering of the distracting stimuli whereas small congruency effects are thought to reflect effective filtering.

### 2018-12-09 manuscript.tex
first draft

@@
 Selective attention is commonly investigated using interference paradigms such as the Stroop (1935) and flanker (Eriksen \& Eriksen, 1974) tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor.
-Performance is typically better on congruent versus incongruent trials and the difference-the congruency effect-taken as an index of attentional priorities.
+Performance is typically better on congruent versus incongruent trials and the difference---the congruency effect---taken as an index of attentional priorities.
 Large congruency effects are thought to reflect ineffective filtering of the distracting stimuli whereas small congruency effects are thought to reflect effective filtering.

### 2018-12-10 manuscript.Rmd
first draft
update / clean up

@@
  # papaja::apa6_word: default
-  papaja::apa6_pdf: default
-  #redoc::rdocx_reversible
+#  papaja::apa6_pdf: default
+  redoc::rdocx_reversible
 
@@
 
-The importance of the latter issue becomes increasingly clear if we speculate about context-specificity in more complex, real-world environments.
+The importance of the latter issue may become clearer if we speculate about context-specificity in more complex, real-world environments.
 Consider myself, right now, writing this article in a coffee shop.
@@
 
+```{r figure1, echo=FALSE, fig.width=6.7,fig.height=4.51, fig.cap='(ref:figure1)'}
+knitr::include_graphics("images/Task.jpg")
+```
+
 (ref:figure1) Illustration of the stimuli and trial construction.
@@
 The secondary task order, as well as the feature and congruency assignments were all randomized for each participant.
-
-```{r figure1, echo=FALSE, fig.width=6.7,fig.height=4.51, fig.cap='(ref:figure1)'}
-knitr::include_graphics("images/Task.jpg")
-```
 
@@
 
-```{r analysis}
+```{r analysis, echo=FALSE, include=FALSE, eval=TRUE}
 source("data-analysis/analysis.R")
 ```
-
-(ref:figure2) Results from experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent).
 
@@
 ```
+
+(ref:figure2) Results from experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent).
 
@@
 
-![ ](images/table1.pdf) 
+![ ](images/table1.png) 
 \endgroup

### 2019-01-21 manuscript.Rmd
revised

--- 2018-12-09 manuscript.Rmd
@@
 
+mainfont: Times New Roman
 output:
- # papaja::apa6_word: default
+  #papaja::apa6_word: default
   papaja::apa6_pdf: default
@@
 header-includes:
-  - \usepackage{float}
-  - \usepackage{booktabs}
-  - \usepackage{longtable}
-  - \usepackage{array}
-  - \usepackage{multirow}
-  - \usepackage[table]{xcolor}
-  - \usepackage{wrapfig}
-  - \usepackage{colortbl}
-  - \usepackage{pdflscape}
-  - \usepackage{tabu}
-  - \usepackage{threeparttable}
-  - \usepackage{threeparttablex}
-  - \usepackage[normalem]{ulem}
-  - \usepackage{makecell}
-  - \usepackage{setspace}\singlespacing 
+  - \usepackage{setspace}\doublespacing 
   - \newenvironment{zeroindent}
@@
      {\par}  
-  - \setlength{\parskip}{0.25cm plus4mm minus3mm}
+  - \setlength{\parskip}{0pt}
+  - \raggedbottom
 
@@
 ```{r setup, include=FALSE, eval=TRUE,echo=FALSE}
-library("dplyr")
-library("afex")
-library("papaja")
-library("magrittr")
-library("kableExtra")
-
 #As of 2018/12/07 apa_print() requires development version of Papaja
@@
 library(papaja)
+
+source("data-analysis/analysis.R")
+source("data-analysis/table1.R")
 ```
@@
 One explanation for CSPC effects is that the repeated application of attentional priorities in a particular context creates an associative link in episodic memory between the attentional control procedures and the contextual information [@abrahamse_grounding_2016; @brosowsky_memory-guided_2018; @crump_learning_2016; @egner_creatures_2014].
-Once the associative link is established, processing the context is assumed to trigger the retrieval of previous experiences, automatically reinstating the associated attentional priorities.
-Although this explanation seems plausible, it remains largely unclear how such associations are established and perhaps more importantly, it remains unclear what determines which learned associations will be used to guide attention at any given moment.
+Once the associative link is established, processing the context is assumed to trigger the retrieval of previous experiences, automatically reinstating associated attentional priorities.
+As a result, automatic memory-based retrieval allows attentional priorities to be rapidly adjusted in a context-appropriate fashion.
+However, the obligatory nature of memory-based attentional control remains unclear, in particular in situations when multiple contextual features could be used as cues for retrieval.
 
-The importance of the latter issue becomes increasingly clear if we speculate about context-specificity in more complex, real-world environments.
-Consider myself, right now, writing this article in a coffee shop.
-The coffee shop is a complex environment that contains a multitude of contextual cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which I have had many different experiences applying attentional control.
-Although my laptop might cue attentional processing helpful for finishing this article, other features of the coffee shop might cue other, unhelpful attentional processing related to other experiences like socializing and people-watching.
-This is all to say that our environments, and experiences within them, afford many different associative relationships between cognitive processing and environmental cues.
-What then determines which associative relationships will be used to guide attention (or even if such associative relationships are used at all)?
+For example, real-world environments offer a plethora of context cues.
+Consider writing an article in a coffee shop.
+The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), and associated attentional priorities.
+Although a laptop might cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
+Given that all of these cues are available to set attentional priorities, what determines which associative relationships will be used to guide attention?
+On the one hand, context-based retrieval of attentional priorities might be completely obligatory and a writer's attention would be at the mercy of the environment.
+On the other hand, there is some evidence that contextual cuing of attention is not entirely obligatory and can be constrained by task goals, allowing the laptop to take priority as a contextual cue over other contextual cues that are irrelevant to the task at hand.
 
-Task-relevance might be one factor that is important for establishing and using context-attention associations.
-This proposal might seem counter-intuitive as it is typically assumed that the context, within selective attention tasks at least, is completely irrelevant to the task.
-In fact, referring to such stimulus dimensions as the "context" carries with it an implication that the feature is background information, irrelevant to the task-at-hand, and should be ignored by the participant.
-A closer look at CSPC designs however, suggests that the context cues may not be as irrelevant as implied.
-For example, the most commonly used context cue is location [@brosowsky_context-specific_2016; @corballis_independent_2003; @crump_context-specific_2006; @crump_context-specific_2008; @crump_learning_2016; @weidler_attentional_2018; @weidler_transfer_2016].
+Prior work shows that task-relevance is necessary for establishing and using context-attention associations.
+First, the most commonly used context cue is location [@brosowsky_context-specific_2016; @corballis_independent_2003; @crump_context-specific_2006; @crump_context-specific_2008; @crump_learning_2016; @weidler_attentional_2018; @weidler_transfer_2016].
 Although in some sense, the location is irrelevant for identifying the color of a word, it seems disingenuous to consider it completely task-irrelevant.
@@
 
-To date, we are aware of only one study that has looked at task-relevance within the CSPC literature.
+Second, we are aware of only one study that has looked at task-relevance within the CSPC literature.
 Crump, Vaquero, & Milliken [-@crump_context-specific_2008] used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe.
@@
 # Methods
+```{r figure1, echo=FALSE, fig.width=6.7,fig.height=4.51, fig.cap='(ref:figure1)'}
+knitr::include_graphics("images/Task.jpg")
+```
 
@@
 
-```{r figure1, echo=FALSE, fig.width=6.7,fig.height=4.51, fig.cap='(ref:figure1)'}
-knitr::include_graphics("images/Task.jpg")
-```
-
 ## Participants
-
 All participants were recruited from Amazon Mechanical Turk (AMT) and compensated $2.00 for participating.
@@
 
-Design.
+## Design 
 Experiment 1 used a 2x2x3 mixed design with task-relevant context (0% and 100%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
@@
 ## Procedure
-
 All participants were AMT workers who found the experiment using the AMT system.
@@
 Halfway through the experiment participants received new instructions about which feature to count (see Figure 1C).
+
 Each trial began with a blank inter-stimulus interval (ISI) of 400 ms, followed by a fixation cross presented in the center of the screen for 200 ms, then a second blank ISI of 400 ms.
@@
 A response automatically triggered the next trial.
+
 Halfway through the experiment (157 trials), participants received new instructions about which feature to count and to press the button on-screen when they were ready to continue.
 
-```{r analysis}
-source("data-analysis/analysis.R")
+```{r figure2, echo=FALSE,fig.width=6.875, fig.height= 4, fig.cap='(ref:figure2)'}
+#print figure 2
+#source: data-analysis/analysis.R
+figure2
 ```
@@
 
-```{r figure2, echo=FALSE,fig.width=6.875, fig.height= 4, fig.cap='(ref:figure2)'}
-figure2
-```
-
 # Results 
-
 Participants with mean error rates greater than 25% were excluded from the analyses, eliminating `r N_subjects_removed` participants.
@@
 
-\begingroup
-\setlength{\parindent}{0in}
-\vspace{2.5mm}
-\textbf{Table 1. \\ \textit{Reaction times and error rates from Experiment 1.}}
-
-![ ](images/table1.pdf) 
-\endgroup
+```{r echo = FALSE, warning = FALSE, message=FALSE, results='asis'}
+#print latex table
+cat(TR_Table)
+```
 
 # General Discussion
-
 The aim of the current study was to determine whether task-relevance plays a role in the contextual recruitment of selective attention.
@@
 \endgroup
-
-\newpage
-
-```{r tableLatex}
-#if (knitr::opts_knit$get("rmarkdown.pandoc.to")== "latex"){
-#source("data-analysis/table1.R")
-#latexTable1
-#}
-```

### 2019-01-21 manuscript.tex
first draft
update / clean up
revised

--- 2018-12-07 v1-task-relevance-cspc.tex
@@
   \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+    \setmainfont[]{Times New Roman}
 \fi
@@
 \newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+\usepackage{setspace}\doublespacing
+\newenvironment{zeroindent} {\par\setlength{\parindent}{0pt}} {\par}
+\setlength{\parskip}{0pt}
+\raggedbottom
 
@@
 
-\section{Introduction}\label{introduction}
-
-Selective attention processes are commonly investigated using
-interference paradigms such as the Stroop (1935) and flanker (B. A.
-Eriksen \& Eriksen, 1974) tasks, where participants identify a target
-while ignoring a response-congruent or -incongruent distractor.
-Performance is typically better on congruent versus incongruent trials
-and the difference-the congruency effect-taken as an index of
-attentional priorities. Large congruency effects are thought to reflect
-ineffective filtering of the distracting stimuli whereas small
-congruency effects are thought to reflect effective filtering. By
-probing factors that systematically alter congruency effects, we can
-then make inferences about processes that control attentional filtering.
-For example, manipulating the frequency of conflict via the proportion
-of congruent versus incongruent trials has shown to influence the size
-of the congruency effect. Typically, a high proportion congruent
-experiment produces large congruency effects, whereas a low proportion
-congruent experiment produces small congruency effects (Logan \&
-Zbrodoff, 1979; Lowe \& Mitterer, 1982; West \& Baylis, 1998). This
-result is usually explained as strategic control, where participants
-increase attentional control under high-conflict demands and relax
-attentional control under low-conflict demands (Logan, 1980; Logan \&
-Zbrodoff, 1979; Logan, Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer,
-1982). Recent work however, has demonstrated that attentional control is
-not only adjusted by top-down regulation, but can also be triggered
-automatically by environmental cues (Brosowsky \& Crump, 2018; J. Bugg
-\& Crump, 2012; Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \&
-Egner, 2012; Mayr \& Bryck, 2007).
+Selective attention is commonly investigated using interference
+paradigms such as the Stroop (1935) and flanker (B. A. Eriksen \&
+Eriksen, 1974) tasks, where participants identify a target while
+ignoring a response-congruent or -incongruent distractor. Performance is
+typically better on congruent versus incongruent trials and the
+difference---the congruency effect---taken as an index of attentional
+priorities. Large congruency effects are thought to reflect ineffective
+filtering of the distracting stimuli whereas small congruency effects
+are thought to reflect effective filtering. By probing factors that
+systematically alter congruency effects, we can then make inferences
+about processes that control attentional filtering. For example,
+manipulating the frequency of conflict via the proportion of congruent
+versus incongruent trials has shown to influence the size of the
+congruency effect. Typically, a high proportion congruent experiment
+produces large congruency effects, whereas a low proportion congruent
+experiment produces small congruency effects (Logan \& Zbrodoff, 1979;
+Lowe \& Mitterer, 1982; West \& Baylis, 1998). This result is usually
+explained as strategic control, where participants increase attentional
+control under high-conflict demands and relax attentional control under
+low-conflict demands (Logan, 1980; Logan \& Zbrodoff, 1979; Logan,
+Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer, 1982). Recent work
+however, has demonstrated that attentional control is not only adjusted
+by top-down regulation, but can also be triggered automatically by
+environmental cues (Brosowsky \& Crump, 2018; J. Bugg \& Crump, 2012;
+Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \& Egner, 2012;
+Mayr \& Bryck, 2007).
 
@@
 trigger the retrieval of previous experiences, automatically reinstating
-the associated attentional priorities. Although this explanation seems
-plausible, it remains largely unclear how such associations are
-established and perhaps more importantly, it remains unclear what
-determines which learned associations will be used to guide attention at
-any given moment.
+associated attentional priorities. As a result, automatic memory-based
+retrieval allows attentional priorities to be rapidly adjusted in a
+context-appropriate fashion. However, the obligatory nature of
+memory-based attentional control remains unclear, in particular in
+situations when multiple contextual features could be used as cues for
+retrieval.
 
-The importance of the latter issue becomes increasingly clear if we
-speculate about context-specificity in more complex, real-world
-environments. Consider myself, right now, writing this article in a
-coffee shop. The coffee shop is a complex environment that contains a
-multitude of contextual cues (e.g., pictures on the wall, chairs,
-coffee, laptop), each of which I have had many different experiences
-applying attentional control. Although my laptop might cue attentional
-processing helpful for finishing this article, other features of the
-coffee shop might cue other, unhelpful attentional processing related to
-other experiences like socializing and people-watching. This is all to
-say that our environments, and experiences within them, afford many
-different associative relationships between cognitive processing and
-environmental cues. What then determines which associative relationships
-will be used to guide attention (or even if such associative
-relationships are used at all)?
+For example, real-world environments offer a plethora of context cues.
+Consider writing an article in a coffee shop. The coffee shop is a
+complex environment with numerous context cues (e.g., pictures on the
+wall, chairs, coffee, laptop), and associated attentional priorities.
+Although a laptop might cue attentional processing helpful for writing,
+other features of the coffee shop might cue attentional processing
+related to other experiences like socializing and people-watching. Given
+that all of these cues are available to set attentional priorities, what
+determines which associative relationships will be used to guide
+attention? On the one hand, context-based retrieval of attentional
+priorities might be completely obligatory and a writer's attention would
+be at the mercy of the environment. On the other hand, there is some
+evidence that contextual cuing of attention is not entirely obligatory
+and can be constrained by task goals, allowing the laptop to take
+priority as a contextual cue over other contextual cues that are
+irrelevant to the task at hand.
 
-Task-relevance might be one factor that is important for establishing
-and using context-attention associations. This proposal might seem
-counter-intuitive as it is typically assumed that the context, within
-selective attention tasks at least, is completely irrelevant to the
-task. In fact, referring to such stimulus dimensions as the
-\enquote{context} carries with it an implication that the feature is
-background information, irrelevant to the task-at-hand, and should be
-ignored by the participant. A closer look at CSPC designs however,
-suggests that the context cues may not be as irrelevant as implied. For
-example, the most commonly used context cue is location (Brosowsky \&
-Crump, 2016; Corballis \& Gratton, 2003; Crump, 2016; Crump et al.,
-2006; Crump, Vaquero, \& Milliken, 2008; Weidler \& Bugg, 2016; Weidler
-et al., 2018). Although in some sense, the location is irrelevant for
-identifying the color of a word, it seems disingenuous to consider it
-completely task-irrelevant. In order to identify the target, the
-participant must first identify and orient to its location on the
-screen. In this is sense, it is relevant to their ability to complete
-the task and furthermore, location information may receive priority
-during encoding (Logan, 1998; Mayr, 1996). Similar arguments could be
-made about other context features that are inherent to processing the
-target stimulus, like font-type (J. Bugg, Jacoby, \& Toth, 2008) and
-color (Vietze \& Wendt, 2009).
+Prior work shows that task-relevance is necessary for establishing and
+using context-attention associations. First, the most commonly used
+context cue is location (Brosowsky \& Crump, 2016; Corballis \& Gratton,
+2003; Crump, 2016; Crump et al., 2006; Crump, Vaquero, \& Milliken,
+2008; Weidler \& Bugg, 2016; Weidler et al., 2018). Although in some
+sense, the location is irrelevant for identifying the color of a word,
+it seems disingenuous to consider it completely task-irrelevant. In
+order to identify the target, the participant must first identify and
+orient to its location on the screen. In this is sense, it is relevant
+to their ability to complete the task and furthermore, location
+information may receive priority during encoding (Logan, 1998; Mayr,
+1996). Similar arguments could be made about other context features that
+are inherent to processing the target stimulus, like font-type (J. Bugg,
+Jacoby, \& Toth, 2008) and color (Vietze \& Wendt, 2009).
 
-To date, we are aware of only one study that has looked at
-task-relevance within the CSPC literature. Crump, Vaquero, \& Milliken
-(2008) used a Stroop prime-probe task where the distractor word is
-presented first followed by a color patch probe. Critically, they used
-the shape of the color patch probe, either a square or a circle, as the
-contextual dimension; one associated with a high frequency of conflict,
-the other with a low frequency. In one experiment participants were made
-aware of the shape-proportion contingencies but given no additional
-instructions. In the second, participants were given a secondary task to
-count the number of trials that contained a square. The first experiment
-failed to find evidence for context-specificity, whereas the second did.
-Although not testing task-relevance directly, (2013)) found similar
-effects. In this study they used images of male and female faces as
-context cues in a flanker task. When given instructions to think of the
-faces as members of the gender categories they found CSPC effects, but
-when given instructions to think of the faces as individuals they did
-not. These results suggest that making a context dimension relevant to
-the on-going task is important for producing CSPC effects.
+Second, we are aware of only one study that has looked at task-relevance
+within the CSPC literature. Crump, Vaquero, \& Milliken (2008) used a
+Stroop prime-probe task where the distractor word is presented first
+followed by a color patch probe. Critically, they used the shape of the
+color patch probe, either a square or a circle, as the contextual
+dimension; one associated with a high frequency of conflict, the other
+with a low frequency. In one experiment participants were made aware of
+the shape-proportion contingencies but given no additional instructions.
+In the second, participants were given a secondary task to count the
+number of trials that contained a square. The first experiment failed to
+find evidence for context-specificity, whereas the second did. Although
+not testing task-relevance directly, Cañadas, Rodríguez-Bailón,
+Milliken, and Lupiáñez (2013){]} found similar effects. In this study
+they used images of male and female faces as context cues in a flanker
+task. When given instructions to think of the faces as members of the
+gender categories they found CSPC effects, but when given instructions
+to think of the faces as individuals they did not. These results suggest
+that making a context dimension relevant to the on-going task is
+important for producing CSPC effects.
 
@@
 
-Some prior suggests that the task-relevance of contextual information is
+Prior work suggests that the task-relevance of contextual information is
 important for establishing new associations between context cues and
@@
 but also whether learned associations are used. In this case, we would
-expect that there will be smaller congruency effects when the
-high-conflict context dimension is made task-relevant as compared to
-when the low-conflict context dimension is made task-relevant. This
-would demonstrate that participants were able to ignore a previously
-learned association and adopt a new context-specific control strategy.
+expect smaller congruency effects when the high-conflict context
+dimension is made task-relevant as compared to when the low-conflict
+context dimension is made task-relevant. This would demonstrate that
+participants were able to ignore a previously learned association and
+adopt a new context-specific control strategy.
 
@@
 context dimensions were defined by social categories, similar to Cañadas
-et al., (2013). However, they found that social categorization occurred
+et al. (2013). However, they found that social categorization occurred
 spontaneously and it was unclear what impact that would have on the
@@
 images of simple objects where context dimensions were defined by object
-features. Finally, Cañadas et al.(2013) also found that context effects
+features. Finally, Cañadas et al. (2013) also found that context effects
 generalized to novel face images. In our third condition we used
@@
 Participants were included in the study if they completed all trials. We
-posted 150 HITs and 145 participants completed all trials.
+posted 150 HITs and 144 participants completed all trials.
 
@@
 
-Design. Experiment 1 used a 2x2x3 mixed design with task-relevant
-context (0\% and 100\%) and unbiased-item congruency (congruent and
-incongruent) as within-subject factors, and context-type (object,
-social, and social/non-repeating) as the between-subjects factor. All
-three conditions were constructed using the same general method. The
+\subsection{Design}\label{design}
+
+Experiment 1 used a 2x2x3 mixed design with task-relevant context (0\%
+and 100\%) and unbiased-item congruency (congruent and incongruent) as
+within-subject factors, and context-type (object, social, and
+social/non-repeating) as the between-subjects factor. All three
+conditions were constructed using the same general method. The
 experiment was divided into two phases. Each phase consisted of 144
@@
 their count from 0. Halfway through the experiment participants received
-new instructions about which feature to count (see Figure 1C). Each
-trial began with a blank inter-stimulus interval (ISI) of 400 ms,
+new instructions about which feature to count (see Figure 1C).
+
+Each trial began with a blank inter-stimulus interval (ISI) of 400 ms,
 followed by a fixation cross presented in the center of the screen for
@@
 Following a response, accuracy feedback was presented for 1000 ms. A
-response automatically triggered the next trial. Halfway through the
-experiment (157 trials), participants received new instructions about
-which feature to count and to press the button on-screen when they were
-ready to continue.
+response automatically triggered the next trial.
 
-\section{Results}\label{results}
+Halfway through the experiment (157 trials), participants received new
+instructions about which feature to count and to press the button
+on-screen when they were ready to continue.
 
@@
 \centering
-\includegraphics{v1-task-relevance-cspc_files/figure-latex/figure2-1.pdf}
+\includegraphics{manuscript_files/figure-latex/figure2-1.pdf}
 \caption{\label{fig:figure2}Results from experiment 1 showing congruency effects
@@
 \end{figure}
+
+\section{Results}\label{results}
 
@@
 significant two-way interaction between the task-relevant context and
-unbiased-item congruency, \(F(1, 128) = 8.30\),
-\(\mathit{MSE} = 1,608.54\), \(p = .005\), \(\hat{\eta}^2_p = .061\),
-and a non-significant three-way interaction between task-relevant
-context, unbiased-item congruency, and context-type,
-\(F(2, 128) = 0.00\), \(\mathit{MSE} = 1,608.54\), \(p = .996\),
-\(\hat{\eta}^2_p = .000\). Therefore, the congruency effects in error
-rates were also smaller when the context dimension associated with high
-conflict was made task-relevant, corroborating the results of the
-reaction time analysis.
+unbiased-item congruency, \(F(1, 128) = 6.72\),
+\(\mathit{MSE} = 13.93\), \(p = .011\), \(\hat{\eta}^2_p = .050\), and a
+non-significant three-way interaction between task-relevant context,
+unbiased-item congruency, and context-type, \(F(2, 128) = 0.92\),
+\(\mathit{MSE} = 13.93\), \(p = .400\), \(\hat{\eta}^2_p = .014\).
+Therefore, the congruency effects in error rates were also smaller when
+the context dimension associated with high conflict was made
+task-relevant, corroborating the results of the reaction time analysis.
+
+\begin{table}[htbp]
+\caption{Reaction times and error rates from Experiment 1.}
+\label{TR_table}
+\centering
+\begin{tabular}{lllcccc}
+\toprule
+ & & & \multicolumn{2}{c}{Congruent} & \multicolumn{2}{c}{Incongruent} \\
+\cmidrule(rl){4-5}
+\cmidrule(rl){6-7}
+\multicolumn{1}{c}{Task-Relevant Context} & \multicolumn{1}{c}{Condition} & \multicolumn{1}{c}{PC} & \multicolumn{1}{c}{RT} & \multicolumn{1}{c}{ER} & \multicolumn{1}{c}{RT} & \multicolumn{1}{c}{ER}  \\
+\midrule
+\multirow{9}{*}{100\% PC} & \multirow{3}{*}{Object} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{693 (26)} & \multicolumn{1}{l}{4.17 (0.73)} \\
+& & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{585 (23)} & \multicolumn{1}{l}{0.74 (0.27)} & \multicolumn{1}{l}{675 (28)} & \multicolumn{1}{l}{4.81 (0.82)} \\
+& & \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{587 (25)} & \multicolumn{1}{l}{0.69 (0.23)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
+\cmidrule(rl){2-7}
+& \multirow{3}{*}{Social} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{c}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{745 (25)} & \multicolumn{1}{l}{5.86 (0.77)} \\
+& & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{612 (21)} & \multicolumn{1}{l}{0.39 (0.19)} & \multicolumn{1}{l}{722 (26)} & \multicolumn{1}{l}{6.78 (1.04)} \\
+& & \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{616 (20)} & \multicolumn{1}{l}{0.63 (0.2)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
+\cmidrule(rl){2-7}
+& \multirow{3}{*}{Social (NR)} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{813 (25)} & \multicolumn{1}{l}{5.04 (0.74)} \\
+& & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{689 (23)} & \multicolumn{1}{l}{0.19 (0.14)} & \multicolumn{1}{l}{793 (27)} & \multicolumn{1}{l}{5.72 (1.06)} \\
+& & \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{689 (25)} & \multicolumn{1}{l}{0.48 (0.17)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
+\midrule
+\multirow{9}{*}{0\% PC} & \multirow{3}{*}{Object} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{649 (16)} & \multicolumn{1}{l}{3.84 (0.6)} \\
+& & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{587 (17)} & \multicolumn{1}{l}{0.56 (0.21)} & \multicolumn{1}{l}{657 (17)} & \multicolumn{1}{l}{4.17 (1.02)} \\
+& & \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{634 (18)} & \multicolumn{1}{l}{2.69 (0.58)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
+\cmidrule(rl){2-7}
+& \multirow{3}{*}{Social} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{722 (23)} & \multicolumn{1}{l}{5.77 (0.92)} \\
+& & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{633 (20)} & \multicolumn{1}{l}{0.78 (0.5)} & \multicolumn{1}{l}{722 (25)} & \multicolumn{1}{l}{4.75 (0.9)} \\
+& & \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{673 (21)} & \multicolumn{1}{l}{1.84 (0.47)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
+\cmidrule(rl){2-7}
+& \multirow{3}{*}{Social (NR)} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{807 (26)} & \multicolumn{1}{l}{4.55 (0.8)} \\
+& & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{735 (28)} & \multicolumn{1}{l}{0.87 (0.36)} & \multicolumn{1}{l}{818 (30)} & \multicolumn{1}{l}{4.26 (0.8)} \\
+& & \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{779 (34)} & \multicolumn{1}{l}{2.03 (0.4)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
+ & & & & & & \\
+\bottomrule
+\multicolumn{7}{l}{\textit{Note}: RT = Reaction Time (ms);  ER = Error Rates (\%); PC = Proportion Congruent;} \\
+\multicolumn{7}{l}{NR = Non-Repeating; Standard Errors are presented in parantheses.} \\
+\end{tabular}%
+\end{table}
 
@@
 
-The aim of the current study was to investigate whether task-relevance
+The aim of the current study was to determine whether task-relevance
 plays a role in the contextual recruitment of selective attention.
@@
 unbiased context cue that shared features with two frequency biased
-contexts and included a feature-counting task to manipulate the
+contexts and used a feature-counting task to manipulate the
 task-relevance of context dimensions across two blocks of trials.
@@
 can update the contextual recruitment of selective attention in a CSPC
-flanker task. Importantly, we show that making one feature task-relevant
+flanker task. We demonstrated that making one context cue task-relevant
 produced a CSPC effect, even in the presence of a competing contextual
-cue. Moreover, changing the task-relevant context-cue midway through the
-experiment was accompanied by predictable changes in the congruency
-effects. This effect was found to be generalizable across two different
-kinds of stimuli and occurred even when using non-repeating images.
-These results implicate an important role for task-relevance in
-producing context-dependency and are consistent with memory-based
-accounts of CSPC phenomena.
+cue. More important however, we found that changing the task-relevance
+of the contextual cues across blocks of trials was accompanied by
+predictable changes in the congruency effects. These effects were found
+to be generalizable across two different kinds of stimuli and occurred
+even when using non-repeating images, and implicate an important role
+for task-relevance in producing context-dependency and are consistent
+with memory-based accounts of CSPC phenomena.
 
@@
 deployment of contextually mediated attentional resources on perceptual
-tasks. \emph{Journal of Cognitive Psychology}, \emph{0}(0), 1--11.
+tasks. \emph{Journal of Cognitive Psychology}, \emph{29}, 977--987.
 doi:\href{https://doi.org/10.1080/20445911.2017.1353518}{10.1080/20445911.2017.1353518}
@@
 attention: Single experiences with conflict have long-lasting effects on
-cognitive control. \emph{Journal of Experimental Psychology: General}.
+cognitive control. \emph{Journal of Experimental Psychology: General},
+\emph{147}, 1134--1153.
 doi:\href{https://doi.org/10.1037/xge0000431}{10.1037/xge0000431}
@@
 From Proportion Congruent Effects. \emph{Canadian Journal of
-Experimental Psychology= Revue Canadienne de Psychologie Experimentale}.
+Experimental Psychology= Revue Canadienne de Psychologie Experimentale},
+\emph{74}, 91--104.
 
@@
 Fischer, R., \& Dreisbach, G. (2015). Predicting high levels of
-multitasking reduces between-tasks interactions. Retrieved from
-\url{http://psycnet.apa.org/psycinfo/2015-47211-001/}
+multitasking reduces between-tasks interactions., \emph{41}, 1482--1487.
+Retrieved from \url{http://psycnet.apa.org/psycinfo/2015-47211-001/}
 
@@
 adjustment of cognitive control in dual-task performance. \emph{Journal
-of Experimental Psychology: Learning, Memory, and Cognition},
-\emph{40}(2), 399.
+of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40},
+399.
 
@@
 generalizability of context-driven control. \emph{Quarterly Journal of
-Experimental Psychology}, \emph{70}(7), 1292--1304.
+Experimental Psychology}, \emph{70}, 1292--1304.
 doi:\href{https://doi.org/10.1080/17470218.2016.1182193}{10.1080/17470218.2016.1182193}
@@
 Logan, G. D. (1980). Attention and automaticity in Stroop and priming
-tasks: Theory and data. \emph{Cognitive Psychology}, \emph{12}(4),
+tasks: Theory and data. \emph{Cognitive Psychology}, \emph{12},
 523--553.
@@
 obligatory encoding of spatial location. \emph{Journal of Experimental
-Psychology: Human Perception and Performance}, \emph{24}(6), 1720.
+Psychology: Human Perception and Performance}, \emph{24}, 1720.
 
@@
 the color-word Stroop task. \emph{Bulletin of the Psychonomic Society},
-\emph{22}(2), 135--138.
+\emph{22}, 135--138.
 
@@
 database: A free stimulus set of faces and norming data. \emph{Behavior
-Research Methods}, \emph{47}(4), 1122--1135.
+Research Methods}, \emph{47}, 1122--1135.
 doi:\href{https://doi.org/10.3758/s13428-014-0532-5}{10.3758/s13428-014-0532-5}
@@
 Categorical person perception. \emph{British Journal of Psychology},
-\emph{92}(1), 239--255.
+\emph{92}, 239--255.
 
@@
 \emph{Journal of Experimental Psychology: Learning, Memory, and
-Cognition}, \emph{22}(2), 350.
+Cognition}, \emph{22}, 350.
 
@@
 environment: Effects of stimulus/response locations on task selection.
-\emph{Psychological Research}, \emph{71}(1), 107--116.
+\emph{Psychological Research}, \emph{71}, 107--116.
 doi:\href{https://doi.org/10.1007/s00426-005-0039-x}{10.1007/s00426-005-0039-x}
@@
 expressions: Judgments from untrained research participants.
-\emph{Psychiatry Research}, \emph{168}(3), 242--249.
+\emph{Psychiatry Research}, \emph{168}, 242--249.
 doi:\href{https://doi.org/10.1016/j.psychres.2008.05.006}{10.1016/j.psychres.2008.05.006}
@@
 dominance and contextual disintegration on the Stroop interference
-effect in older adults. \emph{Psychology and Aging}, \emph{13}(2), 206.
+effect in older adults. \emph{Psychology and Aging}, \emph{13}, 206.
 

### 2019-01-21 data-analysis/analysis.R

@@ -4,9 +4,6 @@ library(tidyr)
 library(afex)
 library(ggplot2)
 library(cowplot)
-library(tables)
-library(magrittr)
-library(kableExtra)
 #As of 2018/12/07 apa_print() requires development version of Papaja
 #devtools::install_github("crsh/papaja")
 library(papaja)
@@ -128,8 +125,7 @@ RT.graph <- ggplot(RT.Diff,aes(x=Condition, y=Flanker,fill=Task_Relevant_Context
   geom_errorbar(limits, width = .2, position=position_dodge(width=0.9))+
   coord_cartesian(ylim = c(0,150))+
   scale_y_continuous(breaks=seq(0, 150, 10), expand = c(0,0))+
-  theme(panel.grid.major.y = element_line(colour="gray80", size=0.2),
-        axis.text=element_text(size=7.5),
+  theme(axis.text=element_text(size=7.5),
         axis.title=element_text(size=10,face="bold")) +
   labs(title="")+
   ylab("Congruency Effect (ms)")+
@@ -179,8 +175,7 @@ ACC.graph <- ggplot(ACC.Diff,aes(x=Condition, y=Flanker,fill=Task_Relevant_Conte
   geom_errorbar(limits, width = .2, position=position_dodge(width=0.9))+
   coord_cartesian(ylim = c(0,10))+
   scale_y_continuous(breaks=seq(0, 10, 1), expand = c(0,0))+
-  theme(panel.grid.major.y = element_line(colour="gray80", size=0.2),
-        axis.text=element_text(size=7.5),
+  theme(axis.text=element_text(size=7.5),
         axis.title=element_text(size=10,face="bold")) +
   labs(title="")+
   ylab("Congruency Effect (% Error)")+

### 2019-01-21 data-analysis/table1.R

@@ -3,9 +3,6 @@ library(tidyr)
 library(afex)
 library(ggplot2)
 library(cowplot)
-#library(tables)
-library(magrittr)
-library(kableExtra)
 #As of 2018/12/07 apa_print() requires development version of Papaja
 #devtools::install_github("crsh/papaja")
 library(papaja)
@@ -167,36 +164,51 @@ table$TRC<-as.factor(c(rep("100% PC", 9), rep("0% PC", 9)))
 table<-table[c(7,1:6)]
 colnames(table)<-c("Task-Relevant Context","Condition","PC","RT","ER","RT","ER")
 
+forTable<-as.matrix(table[,4:7])
 
-latexTable1<-kable(table,"latex", booktabs = T, row.names = F,align="c", linesep = '') %>%
-  kable_styling(full_width = T, font_size = 7) %>%
-  add_header_above(c(" "," "," ", "Congruent" = 2, "Incongruent" = 2), bold = T, align="c") %>%
-  row_spec(0, bold = T, align="c") %>%
-  column_spec(3, width = "0.5em") %>%
-  column_spec(2, width = "1.1em") %>%
-  collapse_rows(1:2,latex_hline = 'custom', custom_latex_hline = 1:2) %>%
-  footnote(general = "RT = Reaction times (ms); ER = Error rates (%); PC = Proportion Congruent; Standard errors are presented in parentheses.") 
-
-
-
-kable_as_image(landscape(
-  kable(table,"latex", booktabs = T, row.names = F) %>%
-        kable_styling(full_width = T) %>%
-        add_header_above(c(" "," "," ", "Congruent" = 2, "Incongruent" = 2), bold = T, align="c") %>%
-        row_spec(0, bold = T, align="c") %>%
-        collapse_rows(1:2,latex_hline = 'custom', custom_latex_hline = 1:2) %>%
-        footnote(general = "RT = Reaction times (ms); ER = Error rates (%); PC = Proportion Congruent; Standard errors are presented in parentheses.") %>%
-        kable_styling(latex_options = c("scale_down"))
-  ),
[…]

### 2019-01-21 manuscript.tex
typo

@@
 by top-down regulation, but can also be triggered automatically by
-environmental cues (Brosowsky \& Crump, 2018; J. Bugg \& Crump, 2012;
+environmental cues (Brosowsky \& Crump, 2018; Bugg \& Crump, 2012;
 Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \& Egner, 2012;
@@
 paradigms (e.g., Alards-Tomalin, Brosowsky, \& Mondor, 2017; Blais,
-Harris, Sinanian, \& Bunge, 2015; J. Bugg, 2014; Crump, 2016; Crump,
+Harris, Sinanian, \& Bunge, 2015; Bugg, 2014; Crump, 2016; Crump,
 Milliken, Leboe-McGowan, Leboe-McGowan, \& Gao, 2018; Fischer,
@@
 1996). Similar arguments could be made about other context features that
-are inherent to processing the target stimulus, like font-type (J. Bugg,
+are inherent to processing the target stimulus, like font-type (Bugg,
 Jacoby, \& Toth, 2008) and color (Vietze \& Wendt, 2009).
@@
 associations. From a theoretical perspective, this result is consistent
-memory-based accounts of CSPC phenomena (Brosowsky \& Crump, 2018; J.
-Bugg \& Hutchison, 2013; Crump \& Milliken, 2009; Crump et al., 2018,
-2017). Under this view, a memory process encodes attentional priorities
-in the representation of individual experiences and, as a result, become
+memory-based accounts of CSPC phenomena (Brosowsky \& Crump, 2018; Bugg
+\& Hutchison, 2013; Crump \& Milliken, 2009; Crump et al., 2018, 2017).
+Under this view, a memory process encodes attentional priorities in the
+representation of individual experiences and, as a result, become
 associated with the environment where they were used. The subsequent
@@
 \hypertarget{ref-weidler_attentional_2018}{}
-Weidler, B. J., Dey, A., \& Bugg, J. M. (2018). Attentional control
+Weidler, B. J., Dey, A., \& Bugg, J. (2018). Attentional control
 transfers beyond the reference frame. \emph{Psychological Research},

### 2019-01-22 manuscript.Rmd
add PSS

@@
 
-abstract: |
-  Evidence across a wide variety of attention paradigms shows that environmental cues can trigger adjustments to ongoing priorities for attending to relevant and irrelevant information.
+abstract: "Evidence across a wide variety of attention paradigms shows that environmental cues can trigger adjustments to ongoing priorities for attending to relevant and irrelevant information.
 This context-specific control over attention suggests that cognitive control can be both automatic and flexible.
@@
 In short, we found that making new contextual information task-relevant caused participants to ignore a previously learned context-attention association and adopt a new context-specific control strategy; all without changing the experimental stimuli.
-This result suggests that task-relevance is a key determinant of context-specific control.
+This result suggests that task-relevance is a key determinant of context-specific control."
 
 keywords          : "Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance"
-wordcount         : "4402"
+wordcount         : "4024 \\vspace{2mm} \\par \\textit{Public Significance Statement:} Contextual cues have been shown to automatically trigger adjustments in selective attention independent of awareness and intention.
+Here, we find the task-relevance plays an important role in determining which context cues are used to direct attention.
+These findings contribute to a better understanding of how context-dependency might occur in more complex environments and more generally, how learning and memory processes enable flexible control over attention."
 
@@
 Across all three conditions, we found no evidence that using different stimuli had an influence on the size or direction of the CSPC demonstrating generalizability of this phenomenon.
-Furthermore, CSPC effects were present even when using non-repeating images which suggests that context-dependency did rely on image-specific associations but higher-order, learned categorical information.
+Furthermore, CSPC effects were present even when using non-repeating images which suggests that context-dependency did not rely on image-specific associations but higher-order, learned categorical information.
 

### 2019-01-22 manuscript.tex
add PSS

@@
 \textsuperscript{1} The Graduate Center of the City University of New York\\\textsuperscript{2} Brooklyn College of the City University of New York}
-\keywords{Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance\newline\indent Word count: 4402}
+\keywords{Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance\newline\indent Word count: 4024 \vspace{2mm} \par \textit{Public Significance Statement:} Contextual cues have been shown to automatically trigger adjustments in selective attention independent of awareness and intention.
+Here, we find the task-relevance plays an important role in determining which context cues are used to direct attention.
+These findings contribute to a better understanding of how context-dependency might occur in more complex environments and more generally, how learning and memory processes enable flexible control over attention.}
 \usepackage{csquotes}
@@
 control. 
-
 }
@@
 present even when using non-repeating images which suggests that
-context-dependency did rely on image-specific associations but
+context-dependency did not rely on image-specific associations but
 higher-order, learned categorical information.

### 2019-01-22 materials/E1A-Objects/preLoader.js
add materials

@@ -1,0 +1,64 @@
+/////// PreLoad Images ///////
+//Send image URLs to preload array
+var preLoad = {
+    nLoaded: 0, //number of images checked for pre-load
+    yourImages: [], //image array
+    preImages: new Array(),
+    check: new Array(),
+    loading: {},
+    finished: {},
+    progress: {},
+
+
+
+    addURL: function(imgURL, imageList) {
+        //create URL array from imageList
+        for (var i = 0; i <= imageList.length - 1; ++i) {
+            preLoad.yourImages[i] = imgURL + imageList[i];
+        }
+    },
+
+    loadImages: function(loadingDiv, completeDiv, progressDiv) {
+
+        this.loading = loadingDiv;
+        this.finished = completeDiv;
+        this.progress = progressDiv;
+
+        if (this.nLoaded < preLoad.yourImages.length) {
+            this.preImages[this.nLoaded] = new Image();
+            this.preImages[this.nLoaded].onload = function() {
+                preLoad.checkLoad();
+            };
+
+            this.preImages[this.nLoaded].onerror = function() {
+                preLoad.checkLoad();
+            };
+
+
+            this.preImages[this.nLoaded].src = this.yourImages[this.nLoaded];
+            //  document.getElementById("imgPlaceHolder").appendChild(this.preImages[this.index]);
+        }
+    },
+
+    checkLoad: function() {
+        this.nLoaded++;
+        //  preLoad.index = preLoad.index + 1;
+        $(this.progress).html(Math.round((preLoad.nLoaded / preLoad.yourImages.length) * 100) + "%");
+        if (preLoad.nLoaded < preLoad.yourImages.length) {
+            preLoad.loadImages(this.loading, this.finished, this.progress);
+        }
+        if (preLoad.nLoaded == preLoad.yourImages.length && ($(this.loading).css('display') != 'none')) {
+            $(this.loading).hide();
+            $(this.finished).show();
+        }
+    },
+
+    manualCheck: function(complete, incomplete) {
+        if (preLoad.nLoaded == preLoad.yourImages.length) {
+            $(complete).show();
+        } else {
+            $(incomplete).show();
+        }
+    }
+
+};

### 2019-01-22 materials/E1A-Objects/task.js

@@ -1,0 +1,780 @@
+/*
+ * Every item in trialArray represents a single trial
+ * trialArray properties include any information needed to present the stim and
+ * any trial information needed for data analysis
+ */
+
+
+//////////////// Stim & Trial Array Creation //////////////////////////////////
+
+
+tempSets = [
+    [
+        ["b", "b", "g"],
+        ["hat", "chair", "chair"],
+        ["100", "50", "0"]
+    ],
+    [
+        ["b", "b", "g"],
+        ["chair", "hat", "hat"],
+        ["100", "50", "0"]
+    ],
+    [
+        ["b", "g", "g"],
+        ["hat", "hat", "chair"],
+        ["100", "50", "0"]
+    ],
+    [
+        ["b", "g", "g"],
+        ["chair", "chair", "hat"],
+        ["100", "50", "0"]
+    ],
+    [
+        ["b", "b", "g"],
+        ["hat", "chair", "chair"],
+        ["0", "50", "100"]
+    ],
+    [
+        ["b", "b", "g"],
+        ["chair", "hat", "hat"],
+        ["0", "50", "100"]
+    ],
+    [
+        ["b", "g", "g"],
+        ["hat", "hat", "chair"],
+        ["0", "50", "100"]
+    ],
+    [
+        ["b", "g", "g"],
+        ["chair", "chair", "hat"],
+        ["0", "50", "100"]
+    ]
+
+];
+
+
+tempSets = shuffle(tempSets);
+finalSet = tempSets[0];
+
+if (finalSet[0][0] === finalSet[0][1]) {
+    countOrder = [
+        ["color", finalSet[0][1], finalSet[2][0]],
+        ["identity", finalSet[1][1], finalSet[2][2]]
+    ];
+} else {
+    countOrder = [
+        ["identity", finalSet[1][1], finalSet[2][0]],
+        ["color", finalSet[0][1], finalSet[2][2]]
+    ];
+}
+
+countOrder = shuffle(countOrder);
+
+imageList = [
+    "chairb.jpg", "chairg.jpg", "hatb.jpg", "hatg.jpg",
+    "LL.png", "LR.png", "RR.png", "RL.png"
+];
+/* creates arrays of the congruent and incongruent item combinations */
+
+flankerCon = ["LL", "RR"];
+flankerInc = ["LR", "RL"];
+
+conSet = [];
+incSet = [];
+temp = [];
+
+for (i = 0; i <= 2; i++) {
[…]

### 2019-01-22 materials/E1B-Faces/task.js

@@ -1,0 +1,811 @@
+/*
+ * Every item in trialArray represents a single trial
+ * trialArray properties include any information needed to present the stim and
+ * any trial information needed for data analysis
+ */
+
+
+//////////////// Stim & Trial Array Creation //////////////////////////////////
+
+
+tempSets = [
+    [
+        ["M", "M", "F"],
+        ["B", "W", "W"],
+        ["100", "50", "0"]
+    ],
+    [
+        ["M", "M", "F"],
+        ["W", "B", "B"],
+        ["100", "50", "0"]
+    ],
+    [
+        ["M", "F", "F"],
+        ["B", "B", "W"],
+        ["100", "50", "0"]
+    ],
+    [
+        ["M", "F", "F"],
+        ["W", "W", "B"],
+        ["100", "50", "0"]
+    ],
+    [
+        ["M", "M", "F"],
+        ["B", "W", "W"],
+        ["0", "50", "100"]
+    ],
+    [
+        ["M", "M", "F"],
+        ["W", "B", "B"],
+        ["0", "50", "100"]
+    ],
+    [
+        ["M", "F", "F"],
+        ["B", "B", "W"],
+        ["0", "50", "100"]
+    ],
+    [
+        ["M", "F", "F"],
+        ["W", "W", "B"],
+        ["0", "50", "100"]
+    ]
+
+];
+
+
+tempSets = shuffle(tempSets);
+finalSet = tempSets[0];
+
+if (finalSet[0][0] === finalSet[0][1]) {
+    countOrder = [
+        ["gender", finalSet[0][1], finalSet[2][0]],
+        ["race", finalSet[1][1], finalSet[2][2]]
+    ];
+} else {
+    countOrder = [
+        ["race", finalSet[1][1], finalSet[2][0]],
+        ["gender", finalSet[0][1], finalSet[2][2]]
+    ];
+}
+
+countOrder = shuffle(countOrder);
+
+imageList = [
+    "BF.jpg", "BM.jpg", "WF.jpg", "WM.jpg",
+    "LL.png", "LR.png", "RR.png", "RL.png"
+];
+/* creates arrays of the congruent and incongruent item combinations */
+
+flankerCon = ["LL", "RR"];
+flankerInc = ["LR", "RL"];
+
+conSet = [];
+incSet = [];
+temp = [];
+
+for (i = 0; i <= 2; i++) {
+    for (n = 0; n <= 1; n++) {
+        for (m = 0; m <= 2; m++) {
[…]

### 2019-01-22 materials/E1C-Faces-NR/preLoader.js

@@ -1,0 +1,72 @@
+/////// PreLoad Images ///////
+//Send image URLs to preload array
+var preLoad = {
+    nLoaded: 0, //number of images checked for pre-load
+    yourImages: [], //image array
+    preImages: new Array(),
+    check: new Array(),
+    loading: {},
+    finished: {},
+    progress: {},
+    success: 0,
+    fail: 0,
+
+
+
+    addURL: function(imgURL, imageList) {
+        //create URL array from imageList
+        for (var i = 0; i <= imageList.length - 1; ++i) {
+            preLoad.yourImages[i] = imgURL + imageList[i];
+        }
+    },
+
+    loadImages: function(loadingDiv, completeDiv, progressDiv) {
+
+        this.loading = loadingDiv;
+        this.finished = completeDiv;
+        this.progress = progressDiv;
+
+        if (this.nLoaded < preLoad.yourImages.length) {
+            this.preImages[this.nLoaded] = new Image();
+            this.preImages[this.nLoaded].onload = function() {
+                preLoad.checkLoad();
+                preLoad.success ++;
+            };
+
+            this.preImages[this.nLoaded].onerror = function() {
+                preLoad.checkLoad();
+                preLoad.fail ++;
+            };
+
+
+            this.preImages[this.nLoaded].src = this.yourImages[this.nLoaded];
+            //  document.getElementById("imgPlaceHolder").appendChild(this.preImages[this.index]);
+        }
+    },
+
+    checkLoad: function() {
+        this.nLoaded++;
+        //  preLoad.index = preLoad.index + 1;
+        $(this.progress).html(Math.round((preLoad.nLoaded / preLoad.yourImages.length) * 100) + "%");
+        if (preLoad.nLoaded < preLoad.yourImages.length) {
+            preLoad.loadImages(this.loading, this.finished, this.progress);
+        }
+        if (preLoad.nLoaded == preLoad.yourImages.length && ($(this.loading).css('display') != 'none')) {
+            $(this.loading).hide();
+            $(this.finished).show();
+            console.log(preLoad.success);
+            console.log(preLoad.fail);
+        }
+    },
+
+    manualCheck: function(complete, incomplete) {
+        if (preLoad.nLoaded == preLoad.yourImages.length) {
+            $(complete).show();
+            console.log(preLoad.success);
+            console.log(preLoad.fail);
+        } else {
+            $(incomplete).show();
+        }
+    }
+
+};

### 2019-01-22 materials/E1C-Faces-NR/task.js

@@ -1,0 +1,842 @@
+/*
+ * Every item in trialArray represents a single trial
+ * trialArray properties include any information needed to present the stim and
+ * any trial information needed for data analysis
+ */
+
+
+//////////////// Stim & Trial Array Creation //////////////////////////////////
+
+
+tempSets = [
+    [
+        ["M", "M", "F"],
+        ["B", "W", "W"],
+        ["100", "50", "0"]
+    ],
+    [
+        ["M", "M", "F"],
+        ["W", "B", "B"],
+        ["100", "50", "0"]
+    ],
+    [
+        ["M", "F", "F"],
+        ["B", "B", "W"],
+        ["100", "50", "0"]
+    ],
+    [
+        ["M", "F", "F"],
+        ["W", "W", "B"],
+        ["100", "50", "0"]
+    ],
+    [
+        ["M", "M", "F"],
+        ["B", "W", "W"],
+        ["0", "50", "100"]
+    ],
+    [
+        ["M", "M", "F"],
+        ["W", "B", "B"],
+        ["0", "50", "100"]
+    ],
+    [
+        ["M", "F", "F"],
+        ["B", "B", "W"],
+        ["0", "50", "100"]
+    ],
+    [
+        ["M", "F", "F"],
+        ["W", "W", "B"],
+        ["0", "50", "100"]
+    ]
+
+];
+
+
+tempSets = shuffle(tempSets);
+finalSet = tempSets[0];
+
+if (finalSet[0][0] === finalSet[0][1]) {
+    countOrder = [
+        ["gender", finalSet[0][1], finalSet[2][0]],
+        ["race", finalSet[1][1], finalSet[2][2]]
+    ];
+} else {
+    countOrder = [
+        ["race", finalSet[1][1], finalSet[2][0]],
+        ["gender", finalSet[0][1], finalSet[2][2]]
+    ];
+}
+
+countOrder = shuffle(countOrder);
+
+imageList = [
+    "LL.png", "LR.png", "RR.png", "RL.png"
+];
+
+
+
+for (n = 0; n <= 2; n++) {
+    for (i = 1; i <= 96; i++) {
+        imageList.push(finalSet[1][n] + finalSet[0][n] + i + ".jpg");
+    }
+}
+
+/* creates number labels for 96 images in each condition and randomizes the order for condition */
+img_100 = [];
+img_50 = [];
+img_0 = [];
+
[…]

### 2019-01-23 manuscript.tex
update

@@
 \keywords{Attention, Memory, Cognitive Control, Conflict Adaptation, Context-specific, Task Relevance\newline\indent Word count: 4024 \vspace{2mm} \par \textit{Public Significance Statement:} Contextual cues have been shown to automatically trigger adjustments in selective attention independent of awareness and intention.
-Here, we find the task-relevance plays an important role in determining which context cues are used to direct attention.
+Here, we find that task-relevance plays an important role in determining which context cues are used to direct attention.
 These findings contribute to a better understanding of how context-dependency might occur in more complex environments and more generally, how learning and memory processes enable flexible control over attention.}
@@
 \newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
 \usepackage{setspace}\doublespacing
@@
 
-Correspondence concerning this article should be addressed to Nicholaus
-P. Brosowsky, The Graduate Center, CUNY, 365 5th Ave, New York, NY
-10016. E-mail:
-\href{mailto:nbrosowsky@gradcenter.cuny.edu}{\nolinkurl{nbrosowsky@gradcenter.cuny.edu}}}
+Correspondence concerning this article should be addressed to Nicholaus P.
+Brosowsky, The Graduate Center, CUNY, 365 5th Ave, New York, NY 10016.
+E-mail: \href{mailto:nbrosowsky@gradcenter.cuny.edu}{\nolinkurl{nbrosowsky@gradcenter.cuny.edu}}}
 
 \abstract{
-Evidence across a wide variety of attention paradigms shows that
-environmental cues can trigger adjustments to ongoing priorities for
-attending to relevant and irrelevant information. This context-specific
-control over attention suggests that cognitive control can be both
-automatic and flexible. For instance, in selective attention tasks,
-congruency effects are larger for items that appear in a context
-associated with infrequent conflict than in a context associated with
-frequent conflict. Since the to-be-presented context cannot be predicted
-or prepared for in advance, attention is assumed to be rapidly updated
-on-the-fly, triggered by the currently presented context.
-Context-specific control exemplifies how learning and memory processes
-can influence attention to enable cognitive flexibility. However, what
-determines the use of previously learned associations still remains
-unclear. In the current study, we examined whether task-relevance would
-influence the learning and use of context cues in a flanker task. Using
-a secondary counting task, context dimensions associated with differing
-levels of conflict were made task-relevant or -irrelevant across the
-experiment. In short, we found that making new contextual information
-task-relevant caused participants to ignore a previously learned
-context-attention association and adopt a new context-specific control
-strategy; all without changing the experimental stimuli. This result
-suggests that task-relevance is a key determinant of context-specific
-control. 
+Evidence across a wide variety of attention paradigms shows that environmental cues can trigger adjustments to ongoing priorities for attending to relevant and irrelevant information.
+This context-specific control over attention suggests that cognitive control can be both automatic and flexible.
+For instance, in selective attention tasks, congruency effects are larger for items that appear in a context associated with infrequent conflict than in a context associated with frequent conflict.
+Since the to-be-presented context cannot be predicted or prepared for in advance, attention is assumed to be rapidly updated on-the-fly, triggered by the currently presented context.
+Context-specific control exemplifies how learning and memory processes can influence attention to enable cognitive flexibility.
+However, what determines the use of previously learned associations still remains unclear.
+In the current study, we examined whether task-relevance would influence the learning and use of context cues in a flanker task.
+Using a secondary counting task, context dimensions associated with differing levels of conflict were made task-relevant or -irrelevant across the experiment.
+In short, we found that making new contextual information task-relevant caused participants to ignore a previously learned context-attention association and adopt a new context-specific control strategy; all without changing the experimental stimuli.
+This result suggests that task-relevance is a key determinant of context-specific control.
+
 }
@@
 
-Selective attention is commonly investigated using interference
-paradigms such as the Stroop (1935) and flanker (B. A. Eriksen \&
-Eriksen, 1974) tasks, where participants identify a target while
-ignoring a response-congruent or -incongruent distractor. Performance is
-typically better on congruent versus incongruent trials and the
-difference---the congruency effect---taken as an index of attentional
-priorities. Large congruency effects are thought to reflect ineffective
-filtering of the distracting stimuli whereas small congruency effects
-are thought to reflect effective filtering. By probing factors that
-systematically alter congruency effects, we can then make inferences
-about processes that control attentional filtering. For example,
-manipulating the frequency of conflict via the proportion of congruent
-versus incongruent trials has shown to influence the size of the
-congruency effect. Typically, a high proportion congruent experiment
-produces large congruency effects, whereas a low proportion congruent
-experiment produces small congruency effects (Logan \& Zbrodoff, 1979;
-Lowe \& Mitterer, 1982; West \& Baylis, 1998). This result is usually
-explained as strategic control, where participants increase attentional
-control under high-conflict demands and relax attentional control under
-low-conflict demands (Logan, 1980; Logan \& Zbrodoff, 1979; Logan,
-Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer, 1982). Recent work
-however, has demonstrated that attentional control is not only adjusted
-by top-down regulation, but can also be triggered automatically by
-environmental cues (Brosowsky \& Crump, 2018; Bugg \& Crump, 2012;
-Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \& Egner, 2012;
-Mayr \& Bryck, 2007).
+Selective attention is commonly investigated using interference paradigms such as the Stroop (1935) and flanker (Eriksen \& Eriksen, 1974) tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor.
+Performance is typically better on congruent versus incongruent trials and the difference---the congruency effect---taken as an index of attentional priorities.
+Large congruency effects are thought to reflect ineffective filtering of the distracting stimuli whereas small congruency effects are thought to reflect effective filtering.
+By probing factors that systematically alter congruency effects, we can then make inferences about processes that control attentional filtering.
+For example, manipulating the frequency of conflict via the proportion of congruent versus incongruent trials has shown to influence the size of the congruency effect.
+Typically, a high proportion congruent experiment produces large congruency effects, whereas a low proportion congruent experiment produces small congruency effects (Logan \& Zbrodoff, 1979; Lowe \& Mitterer, 1982; West \& Baylis, 1998).
+This result is usually explained as strategic control, where participants increase attentional control under high-conflict demands and relax attentional control under low-conflict demands (Logan, 1980; Logan \& Zbrodoff, 1979; Logan, Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer, 1982).
+Recent work however, has demonstrated that attentional control is not only adjusted by top-down regulation, but can also be triggered automatically by environmental cues (Brosowsky \& Crump, 2018; Bugg \& Crump, 2012; Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \& Egner, 2012; Mayr \& Bryck, 2007).
 
-For example, Crump, Gong, and Milliken (see also, Corballis \& Gratton,
-2003; Crump, Gong, \& Milliken, 2006) presented Stroop stimuli in one of
-two randomly chosen locations and manipulated the frequency of conflict
-associated with each location. One location was associated with a high
-frequency of conflict (25\% congruent trials) and the other with a low
-frequency of conflict (75\% congruent trials). Overall, the proportion
-of congruent trials was 50\% and randomized such that the upcoming
-location could not be predicted. Even so, congruency effects were shown
-to be smaller for trials where the stimulus appeared in the high
-conflict location as compared to the low conflict location. This effect,
-known now as the context-specific proportion congruent effect (CSPC),
-has now been replicated in a number of different selective attention
-paradigms (e.g., Alards-Tomalin, Brosowsky, \& Mondor, 2017; Blais,
-Harris, Sinanian, \& Bunge, 2015; Bugg, 2014; Crump, 2016; Crump,
-Milliken, Leboe-McGowan, Leboe-McGowan, \& Gao, 2018; Fischer,
-Gottschalk, \& Dreisbach, 2014; Hübner \& Mishra, 2016).
+For example, Crump, Gong, and Milliken (Crump, Gong, \& Milliken, 2006; see also, Corballis \& Gratton, 2003) presented Stroop stimuli in one of two randomly chosen locations and manipulated the frequency of conflict associated with each location.
+One location was associated with a high frequency of conflict (25\% congruent trials) and the other with a low frequency of conflict (75\% congruent trials).
+Overall, the proportion of congruent trials was 50\% and randomized such that the upcoming location could not be predicted.
+Even so, congruency effects were shown to be smaller for trials where the stimulus appeared in the high conflict location as compared to the low conflict location.
+This effect, known now as the context-specific proportion congruent effect (CSPC), has now been replicated in a number of different selective attention paradigms (e.g., Alards-Tomalin, Brosowsky, \& Mondor, 2017; Blais, Harris, Sinanian, \& Bunge, 2015; Bugg, 2014; Crump, 2016; Crump, Milliken, Leboe-McGowan, Leboe-McGowan, \& Gao, 2018; Fischer, Gottschalk, \& Dreisbach, 2014; Hübner \& Mishra, 2016).
 
-Critical evidence however, that CSPC effects reflect context-specific
-control rather than other non-control learning processes (e.g., Schmidt
-\& Besner, 2008), comes from work showing that CSPC effects can transfer
-to frequency unbiased items (Brosowsky \& Crump, 2016; Crump \&
-Milliken, 2009; though, see Hutcheon \& Spieler, 2017; Weidler \& Bugg,
-2016; Weidler, Dey, \& Bugg, 2018). Crump and Milliken (2009), for
-example, divided Stroop items into two mutually exclusive sets (e.g.,
-RED/GREEN and BLUE/YELLOW). One set was defined as the frequency biased
-set, and presented with 75\% congruency in one location, and 25\%
-congruency in the other. The second set however, was presented with 50\%
-congruency in both locations. Nevertheless, they found smaller
-congruency effects for unbiased items presented in the high conflict
-location as compared to the low conflict location.
+Critical evidence however, that CSPC effects reflect context-specific control rather than other non-control learning processes (e.g., Schmidt \& Besner, 2008), comes from work showing that CSPC effects can transfer to frequency unbiased items (Brosowsky \& Crump, 2016; Crump \& Milliken, 2009; Weidler \& Bugg, 2016; Weidler, Dey, \& Bugg, 2018; though, see Hutcheon \& Spieler, 2017).
+Crump and Milliken (2009), for example, divided Stroop items into two mutually exclusive sets (e.g., RED/GREEN and BLUE/YELLOW).
+One set was defined as the frequency biased set, and presented with 75\% congruency in one location, and 25\% congruency in the other.
+The second set however, was presented with 50\% congruency in both locations.
+Nevertheless, they found smaller congruency effects for unbiased items presented in the high conflict location as compared to the low conflict location.
 
-One explanation for CSPC effects is that the repeated application of
-attentional priorities in a particular context creates an associative
-link in episodic memory between the attentional control procedures and
-the contextual information (Abrahamse, Braem, Notebaert, \& Verguts,
-2016; Brosowsky \& Crump, 2018; Crump, 2016; Egner, 2014). Once the
-associative link is established, processing the context is assumed to
-trigger the retrieval of previous experiences, automatically reinstating
-associated attentional priorities. As a result, automatic memory-based
-retrieval allows attentional priorities to be rapidly adjusted in a
-context-appropriate fashion. However, the obligatory nature of
-memory-based attentional control remains unclear, in particular in
-situations when multiple contextual features could be used as cues for
-retrieval.
+One explanation for CSPC effects is that the repeated application of attentional priorities in a particular context creates an associative link in episodic memory between the attentional control procedures and the contextual information (Abrahamse, Braem, Notebaert, \& Verguts, 2016; Brosowsky \& Crump, 2018; Crump, 2016; Egner, 2014).
+Once the associative link is established, processing the context is assumed to trigger the retrieval of previous experiences, automatically reinstating associated attentional priorities.
+As a result, automatic memory-based retrieval allows attentional priorities to be rapidly adjusted in a context-appropriate fashion.
+However, the obligatory nature of memory-based attentional control remains unclear, in particular in situations when multiple contextual features could be used as cues for retrieval.
 
 For example, real-world environments offer a plethora of context cues.
-Consider writing an article in a coffee shop. The coffee shop is a
-complex environment with numerous context cues (e.g., pictures on the
-wall, chairs, coffee, laptop), and associated attentional priorities.
-Although a laptop might cue attentional processing helpful for writing,
-other features of the coffee shop might cue attentional processing
-related to other experiences like socializing and people-watching. Given
-that all of these cues are available to set attentional priorities, what
-determines which associative relationships will be used to guide
-attention? On the one hand, context-based retrieval of attentional
-priorities might be completely obligatory and a writer's attention would
-be at the mercy of the environment. On the other hand, there is some
-evidence that contextual cuing of attention is not entirely obligatory
-and can be constrained by task goals, allowing the laptop to take
-priority as a contextual cue over other contextual cues that are
-irrelevant to the task at hand.
+Consider writing an article in a coffee shop.
+The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), and associated attentional priorities.
+Although a laptop might cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
+Given that all of these cues are available to set attentional priorities, what determines which associative relationships will be used to guide attention?
+On the one hand, context-based retrieval of attentional priorities might be completely obligatory and a writer's attention would be at the mercy of the environment.
+On the other hand, there is some evidence that contextual cuing of attention is not entirely obligatory and can be constrained by task goals, allowing the laptop to take priority as a contextual cue over other contextual cues that are irrelevant to the task at hand.
 
-Prior work shows that task-relevance is necessary for establishing and
-using context-attention associations. First, the most commonly used
-context cue is location (Brosowsky \& Crump, 2016; Corballis \& Gratton,
-2003; Crump, 2016; Crump et al., 2006; Crump, Vaquero, \& Milliken,
-2008; Weidler \& Bugg, 2016; Weidler et al., 2018). Although in some
-sense, the location is irrelevant for identifying the color of a word,
-it seems disingenuous to consider it completely task-irrelevant. In
-order to identify the target, the participant must first identify and
-orient to its location on the screen. In this is sense, it is relevant
-to their ability to complete the task and furthermore, location
-information may receive priority during encoding (Logan, 1998; Mayr,
-1996). Similar arguments could be made about other context features that
-are inherent to processing the target stimulus, like font-type (Bugg,
-Jacoby, \& Toth, 2008) and color (Vietze \& Wendt, 2009).
+Prior work shows that task-relevance is necessary for establishing and using context-attention associations.
+First, the most commonly used context cue is location (Brosowsky \& Crump, 2016; Corballis \& Gratton, 2003; Crump, 2016; Crump et al., 2006; Crump, Vaquero, \& Milliken, 2008; Weidler \& Bugg, 2016; Weidler et al., 2018).
+Although in some sense, the location is irrelevant for identifying the color of a word, it seems disingenuous to consider it completely task-irrelevant.
+In order to identify the target, the participant must first identify and orient to its location on the screen.
+In this is sense, it is relevant to their ability to complete the task and furthermore, location information may receive priority during encoding (Logan, 1998; Mayr, 1996).
+Similar arguments could be made about other context features that are inherent to processing the target stimulus, like font-type (Bugg, Jacoby, \& Toth, 2008) and color (Vietze \& Wendt, 2009).
 
-Second, we are aware of only one study that has looked at task-relevance
-within the CSPC literature. Crump, Vaquero, \& Milliken (2008) used a
-Stroop prime-probe task where the distractor word is presented first
-followed by a color patch probe. Critically, they used the shape of the
-color patch probe, either a square or a circle, as the contextual
-dimension; one associated with a high frequency of conflict, the other
-with a low frequency. In one experiment participants were made aware of
-the shape-proportion contingencies but given no additional instructions.
-In the second, participants were given a secondary task to count the
-number of trials that contained a square. The first experiment failed to
-find evidence for context-specificity, whereas the second did. Although
-not testing task-relevance directly, Cañadas, Rodríguez-Bailón,
-Milliken, and Lupiáñez (2013){]} found similar effects. In this study
-they used images of male and female faces as context cues in a flanker
-task. When given instructions to think of the faces as members of the
-gender categories they found CSPC effects, but when given instructions
-to think of the faces as individuals they did not. These results suggest
-that making a context dimension relevant to the on-going task is
-important for producing CSPC effects.
+Second, we are aware of only one study that has looked at task-relevance within the CSPC literature.
+Crump, Vaquero, \& Milliken (2008) used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe.
+Critically, they used the shape of the color patch probe, either a square or a circle, as the contextual dimension; one associated with a high frequency of conflict, the other with a low frequency.
+In one experiment participants were made aware of the shape-proportion contingencies but given no additional instructions.
+In the second, participants were given a secondary task to count the number of trials that contained a square.
+The first experiment failed to find evidence for context-specificity, whereas the second did.
+Although not testing task-relevance directly, Cañadas, Rodríguez-Bailón, Milliken, and Lupiáñez (2013){]} found similar effects.
+In this study they used images of male and female faces as context cues in a flanker task.
+When given instructions to think of the faces as members of the gender categories they found CSPC effects, but when given instructions to think of the faces as individuals they did not.
+These results suggest that making a context dimension relevant to the on-going task is important for producing CSPC effects.
 
-\section{The Current Study}\label{the-current-study}
+\hypertarget{the-current-study}{%
+\section{The Current Study}\label{the-current-study}}
 
-Prior work suggests that the task-relevance of contextual information is
-important for establishing new associations between context cues and
-attentional priorities. Simply put, CSPC effects emerge when context
-cues are somehow made relevant to the task, but do not when made
-irrelevant (Cañadas et al., 2013; Crump et al., 2006, 2008). However, it
-still remains unclear how task-relevance may or may not inform the use
-of previously learned associations. In the current study, we examined
-whether manipulating task-relevance would cause participants to ignore a
-previously learned association and adopt a new context-specific control
-strategy.
+Prior work suggests that the task-relevance of contextual information is important for establishing new associations between context cues and attentional priorities.
+Simply put, CSPC effects emerge when context cues are somehow made relevant to the task, but do not when made irrelevant (Cañadas et al., 2013; Crump et al., 2006, 2008).
+However, it still remains unclear how task-relevance may or may not inform the use of previously learned associations.
+In the current study, we examined whether manipulating task-relevance would cause participants to ignore a previously learned association and adopt a new context-specific control strategy.
 
-A flanker task was used to measure attentional control in an adapted
-CSPC design (Crump \& Milliken, 2009; Crump, Brosowsky, \& Milliken,
-2017). Similar to previous studies, flanker stimuli were presented in
-contexts associated with differing levels of conflict (0\%, 50\%, or
-100\% congruent). However, unlike previous CSPC designs where contexts
-were defined by a single discriminating feature (e.g., upper vs.~lower
-screen locations), contexts were defined by two feature dimensions (see
-Figure 1A). In one condition, for example, contexts were defined by
-object identity (hat or chair) and color (blue or green). Only three out
-of the four possible feature combinations were presented, each
-associated with a different proportion of congruent trials (0\%, 50\%,
-or 100\% congruent). Critically, the frequency unbiased context (50\%
-congruent) always shared a feature with each of the frequency-biased
-contexts (0\% and 100\% congruent). The frequency biased contexts (0\%
-and 100\% congruent) however, did not share any features (see Figure 1C
-for an example).
+A flanker task was used to measure attentional control in an adapted CSPC design (Crump, Brosowsky, \& Milliken, 2017; Crump \& Milliken, 2009).
+Similar to previous studies, flanker stimuli were presented in contexts associated with differing levels of conflict (0\%, 50\%, or 100\% congruent).
+However, unlike previous CSPC designs where contexts were defined by a single discriminating feature (e.g., upper vs.~lower screen locations), contexts were defined by two feature dimensions (see Figure 1A).
+In one condition, for example, contexts were defined by object identity (hat or chair) and color (blue or green).
+Only three out of the four possible feature combinations were presented, each associated with a different proportion of congruent trials (0\%, 50\%, or 100\% congruent).
+Critically, the frequency unbiased context (50\% congruent) always shared a feature with each of the frequency-biased contexts (0\% and 100\% congruent).
+The frequency biased contexts (0\% and 100\% congruent) however, did not share any features (see Figure 1C for an example).
 
-A secondary counting task was used to manipulate the task-relevance of
-the context dimensions (Crump \& Milliken, 2009) which critically,
-switched halfway through the experiment. Participants were instructed to
-keep a running count of one of the overlapping features (e.g.,
-\enquote{count whenever a hat is presented}) which was associated with
-either a high or low frequency of conflict. Halfway through the
-experiment they received new instructions to count the other overlapping
-feature (e.g., \enquote{count whenever a green item is presented}).
-Critically, the set of context images remained the same throughout the
-experiment (see Figure 1C for an example) and the task-relevance of the
-context dimensions was the only aspect of the experiment that changed
-from the first to second phases.
+A secondary counting task was used to manipulate the task-relevance of the context dimensions (Crump \& Milliken, 2009) which critically, switched halfway through the experiment.
+Participants were instructed to keep a running count of one of the overlapping features (e.g., \enquote{count whenever a hat is presented}) which was associated with either a high or low frequency of conflict.
+Halfway through the experiment they received new instructions to count the other overlapping feature (e.g., \enquote{count whenever a green item is presented}).
+Critically, the set of context images remained the same throughout the experiment (see Figure 1C for an example) and the task-relevance of the context dimensions was the only aspect of the experiment that changed from the first to second phases.
 
-The critical measure of interest is the congruency effect produced in
-the frequency unbiased context. If, on the one hand, task-relevance has
-no impact on the use of context-attention associations we would expect
-no differences between the congruency effects when the high-conflict
-context dimension is made task-relevant or the low-conflict context
-dimension is made task-relevant. This could occur because all three
-contexts are treated as individual contexts throughout the whole
-experiment (e.g., Cañadas et al., 2013). Or it could occur because
-associations formed in the first block interfere with learning new
-associations in the second (e.g., Brosowsky \& Crump, 2016). On other
-hand, task-relevance might not only dictate how associations are formed,
-but also whether learned associations are used. In this case, we would
-expect smaller congruency effects when the high-conflict context
-dimension is made task-relevant as compared to when the low-conflict
-context dimension is made task-relevant. This would demonstrate that
-participants were able to ignore a previously learned association and
-adopt a new context-specific control strategy.
+The critical measure of interest is the congruency effect produced in the frequency unbiased context.
+If, on the one hand, task-relevance has no impact on the use of context-attention associations we would expect no differences between the congruency effects when the high-conflict context dimension is made task-relevant or the low-conflict context dimension is made task-relevant.
+This could occur because all three contexts are treated as individual contexts throughout the whole experiment (e.g., Cañadas et al., 2013).
+Or it could occur because associations formed in the first block interfere with learning new associations in the second (e.g., Brosowsky \& Crump, 2016).
+On other hand, task-relevance might not only dictate how associations are formed, but also whether learned associations are used.
+In this case, we would expect smaller congruency effects when the high-conflict context dimension is made task-relevant as compared to when the low-conflict context dimension is made task-relevant.
+This would demonstrate that participants were able to ignore a previously learned association and adopt a new context-specific control strategy.
 
-A secondary goal was to conceptually replicate previous findings and
-test the generalizability of any task-relevance effects. Therefore, we
-included three conditions that differed only in the kinds of stimuli
-used to create context cues. In one condition we used face images where
-context dimensions were defined by social categories, similar to Cañadas
-et al. (2013). However, they found that social categorization occurred
-spontaneously and it was unclear what impact that would have on the
-current results. Therefore, we included another condition that used
-images of simple objects where context dimensions were defined by object
-features. Finally, Cañadas et al. (2013) also found that context effects
-generalized to novel face images. In our third condition we used
-non-repeating face exemplars to examine whether any task-relevance
-effects would also generalize in our design or if learning would be
-image-specific.
+A secondary goal was to conceptually replicate previous findings and test the generalizability of any task-relevance effects.
+Therefore, we included three conditions that differed only in the kinds of stimuli used to create context cues.
+In one condition we used face images where context dimensions were defined by social categories, similar to Cañadas et al.
+(2013).
+However, they found that social categorization occurred spontaneously and it was unclear what impact that would have on the current results.
+Therefore, we included another condition that used images of simple objects where context dimensions were defined by object features.
+Finally, Cañadas et al.
+(2013) also found that context effects generalized to novel face images.
+In our third condition we used non-repeating face exemplars to examine whether any task-relevance effects would also generalize in our design or if learning would be image-specific.
 
-\section{Methods}\label{methods}
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
@@
 \includegraphics{images/Task.jpg}
-\caption{\label{fig:figure1}Illustration of the stimuli and trial construction. Figure
-1A shows the feature dimensions for each of the conditions. Figure 1B
-shows an example trial stimulus containing both the context and flanker
-images. Figure 1C shows an example of how feature dimensions could have
-been assigned to each proportion congruency (PC) condition, and an
-example of the secondary task assignments. The secondary task order, as
-well as the feature and congruency assignments were all randomized for
-each participant.}
+\caption{\label{fig:figure1}Illustration of the stimuli and trial construction.
+Figure 1A shows the feature dimensions for each of the conditions.
+Figure 1B shows an example trial stimulus containing both the context and flanker images.
+Figure 1C shows an example of how feature dimensions could have been assigned to each proportion congruency (PC) condition, and an example of the secondary task assignments.
+The secondary task order, as well as the feature and congruency assignments were all randomized for each participant.}
 \end{figure}
 
-\subsection{Participants}\label{participants}
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
-All participants were recruited from Amazon Mechanical Turk (AMT) and
-compensated \$2.00 for participating. The amount compensated was
-calculated by estimating the maximum amount of time required to complete
-each experiment and multiplying by \$6.00 per hour. For each experiment
-the number of HITs (Human intelligence tasks, an Amazon term for a
-work-unit) refers to the number of participants who initiated the study.
-Participants were included in the study if they completed all trials. We
-posted 150 HITs and 144 participants completed all trials.
+All participants were recruited from Amazon Mechanical Turk (AMT) and compensated \$2.00 for participating.
+The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by \$6.00 per hour.
+For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study.
+Participants were included in the study if they completed all trials.
+We posted 150 HITs and 144 participants completed all trials.
 
-\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli}
+\hypertarget{apparatus-stimuli}{%
+\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli}}
 
-The experiments were programmed using JavaScript, CSS and HTML. The
-program allowed participants to complete task only if they were running
-Safari, Google Chrome, or Firefox web browsers. Flanker stimuli
-consisted of images of five arrows pointed left or right presented at
-250 x 50 pixels (each arrow was 50 x 50 pixels). Context stimuli were
-constructed using images selected from Brady, Konkle, Gill, Oliva, and
-Alvarez (2013) color-rotated to blue and green, and face images from the
-Chicago Face Database (Ma, Correll, \& Wittenbrink, 2015), supplemented
-with the NimStim Set of Facial Expressions (Tottenham et al., 2009). The
-object images were displayed at 250 x 250 pixels, while the face images
-were displayed at 250 x 313 pixels. The experiment ran as a pop-up
-window that filled the entire screen. The background was white, and
-stimuli were presented in the center of the screen.
+The experiments were programmed using JavaScript, CSS and HTML.
+The program allowed participants to complete task only if they were running Safari, Google Chrome, or Firefox web browsers.
+Flanker stimuli consisted of images of five arrows pointed left or right presented at 250 x 50 pixels (each arrow was 50 x 50 pixels).
+Context stimuli were constructed using images selected from Brady, Konkle, Gill, Oliva, and Alvarez (2013) color-rotated to blue and green, and face images from the Chicago Face Database (Ma, Correll, \& Wittenbrink, 2015), supplemented with the NimStim Set of Facial Expressions (Tottenham et al., 2009).
+The object images were displayed at 250 x 250 pixels, while the face images were displayed at 250 x 313 pixels.
+The experiment ran as a pop-up window that filled the entire screen.
+The background was white, and stimuli were presented in the center of the screen.
 
-\subsection{Design}\label{design}
+\hypertarget{design}{%
+\subsection{Design}\label{design}}
 
-Experiment 1 used a 2x2x3 mixed design with task-relevant context (0\%
-and 100\%) and unbiased-item congruency (congruent and incongruent) as
-within-subject factors, and context-type (object, social, and
-social/non-repeating) as the between-subjects factor. All three
-conditions were constructed using the same general method. The
-experiment was divided into two phases. Each phase consisted of 144
-flanker trials (48 trials per context), and 13 count response trials for
-a total of 314 trials. On the count response trials, participants
-indicated how many trials they had counted until that point. The count
-response trials occurred once for every 12 flanker trials and was
-randomly inserted between trial 6 and 12 of each 12-trial block. Each
-phase ended with one additional count response trial.
+Experiment 1 used a 2x2x3 mixed design with task-relevant context (0\% and 100\%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+All three conditions were constructed using the same general method.
+The experiment was divided into two phases.
+Each phase consisted of 144 flanker trials (48 trials per context), and 13 count response trials for a total of 314 trials.
+On the count response trials, participants indicated how many trials they had counted until that point.
+The count response trials occurred once for every 12 flanker trials and was randomly inserted between trial 6 and 12 of each 12-trial block.
+Each phase ended with one additional count response trial.
 
-On every flanker trial, participants were presented with flanker stimuli
-paired with one of three contexts. Each context was associated with a
-different proportion congruency such that two cues were associated with
-a biased frequency (0\% and 100\% proportion congruency), while one was
-associated with an unbiased frequency (50\% proportion congruency). The
-feature dimensions and corresponding context images assigned to each of
-the biased and unbiased item sets were randomly determined for each
-participant. However, context images used for the frequency biased
-trials never shared features, while the frequency unbiased context image
-always shared a feature with each of the frequency biased context images
-(see Figure 1). Additionally, the feature assignments remained the same
-throughout phases 1 and 2, and critically, the only change to the task
-was which feature the participant was instructed to count (see Figure 1C
-for an example).
+On every flanker trial, participants were presented with flanker stimuli paired with one of three contexts.
+Each context was associated with a different proportion congruency such that two cues were associated with a biased frequency (0\% and 100\% proportion congruency), while one was associated with an unbiased frequency (50\% proportion congruency).
+The feature dimensions and corresponding context images assigned to each of the biased and unbiased item sets were randomly determined for each participant.
+However, context images used for the frequency biased trials never shared features, while the frequency unbiased context image always shared a feature with each of the frequency biased context images (see Figure 1).
+Additionally, the feature assignments remained the same throughout phases 1 and 2, and critically, the only change to the task was which feature the participant was instructed to count (see Figure 1C for an example).
 
 All critical aspects of the task were randomized between participants.
-This includes the three chosen context images, the features assigned to
-proportion levels, the features assigned to each counting condition, the
-secondary task order, and the order of trials.
+This includes the three chosen context images, the features assigned to proportion levels, the features assigned to each counting condition, the secondary task order, and the order of trials.
 
-\subsection{Procedure}\label{procedure}
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
-All participants were AMT workers who found the experiment using the AMT
-system. The participant recruitment procedure and tasks were approved by
-the Brooklyn College Institutional Review Board. Each participant read a
-short description of the task and gave consent by pressing a button
-acknowledging they had read the displayed consent form. Participants
-then completed a short demographic survey, and proceeded to the main
-task, which was displayed as a pop-up window. Participants were
-instructed to identify the direction of the center arrow on each trial
-as quickly and accurately as possible by pressing \enquote{z} if the
-arrow pointed left, and \enquote{m} if the arrow pointed right.
-Additionally, they were instructed to silently keep count of the number
-of trials that contained a feature. In the object context condition,
-they were asked to count trials that contained a certain color (blue or
-green) or object-identity (hat or chair) and in the social context
-conditions they were asked to count the number of trials that contained
-appeared a certain gender (male or female) or race (black or white).
-Periodically throughout the experiment, participants were asked to
-report how many trials they had counted until that point and to restart
-their count from 0. Halfway through the experiment participants received
-new instructions about which feature to count (see Figure 1C).
+All participants were AMT workers who found the experiment using the AMT system.
+The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board.
+Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form.
+Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window.
+Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing \enquote{z} if the arrow pointed left, and \enquote{m} if the arrow pointed right.
+Additionally, they were instructed to silently keep count of the number of trials that contained a feature.
+In the object context condition, they were asked to count trials that contained a certain color (blue or green) or object-identity (hat or chair) and in the social context conditions they were asked to count the number of trials that contained appeared a certain gender (male or female) or race (black or white).
+Periodically throughout the experiment, participants were asked to report how many trials they had counted until that point and to restart their count from 0.
+Halfway through the experiment participants received new instructions about which feature to count (see Figure 1C).
 
-Each trial began with a blank inter-stimulus interval (ISI) of 400 ms,
-followed by a fixation cross presented in the center of the screen for
-200 ms, then a second blank ISI of 400 ms. Next, the flanker and context
-stimuli appeared in the center of screen (the flanker above the context
-image; see Figure 1B) and remained on screen until a response was made.
-Following a response, accuracy feedback was presented for 1000 ms. A
-response automatically triggered the next trial.
+Each trial began with a blank inter-stimulus interval (ISI) of 400 ms, followed by a fixation cross presented in the center of the screen for 200 ms, then a second blank ISI of 400 ms.
+Next, the flanker and context stimuli appeared in the center of screen (the flanker above the context image; see Figure 1B) and remained on screen until a response was made.
+Following a response, accuracy feedback was presented for 1000 ms.
+A response automatically triggered the next trial.
 
-Halfway through the experiment (157 trials), participants received new
-instructions about which feature to count and to press the button
-on-screen when they were ready to continue.
+Halfway through the experiment (157 trials), participants received new instructions about which feature to count and to press the button on-screen when they were ready to continue.
 
@@
 \includegraphics{manuscript_files/figure-latex/figure2-1.pdf}
-\caption{\label{fig:figure2}Results from experiment 1 showing congruency effects
-(incongruent - congruent) for frequency unbiased items in reaction times
-(left) and error rates (right) as a function of the task-relevant
-context (100\% proportion congruent versus 0\% proportion congruent).}
+\caption{\label{fig:figure2}Results from experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent).}
 \end{figure}
 
-\section{Results}\label{results}
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
-Participants with mean error rates greater than 25\% were excluded from
-the analyses, eliminating 13 participants. For all remaining
-participants, the correct RTs from frequency unbiased trials in each
-condition were submitted to an outlier removal procedure. The
-non-recursive Van Selst and Jolicoeur outlier removal procedure was
-applied after removing response times greater than 3000 ms (Van Selst \&
-Jolicoeur, 1994). This procedure removed 3.39\% of the total
-observations.
+Participants with mean error rates greater than 25\% were excluded from the analyses, eliminating 13 participants.
+For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure.
+The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms (Van Selst \& Jolicoeur, 1994).
+This procedure removed 3.39\% of the total observations.
 
-The primary question of interest was whether the task-relevance of
-context features associated with different levels of conflict would
-influence the size of the congruency effect for frequency unbiased items
-(see Table 1). To that end, mean correct RTs and mean error rates from
-frequency unbiased trials were submitted to a mixed analysis of variance
-(ANOVA) with task-relevant context (0\% and 100\% PC) and unbiased-item
-congruency (congruent and incongruent) as within-subject factors, and
-context-type (object, social, and social/non-repeating) as the
-between-subjects factor.
+The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1).
+To that end, mean correct RTs and mean error rates from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
 
-The results of the RT analysis revealed the critical, two-way
-interaction between task-relevant context and unbiased-item congruency
-to be significant, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 1,608.54\),
-\(p = .005\), \(\hat{\eta}^2_p = .061\), demonstrating smaller
-congruency effects when the context dimension associated with high
-conflict was made task-relevant. Additionally, the three-way interaction
-between the task-relevant context, unbiased-item congruency, and
-context-type was non-significant, \(F(2, 128) = 0.00\),
-\(\mathit{MSE} = 1,608.54\), \(p = .996\), \(\hat{\eta}^2_p = .000\),
-showing no evidence for differences between the CSPC effects across
-context-type manipulations.
+The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 1,608.54\), \(p = .005\), \(\hat{\eta}^2_p = .061\), demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
+Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, \(F(2, 128) = 0.00\), \(\mathit{MSE} = 1,608.54\), \(p = .996\), \(\hat{\eta}^2_p = .000\), showing no evidence for differences between the CSPC effects across context-type manipulations.
 
-Similarly, the corresponding error analysis also resulted in a
-significant two-way interaction between the task-relevant context and
-unbiased-item congruency, \(F(1, 128) = 6.72\),
-\(\mathit{MSE} = 13.93\), \(p = .011\), \(\hat{\eta}^2_p = .050\), and a
-non-significant three-way interaction between task-relevant context,
-unbiased-item congruency, and context-type, \(F(2, 128) = 0.92\),
-\(\mathit{MSE} = 13.93\), \(p = .400\), \(\hat{\eta}^2_p = .014\).
-Therefore, the congruency effects in error rates were also smaller when
-the context dimension associated with high conflict was made
-task-relevant, corroborating the results of the reaction time analysis.
+Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 128) = 6.72\), \(\mathit{MSE} = 13.93\), \(p = .011\), \(\hat{\eta}^2_p = .050\), and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, \(F(2, 128) = 0.92\), \(\mathit{MSE} = 13.93\), \(p = .400\), \(\hat{\eta}^2_p = .014\).
+Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.
 
@@
 
-\section{General Discussion}\label{general-discussion}
+\hypertarget{general-discussion}{%
+\section{General Discussion}\label{general-discussion}}
 
-The aim of the current study was to determine whether task-relevance
-plays a role in the contextual recruitment of selective attention.
-Specifically, we tested whether manipulating the relative task-relevance
-of context cues could cause participants to ignore a previously learned
-context-association and apply a new association. We created a frequency
-unbiased context cue that shared features with two frequency biased
-contexts and used a feature-counting task to manipulate the
-task-relevance of context dimensions across two blocks of trials.
-Critically, halfway through the experiment participants received new
-instructions changing the task-relevant feature from one frequency
-biased cue to the other.
+The aim of the current study was to determine whether task-relevance plays a role in the contextual recruitment of selective attention.
+Specifically, we tested whether manipulating the relative task-relevance of context cues could cause participants to ignore a previously learned context-association and apply a new association.
+We created a frequency unbiased context cue that shared features with two frequency biased contexts and used a feature-counting task to manipulate the task-relevance of context dimensions across two blocks of trials.
+Critically, halfway through the experiment participants received new instructions changing the task-relevant feature from one frequency biased cue to the other.
 
-The key finding was that the congruency effects for the frequency
-unbiased items were significantly larger when the low-conflict context
-was made task-relevant as compared to when the high-conflict context was
-made task-relevant. This result is consistent with prior CSPC effects
-and, like the previous work, suggests that the context cues triggered
-rapid adjustments to attentional control (Crump \& Milliken, 2009).
-However, unlike prior studies, we were able to experimentally manipulate
-the CSPC effect across blocks of trials without changing any of the
-physical properties of the stimuli. This novel finding demonstrates that
-participants were able to learn and apply one context-attention
-association in the first phase, and subsequently ignore that association
-to learn a new association in the second phase.
+The key finding was that the congruency effects for the frequency unbiased items were significantly larger when the low-conflict context was made task-relevant as compared to when the high-conflict context was made task-relevant.
+This result is consistent with prior CSPC effects and, like the previous work, suggests that the context cues triggered rapid adjustments to attentional control (Crump \& Milliken, 2009).
+However, unlike prior studies, we were able to experimentally manipulate the CSPC effect across blocks of trials without changing any of the physical properties of the stimuli.
+This novel finding demonstrates that participants were able to learn and apply one context-attention association in the first phase, and subsequently ignore that association to learn a new association in the second phase.
 
-This result implicates an important role for task-relevance in producing
-CSPC phenomena. Crump et al. (2008) used shapes as context cues in a
-prime-probe Stroop task and did not find CSPC effects until the context
-cues were made task-relevant. Similarly, Cañadas et al. (2013)
-eliminated the CSPC effect by making the contextual cue effectively
-unrelated to the task. These studies suggest that task-relevance plays
-an important role in establishing associations between contextual
-information and attentional priorities to produce CSPC effects. Our
-finding extends this work in two important ways. First, we show that
-changing the task-relevance of the presented cues corresponded with a
-change in attentional control in the predicted direction. This
-demonstrates that task-relevance is also a key determinant of whether a
-previously learned attention-context association will be used or ignored
-in favor of a new association. Second, we show that task-relevance
-allowed participants resolve competition between two competing
-contextual cues, responding on the basis of one at the expense of the
-other. To our knowledge, this is the first demonstration that CSPC
-effects can be produced when there are multiple, overlapping contextual
-cues available.
+This result implicates an important role for task-relevance in producing CSPC phenomena.
+Crump et al.
+(2008) used shapes as context cues in a prime-probe Stroop task and did not find CSPC effects until the context cues were made task-relevant.
+Similarly, Cañadas et al.
+(2013) eliminated the CSPC effect by making the contextual cue effectively unrelated to the task.
+These studies suggest that task-relevance plays an important role in establishing associations between contextual information and attentional priorities to produce CSPC effects.
+Our finding extends this work in two important ways.
+First, we show that changing the task-relevance of the presented cues corresponded with a change in attentional control in the predicted direction.
+This demonstrates that task-relevance is also a key determinant of whether a previously learned attention-context association will be used or ignored in favor of a new association.
+Second, we show that task-relevance allowed participants resolve competition between two competing contextual cues, responding on the basis of one at the expense of the other.
+To our knowledge, this is the first demonstration that CSPC effects can be produced when there are multiple, overlapping contextual cues available.
 
-In light of prior work, we take this as evidence that the contextual
-recruitment of selective attention, although likely implicit, is not
-obligatory (e.g., Brosowsky \& Crump, 2016), requiring that
-environmental information be incorporated into the task representation.
-Similarly, there appears to be flexibility in which environmental
-features are selected and used to guide attention, which can be rapidly
-updated depending on the task-relevance of those features. Such a result
-lends some insight into how context-specific control might operate in
-more complex, real-world environments, where there is an over-abundance
-of environmental features that afford many different learned
-associations. From a theoretical perspective, this result is consistent
-memory-based accounts of CSPC phenomena (Brosowsky \& Crump, 2018; Bugg
-\& Hutchison, 2013; Crump \& Milliken, 2009; Crump et al., 2018, 2017).
-Under this view, a memory process encodes attentional priorities in the
-representation of individual experiences and, as a result, become
-associated with the environment where they were used. The subsequent
-reoccurrence of a prior context triggers the retrieval and reinstatement
-of those attentional priorities. Our results show however, that all the
-features of the environment may not be treated equally and that only
-task-relevant features are used to probe memory and guide attention.
+In light of prior work, we take this as evidence that the contextual recruitment of selective attention, although likely implicit, is not obligatory (e.g., Brosowsky \& Crump, 2016), requiring that environmental information be incorporated into the task representation.
+Similarly, there appears to be flexibility in which environmental features are selected and used to guide attention, which can be rapidly updated depending on the task-relevance of those features.
+Such a result lends some insight into how context-specific control might operate in more complex, real-world environments, where there is an over-abundance of environmental features that afford many different learned associations.
+From a theoretical perspective, this result is consistent memory-based accounts of CSPC phenomena (Brosowsky \& Crump, 2018; Bugg \& Hutchison, 2013; Crump et al., 2017, 2018; Crump \& Milliken, 2009).
+Under this view, a memory process encodes attentional priorities in the representation of individual experiences and, as a result, become associated with the environment where they were used.
+The subsequent reoccurrence of a prior context triggers the retrieval and reinstatement of those attentional priorities.
+Our results show however, that all the features of the environment may not be treated equally and that only task-relevant features are used to probe memory and guide attention.
 
-Another key result of this study concerned the different stimuli used as
-context cues. Across the three conditions, we varied the type of context
-image and dimensions. We manipulated the type of image presented,
-including both objects (identity and color dimensions) and faces (gender
-and racial dimensions). We also manipulated whether a single set of
-three repeating images were presented (object and social) or a set of
-non-repeating images were presented (social/non-repeating). Across all
-three conditions, we found no evidence that using different stimuli had
-an influence on the size or direction of the CSPC demonstrating
-generalizability of this phenomenon. Furthermore, CSPC effects were
-present even when using non-repeating images which suggests that
-context-dependency did not rely on image-specific associations but
-higher-order, learned categorical information.
+Another key result of this study concerned the different stimuli used as context cues.
+Across the three conditions, we varied the type of context image and dimensions.
+We manipulated the type of image presented, including both objects (identity and color dimensions) and faces (gender and racial dimensions).
+We also manipulated whether a single set of three repeating images were presented (object and social) or a set of non-repeating images were presented (social/non-repeating).
+Across all three conditions, we found no evidence that using different stimuli had an influence on the size or direction of the CSPC demonstrating generalizability of this phenomenon.
+Furthermore, CSPC effects were present even when using non-repeating images which suggests that context-dependency did not rely on image-specific associations but higher-order, learned categorical information.
 
-Traditional models of person perception posit that social categories are
-automatically activated in the presence of social stimuli (e.g., Brewer,
-1988; Devine, 1989; Fiske \& Neuberg, 1990). Cañadas et al. (2013)
-however, found that directing participants to think about faces in terms
-of individual features eliminated context-specific attention effect and
-suggested that momentary motivations may influence the automaticity of
-social categorization. Our results add to this literature by observing
-the influence of momentary motivations (i.e., task-relevance) when there
-is competition between two salient social categories. Specifically, we
-found that participants could categorize on the basis of one social cue
-at the expense of the other, and subsequently switch between them. These
-findings may speak to issues of automaticity in social categorization
-(Macrae \& Bodenhausen, 2001) as well as understanding how the
-situational context can prime one social identity over another (Crisp \&
-Hewstone, 2007). Furthermore, we found no evidence for differences
-between the social and object conditions. This suggests that
-categorization within the CSPC task is quickly and easily learned when
-the task supports such learning and is non-unique to social stimuli.
+Traditional models of person perception posit that social categories are automatically activated in the presence of social stimuli (e.g., Brewer, 1988; Devine, 1989; Fiske \& Neuberg, 1990).
+Cañadas et al.
+(2013) however, found that directing participants to think about faces in terms of individual features eliminated context-specific attention effect and suggested that momentary motivations may influence the automaticity of social categorization.
+Our results add to this literature by observing the influence of momentary motivations (i.e., task-relevance) when there is competition between two salient social categories.
+Specifically, we found that participants could categorize on the basis of one social cue at the expense of the other, and subsequently switch between them.
+These findings may speak to issues of automaticity in social categorization (Macrae \& Bodenhausen, 2001) as well as understanding how the situational context can prime one social identity over another (Crisp \& Hewstone, 2007).
+Furthermore, we found no evidence for differences between the social and object conditions.
+This suggests that categorization within the CSPC task is quickly and easily learned when the task supports such learning and is non-unique to social stimuli.
 
-In sum, our results provide new evidence that changes in task-relevance
-can update the contextual recruitment of selective attention in a CSPC
-flanker task. We demonstrated that making one context cue task-relevant
-produced a CSPC effect, even in the presence of a competing contextual
-cue. More important however, we found that changing the task-relevance
-of the contextual cues across blocks of trials was accompanied by
-predictable changes in the congruency effects. These effects were found
-to be generalizable across two different kinds of stimuli and occurred
-even when using non-repeating images, and implicate an important role
-for task-relevance in producing context-dependency and are consistent
-with memory-based accounts of CSPC phenomena.
+In sum, our results provide new evidence that changes in task-relevance can update the contextual recruitment of selective attention in a CSPC flanker task.
+We demonstrated that making one context cue task-relevant produced a CSPC effect, even in the presence of a competing contextual cue.
+More important however, we found that changing the task-relevance of the contextual cues across blocks of trials was accompanied by predictable changes in the congruency effects.
+These effects were found to be generalizable across two different kinds of stimuli and occurred even when using non-repeating images, and implicate an important role for task-relevance in producing context-dependency and are consistent with memory-based accounts of CSPC phenomena.
 
@@
 
-\section{References}\label{references}
+\hypertarget{references}{%
+\section{References}\label{references}}
 
 \begingroup
-\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
 
 \hypertarget{refs}{}
-\hypertarget{ref-abrahamse_grounding_2016}{}
-Abrahamse, E., Braem, S., Notebaert, W., \& Verguts, T. (2016).
-Grounding cognitive control in associative learning. \emph{Psychological
-Bulletin}, \emph{142}, 693--728.
+\leavevmode\hypertarget{ref-abrahamse_grounding_2016}{}%
+Abrahamse, E., Braem, S., Notebaert, W., \& Verguts, T.
+(2016).
+Grounding cognitive control in associative learning.
+\emph{Psychological Bulletin}, \emph{142}, 693--728.
 doi:\href{https://doi.org/10.1037/bul0000047}{10.1037/bul0000047}
 
-\hypertarget{ref-alards-tomalin_auditory_2017}{}
-Alards-Tomalin, D., Brosowsky, N. P., \& Mondor, T. A. (2017). Auditory
-statistical learning: Predictive frequency information affects the
-deployment of contextually mediated attentional resources on perceptual
-tasks. \emph{Journal of Cognitive Psychology}, \emph{29}, 977--987.
+\leavevmode\hypertarget{ref-alards-tomalin_auditory_2017}{}%
+Alards-Tomalin, D., Brosowsky, N.
+P., \& Mondor, T.
+A.
+(2017).
+Auditory statistical learning: Predictive frequency information affects the deployment of contextually mediated attentional resources on perceptual tasks.
+\emph{Journal of Cognitive Psychology}, \emph{29}, 977--987.
 doi:\href{https://doi.org/10.1080/20445911.2017.1353518}{10.1080/20445911.2017.1353518}
 
-\hypertarget{ref-blais_trial-by-trial_2015}{}
-Blais, C., Harris, M. B., Sinanian, M. H., \& Bunge, S. A. (2015).
-Trial-by-trial adjustments in control triggered by incidentally encoded
-semantic cues. \emph{The Quarterly Journal of Experimental Psychology},
-\emph{68}, 1920--1930.
+\leavevmode\hypertarget{ref-blais_trial-by-trial_2015}{}%
+Blais, C., Harris, M.
+B., Sinanian, M.
+H., \& Bunge, S.
+A.
+(2015).
+Trial-by-trial adjustments in control triggered by incidentally encoded semantic cues.
+\emph{The Quarterly Journal of Experimental Psychology}, \emph{68}, 1920--1930.
 doi:\href{https://doi.org/10.1080/17470218.2014.1000346}{10.1080/17470218.2014.1000346}
 
-\hypertarget{ref-brady_visual_2013}{}
-Brady, T. F., Konkle, T., Gill, J., Oliva, A., \& Alvarez, G. A. (2013).
-Visual long-term memory has the same limit on fidelity as visual working
-memory. \emph{Psychological Science}, \emph{24}, 981--990.
+\leavevmode\hypertarget{ref-brady_visual_2013}{}%
+Brady, T.
+F., Konkle, T., Gill, J., Oliva, A., \& Alvarez, G.
+A.
+(2013).
+Visual long-term memory has the same limit on fidelity as visual working memory.
+\emph{Psychological Science}, \emph{24}, 981--990.
 doi:\href{https://doi.org/10.1177/0956797612465439}{10.1177/0956797612465439}
 
-\hypertarget{ref-brewer_dual_1988}{}
-Brewer, M. B. (1988). A dual process model of impression formation. In
-R. S. Wyer Jr \& T. K. Srull (Eds.), \emph{A dual-process model of
-impression formation: Advances in social cognition} (Vol. 1, pp. 1--36).
+\leavevmode\hypertarget{ref-brewer_dual_1988}{}%
+Brewer, M.
+B.
+(1988).
+A dual process model of impression formation.
+In R.
+S.
+Wyer Jr \& T.
+K.
+Srull (Eds.), \emph{A dual-process model of impression formation: Advances in social cognition} (Vol.
+1, pp.
+1--36).
 Hillsdale, NJ: Erlbaum.
 
-\hypertarget{ref-brosowsky_context-specific_2016}{}
-Brosowsky, N. P., \& Crump, M. J. (2016). Context-specific attentional
-sampling: Intentional control as a pre-requisite for contextual control.
+\leavevmode\hypertarget{ref-brosowsky_context-specific_2016}{}%
+Brosowsky, N.
+P., \& Crump, M.
+J.
+(2016).
+Context-specific attentional sampling: Intentional control as a pre-requisite for contextual control.
 \emph{Consciousness and Cognition}, \emph{44}, 146--160.
@@
 
-\hypertarget{ref-brosowsky_memory-guided_2018}{}
-Brosowsky, N. P., \& Crump, M. J. C. (2018). Memory-guided selective
-attention: Single experiences with conflict have long-lasting effects on
-cognitive control. \emph{Journal of Experimental Psychology: General},
-\emph{147}, 1134--1153.
+\leavevmode\hypertarget{ref-brosowsky_memory-guided_2018}{}%
+Brosowsky, N.
+P., \& Crump, M.
+J.
+C.
+(2018).
+Memory-guided selective attention: Single experiences with conflict have long-lasting effects on cognitive control.
+\emph{Journal of Experimental Psychology: General}, \emph{147}, 1134--1153.
 doi:\href{https://doi.org/10.1037/xge0000431}{10.1037/xge0000431}
 
-\hypertarget{ref-bugg_conflict-triggered_2014}{}
-Bugg, J. (2014). Conflict-triggered top-down control: Default mode, last
-resort, or no such thing? \emph{Journal of Experimental Psychology:
-Learning, Memory, and Cognition}, \emph{40}(2), 567.
+\leavevmode\hypertarget{ref-bugg_conflict-triggered_2014}{}%
+Bugg, J. (2014). Conflict-triggered top-down control: Default mode, last resort, or no such thing? \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}(2), 567.
 
-\hypertarget{ref-bugg_support_2012}{}
-Bugg, J., \& Crump, M. J. (2012). In support of a distinction between
-voluntary and stimulus-driven control: A review of the literature on
-proportion congruent effects. \emph{Frontiers in Psychology}, \emph{3},
-367.
+\leavevmode\hypertarget{ref-bugg_support_2012}{}%
+Bugg, J., \& Crump, M.
+J.
+(2012).
+In support of a distinction between voluntary and stimulus-driven control: A review of the literature on proportion congruent effects.
+\emph{Frontiers in Psychology}, \emph{3}, 367.
 doi:\href{https://doi.org/10.3389/fpsyg.2012.00367}{10.3389/fpsyg.2012.00367}
 
-\hypertarget{ref-bugg_converging_2013}{}
-Bugg, J., \& Hutchison, K. A. (2013). Converging evidence for control of
-color--word Stroop interference at the item level. \emph{Journal of
-Experimental Psychology: Human Perception and Performance},
-\emph{39}(2), 433.
+\leavevmode\hypertarget{ref-bugg_converging_2013}{}%
+Bugg, J., \& Hutchison, K.
+A.
+(2013).
+Converging evidence for control of color--word Stroop interference at the item level.
+\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{39}(2), 433.
 
-\hypertarget{ref-bugg_multiple_2008}{}
-Bugg, J., Jacoby, L. L., \& Toth, J. P. (2008). Multiple levels of
-control in the Stroop task. \emph{Memory \& Cognition}, \emph{36},
-1484--1494.
+\leavevmode\hypertarget{ref-bugg_multiple_2008}{}%
+Bugg, J., Jacoby, L.
+L., \& Toth, J.
+P.
+(2008).
+Multiple levels of control in the Stroop task.
+\emph{Memory \& Cognition}, \emph{36}, 1484--1494.
 doi:\href{https://doi.org/10.3758/MC.36.8.1484}{10.3758/MC.36.8.1484}
 
-\hypertarget{ref-canadas_social_2013}{}
-Cañadas, E., Rodríguez-Bailón, R., Milliken, B., \& Lupiáñez, J. (2013).
-Social categories as a context for the allocation of attentional
-control. \emph{Journal of Experimental Psychology: General}, \emph{142},
-934--943. doi:\href{https://doi.org/10.1037/a0029794}{10.1037/a0029794}
+\leavevmode\hypertarget{ref-canadas_social_2013}{}%
+Cañadas, E., Rodríguez-Bailón, R., Milliken, B., \& Lupiáñez, J.
+(2013).
+Social categories as a context for the allocation of attentional control.
+\emph{Journal of Experimental Psychology: General}, \emph{142}, 934--943.
+doi:\href{https://doi.org/10.1037/a0029794}{10.1037/a0029794}
 
-\hypertarget{ref-corballis_independent_2003}{}
-Corballis, P. M., \& Gratton, G. (2003). Independent control of
-processing strategies for different locations in the visual field.
+\leavevmode\hypertarget{ref-corballis_independent_2003}{}%
+Corballis, P.
+M., \& Gratton, G.
+(2003).
+Independent control of processing strategies for different locations in the visual field.
 \emph{Biological Psychology}, \emph{64}, 191--209.
@@
 
-\hypertarget{ref-crisp_multiple_2007}{}
-Crisp, R. J., \& Hewstone, M. (2007). Multiple social categorization.
-\emph{Advances in Experimental Social Psychology}, \emph{39}, 163--254.
+\leavevmode\hypertarget{ref-crisp_multiple_2007}{}%
+Crisp, R. J., \& Hewstone, M. (2007). Multiple social categorization. \emph{Advances in Experimental Social Psychology}, \emph{39}, 163--254.
 
-\hypertarget{ref-crump_learning_2016}{}
-Crump, M. J. (2016). Learning to selectively attend from
-context-specific attentional histories: A demonstration and some
-constraints. \emph{Canadian Journal of Experimental Psychology/Revue
-Canadienne de Psychologie Expérimentale}, \emph{70}, 59--77.
+\leavevmode\hypertarget{ref-crump_learning_2016}{}%
+Crump, M.
+J.
+(2016).
+Learning to selectively attend from context-specific attentional histories: A demonstration and some constraints.
+\emph{Canadian Journal of Experimental Psychology/Revue Canadienne de Psychologie Expérimentale}, \emph{70}, 59--77.
 doi:\href{https://doi.org/10.1037/cep0000066}{10.1037/cep0000066}
 
-\hypertarget{ref-crump_flexibility_2009}{}
-Crump, M. J. C., \& Milliken, B. (2009). The flexibility of
-context-specific control: Evidence for context-driven generalization of
-item-specific control settings. \emph{The Quarterly Journal of
-Experimental Psychology}, \emph{62}, 1523--1532.
+\leavevmode\hypertarget{ref-crump_reproducing_2017}{}%
+Crump, M.
+J., Brosowsky, N.
+P., \& Milliken, B.
+(2017).
+Reproducing the location-based context-specific proportion congruent effect for frequency unbiased items: A reply to Hutcheon and Spieler (2016).
+\emph{The Quarterly Journal of Experimental Psychology}, \emph{70}, 1792--1807.
+doi:\href{https://doi.org/10.1080/17470218.2016.1206130}{10.1080/17470218.2016.1206130}
+
+\leavevmode\hypertarget{ref-crump_flexibility_2009}{}%
+Crump, M.
+J.
+C., \& Milliken, B.
+(2009).
+The flexibility of context-specific control: Evidence for context-driven generalization of item-specific control settings.
+\emph{The Quarterly Journal of Experimental Psychology}, \emph{62}, 1523--1532.
 doi:\href{https://doi.org/10.1080/17470210902752096}{10.1080/17470210902752096}
 
-\hypertarget{ref-crump_context-dependent_2018}{}
-Crump, M. J. C., Milliken, B., Leboe-McGowan, J., Leboe-McGowan, L., \&
-Gao, X. (2018). Context-Dependent Control of Attention Capture: Evidence
-From Proportion Congruent Effects. \emph{Canadian Journal of
-Experimental Psychology= Revue Canadienne de Psychologie Experimentale},
-\emph{74}, 91--104.
+\leavevmode\hypertarget{ref-crump_context-dependent_2018}{}%
+Crump, M.
+J.
+C., Milliken, B., Leboe-McGowan, J., Leboe-McGowan, L., \& Gao, X.
+(2018).
+Context-Dependent Control of Attention Capture: Evidence From Proportion Congruent Effects.
+\emph{Canadian Journal of Experimental Psychology= Revue Canadienne de Psychologie Experimentale}, \emph{74}, 91--104.
 
-\hypertarget{ref-crump_reproducing_2017}{}
-Crump, M. J., Brosowsky, N. P., \& Milliken, B. (2017). Reproducing the
-location-based context-specific proportion congruent effect for
-frequency unbiased items: A reply to Hutcheon and Spieler (2016).
-\emph{The Quarterly Journal of Experimental Psychology}, \emph{70},
-1792--1807.
-doi:\href{https://doi.org/10.1080/17470218.2016.1206130}{10.1080/17470218.2016.1206130}
-
-\hypertarget{ref-crump_context-specific_2006}{}
-Crump, M. J., Gong, Z., \& Milliken, B. (2006). The context-specific
-proportion congruent Stroop effect: Location as a contextual cue.
+\leavevmode\hypertarget{ref-crump_context-specific_2006}{}%
+Crump, M.
+J., Gong, Z., \& Milliken, B.
+(2006).
+The context-specific proportion congruent Stroop effect: Location as a contextual cue.
 \emph{Psychonomic Bulletin \& Review}, \emph{13}, 316--321.
@@
 
-\hypertarget{ref-fischer_predicting_2015}{}
-Fischer, R., \& Dreisbach, G. (2015). Predicting high levels of
-multitasking reduces between-tasks interactions., \emph{41}, 1482--1487.
+\leavevmode\hypertarget{ref-fischer_predicting_2015}{}%
+Fischer, R., \& Dreisbach, G.
+(2015).
+Predicting high levels of multitasking reduces between-tasks interactions., \emph{41}, 1482--1487.
 Retrieved from \url{http://psycnet.apa.org/psycinfo/2015-47211-001/}
 
-\hypertarget{ref-fischer_context-sensitive_2014}{}
-Fischer, R., Gottschalk, C., \& Dreisbach, G. (2014). Context-sensitive
-adjustment of cognitive control in dual-task performance. \emph{Journal
-of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40},
-399.
+\leavevmode\hypertarget{ref-fischer_context-sensitive_2014}{}%
+Fischer, R., Gottschalk, C., \& Dreisbach, G.
+(2014).
+Context-sensitive adjustment of cognitive control in dual-task performance.
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}, 399.
 
-\hypertarget{ref-fiske_continuum_1990}{}
-Fiske, S. T., \& Neuberg, S. L. (1990). A continuum of impression
-formation, from category-based to individuating processes: Influences of
-information and motivation on attention and interpretation. In
-\emph{Advances in experimental social psychology} (Vol. 23, pp. 1--74).
+\leavevmode\hypertarget{ref-fiske_continuum_1990}{}%
+Fiske, S.
+T., \& Neuberg, S.
+L.
+(1990).
+A continuum of impression formation, from category-based to individuating processes: Influences of information and motivation on attention and interpretation.
+In \emph{Advances in experimental social psychology} (Vol.
+23, pp.
+1--74).
 Elsevier.
 
-\hypertarget{ref-hutcheon_limits_2017}{}
-Hutcheon, T. G., \& Spieler, D. H. (2017). Limits on the
-generalizability of context-driven control. \emph{Quarterly Journal of
-Experimental Psychology}, \emph{70}, 1292--1304.
+\leavevmode\hypertarget{ref-hutcheon_limits_2017}{}%
+Hutcheon, T.
+G., \& Spieler, D.
+H.
+(2017).
+Limits on the generalizability of context-driven control.
+\emph{Quarterly Journal of Experimental Psychology}, \emph{70}, 1292--1304.
 doi:\href{https://doi.org/10.1080/17470218.2016.1182193}{10.1080/17470218.2016.1182193}
 
-\hypertarget{ref-hubner_location-specific_2016}{}
-Hübner, R., \& Mishra, S. (2016). Location-specific attentional control
-is also possible in the Simon task. \emph{Psychonomic Bulletin \&
-Review}, \emph{23}, 1867--1872.
+\leavevmode\hypertarget{ref-hubner_location-specific_2016}{}%
+Hübner, R., \& Mishra, S.
+(2016).
+Location-specific attentional control is also possible in the Simon task.
+\emph{Psychonomic Bulletin \& Review}, \emph{23}, 1867--1872.
 doi:\href{https://doi.org/10.3758/s13423-016-1057-y}{10.3758/s13423-016-1057-y}
 
-\hypertarget{ref-king_priming_2012}{}
-King, J. A., Korb, F. M., \& Egner, T. (2012). Priming of control:
-Implicit contextual cuing of top-down attentional set. \emph{The Journal
-of Neuroscience}, \emph{32}, 8192--8200.
+\leavevmode\hypertarget{ref-king_priming_2012}{}%
+King, J.
+A., Korb, F.
+M., \& Egner, T.
+(2012).
+Priming of control: Implicit contextual cuing of top-down attentional set.
+\emph{The Journal of Neuroscience}, \emph{32}, 8192--8200.
 doi:\href{https://doi.org/10.1523/JNEUROSCI.0934-12.2012}{10.1523/JNEUROSCI.0934-12.2012}
 
-\hypertarget{ref-logan_attention_1980}{}
-Logan, G. D. (1980). Attention and automaticity in Stroop and priming
-tasks: Theory and data. \emph{Cognitive Psychology}, \emph{12},
-523--553.
+\leavevmode\hypertarget{ref-logan_attention_1980}{}%
+Logan, G. D. (1980). Attention and automaticity in Stroop and priming tasks: Theory and data. \emph{Cognitive Psychology}, \emph{12}, 523--553.
 
-\hypertarget{ref-logan_what_1998}{}
-Logan, G. D. (1998). What is learned during automatization? II.
-obligatory encoding of spatial location. \emph{Journal of Experimental
-Psychology: Human Perception and Performance}, \emph{24}, 1720.
+\leavevmode\hypertarget{ref-logan_what_1998}{}%
+Logan, G. D. (1998). What is learned during automatization? II. Obligatory encoding of spatial location. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{24}, 1720.
 
-\hypertarget{ref-logan_when_1979}{}
-Logan, G. D., \& Zbrodoff, N. J. (1979). When it helps to be misled:
-Facilitative effects of increasing the frequency of conflicting stimuli
-in a Stroop-like task. \emph{Memory \& Cognition}, \emph{7}, 166--174.
+\leavevmode\hypertarget{ref-logan_when_1979}{}%
+Logan, G.
+D., \& Zbrodoff, N.
+J.
+(1979).
+When it helps to be misled: Facilitative effects of increasing the frequency of conflicting stimuli in a Stroop-like task.
+\emph{Memory \& Cognition}, \emph{7}, 166--174.
 doi:\href{https://doi.org/10.3758/BF03197535}{10.3758/BF03197535}
 
-\hypertarget{ref-logan_strategies_1984}{}
-Logan, G. D., Zbrodoff, N. J., \& Williamson, J. (1984). Strategies in
-the color-word Stroop task. \emph{Bulletin of the Psychonomic Society},
-\emph{22}, 135--138.
+\leavevmode\hypertarget{ref-logan_strategies_1984}{}%
+Logan, G. D., Zbrodoff, N. J., \& Williamson, J. (1984). Strategies in the color-word Stroop task. \emph{Bulletin of the Psychonomic Society}, \emph{22}, 135--138.
 
-\hypertarget{ref-lowe_selective_1982}{}
-Lowe, D. G., \& Mitterer, J. O. (1982). Selective and divided Attention
-in a Stroop task. \emph{Canadian Journal of Psychology/Revue Canadienne
-de Psychologie}, \emph{36}(4), 684.
+\leavevmode\hypertarget{ref-lowe_selective_1982}{}%
+Lowe, D. G., \& Mitterer, J. O. (1982). Selective and divided Attention in a Stroop task. \emph{Canadian Journal of Psychology/Revue Canadienne de Psychologie}, \emph{36}(4), 684.
 
-\hypertarget{ref-ma_chicago_2015}{}
-Ma, D. S., Correll, J., \& Wittenbrink, B. (2015). The Chicago face
-database: A free stimulus set of faces and norming data. \emph{Behavior
-Research Methods}, \emph{47}, 1122--1135.
+\leavevmode\hypertarget{ref-ma_chicago_2015}{}%
+Ma, D.
+S., Correll, J., \& Wittenbrink, B.
+(2015).
+The Chicago face database: A free stimulus set of faces and norming data.
+\emph{Behavior Research Methods}, \emph{47}, 1122--1135.
 doi:\href{https://doi.org/10.3758/s13428-014-0532-5}{10.3758/s13428-014-0532-5}
 
-\hypertarget{ref-macrae_social_2001}{}
-Macrae, C. N., \& Bodenhausen, G. V. (2001). Social cognition:
-Categorical person perception. \emph{British Journal of Psychology},
-\emph{92}, 239--255.
+\leavevmode\hypertarget{ref-macrae_social_2001}{}%
+Macrae, C. N., \& Bodenhausen, G. V. (2001). Social cognition: Categorical person perception. \emph{British Journal of Psychology}, \emph{92}, 239--255.
 
-\hypertarget{ref-mayr_spatial_1996}{}
-Mayr, U. (1996). Spatial attention and implicit sequence learning:
-Evidence for independent learning of spatial and nonspatial sequences.
-\emph{Journal of Experimental Psychology: Learning, Memory, and
-Cognition}, \emph{22}, 350.
+\leavevmode\hypertarget{ref-mayr_spatial_1996}{}%
+Mayr, U.
+(1996).
+Spatial attention and implicit sequence learning: Evidence for independent learning of spatial and nonspatial sequences.
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{22}, 350.
 
-\hypertarget{ref-mayr_outsourcing_2007}{}
-Mayr, U., \& Bryck, R. L. (2007). Outsourcing control to the
-environment: Effects of stimulus/response locations on task selection.
+\leavevmode\hypertarget{ref-mayr_outsourcing_2007}{}%
+Mayr, U., \& Bryck, R.
+L.
+(2007).
+Outsourcing control to the environment: Effects of stimulus/response locations on task selection.
 \emph{Psychological Research}, \emph{71}, 107--116.
@@
 
-\hypertarget{ref-schmidt_stroop_2008}{}
-Schmidt, J. R., \& Besner, D. (2008). The Stroop effect: Why proportion
-congruent has nothing to do with congruency and everything to do with
-contingency. \emph{Journal of Experimental Psychology: Learning, Memory,
-and Cognition}, \emph{34}, 514--523.
+\leavevmode\hypertarget{ref-schmidt_stroop_2008}{}%
+Schmidt, J.
+R., \& Besner, D.
+(2008).
+The Stroop effect: Why proportion congruent has nothing to do with congruency and everything to do with contingency.
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{34}, 514--523.
 doi:\href{https://doi.org/10.1037/0278-7393.34.3.514}{10.1037/0278-7393.34.3.514}
 
-\hypertarget{ref-stroop_studies_1935}{}
-Stroop, J. R. (1935). Studies of interference in serial verbal
-reactions. \emph{Journal of Experimental Psychology}, \emph{18}, 643.
-doi:\href{https://doi.org/10.1037/h0054651}{10.1037/h0054651}
+\leavevmode\hypertarget{ref-stroop_studies_1935}{}%
+Stroop, J. R. (1935). Studies of interference in serial verbal reactions. \emph{Journal of Experimental Psychology}, \emph{18}, 643. doi:\href{https://doi.org/10.1037/h0054651}{10.1037/h0054651}
 
-\hypertarget{ref-tottenham_nimstim_2009}{}
-Tottenham, N., Tanaka, J. W., Leon, A. C., McCarry, T., Nurse, M., Hare,
-T. A., \ldots{} Nelson, C. (2009). The NimStim set of facial
-expressions: Judgments from untrained research participants.
+\leavevmode\hypertarget{ref-tottenham_nimstim_2009}{}%
+Tottenham, N., Tanaka, J.
+W., Leon, A.
+C., McCarry, T., Nurse, M., Hare, T.
+A., \ldots{} Nelson, C.
+(2009).
+The NimStim set of facial expressions: Judgments from untrained research participants.
 \emph{Psychiatry Research}, \emph{168}, 242--249.
@@
 
-\hypertarget{ref-van_selst_solution_1994}{}
-Van Selst, M., \& Jolicoeur, P. (1994). A solution to the effect of
-sample size on outlier elimination. \emph{The Quarterly Journal of
-Experimental Psychology Section A}, \emph{47}, 631--650.
+\leavevmode\hypertarget{ref-van_selst_solution_1994}{}%
+Van Selst, M., \& Jolicoeur, P.
+(1994).
+A solution to the effect of sample size on outlier elimination.
+\emph{The Quarterly Journal of Experimental Psychology Section A}, \emph{47}, 631--650.
 doi:\href{https://doi.org/10.1080/14640749408401131}{10.1080/14640749408401131}
 
-\hypertarget{ref-vietze_context_2009}{}
-Vietze, I., \& Wendt, M. (2009). Context specificity of conflict
-frequency-dependent control. \emph{The Quarterly Journal of Experimental
-Psychology}, \emph{62}, 1391--1400.
+\leavevmode\hypertarget{ref-vietze_context_2009}{}%
+Vietze, I., \& Wendt, M.
+(2009).
+Context specificity of conflict frequency-dependent control.
+\emph{The Quarterly Journal of Experimental Psychology}, \emph{62}, 1391--1400.
 doi:\href{https://doi.org/10.1080/17470210802426908}{10.1080/17470210802426908}
 
-\hypertarget{ref-weidler_transfer_2016}{}
-Weidler, B. J., \& Bugg, J. (2016). Transfer of location-specific
-control to untrained locations. \emph{The Quarterly Journal of
-Experimental Psychology}, \emph{69}, 2202--2217.
+\leavevmode\hypertarget{ref-weidler_transfer_2016}{}%
+Weidler, B.
+J., \& Bugg, J.
+(2016).
+Transfer of location-specific control to untrained locations.
+\emph{The Quarterly Journal of Experimental Psychology}, \emph{69}, 2202--2217.
 doi:\href{https://doi.org/10.1080/17470218.2015.1111396}{10.1080/17470218.2015.1111396}
 
-\hypertarget{ref-weidler_attentional_2018}{}
-Weidler, B. J., Dey, A., \& Bugg, J. (2018). Attentional control
-transfers beyond the reference frame. \emph{Psychological Research},
-1--14.
+\leavevmode\hypertarget{ref-weidler_attentional_2018}{}%
+Weidler, B. J., Dey, A., \& Bugg, J. (2018). Attentional control transfers beyond the reference frame. \emph{Psychological Research}, 1--14.
 
-\hypertarget{ref-west_effects_1998}{}
-West, R., \& Baylis, G. C. (1998). Effects of increased response
-dominance and contextual disintegration on the Stroop interference
-effect in older adults. \emph{Psychology and Aging}, \emph{13}, 206.
+\leavevmode\hypertarget{ref-west_effects_1998}{}%
+West, R., \& Baylis, G. C. (1998). Effects of increased response dominance and contextual disintegration on the Stroop interference effect in older adults. \emph{Psychology and Aging}, \emph{13}, 206.
 

### 2019-06-30 manuscript_pretty.Rmd
begin revisions / add expo

--- 2019-01-22 manuscript.Rmd
@@
 wordcount         : "4024 \\vspace{2mm} \\par \\textit{Public Significance Statement:} Contextual cues have been shown to automatically trigger adjustments in selective attention independent of awareness and intention.
-Here, we find the task-relevance plays an important role in determining which context cues are used to direct attention.
+Here, we find that task-relevance plays an important role in determining which context cues are used to direct attention.
 These findings contribute to a better understanding of how context-dependency might occur in more complex environments and more generally, how learning and memory processes enable flexible control over attention."
@@
 
+indent: TRUE
 #output: 
@@
 header-includes:
-  - \usepackage{setspace}\doublespacing 
-  - \newenvironment{zeroindent}
-     {\par\setlength{\parindent}{0pt}}
-     {\par}  
+  - \usepackage{setspace}\singlespacing 
+  # - \newenvironment{zeroindent}
+  #    {\par\setlength{\parindent}{5pt}}
+  #    {\par}  
   - \setlength{\parskip}{0pt}
@@
 
-source("data-analysis/analysis.R")
+source("data-analysis/analysis_E1.R")
+source("data-analysis/analysis_E2.R")
+source("data-analysis/analysis_E3.R")
 source("data-analysis/table1.R")
+source("data-analysis/analysis_E1_Exploratory.R")
 ```
@@
 As a result, automatic memory-based retrieval allows attentional priorities to be rapidly adjusted in a context-appropriate fashion.
+How associations between attentional priorities and context cues are formed and used still remains unclear however.
+The current study addresses two issues.
+
+First, how is attentional control resolved when multiple contextual features could be used as cues?
+Second, it remains unclear how  Historically, theories of automaticity and attentional control have emphasized the role of practice and likened the process to skill-learning ().
+
 However, the obligatory nature of memory-based attentional control remains unclear, in particular in situations when multiple contextual features could be used as cues for retrieval.
+
+<!-- 
+Furthermore, understanding how associations are formed and used is not well understood.
+Theories of automaticity and attentional control historically have emphasized the role of practice - difficult to suppress once learned..
+Shiffrin and Schneider, Treisman, etc..
+everyone basically.
+
+Early CSPC work too thought that practice is important for "associations to form"
+
+Memory-based theories on the other hand, take a more nuanced view.
+Practice is only important to the extent that improves memory retrieval.
+If retrieval cues can --  distinguish between prior episodes.
+
+Therefore, the skill-learning view of automaticity would predict that associations take time to develop through practice, and once learned, difficult to suppress. 
+-->
 
@@
 
-# The Current Study
+# Experiment 1
 
@@
 ```{r figure1, echo=FALSE, fig.width=6.7,fig.height=4.51, fig.cap='(ref:figure1)'}
+#, out.width="\\textwidth", fig.env="figure*"
 knitr::include_graphics("images/Task.jpg")
@@
 ```{r figure2, echo=FALSE,fig.width=6.875, fig.height= 4, fig.cap='(ref:figure2)'}
+#, out.width="\\textwidth", fig.env="figure*"
 #print figure 2
@@
 
-(ref:figure2) Results from experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent).
+(ref:figure2) Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent).
+Task-relevance was manipulated by the secondary feature-counting task.
 
@@
 
-```{r echo = FALSE, warning = FALSE, message=FALSE, results='asis'}
-#print latex table
+## Exploratory Analyses: Order Effects
+
+```{r figure2b, echo=FALSE,fig.width=6.875, fig.height= 4, fig.cap='(ref:figure2)'}
+#, out.width="\\textwidth", fig.env="figure*"
+#print figure 2
+#source: data-analysis/analysis.R
+figure2B
+```
+
+Previous work has shown that the effects of shifting between list-wide proportion congruent phases is asymmetrical.
+Abrahamse et al....
+found that...
+In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from one context cue to another.
+We therefore randomized the order across participants to control for the effects of order.
+However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was symmetrical in our study.
+
+To address this question, we collapsed over context-type and categorized participants according to the order of the counting task: 100% congruent to 0% congruent (100%-0%) or 0% congruent to 100% congruent (0%-100%).
+We again removed participants with error rates greater than 25% and adopted the same outlier removal procedure as described above.
+We submitted mean correct RTs for frequency unbiased items to a 2x2x2 mixed ANOVA with task-relevant context (0% and 100% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and phase order (100%-0% and 0%-100%) as the between-subjects factor.
+
+Consistent with the original analysis, two-way interaction between task-relevant context and congruency remained significant,`r E1_Order_A$Congruency_Task_Relevant_Context`.
+However, the three-way interaction was non-significant, `r E1_Order_A$Order_Congruency_Task_Relevant_Context`.
+Therefor, we did not find statistical support for a list-shift asymmetry.
+Additionally, the asymmetry we do see in this sample is in the opposite direction than would be predicted given the prior results ().
+
+We also conducted a more severe test of the list-shift hypothesis.
+Abrahamse et al.'s interpretation of the list shift effect was that participants had to learn to adjust to the new cues.
+Therefore, we might expect that any asymmetry would be exaggerated near the point of transition.
+We repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.
+
+Again, the three-way interaction was non-significant, `r E1_Order_B$Order_Congruency_Task_Relevant_Context`.
+Interestingly, the two-way interaction between congruency and task-relevant context is also still significant, `r E1_Order_B$Congruency_Task_Relevant_Context`.
+This result supports the notion there was no asymmetry and that the shift in context-dependent effects occur almost immediately after the transition.
+
+```{r echo=FALSE, results='asis'}
+#, fig.align="center", fig.cap="" ,out.width="\\textwidth", fig.env="figure*"
 cat(TR_Table)
+
+#knitr::include_graphics("images/table1.pdf")
 ```
+
+<!-- ```{r echo=FALSE, echo = FALSE, warning = FALSE, message=FALSE, results='asis', out.width="\\textwidth"} -->
+<!-- #print latex table -->
+<!-- cat(TR_Table) -->
+<!-- ``` -->
+
+# Experiment 2
+
+In Experiment 1, we found that
+
+# Methods
+
+## Participants
+All participants were recruited from Amazon Mechanical Turk (AMT) and compensated $2.00 for participating.
+The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by $6.00 per hour.
+For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study.
+Participants were included in the study if they completed all trials.
+We posted 50 HITs and 50 participants completed all trials.
+
+## Apparatus & Stimuli
+
+The apparatus and stimuli were identical to Experiment 1. The context stimuli were identical to those used for the object condition in Experiment 1.
+
+## Design 
+Experiment 1 used a 2x3 within-subjects design with proportion congruent (25%, 50%, and 75%) and  congruency (congruent and incongruent) as factors.
+The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials or instructions informing participants about the proportion manipulations.
+The design in every other respect was identical to Experiment 1.
+
+## Procedure
+All participants were AMT workers who found the experiment using the AMT system.
+The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board.
+Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form.
+Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window.
+Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing 'z' if the arrow pointed left, and 'm' if the arrow pointed right.
+
+Each trial began with a blank inter-stimulus interval (ISI) of 400 ms, followed by a fixation cross presented in the center of the screen for 200 ms, then a second blank ISI of 400 ms.
+Next, the flanker and context stimuli appeared in the center of screen (the flanker above the context image; see Figure 1B) and remained on screen until a response was made.
+Following a response, accuracy feedback was presented for 1000 ms.
+A response automatically triggered the next trial.
+
+```{r figure3, echo=FALSE, fig.width=3.6, fig.height=4, fig.cap='(ref:figure3)'}
+#print figure 3
+#source: data-analysis/analysis_E2.R
+figure3
+```
+
+(ref:figure3) Results from Experiment 2 showing congruency effects (incongruent - congruent) across proportion congruency (25%, 75%, and 100% PC) in reaction times (left) and error rates (right).
+
+# Results
+Participants with mean error rates greater than 25% were excluded from the analyses, eliminating `r N_subjects_removed_E2` participants.
+For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure.
+The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms [@van_selst_solution_1994].
+This procedure removed `r round(percent_removed_E2*100,digits = 2)`% of the total observations.
+
+The questions of interest were whether participants would learn the associations between the context cues without the task-relevance manipulation (i.e., the counting task) and whether responding to the unbiased cues would be influenced by the presence of the biased cues.
+To that end, mean correct RTs and mean error rates were submitted to an analysis of variance (ANOVA) with proportion congruent (25%, 50%, and 75%) and congruency (congruent and incongruent) as within-subject factors.
+
+The results of the RT analysis revealed the critical, two-way interaction between proportion congruency and congruency to be non-significant, `r RT_ANOVA_E2$PC_Congruency`.
+Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA_E2$PC_Congruency`.
+Therefore, there was no evidence that the context cues, absent the counting task, systematically influenced the congruency effect.
+
+# Experiment 3
+
+# Methods
+
+## Participants
+All participants were recruited from Amazon Mechanical Turk (AMT) and compensated $2.00 for participating.
+The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by $6.00 per hour.
+For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study.
+Participants were included in the study if they completed all trials.
+We posted 50 HITs and 50 participants completed all trials.
+
+## Apparatus & Stimuli
+
+The apparatus and stimuli were identical to Experiment 1. The context stimuli were identical to those used for the object condition in Experiment 1.
+
+## Design 
+Experiment 1 used a 2x3 within-subjects design with proportion congruent (25%, 50%, and 75%) and  congruency (congruent and incongruent) as factors.
+The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials or instructions informing participants about the proportion manipulations.
+The design in every other respect was identical to Experiment 1.
+
+## Procedure
+All participants were AMT workers who found the experiment using the AMT system.
+The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board.
+Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form.
+Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window.
+Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing 'z' if the arrow pointed left, and 'm' if the arrow pointed right.
+
+Each trial began with a blank inter-stimulus interval (ISI) of 400 ms, followed by a fixation cross presented in the center of the screen for 200 ms, then a second blank ISI of 400 ms.
+Next, the flanker and context stimuli appeared in the center of screen (the flanker above the context image; see Figure 1B) and remained on screen until a response was made.
+Following a response, accuracy feedback was presented for 1000 ms.
+A response automatically triggered the next trial.
+
+```{r figure4, echo=FALSE, fig.cap='(ref:figure4)', fig.width=3.6, fig.height=3.5}
+#print figure 3
+#source: data-analysis/analysis_E2.R
+figure4
+```
+
+(ref:figure4) Results from Experiment 3 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent).
+Task-relevance was manipulated through explicit instructions.
+
+# Results
+Participants with mean error rates greater than 25% were excluded from the analyses, eliminating `r N_subjects_removed_E3` participants.
+For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure.
+The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms [@van_selst_solution_1994].
+This procedure removed `r round(percent_removed_E3*100,digits = 2)`% of the total observations.
+
+The primary question of interest was whether the task-relevance of context features (made relevant through explicit task instructions) associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items.
+Mean correct RTs and mean error rates from frequency unbiased trials were submitted to an analysis of variance (ANOVA) with task-relevant context (0% and 100% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors.
+
+The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be non-significant, `r RT_ANOVA_E3$Task_Relevant_Context_Congruency`.
+Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA_E3$Task_Relevant_Context_Congruency`.
 
@@
 
-\newpage
-
 # References

### 2019-06-30 manuscript_pretty.tex
begin revisions / add expo

--- 2019-01-23 manuscript.tex
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 \newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-\usepackage{setspace}\doublespacing
-\newenvironment{zeroindent} {\par\setlength{\parindent}{0pt}} {\par}
+\usepackage{setspace}
+
+\singlespacing
 \setlength{\parskip}{0pt}
@@
 
-\hypertarget{the-current-study}{%
-\section{The Current Study}\label{the-current-study}}
+\hypertarget{experiment-1}{%
+\section{Experiment 1}\label{experiment-1}}
 
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/figure2-1.pdf}
-\caption{\label{fig:figure2}Results from experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent).}
+\includegraphics{manuscript_pretty_files/figure-latex/figure2-1.pdf}
+\caption{\label{fig:figure2}Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent).
+Task-relevance was manipulated by the secondary feature-counting task.}
 \end{figure}
@@
 Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.
+
+\hypertarget{exploratory-analyses-order-effects}{%
+\subsection{Exploratory Analyses: Order Effects}\label{exploratory-analyses-order-effects}}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_pretty_files/figure-latex/figure2b-1.pdf}
+\caption{\label{fig:figure2b}Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent).
+Task-relevance was manipulated by the secondary feature-counting task.}
+\end{figure}
+
+Previous work has shown that the effects of shifting between list-wide proportion congruent phases is asymmetrical.
+Abrahamse et al\ldots{}.
+found that\ldots{} In our study, we were primarily interested in whether participants could use context cues despite the presence of competing, contradictory cues, and whether they could switch from one context cue to another.
+We therefore randomized the order across participants to control for the effects of order.
+However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was symmetrical in our study.
+
+To address this question, we collapsed over context-type and categorized participants according to the order of the counting task: 100\% congruent to 0\% congruent (100\%-0\%) or 0\% congruent to 100\% congruent (0\%-100\%).
+We again removed participants with error rates greater than 25\% and adopted the same outlier removal procedure as described above.
+We submitted mean correct RTs for frequency unbiased items to a 2x2x2 mixed ANOVA with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and phase order (100\%-0\% and 0\%-100\%) as the between-subjects factor.
+
+Consistent with the original analysis, two-way interaction between task-relevant context and congruency remained significant,\(F(1, 129) = 8.92\), \(\mathit{MSE} = 1,627.84\), \(p = .003\), \(\hat{\eta}^2_p = .065\).
+However, the three-way interaction was non-significant, \(F(1, 129) = 2.56\), \(\mathit{MSE} = 1,627.84\), \(p = .112\), \(\hat{\eta}^2_p = .019\).
+Therefor, we did not find statistical support for a list-shift asymmetry.
+Additionally, the asymmetry we do see in this sample is in the opposite direction than would be predicted given the prior results ().
+
+We also conducted a more severe test of the list-shift hypothesis.
+Abrahamse et al.'s interpretation of the list shift effect was that participants had to learn to adjust to the new cues.
+Therefore, we might expect that any asymmetry would be exaggerated near the point of transition.
+We repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.
+
+Again, the three-way interaction was non-significant, \(F(1, 129) = 0.02\), \(\mathit{MSE} = 2,866.15\), \(p = .902\), \(\hat{\eta}^2_p = .000\).
+Interestingly, the two-way interaction between congruency and task-relevant context is also still significant, \(F(1, 129) = 6.65\), \(\mathit{MSE} = 2,866.15\), \(p = .011\), \(\hat{\eta}^2_p = .049\).
+This result supports the notion there was no asymmetry and that the shift in context-dependent effects occur almost immediately after the transition.
 
@@
 \end{table}
+
+\hypertarget{experiment-2}{%
+\section{Experiment 2}\label{experiment-2}}
+
+In Experiment 1, we found that
+
+\hypertarget{methods-1}{%
+\section{Methods}\label{methods-1}}
+
+\hypertarget{participants-1}{%
+\subsection{Participants}\label{participants-1}}
+
+All participants were recruited from Amazon Mechanical Turk (AMT) and compensated \$2.00 for participating.
+The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by \$6.00 per hour.
+For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study.
+Participants were included in the study if they completed all trials.
+We posted 50 HITs and 50 participants completed all trials.
+
+\hypertarget{apparatus-stimuli-1}{%
+\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli-1}}
+
+The apparatus and stimuli were identical to Experiment 1. The context stimuli were identical to those used for the object condition in Experiment 1.
+
+\hypertarget{design-1}{%
+\subsection{Design}\label{design-1}}
+
+Experiment 1 used a 2x3 within-subjects design with proportion congruent (25\%, 50\%, and 75\%) and congruency (congruent and incongruent) as factors.
+The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials or instructions informing participants about the proportion manipulations.
+The design in every other respect was identical to Experiment 1.
+
+\hypertarget{procedure-1}{%
+\subsection{Procedure}\label{procedure-1}}
+
+All participants were AMT workers who found the experiment using the AMT system.
+The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board.
+Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form.
+Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window.
+Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing \enquote{z} if the arrow pointed left, and \enquote{m} if the arrow pointed right.
+
+Each trial began with a blank inter-stimulus interval (ISI) of 400 ms, followed by a fixation cross presented in the center of the screen for 200 ms, then a second blank ISI of 400 ms.
+Next, the flanker and context stimuli appeared in the center of screen (the flanker above the context image; see Figure 1B) and remained on screen until a response was made.
+Following a response, accuracy feedback was presented for 1000 ms.
+A response automatically triggered the next trial.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_pretty_files/figure-latex/figure3-1.pdf}
+\caption{\label{fig:figure3}Results from Experiment 2 showing congruency effects (incongruent - congruent) across proportion congruency (25\%, 75\%, and 100\% PC) in reaction times (left) and error rates (right).}
+\end{figure}
+
+\hypertarget{results-1}{%
+\section{Results}\label{results-1}}
+
+Participants with mean error rates greater than 25\% were excluded from the analyses, eliminating 3 participants.
+For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure.
+The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms (Van Selst \& Jolicoeur, 1994).
+This procedure removed 3.14\% of the total observations.
+
+The questions of interest were whether participants would learn the associations between the context cues without the task-relevance manipulation (i.e., the counting task) and whether responding to the unbiased cues would be influenced by the presence of the biased cues.
+To that end, mean correct RTs and mean error rates were submitted to an analysis of variance (ANOVA) with proportion congruent (25\%, 50\%, and 75\%) and congruency (congruent and incongruent) as within-subject factors.
+
+The results of the RT analysis revealed the critical, two-way interaction between proportion congruency and congruency to be non-significant, \(F(2, 92) = 0.85\), \(\mathit{MSE} = 498.56\), \(p = .431\), \(\hat{\eta}^2_p = .018\).
+Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(2, 92) = 0.45\), \(\mathit{MSE} = 4.61\), \(p = .641\), \(\hat{\eta}^2_p = .010\).
+Therefore, there was no evidence that the context cues, absent the counting task, systematically influenced the congruency effect.
+
+\hypertarget{experiment-3}{%
+\section{Experiment 3}\label{experiment-3}}
+
+\hypertarget{methods-2}{%
+\section{Methods}\label{methods-2}}
+
+\hypertarget{participants-2}{%
+\subsection{Participants}\label{participants-2}}
+
+All participants were recruited from Amazon Mechanical Turk (AMT) and compensated \$2.00 for participating.
+The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by \$6.00 per hour.
+For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study.
+Participants were included in the study if they completed all trials.
+We posted 50 HITs and 50 participants completed all trials.
+
+\hypertarget{apparatus-stimuli-2}{%
+\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli-2}}
+
+The apparatus and stimuli were identical to Experiment 1. The context stimuli were identical to those used for the object condition in Experiment 1.
+
+\hypertarget{design-2}{%
+\subsection{Design}\label{design-2}}
+
+Experiment 1 used a 2x3 within-subjects design with proportion congruent (25\%, 50\%, and 75\%) and congruency (congruent and incongruent) as factors.
+The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials or instructions informing participants about the proportion manipulations.
+The design in every other respect was identical to Experiment 1.
+
+\hypertarget{procedure-2}{%
+\subsection{Procedure}\label{procedure-2}}
+
+All participants were AMT workers who found the experiment using the AMT system.
+The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board.
+Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form.
+Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window.
+Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing \enquote{z} if the arrow pointed left, and \enquote{m} if the arrow pointed right.
+
+Each trial began with a blank inter-stimulus interval (ISI) of 400 ms, followed by a fixation cross presented in the center of the screen for 200 ms, then a second blank ISI of 400 ms.
+Next, the flanker and context stimuli appeared in the center of screen (the flanker above the context image; see Figure 1B) and remained on screen until a response was made.
+Following a response, accuracy feedback was presented for 1000 ms.
+A response automatically triggered the next trial.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_pretty_files/figure-latex/figure4-1.pdf}
+\caption{\label{fig:figure4}Results from Experiment 3 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent).
+Task-relevance was manipulated through explicit instructions.}
+\end{figure}
+
+\hypertarget{results-2}{%
+\section{Results}\label{results-2}}
+
+Participants with mean error rates greater than 25\% were excluded from the analyses, eliminating 4 participants.
+For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure.
+The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms (Van Selst \& Jolicoeur, 1994).
+This procedure removed 3.42\% of the total observations.
+
+The primary question of interest was whether the task-relevance of context features (made relevant through explicit task instructions) associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items.
+Mean correct RTs and mean error rates from frequency unbiased trials were submitted to an analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors.
+
+The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be non-significant, \(F(1, 45) = 0.02\), \(\mathit{MSE} = 2,015.27\), \(p = .876\), \(\hat{\eta}^2_p = .001\).
+Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 45) = 0.66\), \(\mathit{MSE} = 14.26\), \(p = .420\), \(\hat{\eta}^2_p = .014\).
 
@@
 These effects were found to be generalizable across two different kinds of stimuli and occurred even when using non-repeating images, and implicate an important role for task-relevance in producing context-dependency and are consistent with memory-based accounts of CSPC phenomena.
-
-\newpage
 

### 2019-06-30 cleaning.R

@@ -1,0 +1,130 @@
+#load("raw_data_E3.Rda")
+
+data$Condition <- NA
+
+data <- data %>% 
+    mutate(Subject = rep(1:50, each = 288)) %>%
+    group_by(subID) %>%
+    mutate(Phase = c(rep(1,144),rep(2,144)),
+           block = c(rep(1,72),rep(2,72),rep(1,72),rep(2,72))
+    )
+
+data$ACC <- as.numeric(as.character(data$ACC))
+data$trial <- as.numeric(as.character(data$trial))
+
+data <- data %>%
+    mutate(
+        Frequency = case_when(trialProp == "0" ~ "biased",
+                              trialProp == "100" ~ "biased",
+                              trialProp == "50" ~ "unbiased"),
+        Task_Relevant_Context = case_when(as.character(countProp) == "0" ~ "0% Con",
+                                          as.character(countProp) == "100" ~ "100% Con"),
+        order = case_when(order == "B1 0" ~ "0-100",
+                          order == "B1 100" ~ "100-0")
+    )
+
+
+data <- data %>%
+    rename(Trial = trial,
+           Congruency = trialCongruency,
+           Order = order,
+           Block = block
+           )
+
+data <- data %>%
+    ungroup() %>%
+    select(
+        Condition,
+        Subject,
+        Order,
+        Phase,
+        Block,
+        Trial,
+        Task_Relevant_Context,
+        Frequency,
+        Congruency,
+        ACC,
+        RT
+    )
+
+raw_data_E3 <- data
+save(raw_data_E3, file="raw_data_E3.Rda")
+
+load("demographics_E3.Rda")
+
+questData$expTime<- ((as.numeric(as.character(questData$completeTime)) - as.numeric(as.character(questData$startTime)))/1000)/60
+questData$Exp<- "E3"
+questData <- questData %>%
+    select(Exp,subnum,expTime,country,gender,age,handedness,vision,english,browser,count1_Cat,count1_Feat,count1_Prop,count2_Cat,count2_Feat,count2_Prop, task_feedback)
+
+demographics_E3 <- questData
+save(demographics_E3, file="demographics_E3.Rda")
+
+
+#load("raw_data_E2.Rda")
+
+data$Condition <- NA
+
+data <- data %>% 
+    mutate(Subject = rep(1:50, each = 288)) %>%
+    group_by(subID) %>%
+    mutate(Phase = c(rep(1,144),rep(2,144)),
[…]

### 2019-06-30 data-analysis/analysis_E1.R

@@ -1,0 +1,352 @@
+
+library(dplyr)
+library(tidyr)
+library(afex)
+library(ggplot2)
+library(cowplot)
+#As of 2018/12/07 apa_print() requires development version of Papaja
+#devtools::install_github("crsh/papaja")
+library(papaja)
+
+
+folderName <- function(){
+  wd<-getwd()
+  wd<-strsplit(wd,"/")
+  wd<-wd[[1]][length(wd[[1]])]
+  
+  return(wd)
+}
+
+
+vjoutNR <- function(x,n) {
+  xm <- mean(x)
+  xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
+             25, 30, 35, 50, 80)
+  stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
+            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
+            2.45, 2.48, 2.5)
+  stdindex <- length(xsize[xsize <= length(x)])
+  removed <- x[x < xm+sd(x)*stds[stdindex]]
+  removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
+  proportionRemoved <- length(removed)/length(x)
+  finaldata<-c(mean(removed),1-proportionRemoved)
+  return(finaldata[[n]])
+}
+
+
+
+load("data-analysis/raw_data_E1.Rda")
+
+
+# Find subs with < 75% accuracy
+low_acc <- raw_data %>%
+  group_by(Subject,Condition,Task_Relevant_Context,Frequency,Congruency) %>%
+  summarise(meanAccuracy = mean(ACC)) %>%
+  filter(meanAccuracy < .75) %>%
+  .$Subject
+
+N_subjects_removed<-length(unique(low_acc))
+
+## summarise by subject
+RT.DF <- raw_data %>%
+  filter(
+    RT < 3000,
+    RT > 0,
+    ACC == TRUE,
+    Subject%in%low_acc == FALSE
+  ) %>%
+  group_by(Condition,Subject,Order,Phase,Block,Frequency,Task_Relevant_Context,Congruency)%>%
+  summarise(vjoutRT = vjoutNR(RT,1))
+
+## Find percentage of trials removed 
+percent_removed <- raw_data %>%
+  filter(
+    RT < 3000,
+    RT > 0,
[…]

### 2019-06-30 data-analysis/analysis_E1_Exploratory.R

@@ -1,0 +1,460 @@
+
+## SETUP -------------------
+library(dplyr)
+library(tidyr)
+library(afex)
+library(ggplot2)
+library(cowplot)
+library(forcats)
+#As of 2018/12/07 apa_print() requires development version of Papaja
+#devtools::install_github("crsh/papaja")
+library(papaja)
+
+# van selst and jolicour outlier removal (non-recursive)
+vjoutNR <- function(x,n) {
+  xm <- mean(x)
+  xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
+             25, 30, 35, 50, 80)
+  stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
+            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
+            2.45, 2.48, 2.5)
+  stdindex <- length(xsize[xsize <= length(x)])
+  removed <- x[x > xm+sd(x)*stds[stdindex]]
+  removed <- c(removed, x[x < xm-(sd(x)*stds[stdindex])])
+  
+  retained <- x[x < xm+sd(x)*stds[stdindex]]
+  retained <- retained[retained > xm - (sd(x)*stds[stdindex])]
+  
+  proportionRemoved <- length(retained)/length(x)
+  finaldata<-list(
+    mean(retained),
+    1-proportionRemoved,
+    retained,
+    removed
+  )
+  return(finaldata[[n]])
+}
+
+## Pre-process data ------------------------------------
+load("data-analysis/raw_data_E1.Rda")
+
+levels(raw_data$Order) <- c("MI-MC","MC-MI")
+raw_data$Order <- factor(raw_data$Order, c("MC-MI","MI-MC" ))
+ 
+# Find subs with < 75% accuracy
+  low_acc <- raw_data %>%
+    group_by(Subject,Condition,Task_Relevant_Context,Frequency,Congruency) %>%
+    summarise(meanAccuracy = mean(ACC)) %>%
+    filter(meanAccuracy < .75) %>%
+    .$Subject
+  
+  N_subjects_removed<-length(unique(low_acc))
+
+
+## Exploratory analysis: Order assymmetry ----------------------------------------
+
+# summarize by subject
+RT.DF <- raw_data %>%
+  filter(
+    RT < 3000,
+    RT > 0,
[…]

### 2019-06-30 data-analysis/analysis_E2.R

@@ -35,77 +35,78 @@ vjoutNR <- function(x,n) {
 
 
 
-load("data-analysis/raw_data.Rda")
+load("data-analysis/raw_data_E2.Rda")
+load("data-analysis/demographics_E2.Rda")
+
 
 
 # Find subs with < 75% accuracy
-low_acc <- raw_data %>%
-  group_by(Subject,Condition,Task_Relevant_Context,Frequency,Congruency) %>%
+low_acc <- raw_data_E2 %>%
+  group_by(Subject,Condition,PC,Congruency) %>%
   summarise(meanAccuracy = mean(ACC)) %>%
   filter(meanAccuracy < .75) %>%
   .$Subject
 
-N_subjects_removed<-length(unique(low_acc))
+N_subjects_removed_E2 <-length(unique(low_acc))
 
 ## summarise by subject
-RT.DF <- raw_data %>%
+RT.DF <- raw_data_E2 %>%
   filter(
     RT < 3000,
     RT > 0,
     ACC == TRUE,
     Subject%in%low_acc == FALSE
   ) %>%
-  group_by(Condition,Subject,Order,Phase,Block,Frequency,Task_Relevant_Context,Congruency)%>%
+  group_by(Subject,PC,Congruency)%>%
   summarise(vjoutRT = vjoutNR(RT,1))
 
 ## Find percentage of trials removed 
-percent_removed <- raw_data %>%
+percent_removed_E2 <- raw_data_E2 %>%
   filter(
     RT < 3000,
     RT > 0,
     ACC == TRUE,
     Subject%in%low_acc == FALSE
   ) %>%
-  group_by(Condition,Subject,Order,Phase,Frequency,Task_Relevant_Context,Congruency)%>%
+  group_by(Subject,PC,Congruency)%>%
   summarise(percent_removed = vjoutNR(RT,2)) %>%
   ungroup() %>%
   summarise(avg_removed = mean(percent_removed)) %>%
   .$avg_removed
 
-## Analyze RTs for frequency unbiased items
+## Analyze RTs 
 RT.Analysis <- RT.DF %>%
-  filter(
-    Frequency == "unbiased"
-  ) %>%
-  group_by(Condition,Subject,Task_Relevant_Context,Congruency) %>%
+  group_by(Subject,PC,Congruency) %>%
   summarise(meanRT = mean(vjoutRT))
 
[…]

### 2019-06-30 data-analysis/analysis_E3.R

@@ -1,0 +1,234 @@
+
+library(dplyr)
+library(tidyr)
+library(afex)
+library(ggplot2)
+library(cowplot)
+#As of 2018/12/07 apa_print() requires development version of Papaja
+#devtools::install_github("crsh/papaja")
+library(papaja)
+
+
+folderName <- function(){
+  wd<-getwd()
+  wd<-strsplit(wd,"/")
+  wd<-wd[[1]][length(wd[[1]])]
+  
+  return(wd)
+}
+
+
+vjoutNR <- function(x,n) {
+  xm <- mean(x)
+  xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
+             25, 30, 35, 50, 80)
+  stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
+            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
+            2.45, 2.48, 2.5)
+  stdindex <- length(xsize[xsize <= length(x)])
+  removed <- x[x < xm+sd(x)*stds[stdindex]]
+  removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
+  proportionRemoved <- length(removed)/length(x)
+  finaldata<-c(mean(removed),1-proportionRemoved)
+  return(finaldata[[n]])
+}
+
+
+
+load("data-analysis/raw_data_E3.Rda")
+# load("data-analysis/demographics_E3.Rda")
+# demographics_E3$Subject <- demographics_E3$subnum
+# 
+# raw_data_E3 <- inner_join(raw_data_E3, demographics_E3, by = "Subject")
+# raw_data_E3 <- raw_data_E3 %>%
+#   mutate(task_feedback = as.numeric(as.character(task_feedback))) %>%
+#   filter(!is.na(task_feedback),
+#                 task_feedback > 3)
+
+# Find subs with < 75% accuracy
+low_acc <- raw_data_E3 %>%
+  group_by(Subject,Condition,Task_Relevant_Context,Frequency,Congruency) %>%
+  summarise(meanAccuracy = mean(ACC)) %>%
+  filter(meanAccuracy < .75) %>%
+  .$Subject
+
+N_subjects_removed_E3 <-length(unique(low_acc))
+
+## summarise by subject
+RT.DF <- raw_data_E3 %>%
[…]

### 2019-06-30 data-analysis/power_simulation.R

@@ -1,0 +1,356 @@
+
+library(dplyr)
+library(tidyr)
+library(afex)
+library(ggplot2)
+library(cowplot)
+#As of 2018/12/07 apa_print() requires development version of Papaja
+#devtools::install_github("crsh/papaja")
+library(papaja)
+
+######### FUNCTIONS ##########3
+
+### Outlier removal function
+vjoutNR <- function(x,n) {
+    if(length(x) == 1){return (x)}
+    xm <- mean(x)
+    xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
+               25, 30, 35, 50, 80)
+    stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
+              2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
+              2.45, 2.48, 2.5)
+    stdindex <- length(xsize[xsize <= length(x)])
+    removed <- x[x < xm+sd(x)*stds[stdindex]]
+    removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
+    proportionRemoved <- length(removed)/length(x)
+    finaldata<-c(mean(removed),1-proportionRemoved)
+    return(finaldata[[n]])
+}
+
+### Run single simulation 
+run_sim <- function(pop_mean = NULL,
+                    pop_sd = NULL,
+                    effect_estimate = "B",
+                    effect_dist = "3/3",
+                    effect_size = 5,
+                    n_subs = 20,
+                    upper = pop_mean + 2 * pop_sd,
+                    lower = pop_mean - 2 * pop_sd) {
+    
+    n_subs <- n_subs * 3
+    
+    # sample some rts
+    # over-sample and discard overflow
+    rts <- c()
+    while (length(rts) < (n_subs * 2)) {
+        # over sample d
+        t <- rnorm((n_subs * 3),mean = pop_mean,sd = pop_sd)
+        rts <- t[t > lower & t < upper]
+    }
+    rts <- rts[1:(n_subs * 2)]
+    
+    ### Add effect
+    if (effect_dist == "3/3") {
+        rts[1:(length(rts) / 2)] <- rts[1:(length(rts) / 2)] + effect_size
+    }
+    
+    if (effect_dist == "2/3") {
+        rts[1:(length(rts) / 3)] <- rts[1:(length(rts) / 3)] + effect_size
+    }
+    
+    if (effect_dist ==  "1/3") {
[…]

### 2019-06-30 data-analysis/table1.R

@@ -34,7 +34,7 @@ vjoutNR <- function(x,n) {
 
 
 ## manuscript.Rmd is called from parent
-load("data-analysis/raw_data.Rda")
+load("data-analysis/raw_data_E1.Rda")
 
 
 
@@ -211,4 +211,6 @@ TR_Table<-paste(
     "\\end{table}",
     sep = "\n"
 )
+
+print(kableExtra::kable(TR_Table,format="latex"))
     

### 2019-07-17 manuscript_pretty.Rmd
working - incomplete

@@
 source("data-analysis/analysis_E1_Exploratory.R")
+source("data-analysis/plot-power-simulation.R")
 ```
 
-Selective attention is commonly investigated using interference paradigms such as the Stroop [-@stroop_studies_1935] and flanker [@eriksen_effects_1974] tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor.
+Selective attention is commonly investigated using interference paradigms like the Stroop [-@stroop_studies_1935] and flanker [@eriksen_effects_1974] tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor.
 Performance is typically better on congruent versus incongruent trials and the difference---the congruency effect---taken as an index of attentional priorities.
@@
 How associations between attentional priorities and context cues are formed and used still remains unclear however.
-The current study addresses two issues.
+The current study addresses two related issues.
 
-First, how is attentional control resolved when multiple contextual features could be used as cues?
-Second, it remains unclear how  Historically, theories of automaticity and attentional control have emphasized the role of practice and likened the process to skill-learning ().
+First, how is attentional control resolved when multiple contextual features could be used as cues? Second, it remains unclear how
+
+Historically, theories of automaticity and attentional control have emphasized the role of practice and likened the learning process to the automaticity of skill-learning ().
 
@@
 
+## Data Analysis 
+All analyses in this and the following experiments were performed in R [@r_software_2019] using a variety of R packages ().
+In particular, we used the afex and car packages [@r_afex_2019; @r_car_2019] to perform all the Null Hypothesis Significance Tests, the BayesFactor package to perform Bayesian analyses [@r_bayesfactor_2018], and the conflictPower package to perform the simulation-based sensitivity and power analyses [@r_conflictPower_2019].
+All data and scripts can be found
+
+We supplemented each Null Hypothesis Significance Test with a Bayes Factor analysis (Rouder, Speckman..
+2009).
+Using conventional frequentist testing it is not possible to quantify the evidence for a null effect.
+Bayes Factors, however, quantify the degree to which the observed data are compatible with either the alternative or null hypothesis (Dienes, 2014; Rouder et al., 2014).
+All Bayesian analyses were performed using the R package BayesFactor and Bayes Factors (BFs) were calculated using its default settings (Morey and Rouder, 2014).
+Following the guidelines recommended by Rouder et al.
+(2009)
+
 # Results
@@
 The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1).
-To that end, mean correct RTs and mean error rates from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0% and 100% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+To that end, congruency effects (incongruent minus congruent performance) from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0% and 100% PC) and context-type (object, social, and social/non-repeating) as the between-subjects factor.
 
-The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, `r RT_ANOVA$Task_Relevant_Context_Congruency`, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
-Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, `r RT_ANOVA$Condition_Task_Relevant_Context_Congruency`, showing no evidence for differences between the CSPC effects across context-type manipulations.
+The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, `r RT_ANOVA$Task_Relevant_Context`, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
+Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, `r RT_ANOVA$Condition_Task_Relevant_Context`, showing no evidence for differences between the CSPC effects across context-type manipulations.
 
-Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA$Task_Relevant_Context_Congruency`, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, `r ACC_ANOVA$Condition_Task_Relevant_Context_Congruency`.
+Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA$Task_Relevant_Context`, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, `r ACC_ANOVA$Condition_Task_Relevant_Context`.
 Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.
@@
 
-```{r figure3, echo=FALSE, fig.width=3.6, fig.height=4, fig.cap='(ref:figure3)'}
-#print figure 3
-#source: data-analysis/analysis_E2.R
-figure3
-```
-
-(ref:figure3) Results from Experiment 2 showing congruency effects (incongruent - congruent) across proportion congruency (25%, 75%, and 100% PC) in reaction times (left) and error rates (right).
-
 # Results
@@
 Therefore, there was no evidence that the context cues, absent the counting task, systematically influenced the congruency effect.
+
+```{r figure3, echo=FALSE, fig.width=3.25, fig.height=4, fig.cap='(ref:figure3)'}
+#print figure 3
+#source: data-analysis/analysis_E2.R
+figure3
+```
+
+(ref:figure3) Results from Experiment 2 showing congruency effects (incongruent - congruent) across proportion congruency (25%, 75%, and 100% PC) in reaction times (left) and error rates (right).
 
@@
 
-```{r figure4, echo=FALSE, fig.cap='(ref:figure4)', fig.width=3.6, fig.height=3.5}
+```{r figure4, echo=FALSE, fig.cap='(ref:figure4)', fig.width=3.25, fig.height=3.5}
 #print figure 3
@@
 Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA_E3$Task_Relevant_Context_Congruency`.
+
+# Estimating reproducability by simulation-based sensitivity- and power-analyses
+
+```{r figure5, echo=FALSE, fig.cap='(ref:figure5)', fig.width=6.875, fig.height= 5}
+#print figure 3
+#source: data-analysis/plot-power-simulation.R
+figure5
+```
+
+(ref:figure5) Results from Experiment 3 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent).
+Task-relevance was manipulated through explicit instructions.
 

### 2019-07-17 manuscript_pretty.tex
working - incomplete

@@
 
-Selective attention is commonly investigated using interference paradigms such as the Stroop (1935) and flanker (Eriksen \& Eriksen, 1974) tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor.
+Selective attention is commonly investigated using interference paradigms like the Stroop (1935) and flanker (Eriksen \& Eriksen, 1974) tasks, where participants identify a target while ignoring a response-congruent or -incongruent distractor.
 Performance is typically better on congruent versus incongruent trials and the difference---the congruency effect---taken as an index of attentional priorities.
@@
 As a result, automatic memory-based retrieval allows attentional priorities to be rapidly adjusted in a context-appropriate fashion.
+How associations between attentional priorities and context cues are formed and used still remains unclear however.
+The current study addresses two related issues.
+
+First, how is attentional control resolved when multiple contextual features could be used as cues? Second, it remains unclear how
+
+Historically, theories of automaticity and attentional control have emphasized the role of practice and likened the learning process to the automaticity of skill-learning ().
+
 However, the obligatory nature of memory-based attentional control remains unclear, in particular in situations when multiple contextual features could be used as cues for retrieval.
@@
 
+\hypertarget{data-analysis}{%
+\section{Data Analysis}\label{data-analysis}}
+
+All analyses in this and the following experiments were performed in R (R Core Team, 2019) using a variety of R packages ().
+In particular, we used the afex and car packages (Fox \& Weisberg, 2019; Singmann, Bolker, Westfall, \& Aust, 2019) to perform all the Null Hypothesis Significance Tests, the BayesFactor package to perform Bayesian analyses (Morey \& Rouder, 2018), and the conflictPower package to perform the simulation-based sensitivity and power analyses (Crump \& Brosowsky, 2019).
+All data and scripts can be found
+
+We supplemented each Null Hypothesis Significance Test with a Bayes Factor analysis (Rouder, Speckman..
+2009).
+Using conventional frequentist testing it is not possible to quantify the evidence for a null effect.
+Bayes Factors, however, quantify the degree to which the observed data are compatible with either the alternative or null hypothesis (Dienes, 2014; Rouder et al., 2014).
+All Bayesian analyses were performed using the R package BayesFactor Version XXXXX and Bayes Factors (BFs) were calculated using its default settings (Morey and Rouder, 2014).
+Following the guidelines recommended by Rouder et al.~(2009)
+
 \hypertarget{results}{%
@@
 The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1).
-To that end, mean correct RTs and mean error rates from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+To that end, congruency effects (incongruent minus congruent performance) from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) and context-type (object, social, and social/non-repeating) as the between-subjects factor.
 
-The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 1,608.54\), \(p = .005\), \(\hat{\eta}^2_p = .061\), demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
-Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, \(F(2, 128) = 0.00\), \(\mathit{MSE} = 1,608.54\), \(p = .996\), \(\hat{\eta}^2_p = .000\), showing no evidence for differences between the CSPC effects across context-type manipulations.
+The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 3,217.08\), \(p = .005\), \(\hat{\eta}^2_p = .061\) 90\% CI \([0.01\), \(0.14]\), demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
+Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, \(F(2, 128) < 0.01\), \(\mathit{MSE} = 3,217.08\), \(p = .996\), \(\hat{\eta}^2_p < .001\) 90\% CI \([0\), \(1]\), showing no evidence for differences between the CSPC effects across context-type manipulations.
 
-Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 128) = 6.72\), \(\mathit{MSE} = 13.93\), \(p = .011\), \(\hat{\eta}^2_p = .050\), and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, \(F(2, 128) = 0.92\), \(\mathit{MSE} = 13.93\), \(p = .400\), \(\hat{\eta}^2_p = .014\).
+Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 128) = 6.72\), \(\mathit{MSE} = 27.87\), \(p = .011\), \(\hat{\eta}^2_p = .050\), and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, \(F(2, 128) = 0.92\), \(\mathit{MSE} = 27.87\), \(p = .400\), \(\hat{\eta}^2_p = .014\).
 Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.
@@
 Abrahamse et al\ldots{}.
-found that\ldots{} In our study, we were primarily interested in whether participants could use context cues despite the presence of competing, contradictory cues, and whether they could switch from one context cue to another.
+found that\ldots{} In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from one context cue to another.
 We therefore randomized the order across participants to control for the effects of order.
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_pretty_files/figure-latex/figure3-1.pdf}
-\caption{\label{fig:figure3}Results from Experiment 2 showing congruency effects (incongruent - congruent) across proportion congruency (25\%, 75\%, and 100\% PC) in reaction times (left) and error rates (right).}
-\end{figure}
-
 \hypertarget{results-1}{%
@@
 Therefore, there was no evidence that the context cues, absent the counting task, systematically influenced the congruency effect.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_pretty_files/figure-latex/figure3-1.pdf}
+\caption{\label{fig:figure3}Results from Experiment 2 showing congruency effects (incongruent - congruent) across proportion congruency (25\%, 75\%, and 100\% PC) in reaction times (left) and error rates (right).}
+\end{figure}
 
@@
 Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 45) = 0.66\), \(\mathit{MSE} = 14.26\), \(p = .420\), \(\hat{\eta}^2_p = .014\).
+
+\hypertarget{estimating-reproducability-by-simulation-based-sensitivity--and-power-analyses}{%
+\section{Estimating reproducability by simulation-based sensitivity- and power-analyses}\label{estimating-reproducability-by-simulation-based-sensitivity--and-power-analyses}}
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_pretty_files/figure-latex/figure5-1.pdf}
+\caption{\label{fig:figure5}Results from Experiment 3 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent).
+Task-relevance was manipulated through explicit instructions.}
+\end{figure}
 
@@
 \emph{Psychological Bulletin}, \emph{142}, 693--728.
-doi:\href{https://doi.org/10.1037/bul0000047}{10.1037/bul0000047}
+\url{https://doi.org/10.1037/bul0000047}
 
@@
 \emph{Journal of Cognitive Psychology}, \emph{29}, 977--987.
-doi:\href{https://doi.org/10.1080/20445911.2017.1353518}{10.1080/20445911.2017.1353518}
+\url{https://doi.org/10.1080/20445911.2017.1353518}
 
@@
 \emph{The Quarterly Journal of Experimental Psychology}, \emph{68}, 1920--1930.
-doi:\href{https://doi.org/10.1080/17470218.2014.1000346}{10.1080/17470218.2014.1000346}
+\url{https://doi.org/10.1080/17470218.2014.1000346}
 
@@
 \emph{Psychological Science}, \emph{24}, 981--990.
-doi:\href{https://doi.org/10.1177/0956797612465439}{10.1177/0956797612465439}
+\url{https://doi.org/10.1177/0956797612465439}
 
@@
 \emph{Consciousness and Cognition}, \emph{44}, 146--160.
-doi:\href{https://doi.org/10.1016/j.concog.2016.07.001}{10.1016/j.concog.2016.07.001}
+\url{https://doi.org/10.1016/j.concog.2016.07.001}
 
@@
 \emph{Journal of Experimental Psychology: General}, \emph{147}, 1134--1153.
-doi:\href{https://doi.org/10.1037/xge0000431}{10.1037/xge0000431}
+\url{https://doi.org/10.1037/xge0000431}
 
@@
 \emph{Frontiers in Psychology}, \emph{3}, 367.
-doi:\href{https://doi.org/10.3389/fpsyg.2012.00367}{10.3389/fpsyg.2012.00367}
+\url{https://doi.org/10.3389/fpsyg.2012.00367}
 
@@
 \leavevmode\hypertarget{ref-bugg_multiple_2008}{}%
-Bugg, J., Jacoby, L.
-L., \& Toth, J.
-P.
-(2008).
-Multiple levels of control in the Stroop task.
-\emph{Memory \& Cognition}, \emph{36}, 1484--1494.
-doi:\href{https://doi.org/10.3758/MC.36.8.1484}{10.3758/MC.36.8.1484}
+Bugg, J., Jacoby, L. L., \& Toth, J. P. (2008). Multiple levels of control in the Stroop task. \emph{Memory \& Cognition}, \emph{36}, 1484--1494. \url{https://doi.org/10.3758/MC.36.8.1484}
 
@@
 \emph{Journal of Experimental Psychology: General}, \emph{142}, 934--943.
-doi:\href{https://doi.org/10.1037/a0029794}{10.1037/a0029794}
+\url{https://doi.org/10.1037/a0029794}
 
@@
 \emph{Biological Psychology}, \emph{64}, 191--209.
-doi:\href{https://doi.org/10.1016/S0301-0511(03)00109-1}{10.1016/S0301-0511(03)00109-1}
+\url{https://doi.org/10.1016/S0301-0511(03)00109-1}
 
@@
 \emph{Canadian Journal of Experimental Psychology/Revue Canadienne de Psychologie Expérimentale}, \emph{70}, 59--77.
-doi:\href{https://doi.org/10.1037/cep0000066}{10.1037/cep0000066}
+\url{https://doi.org/10.1037/cep0000066}
 
@@
 \emph{The Quarterly Journal of Experimental Psychology}, \emph{70}, 1792--1807.
-doi:\href{https://doi.org/10.1080/17470218.2016.1206130}{10.1080/17470218.2016.1206130}
+\url{https://doi.org/10.1080/17470218.2016.1206130}
+
+\leavevmode\hypertarget{ref-r_conflictPower_2019}{}%
+Crump, M. J. C., \& Brosowsky, N. P. (2019). \emph{ConflictPower: Simulation based power analysis for adaptive control designs}.
 
@@
 \emph{The Quarterly Journal of Experimental Psychology}, \emph{62}, 1523--1532.
-doi:\href{https://doi.org/10.1080/17470210902752096}{10.1080/17470210902752096}
+\url{https://doi.org/10.1080/17470210902752096}
 
@@
 \emph{Psychonomic Bulletin \& Review}, \emph{13}, 316--321.
-doi:\href{https://doi.org/10.3758/BF03193850}{10.3758/BF03193850}
+\url{https://doi.org/10.3758/BF03193850}
 
@@
 \emph{Consciousness and Cognition}, \emph{17}, 22--36.
-doi:\href{https://doi.org/10.1016/j.concog.2007.01.004}{10.1016/j.concog.2007.01.004}
+\url{https://doi.org/10.1016/j.concog.2007.01.004}
 
@@
 \emph{Frontiers in Psychology}, \emph{5}, 1247.
-doi:\href{https://doi.org/10.3389/fpsyg.2014.01247}{10.3389/fpsyg.2014.01247}
+\url{https://doi.org/10.3389/fpsyg.2014.01247}
 
@@
 \emph{Perception \& Psychophysics}, \emph{16}, 143--149.
-doi:\href{https://doi.org/10.3758/BF03203267}{10.3758/BF03203267}
+\url{https://doi.org/10.3758/BF03203267}
 
@@
 
+\leavevmode\hypertarget{ref-r_car_2019}{}%
+Fox, J., \& Weisberg, S. (2019). \emph{An R companion to applied regression} (Third). Thousand Oaks CA: Sage. Retrieved from \url{https://socialsciences.mcmaster.ca/jfox/Books/Companion/}
+
 \leavevmode\hypertarget{ref-hutcheon_limits_2017}{}%
@@
 \emph{Quarterly Journal of Experimental Psychology}, \emph{70}, 1292--1304.
-doi:\href{https://doi.org/10.1080/17470218.2016.1182193}{10.1080/17470218.2016.1182193}
+\url{https://doi.org/10.1080/17470218.2016.1182193}
 
@@
 \emph{Psychonomic Bulletin \& Review}, \emph{23}, 1867--1872.
-doi:\href{https://doi.org/10.3758/s13423-016-1057-y}{10.3758/s13423-016-1057-y}
+\url{https://doi.org/10.3758/s13423-016-1057-y}
 
@@
 \emph{The Journal of Neuroscience}, \emph{32}, 8192--8200.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.0934-12.2012}{10.1523/JNEUROSCI.0934-12.2012}
+\url{https://doi.org/10.1523/JNEUROSCI.0934-12.2012}
 
@@
 \emph{Memory \& Cognition}, \emph{7}, 166--174.
-doi:\href{https://doi.org/10.3758/BF03197535}{10.3758/BF03197535}
+\url{https://doi.org/10.3758/BF03197535}
 
@@
 \emph{Behavior Research Methods}, \emph{47}, 1122--1135.
-doi:\href{https://doi.org/10.3758/s13428-014-0532-5}{10.3758/s13428-014-0532-5}
+\url{https://doi.org/10.3758/s13428-014-0532-5}
 
@@
 \emph{Psychological Research}, \emph{71}, 107--116.
-doi:\href{https://doi.org/10.1007/s00426-005-0039-x}{10.1007/s00426-005-0039-x}
+\url{https://doi.org/10.1007/s00426-005-0039-x}
+
+\leavevmode\hypertarget{ref-r_bayesfactor_2018}{}%
+Morey, R. D., \& Rouder, J. N. (2018). \emph{BayesFactor: Computation of bayes factors for common designs}. Retrieved from \url{https://CRAN.R-project.org/package=BayesFactor}
+
+\leavevmode\hypertarget{ref-r_software_2019}{}%
+R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
@@
 \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{34}, 514--523.
-doi:\href{https://doi.org/10.1037/0278-7393.34.3.514}{10.1037/0278-7393.34.3.514}
+\url{https://doi.org/10.1037/0278-7393.34.3.514}
+
+\leavevmode\hypertarget{ref-r_afex_2019}{}%
+Singmann, H., Bolker, B., Westfall, J., \& Aust, F. (2019). \emph{Afex: Analysis of factorial experiments}. Retrieved from \url{https://CRAN.R-project.org/package=afex}
 
 \leavevmode\hypertarget{ref-stroop_studies_1935}{}%
-Stroop, J. R. (1935). Studies of interference in serial verbal reactions. \emph{Journal of Experimental Psychology}, \emph{18}, 643. doi:\href{https://doi.org/10.1037/h0054651}{10.1037/h0054651}
+Stroop, J. R. (1935). Studies of interference in serial verbal reactions. \emph{Journal of Experimental Psychology}, \emph{18}, 643. \url{https://doi.org/10.1037/h0054651}
 
@@
 \emph{Psychiatry Research}, \emph{168}, 242--249.
-doi:\href{https://doi.org/10.1016/j.psychres.2008.05.006}{10.1016/j.psychres.2008.05.006}
+\url{https://doi.org/10.1016/j.psychres.2008.05.006}
 
@@
 \emph{The Quarterly Journal of Experimental Psychology Section A}, \emph{47}, 631--650.
-doi:\href{https://doi.org/10.1080/14640749408401131}{10.1080/14640749408401131}
+\url{https://doi.org/10.1080/14640749408401131}
 
@@
 \emph{The Quarterly Journal of Experimental Psychology}, \emph{62}, 1391--1400.
-doi:\href{https://doi.org/10.1080/17470210802426908}{10.1080/17470210802426908}
+\url{https://doi.org/10.1080/17470210802426908}
 
@@
 \emph{The Quarterly Journal of Experimental Psychology}, \emph{69}, 2202--2217.
-doi:\href{https://doi.org/10.1080/17470218.2015.1111396}{10.1080/17470218.2015.1111396}
+\url{https://doi.org/10.1080/17470218.2015.1111396}
 

### 2019-07-17 data-analysis/analysis_E1.R

@@ -4,9 +4,11 @@ library(tidyr)
 library(afex)
 library(ggplot2)
 library(cowplot)
+library(BayesFactor)
 #As of 2018/12/07 apa_print() requires development version of Papaja
 #devtools::install_github("crsh/papaja")
 library(papaja)
+library(apaTables)
 
 
 folderName <- function(){
@@ -34,7 +36,23 @@ vjoutNR <- function(x,n) {
 }
 
 
+print_eta_CI <- function(Fval, conf = .90, df1, df2){
+  limits <- apaTables::get.ci.partial.eta.squared(F.value=Fval, df1=df1, df2=df2, conf.level=conf)
+  return(paste0("90\\% CI $[",round(limits$LL, 2),"$, $",round(limits$UL, 2),"]$"))
+}
 
+print_apa_ci <- function(aov_table){
+  pap <- apa_print(aov_table, es = "pes")$full_result
+  
+  for(i in 1:length(pap)){
+    pap[i] <- paste(pap[i], print_eta_CI(Fval = aov_table$anova_table$`F`[i], df1 = aov_table$anova_table$`num Df`[i], df2 = aov_table$anova_table$`den Df`[i]), sep = " ")
+    pap[i] <- gsub("p = .000", "p < .001", pap[i])
+    pap[i] <- gsub(") = 0.00", ") < 0.01", pap[i])
+  }
+  return(pap)
+}
+
+################## ANALYSIS #########################
 load("data-analysis/raw_data_E1.Rda")
 
 
@@ -78,10 +96,16 @@ RT.Analysis <- RT.DF %>%
     Frequency == "unbiased"
   ) %>%
   group_by(Condition,Subject,Task_Relevant_Context,Congruency) %>%
-  summarise(meanRT = mean(vjoutRT))
+  summarise(meanRT = mean(vjoutRT))%>%
+  spread(Congruency,meanRT) %>%
+  mutate(CE = inc - con) %>%
+  select(-con:-inc)
 
-RT_ANOVA <- aov_car(meanRT ~ Condition*Task_Relevant_Context*Congruency + Error(Subject/Task_Relevant_Context*Congruency), data = RT.Analysis)
-RT_ANOVA <- apa_print(RT_ANOVA, es = "pes")$full_result
+aov_table <- aov_car(CE ~ Condition*Task_Relevant_Context + Error(Subject/Task_Relevant_Context), data = RT.Analysis)
[…]

### 2019-07-17 data-analysis/analysis_E1_Exploratory.R

@@ -6,6 +6,7 @@ library(afex)
 library(ggplot2)
 library(cowplot)
 library(forcats)
+library(BayesFactor)
 #As of 2018/12/07 apa_print() requires development version of Papaja
 #devtools::install_github("crsh/papaja")
 library(papaja)
@@ -113,6 +114,27 @@ order_effect_plot <-ggplot(RT.summary,aes(x=Order, y=m, fill=Task_Relevant_Conte
 
 E1_Order_A <- aov_car(vjoutRT ~ Congruency*Task_Relevant_Context*Order + Error(Subject/Congruency*Task_Relevant_Context), data = RT.DF %>% filter(Frequency == "unbiased"))
 E1_Order_A <- apa_print(E1_Order_A, es = "pes")$full_result
+
+
+
+################### Bayesian Analysis #####################
+
+## Analyze RTs for frequency unbiased items
+RT.Analysis <- RT.DF  %>%
+  filter(!is.nan(vjoutRT)) %>%
+  filter(Frequency == "unbiased",
+         Subject%in%low_acc == FALSE) %>%
+  group_by(Subject,Order,Task_Relevant_Context,Congruency) %>%
+  summarize(vjoutRT = mean(vjoutRT)) %>%
+  spread(Congruency, vjoutRT) %>%
+  mutate(Diff = inc - con) %>%
+  filter(!is.na(Diff))
+
+
+
+RT_BF_E1_exploreA = BayesFactor::anovaBF(Diff ~ Order*Task_Relevant_Context + Subject, data = RT.Analysis,
+                          whichRandom="Subject", iterations=10000)
+
 
 # 
 # RT.summary <- RT.DF %>%
@@ -377,6 +399,47 @@ E1_Order_B <- aov_car(vjoutRT ~ Congruency*Task_Relevant_Context*Order + Error(S
 E1_Order_B <- apa_print(E1_Order_B, es = "pes")$full_result
 
 
+################### Bayesian Analysis #####################
+
+
+RT.summary <- RT.DF %>%
+  filter(!is.nan(vjoutRT)) %>%
+  filter(Frequency == "unbiased",
+         Transition != "other",
+         Subject%in%missing == FALSE) %>%
+  group_by(Subject,Order,Task_Relevant_Context,Congruency) %>%
+  summarize(vjoutRT = mean(vjoutRT)) %>%
+  spread(Congruency, vjoutRT) %>%
+  mutate(Diff = inc - con) %>%
+  filter(!is.na(Diff)) %>%
[…]

### 2019-07-17 data-analysis/analysis_E2.R

@@ -192,12 +192,31 @@ figure3<-plot_grid(RT.graph,NULL,ACC.graph,
                    rel_widths = c(1, 0.05, 1),
                    labels = c("A", "", "B"))
 
-title <- ggdraw() + draw_label("Experiment 2", fontface='bold')
-figure3<-plot_grid(title, figure3, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
+#title <- ggdraw() + draw_label("Experiment 2", fontface='bold')
+#figure3<-plot_grid(title, figure3, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
 
  ggsave("figure3.pdf", device = "pdf", dpi = 600,
-       width = 6.875, height = 4, units = "in") 
+       width = 3.25, height = 3.75, units = "in") 
 
 #clean up environment
 #rm(list=c("ACC.analysis","aov.out","raw_data_E2","RT.Analysis","RT.DF","low_acc","vjoutNR", "RT.Diff"))
 
+ 
+ ################### Bayesian Analysis #####################
+ 
+ ## Analyze RTs for frequency unbiased items
+ RT.Analysis <- RT.DF %>%
+   ungroup() %>%
+   mutate(Subject = factor(Subject),
+          PC = factor(PC)) %>%
+   group_by(Subject,PC,Congruency) %>%
+   summarise(meanRT = mean(vjoutRT)) %>%
+   spread(Congruency, meanRT) %>%
+   ungroup()%>%
+   mutate(Diff = inc - con)
+ 
+ 
+ 
+ RT_BF_E2 = BayesFactor::anovaBF(Diff ~ PC + Subject, data = RT.Analysis,
+                           whichRandom="Subject", iterations=10000)
+ 

### 2019-07-17 data-analysis/analysis_E3.R

@@ -223,12 +223,32 @@ figure4<-plot_grid(RT.graph,NULL,ACC.graph,
                    rel_widths = c(1, 0.05, 1),
                    labels = c("A", "", "B"))
 
-title <- ggdraw() + draw_label("Experiment 3", fontface='bold')
-figure4<-plot_grid(title, figure4, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
+#title <- ggdraw() + draw_label("Experiment 3", fontface='bold')
+#figure4<-plot_grid(title, figure4, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins
 
 ggsave("figure4.pdf", device = "pdf", dpi = 600,
-      width = 3.6, height = 4, units = "in") 
+      width = 3.25, height = 3.75, units = "in") 
 
 #clean up environment
 #rm(list=c("ACC.analysis","aov.out","raw_data_E3","RT.Analysis","RT.DF","low_acc","vjoutNR", "RT.Diff"))
 
+
+################### Bayesian Analysis #####################
+
+## Analyze RTs for frequency unbiased items
+RT.Analysis <- RT.DF %>%
+  filter(
+    Frequency == "unbiased"
+  ) %>%
+  ungroup() %>%
+  mutate(Subject = factor(Subject),
+         Task_Relevant_Context = factor(Task_Relevant_Context)) %>%
+  group_by(Subject,Task_Relevant_Context,Congruency) %>%
+  summarise(meanRT = mean(vjoutRT)) %>%
+  spread(Congruency, meanRT) %>%
+  mutate(Diff = inc - con) 
+
+
+
+RT_BF_E3 = BayesFactor::anovaBF(Diff ~ Task_Relevant_Context + Subject, data = RT.Analysis,
+                          whichRandom="Subject",whichModel ="withmain", iterations=10000)

### 2019-07-17 data-analysis/plot-power-simulation.R

@@ -1,0 +1,113 @@
+load(file="data-analysis/sim_effectSizes.Rda")
+
+
+sim_effectSizes <- sim_effectSizes %>% filter(effect.size < 41)
+
+plot.1 <- ggplot(sim_effectSizes[sim_effectSizes$effect != "CSPC x Condition",], aes(effect.size, prop.sig, color = effect)) + 
+  geom_smooth( aes(color = effect), se = FALSE, method = "gam", formula = y ~ s(log(x)))+
+  geom_point(aes(x = effect.size, y = prop.sig, color=effect, shape = effect), size = 2) +
+  geom_vline(xintercept = 20, linetype = "dashed") +
+  scale_color_manual(values = c("#006d2c", "#41ab5d", "#a1d99b")) +
+  labs(y = "Proportion p < .05", x = "Effect Size (ms)", color = "Effect", shape = "Effect") +
+  scale_x_continuous(limits = c(0, 40), breaks=c(seq(from=0, to=40, by=5)), expand = expand_scale(mult = c(0,0.05)))+
+  scale_y_continuous(limits = c(0, 1.01), breaks=c(seq(from=0, to=1, by=.1)), expand = expand_scale(mult =c(0,0.01)) )+
+  theme(axis.text=element_text(size=7.5),
+        axis.title=element_text(size=10,face="bold"),       
+        legend.position = c(.6, .3),
+        #legend.direction = "horizontal",
+        #legend.background = element_rect(colour = "white", fill = "white", size=1),
+        #legend.box.background = element_rect(colour = "black"),
+        legend.margin = margin(t = .1, r = .10, b = .05, l = .1, unit = "cm"),
+        legend.text = element_text(size = 8),
+        legend.title = element_text(size = 8)
+  ) 
+
+sim_effectSizes <- sim_effectSizes[sim_effectSizes$effect == "CSPC x Condition",]
+levels(sim_effectSizes$effect) <- c("CSPC x\nCondition", "CSPC (N = 50)","CSPC (N = 150)")
+
+plot.2 <- ggplot(sim_effectSizes, aes(effect.size, prop.sig, color = effect)) + 
+  geom_smooth( aes(color = effect), se = FALSE, method = "gam", formula = y ~ s(log(x)))+
+  geom_point(aes(x = effect.size, y = prop.sig, color=effect, shape = effect), size = 2) +
+  geom_vline(xintercept = 20, linetype = "dashed") +
[…]

### 2019-07-17 data-analysis/power_simulation.R

@@ -1,356 +1,261 @@
-
 library(dplyr)
 library(tidyr)
 library(afex)
 library(ggplot2)
 library(cowplot)
+library(retimes)
+library(doParallel)
+
 #As of 2018/12/07 apa_print() requires development version of Papaja
 #devtools::install_github("crsh/papaja")
 library(papaja)
 
-######### FUNCTIONS ##########3
-
-### Outlier removal function
-vjoutNR <- function(x,n) {
-    if(length(x) == 1){return (x)}
-    xm <- mean(x)
-    xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
-               25, 30, 35, 50, 80)
-    stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
-              2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
-              2.45, 2.48, 2.5)
-    stdindex <- length(xsize[xsize <= length(x)])
-    removed <- x[x < xm+sd(x)*stds[stdindex]]
-    removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
-    proportionRemoved <- length(removed)/length(x)
-    finaldata<-c(mean(removed),1-proportionRemoved)
-    return(finaldata[[n]])
-}
-
-### Run single simulation 
-run_sim <- function(pop_mean = NULL,
-                    pop_sd = NULL,
-                    effect_estimate = "B",
-                    effect_dist = "3/3",
-                    effect_size = 5,
-                    n_subs = 20,
-                    upper = pop_mean + 2 * pop_sd,
-                    lower = pop_mean - 2 * pop_sd) {
-    
-    n_subs <- n_subs * 3
-    
-    # sample some rts
-    # over-sample and discard overflow
-    rts <- c()
-    while (length(rts) < (n_subs * 2)) {
-        # over sample d
-        t <- rnorm((n_subs * 3),mean = pop_mean,sd = pop_sd)
-        rts <- t[t > lower & t < upper]
-    }
-    rts <- rts[1:(n_subs * 2)]
-    
-    ### Add effect
-    if (effect_dist == "3/3") {
-        rts[1:(length(rts) / 2)] <- rts[1:(length(rts) / 2)] + effect_size
-    }
-    
[…]

### 2019-07-17 data-analysis/vj-outlier-removal-NR.R

@@ -1,0 +1,25 @@
+### Outlier removal function
+#' Title
+#'
+#' @param x 
+#' @param n 
+#'
+#' @return
+#' @export
+#'
+#' @examples
+vjoutNR <- function(x,n) {
+  if(length(x) == 1){return (x)}
+  xm <- mean(x)
+  xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
+             25, 30, 35, 50, 80)
+  stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
+            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
+            2.45, 2.48, 2.5)
+  stdindex <- length(xsize[xsize <= length(x)])
+  removed <- x[x < xm+sd(x)*stds[stdindex]]
+  removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
+  proportionRemoved <- length(removed)/length(x)
+  finaldata<-c(mean(removed),1-proportionRemoved)
+  return(finaldata[[n]])
+}

### 2019-07-17 manuscript_pretty.Rmd
revision in progress

@@
 ## Participants
-All participants were recruited from Amazon Mechanical Turk (AMT) and compensated $2.00 for participating.
-The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by $6.00 per hour.
+All participants were recruited from Amazon Mechanical Turk (AMT) and compensated \$2.00 for participating.
+The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by \$6.00 per hour.
 For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study.
@@
 Experiment 1 used a 2x2x3 mixed design with task-relevant context (0% and 100%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+
 All three conditions were constructed using the same general method.
@@
 ## Data Analysis 
-All analyses in this and the following experiments were performed in R [@r_software_2019] using a variety of R packages ().
-In particular, we used the afex and car packages [@r_afex_2019; @r_car_2019] to perform all the Null Hypothesis Significance Tests, the BayesFactor package to perform Bayesian analyses [@r_bayesfactor_2018], and the conflictPower package to perform the simulation-based sensitivity and power analyses [@r_conflictPower_2019].
-All data and scripts can be found
+All analyses in this and the following experiments were performed in R [@r_software_2019] using a variety of R packages and resources [@r_wickham_ggplot2_2016; @r_wickham_dplyr_2019; @r_papaja_2018; @r_cowplot_2019].
+Of particular note: we used the afex and car packages to perform all the Null Hypothesis Significance Tests [@r_afex_2019; @r_car_2019], the BayesFactor package to perform Bayesian analyses [@r_bayesfactor_2018], and the conflictPower package to perform the simulation-based sensitivity and power analyses [@r_conflictPower_2019].
+All data and scripts can be found on the Open Science Framework (https://osf.io/ztcyb/).
 
-We supplemented each Null Hypothesis Significance Test with a Bayes Factor analysis (Rouder, Speckman..
-2009).
+We supplemented each Null Hypothesis Significance Test with a Bayes Factor analysis [@rouder_bayesian_2009].
 Using conventional frequentist testing it is not possible to quantify the evidence for a null effect.
-Bayes Factors, however, quantify the degree to which the observed data are compatible with either the alternative or null hypothesis (Dienes, 2014; Rouder et al., 2014).
-All Bayesian analyses were performed using the R package BayesFactor and Bayes Factors (BFs) were calculated using its default settings (Morey and Rouder, 2014).
-Following the guidelines recommended by Rouder et al.
-(2009)
+A Bayes Factor, however, is a continuous measure of the relative strength of evidence and can quantify the degree to which the data are compatible with the null over the alternative hypothesis [@dienes_using_2014; @rouder_bayesian_2009].
+All Bayesian analyses were performed using the R package BayesFactor and Bayes Factors ($\mathrm{BFs}$) were calculated using its default settings [@r_bayesfactor_2018].
+$\mathrm{BF}_{\textrm{10}}$ indicates evidence in favor of the alternative hypothesis whereas $\mathrm{BF}_{\textrm{01}}$ indicates evidence in favor of the null hypothesis.
+To simplify the interpretation, we report the Bayes Factor in the direction the data supports (e.g.,  $\mathrm{BF}_{\textrm{01}}$ when there is more evidence in favor of the null over alternative hypothesis).
+As per previous recommendations, we refer to a $\mathrm{BF > 3}$ as "moderate" and $\mathrm{BF > 10}$ as "strong" evidence [@jeffreys1961theory; @rouder_bayesian_2009].
 
@@
 The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1).
-To that end, congruency effects (incongruent minus congruent performance) from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0% and 100% PC) and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+To that end, congruency effects (incongruent minus congruent performance) from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) as the within-subjects factor and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+We supplement each Null Hypothesis Significance Test with a corresponding Bayesian analysis.
 
-The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, `r RT_ANOVA$Task_Relevant_Context`, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
-Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, `r RT_ANOVA$Condition_Task_Relevant_Context`, showing no evidence for differences between the CSPC effects across context-type manipulations.
+The results of the reaction time analysis revealed a significant effect of the task-relevant context, `r RT_ANOVA$Task_Relevant_Context`, with moderate evidence in favor of the alternative, `r pRT_BF[[2]]`.
+Specifically, we found smaller congruency effects when the context dimension associated with high conflict was made task-relevant as compared to when the low conflict dimension was made task-relevant.
+The main effect of context-type, however, was non-significant, `r RT_ANOVA$Condition`, with moderate evidence in favor of the null hypothesis, `r pRT_BF[[1]]`.
+The two-way interaction between the task-relevant context and context-type was also non-significant, `r RT_ANOVA$Condition_Task_Relevant_Context`, with moderate evidence in favor of the null hypothesis, `r pRT_BF[[4]]`.
+Finally, the preferred model containing only the task-relevant context was preferred over the model containing the both factors and the interaction by a factor of `r BF_contrast`.
+Therefore, congruency effects did not vary across context-types and, more importantly, the effect of task-relevance did not vary across context-types.
 
-Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA$Task_Relevant_Context`, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, `r ACC_ANOVA$Condition_Task_Relevant_Context`.
-Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.
+Similarly, the corresponding error analysis also resulted a significant effect of the task-relevant context, `r ACC_ANOVA$Task_Relevant_Context`, with moderate evidence in favor of the alternative evidence `r pACC_BF[[2]]`; A non-significant effect of context-type, `r ACC_ANOVA$Condition`, with moderate evidence for the null hypothesis, `r pACC_BF[[1]]`; And a non-significant interaction between task-relevant context and context-type,`r ACC_ANOVA$Condition_Task_Relevant_Context`, with strong evidence in favor of the null hypothesis,`r pACC_BF[[4]]`.
+Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant and effects did not vary across context-type, corroborating the results of the reaction time analysis.
 
-## Exploratory Analyses: Order Effects
+## Exploratory analyses: Order effects
 
-```{r figure2b, echo=FALSE,fig.width=6.875, fig.height= 4, fig.cap='(ref:figure2)'}
+```{r figure2b, echo=FALSE,fig.width=6.875, fig.height= 4, fig.cap='(ref:figure2b)'}
 #, out.width="\\textwidth", fig.env="figure*"
@@
 
-Previous work has shown that the effects of shifting between list-wide proportion congruent phases is asymmetrical.
-Abrahamse et al....
-found that...
-In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from one context cue to another.
+(ref:figure2b) Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent) and phase order (100% to 0% PC versus 0% to 100% PC).
+Figure A shows a summary of the data containing all trials, whereas Figure B shows a summary of the data restricted to the 24 trials immediately before and 24 trials immediately after the transition.
+In both cases, the interaction was non-significant ($p > .05$) and Bayesian analyses showed moderate evidence in favor of the null hypothesis ($\mathrm{BF}_{\textrm{01}} > 3$).
+
+Previous work has shown that shifting between list-wide proportion congruent phases produced asymmetrical effects.
+Specifically, @abrahamse_attention_2013 found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects.
+The authors suggested that the assymetry is caused by a learned attentional modulation in the mostly-incongruent block carrying over into the mostly-congruent block.
+In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from the use of one context cue to another.
 We therefore randomized the order across participants to control for the effects of order.
-However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was symmetrical in our study.
+However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was asymmetrical.
 
@@
 We again removed participants with error rates greater than 25% and adopted the same outlier removal procedure as described above.
-We submitted mean correct RTs for frequency unbiased items to a 2x2x2 mixed ANOVA with task-relevant context (0% and 100% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and phase order (100%-0% and 0%-100%) as the between-subjects factor.
+We submitted congruency effects for frequency unbiased items to a 2x2 mixed ANOVA with task-relevant context (0% and 100% PC) as within-subject factors and phase order (100%-0% and 0%-100%) as the between-subjects factor, and supplemented each test with a corresponding Bayesian analysis.
 
-Consistent with the original analysis, two-way interaction between task-relevant context and congruency remained significant,`r E1_Order_A$Congruency_Task_Relevant_Context`.
-However, the three-way interaction was non-significant, `r E1_Order_A$Order_Congruency_Task_Relevant_Context`.
-Therefor, we did not find statistical support for a list-shift asymmetry.
-Additionally, the asymmetry we do see in this sample is in the opposite direction than would be predicted given the prior results ().
+Consistent with the original analysis, the effect of task-relevant context was significant,`r E1_Order_A$Task_Relevant_Context`, with moderate evidence in favor of the alternative, `r pE1_Order_A_BF[[2]]`.
+However, the two-way interaction between task-relevant context and phase order was non-significant, `r E1_Order_A$Order_Task_Relevant_Context`, with moderate evidence in favor of the null hypothesis, `r pE1_Order_A_BF[[4]]`.
+Therefore, we did not find statistical support for a list-shift asymmetry.
+Additionally, the (non-significant) asymmetrical effects we do see in this sample is in the opposite direction than would be predicted given the prior research [e.g., @abrahamse_attention_2013].
 
-We also conducted a more severe test of the list-shift hypothesis.
-Abrahamse et al.'s interpretation of the list shift effect was that participants had to learn to adjust to the new cues.
-Therefore, we might expect that any asymmetry would be exaggerated near the point of transition.
-We repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.
+We conducted an additional, more severe test, of the list-shift hypothesis.
+Given that the asymmetry is interpreted as resulting from a carry-over of learned attentional modulation across phases, we might expect that any asymmetry would be exaggerated near the point of transition.
+We therefore repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.
 
-Again, the three-way interaction was non-significant, `r E1_Order_B$Order_Congruency_Task_Relevant_Context`.
-Interestingly, the two-way interaction between congruency and task-relevant context is also still significant, `r E1_Order_B$Congruency_Task_Relevant_Context`.
-This result supports the notion there was no asymmetry and that the shift in context-dependent effects occur almost immediately after the transition.
+Again, the interaction between task-relevant context and phase order was non-significant, `r E1_Order_B$Order_Task_Relevant_Context`, with moderate to strong evidence in favor of the null `r pE1_Order_B_BF[[4]]`.
+Interestingly, the main effect of task-relevant context was still significant, `r E1_Order_B$Task_Relevant_Context`, with moderate evidence in favor of the alternative, `r pE1_Order_B_BF[[2]]`.
+This result supports the conclusion that there was no asymmetry.
+Additionally, the the shift in context-dependent effects appears to have taken place almost immediately after the transition.
 

### 2019-07-17 manuscript_pretty.tex
revision in progress

--- 2019-06-30 manuscript_pretty.tex
@@
 Experiment 1 used a 2x2x3 mixed design with task-relevant context (0\% and 100\%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+
 All three conditions were constructed using the same general method.
@@
 
+\hypertarget{data-analysis}{%
+\subsection{Data Analysis}\label{data-analysis}}
+
+All analyses in this and the following experiments were performed in R (R Core Team, 2019) using a variety of R packages and resources (Aust \& Barth, 2018; Wickham, 2016; Wickham, François, Henry, \& Müller, 2019; Wilke, 2019).
+Of particular note: we used the afex and car packages to perform all the Null Hypothesis Significance Tests (Fox \& Weisberg, 2019; Singmann, Bolker, Westfall, \& Aust, 2019), the BayesFactor package to perform Bayesian analyses (Morey \& Rouder, 2018), and the conflictPower package to perform the simulation-based sensitivity and power analyses (Crump \& Brosowsky, 2019).
+All data and scripts can be found on the Open Science Framework (\url{https://osf.io/ztcyb/}).
+
+We supplemented each Null Hypothesis Significance Test with a Bayes Factor analysis (Rouder, Speckman, Sun, Morey, \& Iverson, 2009).
+Using conventional frequentist testing it is not possible to quantify the evidence for a null effect.
+A Bayes Factor, however, is a continuous measure of the relative strength of evidence and can quantify the degree to which the data are compatible with the null over the alternative hypothesis (Dienes, 2014; Rouder et al., 2009).
+All Bayesian analyses were performed using the R package BayesFactor and Bayes Factors (\(\mathrm{BFs}\)) were calculated using its default settings (Morey \& Rouder, 2018).
+\(\mathrm{BF}_{\textrm{10}}\) indicates evidence in favor of the alternative hypothesis whereas \(\mathrm{BF}_{\textrm{01}}\) indicates evidence in favor of the null hypothesis.
+To simplify the interpretation, we report the Bayes Factor in the direction the data supports (e.g., \(\mathrm{BF}_{\textrm{01}}\) when there is more evidence in favor of the null over alternative hypothesis).
+As per previous recommendations, we refer to a \(\mathrm{BF > 3}\) as \enquote{moderate} and \(\mathrm{BF > 10}\) as \enquote{strong} evidence (Jeffreys, 1961; Rouder et al., 2009).
+
 \hypertarget{results}{%
@@
 The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1).
-To that end, mean correct RTs and mean error rates from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+To that end, congruency effects (incongruent minus congruent performance) from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) as the within-subjects factor and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+We supplement each Null Hypothesis Significance Test with a corresponding Bayesian analysis.
 
-The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 1,608.54\), \(p = .005\), \(\hat{\eta}^2_p = .061\), demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
-Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, \(F(2, 128) = 0.00\), \(\mathit{MSE} = 1,608.54\), \(p = .996\), \(\hat{\eta}^2_p = .000\), showing no evidence for differences between the CSPC effects across context-type manipulations.
+The results of the reaction time analysis revealed a significant effect of the task-relevant context, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 3,217.08\), \(p = .005\), \(\hat{\eta}^2_p = .061\), 90\% CI \([0.01\), \(0.14]\), with moderate evidence in favor of the alternative, \(\mathrm{BF}_{\textrm{10}} = 6.87\) \([\pm 1.41\%]\).
+Specifically, we found smaller congruency effects when the context dimension associated with high conflict was made task-relevant as compared to when the low conflict dimension was made task-relevant.
+The main effect of context-type, however, was non-significant, \(F(2, 128) = 1.51\), \(\mathit{MSE} = 6,368.18\), \(p = .225\), \(\hat{\eta}^2_p = .023\), 90\% CI \([0\), \(0.07]\), with moderate evidence in favor of the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 3.96\) \([\pm 1.52\%]\).
+The two-way interaction between the task-relevant context and context-type was also non-significant, \(F(2, 128) < 0.01\), \(\mathit{MSE} = 3,217.08\), \(p = .996\), \(\hat{\eta}^2_p < .001\), 90\% CI \([0\), \(1]\), with moderate evidence in favor of the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 7.9\) \([\pm 1.49\%]\).
+Finally, the preferred model containing only the task-relevant context was preferred over the model containing the both factors and the interaction by a factor of \(54.25\) \([\pm 2.05\%]\).
+Therefore, congruency effects did not vary across context-types and, more importantly, the effect of task-relevance did not vary across context-types.
 
-Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 128) = 6.72\), \(\mathit{MSE} = 13.93\), \(p = .011\), \(\hat{\eta}^2_p = .050\), and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, \(F(2, 128) = 0.92\), \(\mathit{MSE} = 13.93\), \(p = .400\), \(\hat{\eta}^2_p = .014\).
-Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.
+Similarly, the corresponding error analysis also resulted a significant effect of the task-relevant context, \(F(1, 128) = 6.72\), \(\mathit{MSE} = 27.87\), \(p = .011\), \(\hat{\eta}^2_p = .050\), 90\% CI \([0.01\), \(0.12]\), with moderate evidence in favor of the alternative evidence \(\mathrm{BF}_{\textrm{10}} = 3.13\) \([\pm 5.2\%]\); A non-significant effect of context-type, \(F(2, 128) = 0.81\), \(\mathit{MSE} = 51.40\), \(p = .449\), \(\hat{\eta}^2_p = .012\), 90\% CI \([0\), \(0.05]\), with moderate evidence for the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 7.54\) \([\pm 1.22\%]\); And a non-significant interaction between task-relevant context and context-type,\(F(2, 128) = 0.92\), \(\mathit{MSE} = 27.87\), \(p = .400\), \(\hat{\eta}^2_p = .014\), 90\% CI \([0\), \(0.05]\), with strong evidence in favor of the null hypothesis,\(\mathrm{BF}_{\textrm{01}} = 15.04\) \([\pm 2.57\%]\).
+Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant and effects did not vary across context-type, corroborating the results of the reaction time analysis.
 
 \hypertarget{exploratory-analyses-order-effects}{%
-\subsection{Exploratory Analyses: Order Effects}\label{exploratory-analyses-order-effects}}
+\subsection{Exploratory analyses: Order effects}\label{exploratory-analyses-order-effects}}
 
@@
 \includegraphics{manuscript_pretty_files/figure-latex/figure2b-1.pdf}
-\caption{\label{fig:figure2b}Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent).
-Task-relevance was manipulated by the secondary feature-counting task.}
+\caption{\label{fig:figure2b}Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent) and phase order (100\% to 0\% PC versus 0\% to 100\% PC).
+Figure A shows a summary of the data containing all trials, whereas Figure B shows a summary of the data restricted to the 24 trials immediately before and 24 trials immediately after the transition.
+In both cases, the analyses resulted in no significant interaction (\(p > .05\)) and moderate evidence in favor of the null hypothesis (\(\mathrm{BF}_{\textrm{01}} > 3\)).}
 \end{figure}
 
-Previous work has shown that the effects of shifting between list-wide proportion congruent phases is asymmetrical.
-Abrahamse et al\ldots{}.
-found that\ldots{} In our study, we were primarily interested in whether participants could use context cues despite the presence of competing, contradictory cues, and whether they could switch from one context cue to another.
+Previous work has shown that shifting between list-wide proportion congruent phases produced asymmetrical effects.
+Specifically, Abrahamse, Duthoo, Notebaert, and Risko (2013) found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects.
+The authors suggested that the assymetry is caused by a learned attentional modulation in the mostly-incongruent block carrying over into the mostly-congruent block.
+In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from the use of one context cue to another.
 We therefore randomized the order across participants to control for the effects of order.
-However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was symmetrical in our study.
+However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was asymmetrical.
 
@@
 We again removed participants with error rates greater than 25\% and adopted the same outlier removal procedure as described above.
-We submitted mean correct RTs for frequency unbiased items to a 2x2x2 mixed ANOVA with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and phase order (100\%-0\% and 0\%-100\%) as the between-subjects factor.
+We submitted congruency effects for frequency unbiased items to a 2x2 mixed ANOVA with task-relevant context (0\% and 100\% PC) as within-subject factors and phase order (100\%-0\% and 0\%-100\%) as the between-subjects factor, and supplemented each test with a corresponding Bayesian analysis.
 
-Consistent with the original analysis, two-way interaction between task-relevant context and congruency remained significant,\(F(1, 129) = 8.92\), \(\mathit{MSE} = 1,627.84\), \(p = .003\), \(\hat{\eta}^2_p = .065\).
-However, the three-way interaction was non-significant, \(F(1, 129) = 2.56\), \(\mathit{MSE} = 1,627.84\), \(p = .112\), \(\hat{\eta}^2_p = .019\).
+Consistent with the original analysis, the effect of task-relevant context was significant,\(F(1, 129) = 8.92\), \(\mathit{MSE} = 3,255.69\), \(p = .003\), \(\hat{\eta}^2_p = .065\), 90\% CI \([0.01\), \(0.14]\), with moderate evidence in favor of the alternative, \(\mathrm{BF}_{\textrm{10}} = 8.11\) \([\pm 0.83\%]\).
+However, the two-way interaction between task-relevant context and phase order was non-significant, \(F(1, 129) = 2.56\), \(\mathit{MSE} = 3,255.69\), \(p = .112\), \(\hat{\eta}^2_p = .019\), 90\% CI \([0\), \(0.07]\), with moderate evidence in favor of the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 4.92\) \([\pm 2.95\%]\).
 Therefor, we did not find statistical support for a list-shift asymmetry.
-Additionally, the asymmetry we do see in this sample is in the opposite direction than would be predicted given the prior results ().
+Additionally, the (non-significant) asymmetry we do see in this sample is in the opposite direction than would be predicted given the prior research (e.g., Abrahamse et al., 2013).
 
-We also conducted a more severe test of the list-shift hypothesis.
-Abrahamse et al.'s interpretation of the list shift effect was that participants had to learn to adjust to the new cues.
-Therefore, we might expect that any asymmetry would be exaggerated near the point of transition.
-We repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.
+Additionally, we conducted a more severe test of the list-shift hypothesis.
+Given that the asymmetry is interpreted as resulting from a carry-over of learned attentional modulation across phases, we might expect that any asymmetry would be exaggerated near the point of transition.
+We therefore repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.
 
-Again, the three-way interaction was non-significant, \(F(1, 129) = 0.02\), \(\mathit{MSE} = 2,866.15\), \(p = .902\), \(\hat{\eta}^2_p = .000\).
-Interestingly, the two-way interaction between congruency and task-relevant context is also still significant, \(F(1, 129) = 6.65\), \(\mathit{MSE} = 2,866.15\), \(p = .011\), \(\hat{\eta}^2_p = .049\).
-This result supports the notion there was no asymmetry and that the shift in context-dependent effects occur almost immediately after the transition.
+Again, the interaction between task-relevant context and phase order was non-significant, \(F(1, 129) = 0.02\), \(\mathit{MSE} = 5,732.31\), \(p = .902\), \(\hat{\eta}^2_p < .001\), 90\% CI \([0\), \(0.01]\), with moderate to strong evidence in favor of the null \(\mathrm{BF}_{\textrm{01}} = 8.88\) \([\pm 2.88\%]\).
+Interestingly, the main effect of task-relevant context was still significant, \(F(1, 129) = 6.65\), \(\mathit{MSE} = 5,732.31\), \(p = .011\), \(\hat{\eta}^2_p = .049\), 90\% CI \([0.01\), \(0.12]\), with moderate evidence in favor of the alternative, \(\mathrm{BF}_{\textrm{10}} = 3.22\) \([\pm 2.16\%]\).
+This result supports the conclusion that there was no asymmetry.
+Additionally, the the shift in context-dependent effects appears to have taken place almost immediately after the transition.
 
@@
 
+\leavevmode\hypertarget{ref-abrahamse_attention_2013}{}%
+Abrahamse, E.
+L., Duthoo, W., Notebaert, W., \& Risko, E.
+F.
+(2013).
+Attention modulation by proportion congruency: The asymmetrical list shifting effect.
+\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{39}, 1552.
+Retrieved from \url{http://psycnet.apa.org/journals/xlm/39/5/1552/}
+
 \leavevmode\hypertarget{ref-alards-tomalin_auditory_2017}{}%
@@
 doi:\href{https://doi.org/10.1080/20445911.2017.1353518}{10.1080/20445911.2017.1353518}
+
+\leavevmode\hypertarget{ref-r_papaja_2018}{}%
+Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
 
@@
 
+\leavevmode\hypertarget{ref-r_conflictPower_2019}{}%
+Crump, M. J. C., \& Brosowsky, N. P. (2019). \emph{ConflictPower: Simulation based power analysis for adaptive control designs}. Retrieved from \url{https://github.com/CrumpLab/conflictPower}
+
 \leavevmode\hypertarget{ref-crump_flexibility_2009}{}%
@@
 Devine, P. G. (1989). Stereotypes and prejudice: Their automatic and controlled components. \emph{Journal of Personality and Social Psychology}, \emph{56}(1), 5.
+
+\leavevmode\hypertarget{ref-dienes_using_2014}{}%
+Dienes, Z. (2014). Using Bayes to get the most out of non-significant results. \emph{Frontiers in Psychology}, \emph{5}. doi:\href{https://doi.org/10.3389/fpsyg.2014.00781}{10.3389/fpsyg.2014.00781}
 
@@
 
+\leavevmode\hypertarget{ref-r_car_2019}{}%
+Fox, J., \& Weisberg, S. (2019). \emph{An R companion to applied regression} (Third.). Thousand Oaks CA: Sage. Retrieved from \url{https://socialsciences.mcmaster.ca/jfox/Books/Companion/}
+
 \leavevmode\hypertarget{ref-hutcheon_limits_2017}{}%
@@
 doi:\href{https://doi.org/10.3758/s13423-016-1057-y}{10.3758/s13423-016-1057-y}
+
+\leavevmode\hypertarget{ref-jeffreys1961theory}{}%
+Jeffreys, H. (1961). \emph{Theory of probability, clarendon}. Oxford: Oxford University Press, Clarendon Press.
 
@@
 
+\leavevmode\hypertarget{ref-r_bayesfactor_2018}{}%
+Morey, R. D., \& Rouder, J. N. (2018). \emph{BayesFactor: Computation of bayes factors for common designs}. Retrieved from \url{https://CRAN.R-project.org/package=BayesFactor}
+
+\leavevmode\hypertarget{ref-r_software_2019}{}%
+R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-rouder_bayesian_2009}{}%
+Rouder, J.
+N., Speckman, P.
+L., Sun, D., Morey, R.
+D., \& Iverson, G.
+(2009).
+Bayesian t tests for accepting and rejecting the null hypothesis.
+\emph{Psychonomic Bulletin \& Review}, \emph{16}, 225--237.
+doi:\href{https://doi.org/10.3758/PBR.16.2.225}{10.3758/PBR.16.2.225}
+
 \leavevmode\hypertarget{ref-schmidt_stroop_2008}{}%
@@
 doi:\href{https://doi.org/10.1037/0278-7393.34.3.514}{10.1037/0278-7393.34.3.514}
+
+\leavevmode\hypertarget{ref-r_afex_2019}{}%
+Singmann, H., Bolker, B., Westfall, J., \& Aust, F. (2019). \emph{Afex: Analysis of factorial experiments}. Retrieved from \url{https://CRAN.R-project.org/package=afex}
 
@@
 
+\leavevmode\hypertarget{ref-r_wickham_ggplot2_2016}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-r_wickham_dplyr_2019}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\hypertarget{ref-r_cowplot_2019}{}%
+Wilke, C. O. (2019). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
+
 \endgroup

### 2019-07-17 data-analysis/analysis_E1.R

@@ -10,6 +10,7 @@ library(BayesFactor)
 library(papaja)
 library(apaTables)
 
+set.seed(1983)
 
 folderName <- function(){
   wd<-getwd()
@@ -38,18 +39,32 @@ vjoutNR <- function(x,n) {
 
 print_eta_CI <- function(Fval, conf = .90, df1, df2){
   limits <- apaTables::get.ci.partial.eta.squared(F.value=Fval, df1=df1, df2=df2, conf.level=conf)
-  return(paste0("90\\% CI $[",round(limits$LL, 2),"$, $",round(limits$UL, 2),"]$"))
+  return(paste0(", 90\\% CI $[",round(limits$LL, 2),"$, $",round(limits$UL, 2),"]$"))
 }
 
 print_apa_ci <- function(aov_table){
   pap <- apa_print(aov_table, es = "pes")$full_result
   
   for(i in 1:length(pap)){
-    pap[i] <- paste(pap[i], print_eta_CI(Fval = aov_table$anova_table$`F`[i], df1 = aov_table$anova_table$`num Df`[i], df2 = aov_table$anova_table$`den Df`[i]), sep = " ")
+    pap[i] <- paste0(pap[i], print_eta_CI(Fval = aov_table$anova_table$`F`[i], df1 = aov_table$anova_table$`num Df`[i], df2 = aov_table$anova_table$`den Df`[i]))
     pap[i] <- gsub("p = .000", "p < .001", pap[i])
     pap[i] <- gsub(") = 0.00", ") < 0.01", pap[i])
   }
   return(pap)
+}
+
+print_bf <- function(bf){
+  result <- list()
+  for (i in 1:length(bf)){
+    if(extractBF(bf[i])$bf < 1){
+      result[i] <- paste0("$\\mathrm{BF}_{\\textrm{01}} = ", round(extractBF(1/bf[i])$bf, digits = 2),"$ $[\\pm ", round(extractBF(bf[i])$error*100,digits=2), "\\%]$")
+    } else {
+      result[i] <- paste0("$\\mathrm{BF}_{\\textrm{10}} = ", round(extractBF(bf[i])$bf, digits = 2),"$ $[\\pm ", round(extractBF(bf[i])$error*100,digits=2), "\\%]$")
+      
+    }
+  }
+  
+  return(result)
 }
 
 ################## ANALYSIS #########################
@@ -107,6 +122,13 @@ RT_ANOVA <- print_apa_ci(aov_table)
[…]

### 2019-07-17 data-analysis/analysis_E1_Exploratory.R

@@ -11,6 +11,8 @@ library(BayesFactor)
 #devtools::install_github("crsh/papaja")
 library(papaja)
 
+set.seed(10000)
+
 # van selst and jolicour outlier removal (non-recursive)
 vjoutNR <- function(x,n) {
   xm <- mean(x)
@@ -36,11 +38,43 @@ vjoutNR <- function(x,n) {
   return(finaldata[[n]])
 }
 
+
+print_eta_CI <- function(Fval, conf = .90, df1, df2){
+  limits <- apaTables::get.ci.partial.eta.squared(F.value=Fval, df1=df1, df2=df2, conf.level=conf)
+  return(paste0(", 90\\% CI $[",round(limits$LL, 2),"$, $",round(limits$UL, 2),"]$"))
+}
+
+print_apa_ci <- function(aov_table){
+  pap <- apa_print(aov_table, es = "pes")$full_result
+  
+  for(i in 1:length(pap)){
+    pap[i] <- paste0(pap[i], print_eta_CI(Fval = aov_table$anova_table$`F`[i], df1 = aov_table$anova_table$`num Df`[i], df2 = aov_table$anova_table$`den Df`[i]))
+    pap[i] <- gsub("p = .000", "p < .001", pap[i])
+    pap[i] <- gsub(") = 0.00", ") < 0.01", pap[i])
+  }
+  return(pap)
+}
+
+print_bf <- function(bf){
+  result <- list()
+  for (i in 1:length(bf)){
+    if(extractBF(bf[i])$bf < 1){
+      result[i] <- paste0("$\\mathrm{BF}_{\\textrm{01}} = ", round(extractBF(1/bf[i])$bf, digits = 2),"$ $[\\pm ", round(extractBF(bf[i])$error*100,digits=2), "\\%]$")
+    } else {
+      result[i] <- paste0("$\\mathrm{BF}_{\\textrm{10}} = ", round(extractBF(bf[i])$bf, digits = 2),"$ $[\\pm ", round(extractBF(bf[i])$error*100,digits=2), "\\%]$")
+      
+    }
+  }
+  
+  return(result)
+}
+
+
 ## Pre-process data ------------------------------------
 load("data-analysis/raw_data_E1.Rda")
 
-levels(raw_data$Order) <- c("MI-MC","MC-MI")
-raw_data$Order <- factor(raw_data$Order, c("MC-MI","MI-MC" ))
[…]

### 2019-07-19 manuscript_pretty.Rmd
working - incomplete

@@
 As a result, automatic memory-based retrieval allows attentional priorities to be rapidly adjusted in a context-appropriate fashion.
-How associations between attentional priorities and context cues are formed and used still remains unclear however.
-The current study addresses two related issues.
+How the learning and reinstatement process works however, remains largely unclear.
 
-First, how is attentional control resolved when multiple contextual features could be used as cues? Second, it remains unclear how
+The current study addresses two related issues: First, how is attentional control resolved when multiple contextual features could be used as cues?
+And second, what determines the expression of previously learned attentional associations?
 
-Historically, theories of automaticity and attentional control have emphasized the role of practice and likened the learning process to the automaticity of skill-learning ().
-
-However, the obligatory nature of memory-based attentional control remains unclear, in particular in situations when multiple contextual features could be used as cues for retrieval.
-
-<!-- 
-Furthermore, understanding how associations are formed and used is not well understood.
-Theories of automaticity and attentional control historically have emphasized the role of practice - difficult to suppress once learned..
-Shiffrin and Schneider, Treisman, etc..
-everyone basically.
-
-Early CSPC work too thought that practice is important for "associations to form"
-
-Memory-based theories on the other hand, take a more nuanced view.
-Practice is only important to the extent that improves memory retrieval.
-If retrieval cues can --  distinguish between prior episodes.
-
-Therefore, the skill-learning view of automaticity would predict that associations take time to develop through practice, and once learned, difficult to suppress. 
--->
-
-For example, real-world environments offer a plethora of context cues.
-Consider writing an article in a coffee shop.
-The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), and associated attentional priorities.
+Real-world environments can offer a plethora of context cues.
+For instance, consider someone writing in a coffee shop.
+The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop) associated with many experiences that afford different attentional priorities.
 Although a laptop might cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
 Given that all of these cues are available to set attentional priorities, what determines which associative relationships will be used to guide attention?
-On the one hand, context-based retrieval of attentional priorities might be completely obligatory and a writer's attention would be at the mercy of the environment.
-On the other hand, there is some evidence that contextual cuing of attention is not entirely obligatory and can be constrained by task goals, allowing the laptop to take priority as a contextual cue over other contextual cues that are irrelevant to the task at hand.
+On the one hand, context-based retrieval of attentional priorities might be completely obligatory: the mere presence of learned cues trigger attention in a ballistic manner [e.g., @schneider_controlled_1977; @shiffrin_controlled_1977].
+A writer's attention in this case would be at the mercy of the environment and the most strongly associated cues.
+On the other hand, contextual cuing of attention may not be entirely obligatory.
+Our current task-goals, for instance, might constrain the expression of previously learned associations, allowing, for instance, the laptop to take priority as a contextual cue over other cues that are irrelevant to the task at hand.
 
-Prior work shows that task-relevance is necessary for establishing and using context-attention associations.
-First, the most commonly used context cue is location [@brosowsky_context-specific_2016; @corballis_independent_2003; @crump_context-specific_2006; @crump_context-specific_2008; @crump_learning_2016; @weidler_attentional_2018; @weidler_transfer_2016].
-Although in some sense, the location is irrelevant for identifying the color of a word, it seems disingenuous to consider it completely task-irrelevant.
+Historically, perspectives of automaticity and attentional control have emphasized the role of practice and likened the learning process to the development of automaticity in skill-learning [@schneider_controlled_1977; @shiffrin_controlled_1977; @logan_toward_1988; @logan_attention_1992].
+Under this view, forming an association requires many repeated experiences pairing a cue with a set of attentional priorities.
+Once formed however, they become habitual or hard-wired and the mere presence of the cue is suffificient to automatically adjust attention.
+Learned associations are therefore ballistic, difficult to suppress, and difficult to unlearn [e.g., @schneider_controlled_1977; @shiffrin_controlled_1977; @posner_attention_1975; @posner_facilitation_1975; @treisman_contextual_1960; @treisman_selective_1964; @treisman_strategies_1969].
+This view is reflected in moodern work on contextual cuing where it is assumed that learned associations require practice [e.g., @lehle_fly_2008; @crump_learning_2016], form without awareness or intention, triggered automatically by the mere presence of the cue [@crump_context-specific_2006; @crump_contextual_2010; @crump_context-specific_2008; @king_priming_2012; @reuss_unconscious_2014; though, see @brosowsky_context-specific_2016].
+
+Memory-based perspectives however, take a more nuanced view [@norman_memory_1969; @norman_memory_1976; @abrahamse_grounding_2016; @brosowsky_memory-guided_2018; @crump_learning_2016; @egner_creatures_2014].
+Here, practice is only important to the extent that it improves memory retrieval.
+If a few prior experiences are distinct, and easily retrievable, it could support the reinstatement of a learned attentional association despite very little practice [e.g., @brosowsky_memory-guided_2018].
+Conversely, if prior experiences are difficult to retrieve, then learned associations may not be expressed, even after much practice.
+This view offers one potential path for flexibility in the expression of learned associations.
+Learning an association is the process of encoding into memory experiences where attentional priorities and cues co-occur.
+Memory retrieval is a similarity-based, cue-driven process [e.g., @jacoby_interpreting_1978; @hintzman_minerva_1984; @hintzman_schema_1986; @hintzman_judgments_1988].
+Presumably, the features of our immediate environment automatically cue memory and reinstate the retrieved attentional priorites [@logan_toward_1988; @logan_attention_1992].
+However, to the extent that you could manipulate memory retrieval, you should be able manipulate the expression of learned associations.
+
+Here, we examine whether task-relevance influences the retrieval of previously used attentional priorities.
+We hypothesized that the cue-driven, memory-retrieval process might be constrained to the features of our environment that are relevant to our on-going task and goals.
+If this is the case, then a previously learned association should be easily ignored if that feature was made irrelevant to the task because that feature would no longer contribute to memory-retrieval.
+Furthermore, it would suggest that the mere presence of a cue is not sufficient for automatically directing attention, but instead requires some task-integration.
+
+Recent work lends some credence to the possibility that task-relevance is necessary for establishing and using context-attention associations.
+The most commonly used context cue is location [@brosowsky_context-specific_2016; @corballis_independent_2003; @crump_context-specific_2006; @crump_context-specific_2008; @crump_learning_2016; @weidler_attentional_2018; @weidler_transfer_2016], often claimed to be irrelevant to the on-going conflict task.
+Although in some sense, the location is irrelevant for identifying the color of a word in a Stroop task, it seems disingenuous to consider it completely task-irrelevant.
 In order to identify the target, the participant must first identify and orient to its location on the screen.
-In this is sense, it is relevant to their ability to complete the task and furthermore, location information may receive priority during encoding [@logan_what_1998; @mayr_spatial_1996].
+In this is sense, it is relevant to their ability to complete the task.
+Further, there is some evidence that location information may receive priority during encoding [@logan_what_1998; @mayr_spatial_1996].
 Similar arguments could be made about other context features that are inherent to processing the target stimulus, like font-type [@bugg_multiple_2008] and color [@vietze_context_2009].
 
-Second, we are aware of only one study that has looked at task-relevance within the CSPC literature.
+We are aware of only one study that has looked at task-relevance within the CSPC literature.
 Crump, Vaquero, & Milliken [-@crump_context-specific_2008] used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe.
@@
 The first experiment failed to find evidence for context-specificity, whereas the second did.
-Although not testing task-relevance directly, @canadas_social_2013] found similar effects.
+Although not testing task-relevance directly, @canadas_social_2013 found similar effects.
 In this study they used images of male and female faces as context cues in a flanker task.
@@
 
-Prior work suggests that the task-relevance of contextual information is important for establishing new associations between context cues and attentional priorities.
-Simply put, CSPC effects emerge when context cues are somehow made relevant to the task, but do not when made irrelevant [@canadas_social_2013; @crump_context-specific_2006; @crump_context-specific_2008].
-However, it still remains unclear how task-relevance may or may not inform the use of previously learned associations.
-In the current study, we examined whether manipulating task-relevance would cause participants to ignore a previously learned association and adopt a new context-specific control strategy.
+Prior work suggests that the task-relevance of contextual information could be important for establishing new associations between context cues and attentional priorities.
+Simply put, CSPC effects tend to emerge when context cues are somehow made relevant to the task, but do not when made irrelevant [@canadas_social_2013; @crump_context-specific_2006; @crump_context-specific_2008].
+However, what determines the learning and expression of context-attention associations remains unclear.
+In the current study, we examined whether manipulating task-relevance would allow participants to ignore a previously learned association and adopt a new context-specific control strategy.
 
@@
 #source: data-analysis/analysis.R
-figure2B
+#figure2B
 ```
@@
 Figure A shows a summary of the data containing all trials, whereas Figure B shows a summary of the data restricted to the 24 trials immediately before and 24 trials immediately after the transition.
-In both cases, the interaction was non-significant ($p > .05$) and Bayesian analyses showed moderate evidence in favor of the null hypothesis ($\mathrm{BF}_{\textrm{01}} > 3$).
+In both cases, the interaction was non-significant ($p > .05$) and Bayesian analyses resulted in moderate evidence in favor of the null hypothesis ($\mathrm{BF}_{\textrm{01}} > 3$).
 
@@
 
-We conducted an additional, more severe test, of the list-shift hypothesis.
+We also conduncted an additional, more severe, test of the list-shift hypothesis.
 Given that the asymmetry is interpreted as resulting from a carry-over of learned attentional modulation across phases, we might expect that any asymmetry would be exaggerated near the point of transition.

### 2019-07-19 manuscript_pretty.tex
working - incomplete

@@
 As a result, automatic memory-based retrieval allows attentional priorities to be rapidly adjusted in a context-appropriate fashion.
-How associations between attentional priorities and context cues are formed and used still remains unclear however.
-The current study addresses two related issues.
-
-First, how is attentional control resolved when multiple contextual features could be used as cues? Second, it remains unclear how
-
-Historically, theories of automaticity and attentional control have emphasized the role of practice and likened the learning process to the automaticity of skill-learning ().
-
-However, the obligatory nature of memory-based attentional control remains unclear, in particular in situations when multiple contextual features could be used as cues for retrieval.
-
-For example, real-world environments offer a plethora of context cues.
-Consider writing an article in a coffee shop.
-The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), and associated attentional priorities.
+How the learning and reinstatement process works however, remains largely unclear.
+
+The current study addresses two related issues: First, how is attentional control resolved when multiple contextual features could be used as cues?
+And second, what determines the expression of previously learned attentional associations?
+
+Real-world environments can offer a plethora of context cues.
+For instance, consider someone writing in a coffee shop.
+The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop) associated with many experiences that afford different attentional priorities.
 Although a laptop might cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
 Given that all of these cues are available to set attentional priorities, what determines which associative relationships will be used to guide attention?
-On the one hand, context-based retrieval of attentional priorities might be completely obligatory and a writer's attention would be at the mercy of the environment.
-On the other hand, there is some evidence that contextual cuing of attention is not entirely obligatory and can be constrained by task goals, allowing the laptop to take priority as a contextual cue over other contextual cues that are irrelevant to the task at hand.
-
-Prior work shows that task-relevance is necessary for establishing and using context-attention associations.
-First, the most commonly used context cue is location (Brosowsky \& Crump, 2016; Corballis \& Gratton, 2003; Crump, 2016; Crump et al., 2006; Crump, Vaquero, \& Milliken, 2008; Weidler \& Bugg, 2016; Weidler et al., 2018).
-Although in some sense, the location is irrelevant for identifying the color of a word, it seems disingenuous to consider it completely task-irrelevant.
+On the one hand, context-based retrieval of attentional priorities might be completely obligatory: the mere presence of learned cues trigger attention in a ballistic manner (e.g., Schneider \& Shiffrin, 1977; Shiffrin \& Schneider, 1977).
+A writer's attention in this case would be at the mercy of the environment and the most strongly associated cues.
+On the other hand, contextual cuing of attention may not be entirely obligatory.
+Our current task-goals, for instance, might constrain the expression of previously learned associations, allowing, for instance, the laptop to take priority as a contextual cue over other cues that are irrelevant to the task at hand.
+
+Historically, perspectives of automaticity and attentional control have emphasized the role of practice and likened the learning process to the development of automaticity in skill-learning (Logan, 1988, 1992; Schneider \& Shiffrin, 1977; Shiffrin \& Schneider, 1977).
+Under this view, forming an association requires many repeated experiences pairing a cue with a set of attentional priorities.
+Once formed however, they become habitual or hard-wired and the mere presence of the cue is suffificient to automatically adjust attention.
+Learned associations are therefore ballistic, difficult to suppress, and difficult to unlearn (e.g., Schneider \& Shiffrin, 1977; Posner \& Snyder, 1975a, 1975b; Shiffrin \& Schneider, 1977; Treisman, 1960, 1964, 1969).
+This view is reflected in moodern work on contextual cuing where it is assumed that learned associations require practice (e.g., Lehle \& Hübner, 2008; Crump, 2016), form without awareness or intention, triggered automatically by the mere presence of the cue (Crump et al., 2006; Crump \& Logan, 2010; Crump, Vaquero, \& Milliken, 2008; King et al., 2012; Reuss, Desender, Kiesel, \& Kunde, 2014; cf.
+Brosowsky \& Crump, 2016).
+
+Memory-based perspectives however, take a more nuanced view (Abrahamse et al., 2016; Brosowsky \& Crump, 2018; Crump, 2016; Egner, 2014; Norman, 1969, 1976).
+Here, practice is only important to the extent that it improves memory retrieval.
+If a few prior experiences are distinct, and easily retrievable, it could support the reinstatement of a learned attentional association despite very little practice (e.g., Brosowsky \& Crump, 2018).
+Conversely, if prior experiences are difficult to retrieve, then learned associations may not be expressed, even after much practice.
+This view offers one potential path for flexibility in the expression of learned associations.
+Learning an association is the process of encoding into memory experiences where attentional priorities and cues co-occur.
+Memory retrieval is a similarity-based, cue-driven process (Hintzman, 1984, 1986, 1988; Jacoby, 1978).
+Presumably, the features of our immediate environment automatically cue memory and reinstate the retrieved attentional priorites (Logan, 1988, 1992).
+However, to the extent that you could manipulate memory retrieval, you should be able manipulate the expression of learned associations.
+
+Here, we examine whether task-relevance influences the retrieval of previously used attentional priorities.
+We hypothesized that the cue-driven, memory-retrieval process might be constrained to the features of our environment that are relevant to our on-going task and goals.
+If this is the case, then a previously learned association should be easily ignored if that feature was made irrelevant to the task because that feature would no longer contribute to memory-retrieval.
+Furthermore, it would suggest that the mere presence of a cue is not sufficient for automatically directing attention, but instead requires some task-integration.
+
+Recent work lends some credence to the possibility that task-relevance is necessary for establishing and using context-attention associations.
+The most commonly used context cue is location (Brosowsky \& Crump, 2016; Corballis \& Gratton, 2003; Crump, 2016; Crump et al., 2006, 2008; Weidler \& Bugg, 2016; Weidler et al., 2018), often claimed to be irrelevant to the on-going conflict task.
+Although in some sense, the location is irrelevant for identifying the color of a word in a Stroop task, it seems disingenuous to consider it completely task-irrelevant.
 In order to identify the target, the participant must first identify and orient to its location on the screen.
-In this is sense, it is relevant to their ability to complete the task and furthermore, location information may receive priority during encoding (Logan, 1998; Mayr, 1996).
+In this is sense, it is relevant to their ability to complete the task.
+Further, there is some evidence that location information may receive priority during encoding (Logan, 1998; Mayr, 1996).
 Similar arguments could be made about other context features that are inherent to processing the target stimulus, like font-type (Bugg, Jacoby, \& Toth, 2008) and color (Vietze \& Wendt, 2009).
 
-Second, we are aware of only one study that has looked at task-relevance within the CSPC literature.
+We are aware of only one study that has looked at task-relevance within the CSPC literature.
 Crump, Vaquero, \& Milliken (2008) used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe.
@@
 The first experiment failed to find evidence for context-specificity, whereas the second did.
-Although not testing task-relevance directly, Cañadas, Rodríguez-Bailón, Milliken, and Lupiáñez (2013){]} found similar effects.
+Although not testing task-relevance directly, Cañadas, Rodríguez-Bailón, Milliken, and Lupiáñez (2013) found similar effects.
 In this study they used images of male and female faces as context cues in a flanker task.
@@
 
-Prior work suggests that the task-relevance of contextual information is important for establishing new associations between context cues and attentional priorities.
-Simply put, CSPC effects emerge when context cues are somehow made relevant to the task, but do not when made irrelevant (Cañadas et al., 2013; Crump et al., 2006, 2008).
-However, it still remains unclear how task-relevance may or may not inform the use of previously learned associations.
-In the current study, we examined whether manipulating task-relevance would cause participants to ignore a previously learned association and adopt a new context-specific control strategy.
+Prior work suggests that the task-relevance of contextual information could be important for establishing new associations between context cues and attentional priorities.
+Simply put, CSPC effects tend to emerge when context cues are somehow made relevant to the task, but do not when made irrelevant (Cañadas et al., 2013; Crump et al., 2006, 2008).
+However, it is still unclear whether there is any flexibility in the expression of learned assocations, and more importantly, what determines that flexibility.
+In the current study, we examined whether manipulating task-relevance would allow participants to ignore a previously learned association and adopt a new context-specific control strategy.
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_pretty_files/figure-latex/figure2b-1.pdf}
-\caption{\label{fig:figure2b}Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent) and phase order (100\% to 0\% PC versus 0\% to 100\% PC).
-Figure A shows a summary of the data containing all trials, whereas Figure B shows a summary of the data restricted to the 24 trials immediately before and 24 trials immediately after the transition.
-In both cases, the analyses resulted in no significant interaction (\(p > .05\)) and moderate evidence in favor of the null hypothesis (\(\mathrm{BF}_{\textrm{01}} > 3\)).}
-\end{figure}
-
 Previous work has shown that shifting between list-wide proportion congruent phases produced asymmetrical effects.
@@
 However, the two-way interaction between task-relevant context and phase order was non-significant, \(F(1, 129) = 2.56\), \(\mathit{MSE} = 3,255.69\), \(p = .112\), \(\hat{\eta}^2_p = .019\), 90\% CI \([0\), \(0.07]\), with moderate evidence in favor of the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 4.92\) \([\pm 2.95\%]\).
-Therefor, we did not find statistical support for a list-shift asymmetry.
-Additionally, the (non-significant) asymmetry we do see in this sample is in the opposite direction than would be predicted given the prior research (e.g., Abrahamse et al., 2013).
-
-Additionally, we conducted a more severe test of the list-shift hypothesis.
+Therefore, we did not find statistical support for a list-shift asymmetry.
+Additionally, the (non-significant) asymmetrical effects we do see in this sample is in the opposite direction than would be predicted given the prior research (e.g., Abrahamse et al., 2013).
+
+We also conduncted an additional, more severe, test of the list-shift hypothesis.
 Given that the asymmetry is interpreted as resulting from a carry-over of learned attentional modulation across phases, we might expect that any asymmetry would be exaggerated near the point of transition.
@@
 
+\leavevmode\hypertarget{ref-crump_contextual_2010}{}%
+Crump, M.
+J., \& Logan, G.
+D.
+(2010).
+Contextual control over task-set retrieval.
+\emph{Attention, Perception, \& Psychophysics}, \emph{72}, 2047--2053.
+Retrieved from \url{http://link.springer.com/article/10.3758/BF03196681}
+
 \leavevmode\hypertarget{ref-crump_context-specific_2008}{}%
@@
 
+\leavevmode\hypertarget{ref-hintzman_minerva_1984}{}%
+Hintzman, D.
+L.
+(1984).
+MINERVA 2: A simulation model of human memory.
+\emph{Behavior Research Methods, Instruments, \& Computers}, \emph{16}(2), 96--101.
+Retrieved from \url{http://link.springer.com/article/10.3758/BF03202365}
+
+\leavevmode\hypertarget{ref-hintzman_schema_1986}{}%
+Hintzman, D. L. (1986). Schema abstraction in a multiple-trace memory model. \emph{Psychological Review}, \emph{93}, 411--428.
+
+\leavevmode\hypertarget{ref-hintzman_judgments_1988}{}%
+Hintzman, D. L. (1988). Judgments of frequency and recognition memory in a multiple-trace memory model. \emph{Psychological Review}, \emph{95}(4), 528.
+
 \leavevmode\hypertarget{ref-hutcheon_limits_2017}{}%
@@
 
+\leavevmode\hypertarget{ref-jacoby_interpreting_1978}{}%
+Jacoby, L. L. (1978). On interpreting the effects of repetition: Solving a problem versus remembering a solution. \emph{Journal of Verbal Learning and Verbal Behavior}, \emph{17}(6), 649--667.
+
 \leavevmode\hypertarget{ref-jeffreys1961theory}{}%
@@
 
+\leavevmode\hypertarget{ref-lehle_fly_2008}{}%
+Lehle, C., \& Hübner, R.
+(2008).
+On-the-fly adaptation of selectivity in the flanker task.
+\emph{Psychonomic Bulletin \& Review}, \emph{15}(4), 814--818.
+Retrieved from \url{http://link.springer.com/article/10.3758/PBR.15.4.814}
+
 \leavevmode\hypertarget{ref-logan_attention_1980}{}%
 Logan, G. D. (1980). Attention and automaticity in Stroop and priming tasks: Theory and data. \emph{Cognitive Psychology}, \emph{12}, 523--553.
+
+\leavevmode\hypertarget{ref-logan_toward_1988}{}%
+Logan, G. D. (1988). Toward an instance theory of automatization. \emph{Psychological Review}, \emph{95}, 492--527. doi:\href{https://doi.org/10.1037/0033-295X.95.4.492}{10.1037/0033-295X.95.4.492}
+
+\leavevmode\hypertarget{ref-logan_attention_1992}{}%
+Logan, G. D. (1992). Attention and preattention in theories of automaticity. \emph{The American Journal of Psychology}, 317--339.
 
@@
 
+\leavevmode\hypertarget{ref-norman_memory_1969}{}%
+Norman, D. A. (1969). Memory while shadowing. \emph{Quarterly Journal of Experimental Psychology}, \emph{21}(1), 85--93.
+
+\leavevmode\hypertarget{ref-norman_memory_1976}{}%
+Norman, D. A. (1976). Memory and attention: An introduction to human information processing.
+
+\leavevmode\hypertarget{ref-posner_attention_1975}{}%
+Posner, M.
+I., \& Snyder, C.
+R.
+R.
+(1975a).
+Attention and cognitive control.
+In R.
+L.
+Solso (Ed.), \emph{Information processing and cognition: The Loyola symposium} (pp.
+153--175).
+Hillsdale, NJ: Erlbaum.
+
+\leavevmode\hypertarget{ref-posner_facilitation_1975}{}%
+Posner, M.
+I., \& Snyder, C.
+R.
+R.
+(1975b).
+Facilitation and inhibition in the processing of signals.
+In P.
+M.
+A.
+Rabbit \& S.
+Dornic (Eds.), \emph{Attention and performance V} (pp.
+669--682).
+New York, NY: Academic Press.
+
 \leavevmode\hypertarget{ref-r_software_2019}{}%
 R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-reuss_unconscious_2014}{}%
+Reuss, H., Desender, K., Kiesel, A., \& Kunde, W.
+(2014).
+Unconscious conflicts in unconscious contexts: The role of awareness and timing in flexible conflict adaptation.
+\emph{Journal of Experimental Psychology: General}, \emph{143}, 1701--1718.
+doi:\href{https://doi.org/10.1037/a0036437}{10.1037/a0036437}
 
@@
 
+\leavevmode\hypertarget{ref-schneider_controlled_1977}{}%
+Schneider, W., \& Shiffrin, R. M. (1977). Controlled and automatic human information processing: I. Detection, search, and attention. \emph{Psychological Review}, \emph{84}(1), 1.
+
+\leavevmode\hypertarget{ref-shiffrin_controlled_1977}{}%
+Shiffrin, R.
+M., \& Schneider, W.
+(1977).
+Controlled and automatic human information processing: II.
+Perceptual learning, automatic attending and a general theory.
+\emph{Psychological Review}, \emph{84}, 127--190.
+doi:\href{https://doi.org/10.1037/0033-295X.84.2.127}{10.1037/0033-295X.84.2.127}
+
 \leavevmode\hypertarget{ref-r_afex_2019}{}%
@@
 
+\leavevmode\hypertarget{ref-treisman_contextual_1960}{}%
+Treisman, A. M. (1960). Contextual cues in selective listening. \emph{Quarterly Journal of Experimental Psychology}, \emph{12}(4), 242--248.
+
+\leavevmode\hypertarget{ref-treisman_selective_1964}{}%
+Treisman, A. M. (1964). Selective attention in man. \emph{British Medical Bulletin}.
+
+\leavevmode\hypertarget{ref-treisman_strategies_1969}{}%
+Treisman, A. M. (1969). Strategies and models of selective attention. \emph{Psychological Review}, \emph{76}(3), 282.
+
 \leavevmode\hypertarget{ref-van_selst_solution_1994}{}%

### 2019-07-23 manuscript_pretty.Rmd
revision in-progress

@@
 For instance, consider someone writing in a coffee shop.
-The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop) associated with many experiences that afford different attentional priorities.
+The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which we have different experiences with and afford different learned associations.
 Although a laptop might cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
 Given that all of these cues are available to set attentional priorities, what determines which associative relationships will be used to guide attention?
-On the one hand, context-based retrieval of attentional priorities might be completely obligatory: the mere presence of learned cues trigger attention in a ballistic manner [e.g., @schneider_controlled_1977; @shiffrin_controlled_1977].
-A writer's attention in this case would be at the mercy of the environment and the most strongly associated cues.
+On the one hand, context-based retrieval of attentional priorities might be completely obligatory: the mere presence of learned cues might trigger attention in a ballistic manner [e.g., @schneider_controlled_1977; @shiffrin_controlled_1977].
+A writer's attention in this case would be at the mercy of the environment.
 On the other hand, contextual cuing of attention may not be entirely obligatory.
@@
 Under this view, forming an association requires many repeated experiences pairing a cue with a set of attentional priorities.
-Once formed however, they become habitual or hard-wired and the mere presence of the cue is suffificient to automatically adjust attention.
+Once formed however, it becomes habitual or hard-wired and the mere presence of the cue is suffificient to automatically adjust attention.
 Learned associations are therefore ballistic, difficult to suppress, and difficult to unlearn [e.g., @schneider_controlled_1977; @shiffrin_controlled_1977; @posner_attention_1975; @posner_facilitation_1975; @treisman_contextual_1960; @treisman_selective_1964; @treisman_strategies_1969].
-This view is reflected in moodern work on contextual cuing where it is assumed that learned associations require practice [e.g., @lehle_fly_2008; @crump_learning_2016], form without awareness or intention, triggered automatically by the mere presence of the cue [@crump_context-specific_2006; @crump_contextual_2010; @crump_context-specific_2008; @king_priming_2012; @reuss_unconscious_2014; though, see @brosowsky_context-specific_2016].
+This view is reflected in modern work on contextual cuing where it is assumed that learned associations require practice [e.g., @lehle_fly_2008; @crump_learning_2016], form without awareness or intention, and are triggered automatically by the mere presence of the cue [@crump_context-specific_2006; @crump_contextual_2010; @crump_context-specific_2008; @king_priming_2012; @reuss_unconscious_2014; though, see @brosowsky_context-specific_2016].
 

### 2019-07-23 1st-Submission-01-15-2019/task-relevance-cspc-a51ff3ddedf006918d70484913a01c16b99d6d42/data-analysis/analysis.R

@@ -1,0 +1,207 @@
+
+library(dplyr)
+library(tidyr)
+library(afex)
+library(ggplot2)
+library(cowplot)
+#As of 2018/12/07 apa_print() requires development version of Papaja
+#devtools::install_github("crsh/papaja")
+library(papaja)
+
+
+folderName <- function(){
+  wd<-getwd()
+  wd<-strsplit(wd,"/")
+  wd<-wd[[1]][length(wd[[1]])]
+  
+  return(wd)
+}
+
+
+vjoutNR <- function(x,n) {
+  xm <- mean(x)
+  xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
+             25, 30, 35, 50, 80)
+  stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
+            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
+            2.45, 2.48, 2.5)
+  stdindex <- length(xsize[xsize <= length(x)])
+  removed <- x[x < xm+sd(x)*stds[stdindex]]
+  removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
+  proportionRemoved <- length(removed)/length(x)
+  finaldata<-c(mean(removed),1-proportionRemoved)
+  return(finaldata[[n]])
+}
+
+
+
+load("data-analysis/raw_data.Rda")
+
+
+# Find subs with < 75% accuracy
+low_acc <- raw_data %>%
+  group_by(Subject,Condition,Task_Relevant_Context,Frequency,Congruency) %>%
+  summarise(meanAccuracy = mean(ACC)) %>%
+  filter(meanAccuracy < .75) %>%
+  .$Subject
+
+N_subjects_removed<-length(unique(low_acc))
+
+## summarise by subject
+RT.DF <- raw_data %>%
+  filter(
+    RT < 3000,
+    RT > 0,
+    ACC == TRUE,
+    Subject%in%low_acc == FALSE
+  ) %>%
+  group_by(Condition,Subject,Order,Phase,Block,Frequency,Task_Relevant_Context,Congruency)%>%
+  summarise(vjoutRT = vjoutNR(RT,1))
+
+## Find percentage of trials removed 
+percent_removed <- raw_data %>%
+  filter(
+    RT < 3000,
+    RT > 0,
+    ACC == TRUE,
[…]

### 2019-07-23 1st-Submission-01-15-2019/task-relevance-cspc-a51ff3ddedf006918d70484913a01c16b99d6d42/data-analysis/table1.R

@@ -1,0 +1,214 @@
+library(dplyr)
+library(tidyr)
+library(afex)
+library(ggplot2)
+library(cowplot)
+#As of 2018/12/07 apa_print() requires development version of Papaja
+#devtools::install_github("crsh/papaja")
+library(papaja)
+
+
+folderName <- function(){
+  wd<-getwd()
+  wd<-strsplit(wd,"/")
+  wd<-wd[[1]][length(wd[[1]])]
+  
+  return(wd)
+}
+
+
+vjoutNR <- function(x,n) {
+  xm <- mean(x)
+  xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
+             25, 30, 35, 50, 80)
+  stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
+            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
+            2.45, 2.48, 2.5)
+  stdindex <- length(xsize[xsize <= length(x)])
+  removed <- x[x < xm+sd(x)*stds[stdindex]]
+  removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
+  proportionRemoved <- length(removed)/length(x)
+  finaldata<-c(mean(removed),1-proportionRemoved)
+  return(finaldata[[n]])
+}
+
+
+## manuscript.Rmd is called from parent
+load("data-analysis/raw_data.Rda")
+
+
+
+
+# Find subs with < 75% accuracy
+low_acc <- raw_data %>%
+  group_by(Subject,Condition,Task_Relevant_Context,Frequency,Congruency) %>%
+  summarise(meanAccuracy = mean(ACC)) %>%
+  filter(meanAccuracy < .75) %>%
+  .$Subject
+
+########## Create table
+
+
+## summarise by subject
+RT.DF <- raw_data %>%
+  filter(
+    RT < 3000,
+    RT > 0,
+    ACC == TRUE,
+    Subject%in%low_acc == FALSE
+  ) %>%
+  group_by(Condition,Subject,Frequency,Order,Phase,Block,Frequency,Task_Relevant_Context,Congruency)%>%
+  summarise(vjoutRT = vjoutNR(RT,1)) %>%
+  group_by(Condition,Subject,Frequency,Task_Relevant_Context,Congruency) %>%
[…]

### 2019-07-23 1st-Submission-01-15-2019/task-relevance-cspc-a51ff3ddedf006918d70484913a01c16b99d6d42/materials/E1A-Objects/Required.js

@@ -1,0 +1,154 @@
+//** landingExit.html **//
+
+//* Required functions *//
+
+/*Modernizr: check for flexbox */
+function checkFlex(){
+  if (Modernizr.flexbox) {
+    $(".flexPresent").show();
+    $(".flexAbsent").hide();
+  } else {
+    $(".flexPresent").hide();
+    $(".flexAbsent").show();
+  }
+}
+
+
+//pulls Assignment info//
+function gup(name) {
+    var regexS = "[\\?&]" + name + "=([^&#]*)";
+    var regex = new RegExp(regexS);
+    var tmpURL = window.location.href;
+    var results = regex.exec(tmpURL);
+    if (results === null)
+        return "";
+    else
+        return results[1];
+}
+
+
+
+
+//opens full-screen window of "url"//
+function basicPopup(url) {
+    popupWindow = window.open(url, 'popUpWindow', 'height=' + screen.height + ',width=' + screen.width + ',\
+		left=100,top=100,resizable=yes,scrollbars=yes,toolbar=no,\
+		menubar=no,location=no,directories=no,status=yes');
+}
+
+
+
+//detects which browser the user is using and stores in var Browserinfo//
+var BrowserDetect = {
+    init: function() {
+        this.browser = this.searchString(this.dataBrowser) || "An unknown browser";
+        this.version = this.searchVersion(navigator.userAgent) ||
+            this.searchVersion(navigator.appVersion) ||
+            "an unknown version";
+        this.OS = this.searchString(this.dataOS) || "an unknown OS";
+    },
+    searchString: function(data) {
+        for (var i = 0; i < data.length; i++) {
+            var dataString = data[i].string;
+            var dataProp = data[i].prop;
+            this.versionSearchString = data[i].versionSearch || data[i].identity;
+            if (dataString) {
+                if (dataString.indexOf(data[i].subString) != -1)
+                    return data[i].identity;
+            } else if (dataProp)
+                return data[i].identity;
+        }
+    },
+    searchVersion: function(dataString) {
+        var index = dataString.indexOf(this.versionSearchString);
+        if (index == -1) return;
+        return parseFloat(dataString.substring(index + this.versionSearchString.length + 1));
+    },
+    dataBrowser: [{
+        string: navigator.userAgent,
+        subString: "Chrome",
+        identity: "Chrome"
+    }, {
[…]

### 2019-08-07 manuscript_pretty.Rmd
revision in progress

@@
 Here, practice is only important to the extent that it improves memory retrieval.
-If a few prior experiences are distinct, and easily retrievable, it could support the reinstatement of a learned attentional association despite very little practice [e.g., @brosowsky_memory-guided_2018].
-Conversely, if prior experiences are difficult to retrieve, then learned associations may not be expressed, even after much practice.
-This view offers one potential path for flexibility in the expression of learned associations.
-Learning an association is the process of encoding into memory experiences where attentional priorities and cues co-occur.
+Learning an association is the process of encoding experiences, where attentional priorities and cues co-occur, into memory.
 Memory retrieval is a similarity-based, cue-driven process [e.g., @jacoby_interpreting_1978; @hintzman_minerva_1984; @hintzman_schema_1986; @hintzman_judgments_1988].
 Presumably, the features of our immediate environment automatically cue memory and reinstate the retrieved attentional priorites [@logan_toward_1988; @logan_attention_1992].
-However, to the extent that you could manipulate memory retrieval, you should be able manipulate the expression of learned associations.
+If a few prior experiences are easily retrievable--memories are distinct or very similar to the retrieval cue--it could support the reinstatement of a learned attentional association despite very little practice [e.g., @brosowsky_memory-guided_2018].
+Conversely, if prior experiences are difficult to retrieve--memories are in or low in similarity to the retrieval cue--then learned associations may not be expressed, even after much practice.
+To the extent that you could manipulate memory retrieval, you should be able manipulate the expression of learned associations.
 
@@
 Specifically, @abrahamse_attention_2013 found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects.
-The authors suggested that the assymetry is caused by a learned attentional modulation in the mostly-incongruent block carrying over into the mostly-congruent block.
+The authors posited a learned attentional modulation in the mostly-incongruent block had carried over into the mostly-congruent block.
 In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from the use of one context cue to another.

### 2019-08-07 data-analysis/analysis_E1.R

@@ -12,62 +12,13 @@ library(apaTables)
 
 set.seed(1983)
 
-folderName <- function(){
-  wd<-getwd()
-  wd<-strsplit(wd,"/")
-  wd<-wd[[1]][length(wd[[1]])]
-  
-  return(wd)
-}
-
-
-vjoutNR <- function(x,n) {
-  xm <- mean(x)
-  xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
-             25, 30, 35, 50, 80)
-  stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
-            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
-            2.45, 2.48, 2.5)
-  stdindex <- length(xsize[xsize <= length(x)])
-  removed <- x[x < xm+sd(x)*stds[stdindex]]
-  removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
-  proportionRemoved <- length(removed)/length(x)
-  finaldata<-c(mean(removed),1-proportionRemoved)
-  return(finaldata[[n]])
-}
-
-
-print_eta_CI <- function(Fval, conf = .90, df1, df2){
-  limits <- apaTables::get.ci.partial.eta.squared(F.value=Fval, df1=df1, df2=df2, conf.level=conf)
-  return(paste0(", 90\\% CI $[",round(limits$LL, 2),"$, $",round(limits$UL, 2),"]$"))
-}
-
-print_apa_ci <- function(aov_table){
-  pap <- apa_print(aov_table, es = "pes")$full_result
-  
-  for(i in 1:length(pap)){
-    pap[i] <- paste0(pap[i], print_eta_CI(Fval = aov_table$anova_table$`F`[i], df1 = aov_table$anova_table$`num Df`[i], df2 = aov_table$anova_table$`den Df`[i]))
-    pap[i] <- gsub("p = .000", "p < .001", pap[i])
-    pap[i] <- gsub(") = 0.00", ") < 0.01", pap[i])
-  }
-  return(pap)
-}
-
-print_bf <- function(bf){
-  result <- list()
-  for (i in 1:length(bf)){
-    if(extractBF(bf[i])$bf < 1){
[…]

### 2019-08-07 data-analysis/analysis_E2.R

@@ -8,36 +8,14 @@ library(cowplot)
 #devtools::install_github("crsh/papaja")
 library(papaja)
 
+# Load functions
+source("data-analysis/print_apa_ci.R")
+source("data-analysis/print_bf.R")
+source("data-analysis/outlier_removal.R")
 
-folderName <- function(){
-  wd<-getwd()
-  wd<-strsplit(wd,"/")
-  wd<-wd[[1]][length(wd[[1]])]
-  
-  return(wd)
-}
-
-
-vjoutNR <- function(x,n) {
-  xm <- mean(x)
-  xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
-             25, 30, 35, 50, 80)
-  stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
-            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
-            2.45, 2.48, 2.5)
-  stdindex <- length(xsize[xsize <= length(x)])
-  removed <- x[x < xm+sd(x)*stds[stdindex]]
-  removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
-  proportionRemoved <- length(removed)/length(x)
-  finaldata<-c(mean(removed),1-proportionRemoved)
-  return(finaldata[[n]])
-}
-
-
-
+# Load data
 load("data-analysis/raw_data_E2.Rda")
 load("data-analysis/demographics_E2.Rda")
-
 
 
 # Find subs with < 75% accuracy
@@ -76,36 +54,46 @@ percent_removed_E2 <- raw_data_E2 %>%
 
 ## Analyze RTs 
 RT.Analysis <- RT.DF %>%
+  ungroup() %>%
+  mutate(Subject = factor(Subject),
+         PC = factor(PC)) %>%
   group_by(Subject,PC,Congruency) %>%
-  summarise(meanRT = mean(vjoutRT))
+  summarise(meanRT = mean(vjoutRT)) %>%
+  spread(Congruency, meanRT) %>%
+  ungroup()%>%
+  mutate(CE = inc - con)
 
-RT_ANOVA_E2 <- aov_ez("Subject", "meanRT", RT.Analysis, within = c("PC","Congruency"), anova_table = list(correction = "none", es = "none"))
[…]

### 2019-08-07 data-analysis/analysis_E3.R

@@ -8,42 +8,16 @@ library(cowplot)
 #devtools::install_github("crsh/papaja")
 library(papaja)
 
+# Load functions
+source("data-analysis/print_apa_ci.R")
+source("data-analysis/print_bf.R")
+source("data-analysis/outlier_removal.R")
 
-folderName <- function(){
-  wd<-getwd()
-  wd<-strsplit(wd,"/")
-  wd<-wd[[1]][length(wd[[1]])]
-  
-  return(wd)
-}
-
-
-vjoutNR <- function(x,n) {
-  xm <- mean(x)
-  xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
-             25, 30, 35, 50, 80)
-  stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
-            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
-            2.45, 2.48, 2.5)
-  stdindex <- length(xsize[xsize <= length(x)])
-  removed <- x[x < xm+sd(x)*stds[stdindex]]
-  removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
-  proportionRemoved <- length(removed)/length(x)
-  finaldata<-c(mean(removed),1-proportionRemoved)
-  return(finaldata[[n]])
-}
-
-
-
+# Load data
 load("data-analysis/raw_data_E3.Rda")
 # load("data-analysis/demographics_E3.Rda")
 # demographics_E3$Subject <- demographics_E3$subnum
-# 
-# raw_data_E3 <- inner_join(raw_data_E3, demographics_E3, by = "Subject")
-# raw_data_E3 <- raw_data_E3 %>%
-#   mutate(task_feedback = as.numeric(as.character(task_feedback))) %>%
-#   filter(!is.na(task_feedback),
-#                 task_feedback > 3)
+
 
 # Find subs with < 75% accuracy
 low_acc <- raw_data_E3 %>%
@@ -81,48 +55,60 @@ percent_removed_E3 <- raw_data_E3 %>%
 
 ## Analyze RTs for frequency unbiased items
 RT.Analysis <- RT.DF %>%
-  filter(
-    Frequency == "unbiased"
-  ) %>%
-  group_by(Condition,Subject,Task_Relevant_Context,Congruency) %>%
[…]

### 2019-08-07 data-analysis/outlier_removal.R

@@ -1,0 +1,24 @@
+#' Van Selst and Jolicoer (1994) outlier removal (non-recursive)
+#'
+#' @param x vector of reaction times
+#' @param n calculation to be returned (1 = new mean, 2 = proportion of trials new.x)
+#'
+#' @return 
+#' @export
+#'
+#' @examples
+#' 
+vjoutNR <- function(x,n) {
+    xm <- mean(x)
+    xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
+               25, 30, 35, 50, 80)
+    stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
+              2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
+              2.45, 2.48, 2.5)
+    stdindex <- length(xsize[xsize <= length(x)])
+    new.x <- x[x < xm+sd(x)*stds[stdindex]]
+    new.x <- new.x[new.x > xm - (sd(x)*stds[stdindex])]
+    proportion <- length(new.x)/length(x)
+    finaldata<-c(mean(new.x),1-proportion)
+    return(finaldata[[n]])
+}

### 2019-08-07 data-analysis/print_apa_ci.R

@@ -1,0 +1,23 @@
+#'Print ANOVA output with effect size confidence intervals
+#'
+#' @param aov_table 
+#'
+#' @return
+#' @export
+#'
+#' @examples
+print_apa_ci <- function(aov_table){
+    print_eta_ci <- function(Fval, conf = .90, df1, df2){
+        limits <- apaTables::get.ci.partial.eta.squared(F.value=Fval, df1=df1, df2=df2, conf.level=conf)
+        return(paste0(", 90\\% CI $[",round(limits$LL, 2),"$, $",round(limits$UL, 2),"]$"))
+    }
+    
+    pap <- apa_print(aov_table, es = "pes", correction = "none")$full_result
+    
+    for(i in 1:length(pap)){
+        pap[i] <- paste0(pap[i], print_eta_ci(Fval = aov_table$anova_table$`F`[i], df1 = aov_table$anova_table$`num Df`[i], df2 = aov_table$anova_table$`den Df`[i]))
+        pap[i] <- gsub("p = .000", "p < .001", pap[i])
+        pap[i] <- gsub(") = 0.00", ") < 0.01", pap[i])
+    }
+    return(pap)
+}

### 2019-08-07 data-analysis/print_bf.R

@@ -1,0 +1,21 @@
+#' Print Bayes Factor results with error percentage
+#'
+#' @param bf 
+#'
+#' @return
+#' @export
+#'
+#' @examples
+print_bf <- function(bf){
+    result <- list()
+    for (i in 1:length(bf)){
+        if(extractBF(bf[i])$bf < 1){
+            result[i] <- paste0("$\\mathrm{BF}_{\\textrm{01}} = ", round(extractBF(1/bf[i])$bf, digits = 2),"$ $[\\pm ", round(extractBF(bf[i])$error*100,digits=2), "\\%]$")
+        } else {
+            result[i] <- paste0("$\\mathrm{BF}_{\\textrm{10}} = ", round(extractBF(bf[i])$bf, digits = 2),"$ $[\\pm ", round(extractBF(bf[i])$error*100,digits=2), "\\%]$")
+            
+        }
+    }
+    
+    return(result)
+}

### 2019-08-07 data-analysis/table1.R

@@ -64,7 +64,7 @@ RT.DF <- raw_data %>%
   group_by(Condition,Frequency,Task_Relevant_Context,Congruency) %>%
   summarise(N = n_distinct(Subject),
             RT = mean(meanRT),
-            std = sd(meanRT),
+            sd = sd(meanRT),
             se = std/sqrt(N))
 
 RT.DF$PC <- NA

### 2019-09-16 manuscript_pretty.Rmd
revision in progress

@@
 Real-world environments can offer a plethora of context cues.
-For instance, consider someone writing in a coffee shop.
+Consider someone writing in a coffee shop.
 The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which we have different experiences with and afford different learned associations.
@@
 A writer's attention in this case would be at the mercy of the environment.
-On the other hand, contextual cuing of attention may not be entirely obligatory.
-Our current task-goals, for instance, might constrain the expression of previously learned associations, allowing, for instance, the laptop to take priority as a contextual cue over other cues that are irrelevant to the task at hand.
+On the other hand, our current task-goals might constrain the expression of previously learned associations.
+For instance, the writer's current goals may allow the laptop to take priority over other environmental cues that are irrelevant to the task at hand.
 
@@
 Under this view, forming an association requires many repeated experiences pairing a cue with a set of attentional priorities.
-Once formed however, it becomes habitual or hard-wired and the mere presence of the cue is suffificient to automatically adjust attention.
+Once formed however, it becomes habitual or hard-wired and the mere presence of the cue is sufficient to automatically adjust attention.
 Learned associations are therefore ballistic, difficult to suppress, and difficult to unlearn [e.g., @schneider_controlled_1977; @shiffrin_controlled_1977; @posner_attention_1975; @posner_facilitation_1975; @treisman_contextual_1960; @treisman_selective_1964; @treisman_strategies_1969].
@@
 Here, practice is only important to the extent that it improves memory retrieval.
-Learning an association is the process of encoding experiences, where attentional priorities and cues co-occur, into memory.
+Learning an association is the process of encoding experiences where attentional priorities and cues co-occur.
 Memory retrieval is a similarity-based, cue-driven process [e.g., @jacoby_interpreting_1978; @hintzman_minerva_1984; @hintzman_schema_1986; @hintzman_judgments_1988].
 Presumably, the features of our immediate environment automatically cue memory and reinstate the retrieved attentional priorites [@logan_toward_1988; @logan_attention_1992].
-If a few prior experiences are easily retrievable--memories are distinct or very similar to the retrieval cue--it could support the reinstatement of a learned attentional association despite very little practice [e.g., @brosowsky_memory-guided_2018].
-Conversely, if prior experiences are difficult to retrieve--memories are in or low in similarity to the retrieval cue--then learned associations may not be expressed, even after much practice.
+If a few prior experiences are easily retrievable (i.e., memories are distinct or very similar to the retrieval cue), they could support the reinstatement of a learned attentional association despite very little practice [e.g., @brosowsky_memory-guided_2018].
+Conversely, if prior experiences are difficult to retrieve (i.e., memories are indistinct or low in similarity to the retrieval cue), then learned associations may not be expressed, even after much practice.
 To the extent that you could manipulate memory retrieval, you should be able manipulate the expression of learned associations.
@@
 Recent work lends some credence to the possibility that task-relevance is necessary for establishing and using context-attention associations.
-The most commonly used context cue is location [@brosowsky_context-specific_2016; @corballis_independent_2003; @crump_context-specific_2006; @crump_context-specific_2008; @crump_learning_2016; @weidler_attentional_2018; @weidler_transfer_2016], often claimed to be irrelevant to the on-going conflict task.
-Although in some sense, the location is irrelevant for identifying the color of a word in a Stroop task, it seems disingenuous to consider it completely task-irrelevant.
-In order to identify the target, the participant must first identify and orient to its location on the screen.
-In this is sense, it is relevant to their ability to complete the task.
-Further, there is some evidence that location information may receive priority during encoding [@logan_what_1998; @mayr_spatial_1996].
-Similar arguments could be made about other context features that are inherent to processing the target stimulus, like font-type [@bugg_multiple_2008] and color [@vietze_context_2009].
-
-We are aware of only one study that has looked at task-relevance within the CSPC literature.
 Crump, Vaquero, & Milliken [-@crump_context-specific_2008] used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe.
@@
 These results suggest that making a context dimension relevant to the on-going task is important for producing CSPC effects.
+
+<!-- Furthermore, most commonly used context cue is location [@brosowsky_context-specific_2016; @corballis_independent_2003; @crump_context-specific_2006; @crump_context-specific_2008; @crump_learning_2016; @weidler_attentional_2018; @weidler_transfer_2016], often claimed to be irrelevant to the on-going conflict task.
+Although in some sense, the location is irrelevant for identifying the color of a word in a Stroop task, it seems disingenuous to consider it completely task-irrelevant.
+In order to identify the target, the participant must first identify and orient to its location on the screen.
+In this is sense, it is relevant to their ability to complete the task.
+Further, there is some evidence that location information may receive priority during encoding [@logan_what_1998; @mayr_spatial_1996].
+Similar arguments could be made about other context features that are inherent to processing the target stimulus, like font-type [@bugg_multiple_2008] and color [@vietze_context_2009].
+-->
 
@@
 Previous work has shown that shifting between list-wide proportion congruent phases produced asymmetrical effects.
-Specifically, @abrahamse_attention_2013 found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects.
-The authors posited a learned attentional modulation in the mostly-incongruent block had carried over into the mostly-congruent block.
+@abrahamse_attention_2013 found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects.
+The authors posited a learned attentional modulation in the mostly-incongruent block had carried over into the mostly-congruent block reducing what, typically, would be a large congruency effect.
 In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from the use of one context cue to another.
@@
 
+We made two assumptions in the design of Experiment 1: First, we assumed that task-relevance was required for participants to learn about the associations between context cues and the biased proportion congruency manipulations.
+Our task was inspired by @crump_flexibility_2009 who failed find context-specific effects using a task-irrelevant shape cue until they used a counting task to make the shapes relevant.
+However, location is the most-often used context cue in these kinds of paradigms (e.g., ).
+In these cases, no task-relevance manipulation is necessary to produce CSPC effects using location cues.
+Though, it is arguable whether location is truly task-irrelevant when localizing the target is necessary for responding.
+Regardless, it is unclear in our paradigm whether participants required the counting task to learn about the biased proportion congruency manipulations.
+
+Second, we assumed that the biased proportion congruency manipulations would have no systematic effect on the unbiased items without the counting task.
+Although we randomized all aspects of the task across participants to control for potential confounds, it still remains unclear whether the biased items would influence how paricipants responded to the unbiased items.
+
+Experiment 2, therefore, serves as a control experiment to test these two assumptions.
+Experiment 2 is identical to Experiment 1 with two important changes: First, we removed the counting task and gave no explicit instructions about how to use the context cues; We only informed participants that images would be present throughout the task.
+This allowed us to determine if there was any systematic effect of biased items on the unbiased items absent the counting task.
+Second, we altered the proportion congruency of the biased item sets from 100%/0% to 75%/25%.
+This allowed us to measure the congruency effect for the biased item sets to determine whether participants learned about the associations between proportion congruency and the context cues without the counting task [e.g., @crump_flexibility_2009].
+If this were the case, we would expect larger congruency effects for the 75% proportion congruent items as compared to the 25% proportion congruent items.
+
 # Methods
@@
 ## Design 
-Experiment 1 used a 2x3 within-subjects design with proportion congruent (25%, 50%, and 75%) and  congruency (congruent and incongruent) as factors.
+Experiment 2 used a 2x3 within-subjects design with proportion congruent (25%, 50%, and 75%) and  congruency (congruent and incongruent) as factors.
 The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials or instructions informing participants about the proportion manipulations.
@@
 The questions of interest were whether participants would learn the associations between the context cues without the task-relevance manipulation (i.e., the counting task) and whether responding to the unbiased cues would be influenced by the presence of the biased cues.
-To that end, mean correct RTs and mean error rates were submitted to an analysis of variance (ANOVA) with proportion congruent (25%, 50%, and 75%) and congruency (congruent and incongruent) as within-subject factors.
+To that end, congruency effects (incongruent minus congruent performance) for RTs and error rates were submitted to an analysis of variance (ANOVA) with proportion congruency (25%, 50%, and 75%) as the sole within-subject factor.
 
-The results of the RT analysis revealed the critical, two-way interaction between proportion congruency and congruency to be non-significant, `r RT_ANOVA_E2$PC_Congruency`.
-Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA_E2$PC_Congruency`.
-Therefore, there was no evidence that the context cues, absent the counting task, systematically influenced the congruency effect.
+The results of the RT analysis revealed the effect of proportion congruency to be non-significant, `r RT_ANOVA_E2$PC`, with moderate evidence in favor of the null, `r RT_BF_E2[[1]]`.
+Similarly, the corresponding error analysis also resulted in a non-significant effect of proportion congruency, `r ACC_ANOVA_E2$PC`, with strong evidence in favor of the null, `r ACC_BF_E2[[1]]`.
+Therefore, there was no evidence that the context cues, absent the counting task, systematically influenced the congruency effects in any way.
 
@@
 # Experiment 3
+
+In the current study, we have been homing in on the importance of task-relevance for the contextual recruitment of selective attention.
+In Experiment 1, we found that task-relevance allowed participants to exploit context cues in the presence of a competing, contradictory cue and subsequently ignore the previously learned association in favor of a different context cue.
+In Experiment 2, we conceptually replicated previous work showing that task-relevance was necessary for participants to learn about the biased proportion congruency associations [e.g., @crump_flexibility_2009] and ruled out possible confounding effects of the biased items.
 
@@
 ## Design 
-Experiment 1 used a 2x3 within-subjects design with proportion congruent (25%, 50%, and 75%) and  congruency (congruent and incongruent) as factors.
-The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials or instructions informing participants about the proportion manipulations.
+Experiment 3 used a 2x3 mixed design with task-relevant context (0% and 100%) and unbiased-item congruency (congruent and incongruent) as the within-subject factors.
+The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials.
+However, participants were explicitly informed about the proportion congruency manipulations and instructed to make used of the context cues (see the Procedure section below for more details).
+Therefore, unlike Experiment 1, context images were made task-relevant through explicit instructions rather than the counting task.
 The design in every other respect was identical to Experiment 1.
@@
 Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing 'z' if the arrow pointed left, and 'm' if the arrow pointed right.
+
+Importantly, participants were given further instructions to exploit the proportion congruency associated with context cues.
 
@@
 The aim of the current study was to determine whether task-relevance plays a role in the contextual recruitment of selective attention.
-Specifically, we tested whether manipulating the relative task-relevance of context cues could cause participants to ignore a previously learned context-association and apply a new association.
+In Experiment 1, we tested whether manipulating the relative task-relevance of context cues could cause participants to ignore a previously learned context-association and apply a new association.
 We created a frequency unbiased context cue that shared features with two frequency biased contexts and used a feature-counting task to manipulate the task-relevance of context dimensions across two blocks of trials.

### 2019-09-16 data-analysis/analysis_E1.R

@@ -138,6 +138,7 @@ RT.graph <- ggplot(RT.Diff,aes(x=Condition, y=Flanker,fill=Task_Relevant_Context
   geom_errorbar(limits, width = .2, position=position_dodge(width=0.9))+
   coord_cartesian(ylim = c(0,150))+
   scale_y_continuous(breaks=seq(0, 150, 10), expand = c(0,0))+
+  theme_classic()+
   theme(axis.text=element_text(size=7.5),
         axis.title=element_text(size=10,face="bold")) +
   labs(title="")+
@@ -174,10 +175,6 @@ ACC.Diff <- raw_data %>%
   ) 
 
 
-
-levels(ACC.Diff$Task_Relevant_Context) <- c("100% PC", "0% PC")
-levels(ACC.Diff$Condition) <- c("Object", "Social", "Social (NR)")
-
 ACC.Diff <- raw_data %>%
   mutate(error = (1-ACC)*100) %>%
   filter(
@@ -200,6 +197,8 @@ ACC.Diff <- raw_data %>%
     SE = sd/sqrt(N)
   ) 
 
+levels(ACC.Diff$Task_Relevant_Context) <- c("100% PC", "0% PC")
+levels(ACC.Diff$Condition) <- c("Object", "Social", "Social (NR)")
 
 limits <- aes(ymax = Flanker + SE, ymin = Flanker - SE)
 ACC.graph <- ggplot(ACC.Diff,aes(x=Condition, y=Flanker,fill=Task_Relevant_Context))+
@@ -208,6 +207,7 @@ ACC.graph <- ggplot(ACC.Diff,aes(x=Condition, y=Flanker,fill=Task_Relevant_Conte
   geom_errorbar(limits, width = .2, position=position_dodge(width=0.9))+
   coord_cartesian(ylim = c(0,10))+
   scale_y_continuous(breaks=seq(0, 10, 1), expand = c(0,0))+
+  theme_classic()+
   theme(axis.text=element_text(size=7.5),
         axis.title=element_text(size=10,face="bold")) +
   labs(title="")+
@@ -229,7 +229,7 @@ ACC.graph <- ggplot(ACC.Diff,aes(x=Condition, y=Flanker,fill=Task_Relevant_Conte
 figure2<-plot_grid(RT.graph,NULL,ACC.graph, 
                    nrow = 1, 
                    rel_widths = c(1, 0.05, 1),
-                   labels = c("A", "", "B"))
[…]

### 2019-09-16 data-analysis/analysis_E2.R

@@ -4,6 +4,7 @@ library(tidyr)
 library(afex)
 library(ggplot2)
 library(cowplot)
+library(BayesFactor)
 #As of 2018/12/07 apa_print() requires development version of Papaja
 #devtools::install_github("crsh/papaja")
 library(papaja)
@@ -94,11 +95,19 @@ ACC_BF_E2 = suppressWarnings(print_bf(ACC_BF_E2))
 
 ####### GRAPH FLANKER EFFECTS #########
 RT.Diff <- RT.DF %>%
-  group_by(Frequency, PC) %>%
+  ungroup() %>%
+  mutate(Subject = factor(Subject),
+         PC = factor(PC)) %>%
+  group_by(Subject,PC,Congruency) %>%
+  summarise(meanRT = mean(vjoutRT)) %>%
+  spread(Congruency, meanRT) %>%
+  ungroup()%>%
+  mutate(CE = inc - con) %>%
+  group_by(PC) %>%
   summarise(
     N = n_distinct(Subject), 
-    Flanker = mean(Diff), 
-    sd = sd(Diff), 
+    Flanker = mean(CE), 
+    sd = sd(CE), 
     SE = sd/sqrt(N)
   ) 
 
@@ -110,20 +119,22 @@ RT.graph <- ggplot(RT.Diff,aes(x=PC, y=Flanker,fill=PC))+
   geom_errorbar(limits, width = .2, position=position_dodge(width=0.9))+
   coord_cartesian(ylim = c(0,150))+
   scale_y_continuous(breaks=seq(0, 150, 10), expand = c(0,0))+
+  theme_classic()+
   theme(axis.text=element_text(size=7.5),
         axis.title=element_text(size=10,face="bold")) +
   labs(title="")+
   ylab("Congruency Effect (ms)")+
   xlab("Proportion\nCongruent") +
+  theme_classic()+
   theme(       legend.position=c(1,1),
                legend.justification = c(1,1),
                legend.direction = "horizontal",
-               legend.background = element_rect(colour = "black", fill = "white", size=1),
-               legend.box.background = element_rect(colour = "black"),
+               #legend.background = element_rect(colour = "black", fill = "white", size=1),
+               #legend.box.background = element_rect(colour = "black"),
                legend.margin = margin(t = .1, r = .10, b = .05, l = .1, unit = "cm"),
                legend.text = element_text(size = 8),
                legend.title = element_text(size = 8)
-  )+
[…]

### 2019-09-16 data-analysis/print_bf.R

@@ -7,6 +7,7 @@
 #'
 #' @examples
 print_bf <- function(bf){
+    library(BayesFactor)
     result <- list()
     for (i in 1:length(bf)){
         if(extractBF(bf[i])$bf < 1){

### 2019-09-27 manuscript_pretty.Rmd
working

@@
 
-Real-world environments can offer a plethora of context cues.
-Consider someone writing in a coffee shop.
-The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which we have different experiences with and afford different learned associations.
-Although a laptop might cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
+Real-world environments are complex and contain many potential context cues.
+For instance, consider someone writing in a coffee shop.
+The coffee shop is a rich environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which we have different experiences with and afford different learned associations.
+Although a laptop could cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
 Given that all of these cues are available to set attentional priorities, what determines which associative relationships will be used to guide attention?
 On the one hand, context-based retrieval of attentional priorities might be completely obligatory: the mere presence of learned cues might trigger attention in a ballistic manner [e.g., @schneider_controlled_1977; @shiffrin_controlled_1977].
-A writer's attention in this case would be at the mercy of the environment.
+A writer's attention in this case would be at the mercy of the environment and attention is guided by the strongest association.
 On the other hand, our current task-goals might constrain the expression of previously learned associations.
-For instance, the writer's current goals may allow the laptop to take priority over other environmental cues that are irrelevant to the task at hand.
+The writer's current goals may allow the laptop to take priority over other environmental cues that are irrelevant to the task at hand.
 
@@
 Learning an association is the process of encoding experiences where attentional priorities and cues co-occur.
-Memory retrieval is a similarity-based, cue-driven process [e.g., @jacoby_interpreting_1978; @hintzman_minerva_1984; @hintzman_schema_1986; @hintzman_judgments_1988].
+The expression of previously learned associations however, is dictated by memory retrieval---a similarity-based, cue-driven process [e.g., @jacoby_interpreting_1978; @hintzman_minerva_1984; @hintzman_schema_1986; @hintzman_judgments_1988].
 Presumably, the features of our immediate environment automatically cue memory and reinstate the retrieved attentional priorites [@logan_toward_1988; @logan_attention_1992].
@@
 Conversely, if prior experiences are difficult to retrieve (i.e., memories are indistinct or low in similarity to the retrieval cue), then learned associations may not be expressed, even after much practice.
-To the extent that you could manipulate memory retrieval, you should be able manipulate the expression of learned associations.
+To the extent that you could manipulate memory retrieval, you should als be able manipulate the expression of learned associations.
 
@@
 
-Recent work lends some credence to the possibility that task-relevance is necessary for establishing and using context-attention associations.
+Recent work lends some credence to the possibility that task-relevance is necessary for establishing new context-attention associations.
 Crump, Vaquero, & Milliken [-@crump_context-specific_2008] used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe.
@@
 When given instructions to think of the faces as members of the gender categories they found CSPC effects, but when given instructions to think of the faces as individuals they did not.
-These results suggest that making a context dimension relevant to the on-going task is important for producing CSPC effects.
+These results suggest that making a context dimension relevant to the on-going task is important for establishing new associations and producing CSPC effects.
+However, the extent to which task-relevance influences the expression of previously learned associations is still unknown.
 
@@
 Or it could occur because associations formed in the first block interfere with learning new associations in the second [e.g., @brosowsky_context-specific_2016].
-On other hand, task-relevance might not only dictate how associations are formed, but also whether learned associations are used.
+On other hand, task-relevance may dictate the expression of previously learned associations.
 In this case, we would expect smaller congruency effects when the high-conflict context dimension is made task-relevant as compared to when the low-conflict context dimension is made task-relevant.
@@
 However, location is the most-often used context cue in these kinds of paradigms (e.g., ).
-In these cases, no task-relevance manipulation is necessary to produce CSPC effects using location cues.
-Though, it is arguable whether location is truly task-irrelevant when localizing the target is necessary for responding.
+In these cases, no task-relevance manipulation is necessary to produce CSPC effects, though, it is arguable whether location is truly task-irrelevant when localizing the target is necessary for responding.
 Regardless, it is unclear in our paradigm whether participants required the counting task to learn about the biased proportion congruency manipulations.
@@
 Experiment 2, therefore, serves as a control experiment to test these two assumptions.
-Experiment 2 is identical to Experiment 1 with two important changes: First, we removed the counting task and gave no explicit instructions about how to use the context cues; We only informed participants that images would be present throughout the task.
+Experiment 2 is identical to Experiment 1 with two important changes: First, we removed the counting task, giving no explicit instructions about how to use the context cues; We only informed participants that images would be present throughout the task.
 This allowed us to determine if there was any systematic effect of biased items on the unbiased items absent the counting task.
@@
 
-In the current study, we have been homing in on the importance of task-relevance for the contextual recruitment of selective attention.
-In Experiment 1, we found that task-relevance allowed participants to exploit context cues in the presence of a competing, contradictory cue and subsequently ignore the previously learned association in favor of a different context cue.
+In the current study, we have bene examining the importance of task-relevance for the contextual recruitment of selective attention.
+In Experiment 1, we found that task-relevance allowed participants to exploit context cues in the presence of a competing, contradictory cue and subsequently ignore a previously learned association in favor of a different context cue.
 In Experiment 2, we conceptually replicated previous work showing that task-relevance was necessary for participants to learn about the biased proportion congruency associations [e.g., @crump_flexibility_2009] and ruled out possible confounding effects of the biased items.
+
+Experiment 3
 

### 2019-09-27 manuscript_pretty.tex
working

@@
 
-Real-world environments can offer a plethora of context cues.
+Real-world environments are complex and contain many potential context cues.
 For instance, consider someone writing in a coffee shop.
-The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop) associated with many experiences that afford different attentional priorities.
-Although a laptop might cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
+The coffee shop is a rich environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which we have different experiences with and afford different learned associations.
+Although a laptop could cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
 Given that all of these cues are available to set attentional priorities, what determines which associative relationships will be used to guide attention?
-On the one hand, context-based retrieval of attentional priorities might be completely obligatory: the mere presence of learned cues trigger attention in a ballistic manner (e.g., Schneider \& Shiffrin, 1977; Shiffrin \& Schneider, 1977).
-A writer's attention in this case would be at the mercy of the environment and the most strongly associated cues.
-On the other hand, contextual cuing of attention may not be entirely obligatory.
-Our current task-goals, for instance, might constrain the expression of previously learned associations, allowing, for instance, the laptop to take priority as a contextual cue over other cues that are irrelevant to the task at hand.
+On the one hand, context-based retrieval of attentional priorities might be completely obligatory: the mere presence of learned cues might trigger attention in a ballistic manner (e.g., Schneider \& Shiffrin, 1977; Shiffrin \& Schneider, 1977).
+A writer's attention in this case would be at the mercy of the environment and attention is guided by the strongest association.
+On the other hand, our current task-goals might constrain the expression of previously learned associations.
+The writer's current goals may allow the laptop to take priority over other environmental cues that are irrelevant to the task at hand.
 
@@
 Under this view, forming an association requires many repeated experiences pairing a cue with a set of attentional priorities.
-Once formed however, they become habitual or hard-wired and the mere presence of the cue is suffificient to automatically adjust attention.
+Once formed however, it becomes habitual or hard-wired and the mere presence of the cue is sufficient to automatically adjust attention.
 Learned associations are therefore ballistic, difficult to suppress, and difficult to unlearn (e.g., Schneider \& Shiffrin, 1977; Posner \& Snyder, 1975a, 1975b; Shiffrin \& Schneider, 1977; Treisman, 1960, 1964, 1969).
-This view is reflected in moodern work on contextual cuing where it is assumed that learned associations require practice (e.g., Lehle \& Hübner, 2008; Crump, 2016), form without awareness or intention, triggered automatically by the mere presence of the cue (Crump et al., 2006; Crump \& Logan, 2010; Crump, Vaquero, \& Milliken, 2008; King et al., 2012; Reuss, Desender, Kiesel, \& Kunde, 2014; cf.
-Brosowsky \& Crump, 2016).
+This view is reflected in modern work on contextual cuing where it is assumed that learned associations require practice (e.g., Lehle \& Hübner, 2008; Crump, 2016), form without awareness or intention, and are triggered automatically by the mere presence of the cue (Crump et al., 2006; Crump \& Logan, 2010; Crump, Vaquero, \& Milliken, 2008; King et al., 2012; Reuss, Desender, Kiesel, \& Kunde, 2014; though, see Brosowsky \& Crump, 2016).
 
@@
 Here, practice is only important to the extent that it improves memory retrieval.
-If a few prior experiences are distinct, and easily retrievable, it could support the reinstatement of a learned attentional association despite very little practice (e.g., Brosowsky \& Crump, 2018).
-Conversely, if prior experiences are difficult to retrieve, then learned associations may not be expressed, even after much practice.
-This view offers one potential path for flexibility in the expression of learned associations.
-Learning an association is the process of encoding into memory experiences where attentional priorities and cues co-occur.
-Memory retrieval is a similarity-based, cue-driven process (Hintzman, 1984, 1986, 1988; Jacoby, 1978).
+Learning an association is the process of encoding experiences where attentional priorities and cues co-occur.
+The expression of previously learned associations however, is dictated by memory retrieval---a similarity-based, cue-driven process (e.g., Jacoby, 1978; Hintzman, 1984, 1986, 1988).
 Presumably, the features of our immediate environment automatically cue memory and reinstate the retrieved attentional priorites (Logan, 1988, 1992).
-However, to the extent that you could manipulate memory retrieval, you should be able manipulate the expression of learned associations.
+If a few prior experiences are easily retrievable (i.e., memories are distinct or very similar to the retrieval cue), they could support the reinstatement of a learned attentional association despite very little practice (e.g., Brosowsky \& Crump, 2018).
+Conversely, if prior experiences are difficult to retrieve (i.e., memories are indistinct or low in similarity to the retrieval cue), then learned associations may not be expressed, even after much practice.
+To the extent that you could manipulate memory retrieval, you should als be able manipulate the expression of learned associations.
 
@@
 
-Recent work lends some credence to the possibility that task-relevance is necessary for establishing and using context-attention associations.
-The most commonly used context cue is location (Brosowsky \& Crump, 2016; Corballis \& Gratton, 2003; Crump, 2016; Crump et al., 2006, 2008; Weidler \& Bugg, 2016; Weidler et al., 2018), often claimed to be irrelevant to the on-going conflict task.
-Although in some sense, the location is irrelevant for identifying the color of a word in a Stroop task, it seems disingenuous to consider it completely task-irrelevant.
-In order to identify the target, the participant must first identify and orient to its location on the screen.
-In this is sense, it is relevant to their ability to complete the task.
-Further, there is some evidence that location information may receive priority during encoding (Logan, 1998; Mayr, 1996).
-Similar arguments could be made about other context features that are inherent to processing the target stimulus, like font-type (Bugg, Jacoby, \& Toth, 2008) and color (Vietze \& Wendt, 2009).
-
-We are aware of only one study that has looked at task-relevance within the CSPC literature.
+Recent work lends some credence to the possibility that task-relevance is necessary for establishing new context-attention associations.
 Crump, Vaquero, \& Milliken (2008) used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe.
@@
 Simply put, CSPC effects tend to emerge when context cues are somehow made relevant to the task, but do not when made irrelevant (Cañadas et al., 2013; Crump et al., 2006, 2008).
-However, it is still unclear whether there is any flexibility in the expression of learned assocations, and more importantly, what determines that flexibility.
+However, what determines the learning and expression of context-attention associations remains unclear.
 In the current study, we examined whether manipulating task-relevance would allow participants to ignore a previously learned association and adopt a new context-specific control strategy.
@@
 Or it could occur because associations formed in the first block interfere with learning new associations in the second (e.g., Brosowsky \& Crump, 2016).
-On other hand, task-relevance might not only dictate how associations are formed, but also whether learned associations are used.
+On other hand, task-relevance may dictate the expression of previously learned associations.
 In this case, we would expect smaller congruency effects when the high-conflict context dimension is made task-relevant as compared to when the low-conflict context dimension is made task-relevant.
@@
 Previous work has shown that shifting between list-wide proportion congruent phases produced asymmetrical effects.
-Specifically, Abrahamse, Duthoo, Notebaert, and Risko (2013) found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects.
-The authors suggested that the assymetry is caused by a learned attentional modulation in the mostly-incongruent block carrying over into the mostly-congruent block.
+Abrahamse, Duthoo, Notebaert, and Risko (2013) found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects.
+The authors posited a learned attentional modulation in the mostly-incongruent block had carried over into the mostly-congruent block reducing what, typically, would be a large congruency effect.
 In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from the use of one context cue to another.
@@
 
+We made two assumptions in the design of Experiment 1: First, we assumed that task-relevance was required for participants to learn about the associations between context cues and the biased proportion congruency manipulations.
+Our task was inspired by Crump and Milliken (2009) who failed find context-specific effects using a task-irrelevant shape cue until they used a counting task to make the shapes relevant.
+However, location is the most-often used context cue in these kinds of paradigms (e.g., ).
+In these cases, no task-relevance manipulation is necessary to produce CSPC effects using location cues.
+Though, it is arguable whether location is truly task-irrelevant when localizing the target is necessary for responding.
+Regardless, it is unclear in our paradigm whether participants required the counting task to learn about the biased proportion congruency manipulations.
+
+Second, we assumed that the biased proportion congruency manipulations would have no systematic effect on the unbiased items without the counting task.
+Although we randomized all aspects of the task across participants to control for potential confounds, it still remains unclear whether the biased items would influence how paricipants responded to the unbiased items.
+
+Experiment 2, therefore, serves as a control experiment to test these two assumptions.
+Experiment 2 is identical to Experiment 1 with two important changes: First, we removed the counting task and gave no explicit instructions about how to use the context cues; We only informed participants that images would be present throughout the task.
+This allowed us to determine if there was any systematic effect of biased items on the unbiased items absent the counting task.
+Second, we altered the proportion congruency of the biased item sets from 100\%/0\% to 75\%/25\%.
+This allowed us to measure the congruency effect for the biased item sets to determine whether participants learned about the associations between proportion congruency and the context cues without the counting task (e.g., Crump \& Milliken, 2009).
+If this were the case, we would expect larger congruency effects for the 75\% proportion congruent items as compared to the 25\% proportion congruent items.
+
 \hypertarget{methods-1}{%
@@
 
-Experiment 1 used a 2x3 within-subjects design with proportion congruent (25\%, 50\%, and 75\%) and congruency (congruent and incongruent) as factors.
+Experiment 2 used a 2x3 within-subjects design with proportion congruent (25\%, 50\%, and 75\%) and congruency (congruent and incongruent) as factors.
 The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials or instructions informing participants about the proportion manipulations.
@@
 The questions of interest were whether participants would learn the associations between the context cues without the task-relevance manipulation (i.e., the counting task) and whether responding to the unbiased cues would be influenced by the presence of the biased cues.
-To that end, mean correct RTs and mean error rates were submitted to an analysis of variance (ANOVA) with proportion congruent (25\%, 50\%, and 75\%) and congruency (congruent and incongruent) as within-subject factors.
-
-The results of the RT analysis revealed the critical, two-way interaction between proportion congruency and congruency to be non-significant, \(F(2, 92) = 0.85\), \(\mathit{MSE} = 498.56\), \(p = .431\), \(\hat{\eta}^2_p = .018\).
-Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(2, 92) = 0.45\), \(\mathit{MSE} = 4.61\), \(p = .641\), \(\hat{\eta}^2_p = .010\).
-Therefore, there was no evidence that the context cues, absent the counting task, systematically influenced the congruency effect.
+To that end, congruency effects (incongruent minus congruent performance) for RTs and error rates were submitted to an analysis of variance (ANOVA) with proportion congruency (25\%, 50\%, and 75\%) as the sole within-subject factor.
+
+The results of the RT analysis revealed the effect of proportion congruency to be non-significant, \(F(2, 92) = 0.85\), \(\mathit{MSE} = 997.11\), \(p = .431\), \(\hat{\eta}^2_p = .018\), 90\% CI \([0\), \(0.07]\), with moderate evidence in favor of the null, \(\mathrm{BF}_{\textrm{01}} = 6.91\) \([\pm 0.9\%]\).
+Similarly, the corresponding error analysis also resulted in a non-significant effect of proportion congruency, \(F(2, 92) = 0.45\), \(\mathit{MSE} = 9.23\), \(p = .641\), \(\hat{\eta}^2_p = .010\), 90\% CI \([0\), \(0.05]\), with strong evidence in favor of the null, \(\mathrm{BF}_{\textrm{01}} = 9.93\) \([\pm 1.03\%]\).
+Therefore, there was no evidence that the context cues, absent the counting task, systematically influenced the congruency effects in any way.
 
@@
 
+In the current study, we have been homing in on the importance of task-relevance for the contextual recruitment of selective attention.
+In Experiment 1, we found that task-relevance allowed participants to exploit context cues in the presence of a competing, contradictory cue and subsequently ignore the previously learned association in favor of a different context cue.
+In Experiment 2, we conceptually replicated previous work showing that task-relevance was necessary for participants to learn about the biased proportion congruency associations (e.g., Crump \& Milliken, 2009) and ruled out possible confounding effects of the biased items.
+
 \hypertarget{methods-2}{%
@@
 
-Experiment 1 used a 2x3 within-subjects design with proportion congruent (25\%, 50\%, and 75\%) and congruency (congruent and incongruent) as factors.
-The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials or instructions informing participants about the proportion manipulations.
+Experiment 3 used a 2x3 mixed design with task-relevant context (0\% and 100\%) and unbiased-item congruency (congruent and incongruent) as the within-subject factors.
+The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials.
+However, participants were explicitly informed about the proportion congruency manipulations and instructed to make used of the context cues (see the Procedure section below for more details).
+Therefore, unlike Experiment 1, context images were made task-relevant through explicit instructions rather than the counting task.
 The design in every other respect was identical to Experiment 1.
@@
 Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing \enquote{z} if the arrow pointed left, and \enquote{m} if the arrow pointed right.
+
+Importantly, participants were given further instructions to exploit the proportion congruency associated with context cues.
 
@@
 
-The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be non-significant, \(F(1, 45) = 0.02\), \(\mathit{MSE} = 2,015.27\), \(p = .876\), \(\hat{\eta}^2_p = .001\).
-Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 45) = 0.66\), \(\mathit{MSE} = 14.26\), \(p = .420\), \(\hat{\eta}^2_p = .014\).
+The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be non-significant, .
+Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, .
 
@@
 
-\leavevmode\hypertarget{ref-bugg_multiple_2008}{}%
-Bugg, J., Jacoby, L.
-L., \& Toth, J.
-P.
-(2008).
-Multiple levels of control in the Stroop task.
-\emph{Memory \& Cognition}, \emph{36}, 1484--1494.
-doi:\href{https://doi.org/10.3758/MC.36.8.1484}{10.3758/MC.36.8.1484}
-
 \leavevmode\hypertarget{ref-canadas_social_2013}{}%
@@
 
-\leavevmode\hypertarget{ref-logan_what_1998}{}%
-Logan, G. D. (1998). What is learned during automatization? II. Obligatory encoding of spatial location. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{24}, 1720.
-
 \leavevmode\hypertarget{ref-logan_when_1979}{}%
@@
 Macrae, C. N., \& Bodenhausen, G. V. (2001). Social cognition: Categorical person perception. \emph{British Journal of Psychology}, \emph{92}, 239--255.
-
-\leavevmode\hypertarget{ref-mayr_spatial_1996}{}%
-Mayr, U.
-(1996).
-Spatial attention and implicit sequence learning: Evidence for independent learning of spatial and nonspatial sequences.
-\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{22}, 350.
 
@@
 
-\leavevmode\hypertarget{ref-vietze_context_2009}{}%
-Vietze, I., \& Wendt, M.
-(2009).
-Context specificity of conflict frequency-dependent control.
-\emph{The Quarterly Journal of Experimental Psychology}, \emph{62}, 1391--1400.
-doi:\href{https://doi.org/10.1080/17470210802426908}{10.1080/17470210802426908}
-
 \leavevmode\hypertarget{ref-weidler_transfer_2016}{}%

### 2019-09-27 data-analysis/table1.R

@@ -64,7 +64,7 @@ RT.DF <- raw_data %>%
   group_by(Condition,Frequency,Task_Relevant_Context,Congruency) %>%
   summarise(N = n_distinct(Subject),
             RT = mean(meanRT),
-            sd = sd(meanRT),
+            std = sd(meanRT),
             se = std/sqrt(N))
 
 RT.DF$PC <- NA

### 2019-09-30 manuscript_pretty.Rmd
almost there

@@
 
-In Experiment 1, we found that
+In Experiment 1, we found that manipulating the task-relevance of a shared contextual feature was associated in predictable changes in context-specific proportion congruency effects for frequency unbiased context items; Namely, larger congruency effects when the context was associated with low conflict than when the context was associated with high conflict.
+This suggests that participants learned the association between context and conflict-level in the first block (despite multiple, competing cues), and subsequently ignored that association in the second block to learn a new association.
+Task-relevance then, may not just be important for establishing new associations [e.g.,@crump_flexibility_2009] but also important for determining which learned associations are expressed in the present moment.
 
@@
 
-Experiment 2, therefore, serves as a control experiment to test these two assumptions.
+Experiment 2, therefore, serves as a control experiment to test these two assumptions directly.
 Experiment 2 is identical to Experiment 1 with two important changes: First, we removed the counting task, giving no explicit instructions about how to use the context cues; We only informed participants that images would be present throughout the task.
@@
 
-In the current study, we have bene examining the importance of task-relevance for the contextual recruitment of selective attention.
+In the current study, we have been examining the importance of task-relevance for the contextual recruitment of selective attention.
 In Experiment 1, we found that task-relevance allowed participants to exploit context cues in the presence of a competing, contradictory cue and subsequently ignore a previously learned association in favor of a different context cue.
@@
 
-Experiment 3
+Experiment 3 tests the boundaries of the task-relevance effect found in Experiment 1.
+The evidence thus far suggests that context-cues, rather than being irrelevant to the task (as their namesake would suggest), need to be integrated into the task-representation to guide attentional control.
+There is some evidence that instructions alone can be sufficient to produce list-wide proportion congruency effects, though not item-specific proportion congruency effects (e.g., Entel et al., 2014; though, see Desender, 2018) and not context-specific proportion congruency effects (e.g., ).
+Explicit instructions however, are another way of making context-cues relevant to the on-going task and could serve the same purpose as the counting task---although, instructions are likely a much weaker manipulation than the counting task.
+In Experiment 3, we test whether participants are able to explicitly use the context-cues to guide attentional control through an instruction manipulation.
 
@@
 Importantly, participants were given further instructions to exploit the proportion congruency associated with context cues.
+Halfway through the experiment, participants received new instructions about which context features were relevant and associated with high/low conflict.
+For example:
+
+> *"On every trial you'll see five arrows (pointed left or right) paired with an image.*
+
+> *The images will help you perform this task.*
+
+> *The arrows will either be congruent (the center arrow is the same as the flanking arrows) or incongruent (the center arrow is different from the flanking arrows).
+Incongruent trials are typically harder because you need to ignore the flanking arrows, while the congruent trials are easier, because you do not need to ignore the flanking arrows.*
+
+> *In the first block of the experiment, trials that include a chair (regardless of whether it is blue or green) will be mostly incongruent.
+That is, most of the trials that include a chair will be hard.*
+
+> *This will be helpful to perform the task, so try to proactively use this information when you perform the task."*
 
@@
 
-The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be non-significant, `r RT_ANOVA_E3$Task_Relevant_Context_Congruency`.
-Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA_E3$Task_Relevant_Context_Congruency`.
+The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be non-significant, `r RT_ANOVA_E3$Task_Relevant_Context`.
+Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA_E3$Task_Relevant_Context`.
 
-# Estimating reproducability by simulation-based sensitivity- and power-analyses
+# Estimating replicability by simulation-based sensitivity- and power-analyses
 
@@
 
-(ref:figure5) Results from Experiment 3 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent).
-Task-relevance was manipulated through explicit instructions.
+(ref:figure5) Results from the simulation-based sensitivity and power-analyses.
+Figure A shows the sensitivity of our experimental design to detect a range of effect sizes for the context-specific proportion congruency (CSPC) effect with 50 (e.g., Experiments 2 and 3) and 150 (e.g., Experiment 1) participants.
+Figure B shows the sensitivity to detect the CSPC by context-type interaction with 50 participants per group (e.g., Experiment 1).
+Figures C and D show the estimated power curves for the CSPC and CSPC by context-type effects across sample sizes.
+Each data point represents the proportion of p-values less than .05 from 10,000 simulations.
+
+In Experiment 1, we found no evidence for differences in the task-relevance effect across context-type.
+Similarly, Experiments 2 and 3 failed to find CSPC effects.
+To effectively draw inferences from these results, we need to assess the extent to which our experiments could have detected effects, if present.
+Although replicability has become an important and salient issue in Psychology at large (e.g., ), this issue has also arisen in the context-specific proportion congruency literature (e.g., Brosowsky Crump, Hutcheon speiler, TiCS).
+
+To address this issue in the current study---and to do so transparently---we conducted simulation-based power and sensitivity analyses (Maxwell, Kelley, and Raush, 2008; Brosowsky and Crump) to determine the range effect sizes our experimental design was sensitive to detect and the required sample sizes to detect them.
+We used a Monte Carlo simulation approach with a statistical model of the distributions that underlie the effect of interest (Maxwell, 2008).
+Rather than estimating power based on observed effect sizes from prior experiments (typically, over-estimates), we instead estimated the properties of the base reaction time distributions from our current data and sampled from these distributions using a Monte Carlo simulation approach to estimate the replication success rate across a range of effect sizes and sample sizes.
+
+We created the conflictPower R-package to conduct the Monte Carlo simulations (Crump and Brosowsky; Tics).
+The conflictPower package samples simulated reaction time data for subjects at the trial-level, given base reaction time distributions for the conflict and no-conflict conditions.
+To generate the base reaction time distributions, we fitted ex-Gaussian functions to the reaction time data from individual participants and averaged across all three experiments using the retimes R-package (XXXX).
+We then used the conflictPower package to simulate the results across a range of effect and sample sizes, calculating the proportion of experiments, across $10 000$ simulations, resulting in a p-value less than $.05$ (see Figure 5; for a more detailed explanation of the sampling procedure see Crump and Brosowsky, 2019).
+
+First, the results of these analyses show that our experimental design was reasonably powered to detect CSPC effects.
+In particular, with 150 participants, we estimated 89% power to detect effects as small 10 ms; With only 50 participants, we were still reasonably powered to detect CSPC effects as small as 15 ms at an estimated 78%.
+Understandably, our design was not as sensitive to detecting changes the in the CSPC effect across conditions (in Experiment 1, for example).
+We estimated only 75% power to detect the difference between a 20 ms and 0 ms CSPC effect with 50 participants per group.
+That is, the experimental design could detect the presence/absence of the CSPC effect moderately well, but likely does not reliably detect small changes in the CSPC effect across conditions.
+To reliably detect a 15 ms change in the CSPC effect at roughly 80% power, for example, we estimate would require 100 participants per group.
 

### 2019-09-30 manuscript_pretty.tex
almost there

@@
 
-In Experiment 1, we found that
+In Experiment 1, we found that manipulating the task-relevance of a shared contextual feature was associated in predictable changes in context-specific proportion congruency effects for frequency unbiased context items; Namely, larger congruency effects when the context was associated with low conflict than when the context was associated with high conflict.
+This suggests that participants learned the association between context and conflict-level in the first block (despite multiple, competing cues), and subsequently ignored that association in the second block to learn a new association.
+Task-relevance then, may not just be important for establishing new associations (e.g., Crump \& Milliken, 2009) but also important for determining which learned associations are expressed in the present moment.
 
@@
 
-Experiment 2, therefore, serves as a control experiment to test these two assumptions.
-Experiment 2 is identical to Experiment 1 with two important changes: First, we removed the counting task and gave no explicit instructions about how to use the context cues; We only informed participants that images would be present throughout the task.
+Experiment 2, therefore, serves as a control experiment to test these two assumptions directly.
+Experiment 2 is identical to Experiment 1 with two important changes: First, we removed the counting task, giving no explicit instructions about how to use the context cues; We only informed participants that images would be present throughout the task.
 This allowed us to determine if there was any systematic effect of biased items on the unbiased items absent the counting task.
@@
 
-In the current study, we have been homing in on the importance of task-relevance for the contextual recruitment of selective attention.
-In Experiment 1, we found that task-relevance allowed participants to exploit context cues in the presence of a competing, contradictory cue and subsequently ignore the previously learned association in favor of a different context cue.
+In the current study, we have been examining the importance of task-relevance for the contextual recruitment of selective attention.
+In Experiment 1, we found that task-relevance allowed participants to exploit context cues in the presence of a competing, contradictory cue and subsequently ignore a previously learned association in favor of a different context cue.
 In Experiment 2, we conceptually replicated previous work showing that task-relevance was necessary for participants to learn about the biased proportion congruency associations (e.g., Crump \& Milliken, 2009) and ruled out possible confounding effects of the biased items.
+
+Experiment 3 tests the boundaries of the task-relevance effect found in Experiment 1.
+The evidence thus far suggests that context-cues, rather than being irrelevant to the task (as their namesake would suggest), need to be integrated into the task-representation to guide attentional control.
+There is some evidence that instructions alone can be sufficient to produce list-wide proportion congruency effects, though not item-specific proportion congruency effects (e.g., Entel et al., 2014; though, see Desender, 2018) and not context-specific proportion congruency effects (e.g., ).
+Explicit instructions however, are another way of making context-cues relevant to the on-going task and could serve the same purpose as the counting task---although, instructions are likely a much weaker manipulation than the counting task.
+In Experiment 3, we test whether participants are able to explicitly use the context-cues to guide attentional control through an instruction manipulation.
 
@@
 Importantly, participants were given further instructions to exploit the proportion congruency associated with context cues.
+Halfway through the experiment, participants received new instructions about which context features were relevant and associated with high/low conflict.
+For example:
+
+\begin{quote}
+\emph{"On every trial you'll see five arrows (pointed left or right) paired with an image.}
+\end{quote}
+
+\begin{quote}
+\emph{The images will help you perform this task.}
+\end{quote}
+
+\begin{quote}
+\emph{The arrows will either be congruent (the center arrow is the same as the flanking arrows) or incongruent (the center arrow is different from the flanking arrows).
+Incongruent trials are typically harder because you need to ignore the flanking arrows, while the congruent trials are easier, because you do not need to ignore the flanking arrows.}
+\end{quote}
+
+\begin{quote}
+\emph{In the first block of the experiment, trials that include a chair (regardless of whether it is blue or green) will be mostly incongruent.
+That is, most of the trials that include a chair will be hard.}
+\end{quote}
+
+\begin{quote}
+\emph{This will be helpful to perform the task, so try to proactively use this information when you perform the task."}
+\end{quote}
 
@@
 
-The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be non-significant, .
-Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, .
-
-\hypertarget{estimating-reproducability-by-simulation-based-sensitivity--and-power-analyses}{%
-\section{Estimating reproducability by simulation-based sensitivity- and power-analyses}\label{estimating-reproducability-by-simulation-based-sensitivity--and-power-analyses}}
+The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be non-significant, \(F(1, 45) = 0.02\), \(\mathit{MSE} = 4,030.54\), \(p = .876\), \(\hat{\eta}^2_p = .001\), 90\% CI \([0\), \(0.04]\).
+Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 45) = 0.66\), \(\mathit{MSE} = 28.52\), \(p = .420\), \(\hat{\eta}^2_p = .014\), 90\% CI \([0\), \(0.11]\).
+
+\hypertarget{estimating-replicability-by-simulation-based-sensitivity--and-power-analyses}{%
+\section{Estimating replicability by simulation-based sensitivity- and power-analyses}\label{estimating-replicability-by-simulation-based-sensitivity--and-power-analyses}}
 
@@
 \includegraphics{manuscript_pretty_files/figure-latex/figure5-1.pdf}
-\caption{\label{fig:figure5}Results from Experiment 3 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent).
-Task-relevance was manipulated through explicit instructions.}
+\caption{\label{fig:figure5}Results from the simulation-based sensitivity and power-analyses.
+Figure A shows the sensitivity of our experimental design to detect a range of effect sizes for the context-specific proportion congruency (CSPC) effect with 50 (e.g., Experiments 2 and 3) and 150 (e.g., Experiment 1) participants.
+Figure B shows the sensitivity to detect the CSPC by context-type interaction with 50 participants per group (e.g., Experiment 1).
+Figures C and D show the corresponding power curves for the CSPC and CSPC by context-type effects across sample sizes.}
 \end{figure}
+
+In Experiment 1, we found no evidence for differences in the task-relevance effect across context-type.
+Similarly, Experiments 2 and 3 failed to find CSPC effects.
+To effectively draw inferences from these results, we need to assess the extent to which our experiments could have detected effects, if present.
+Although replicability has become an important and salient issue in Psychology at large (e.g., ), this issue has also arisen in the context-specific proportion congruency literature (e.g., Brosowsky Crump, Hutcheon speiler, TiCS).
+
+To address this issue in the current study---and to do so transparently---we conducted simulation-based power and sensitivity analyses (Maxwell, Kelley, and Raush, 2008; Brosowsky and Crump) to determine the range effect sizes our experimental design was sensitive to detect and the required sample sizes to detect them.
+We used a Monte Carlo simulation approach with a statistical model of the distributions that underlie the effect of interest (Maxwell, 2008).
+Rather than estimating power based on observed effect sizes from prior experiments (typically, over-estimates), we instead estimated the properties of the base reaction time distributions from our current data and sampled from these distributions using a Monte Carlo simulation approach to estimate the replication success rate across a range of effect sizes and sample sizes.
+
+We created the conflictPower R-package to conduct the Monte Carlo simulations (Crump and Brosowsky; Tics).
+The conflictPower package samples simulated reaction time data for subjects at the trial-level, given base reaction time distributions for the conflict and no-conflict conditions.
+To generate the base reaction time distributions, we fitted ex-Gaussian functions to the reaction time data from individual participants and averaged across all three experiments using the retimes R-package (XXXX).
+Using the extimated ex-Gaussian parameters, we used the conflictPower package to simulate the results across a range of effect and sample sizes, calculating the proportion of experiments (across \(10 000\) simulations) resulting in a p-value less than \(.05\) (see Figure 5; for a more detailed explanation of the sampling procedure see Crump and Brosowsky, 2019).
+
+First, the results of these analyses show that our experimental design was reasonably powered to detect CSPC effects.
+In particular, with 150 participants, we estimated 89\% power to detect effects as small 10 ms; With only 50 participants, we were still reasonably powered to detect CSPC effects as small as 15 ms at an estimated 78\%.
+Understandably, our design was not as sensitive to detecting changes the in the CSPC effect across conditions (in Experiment 1, for example).
+For instance, we estimated only 75\% power to detect the difference between a 20 ms and 0 ms CSPC effect with 50 participants per group.
+That is, the experimental design could detect the presence/absence of the CSPC effect moderately well, but likely does not reliably detect small changes in the CSPC effect across conditions.
+To reliably detect a 15 ms change in the CSPC effect, for example, we estimate would require 100 participants per group.
 

### 2019-09-30 data-analysis/analysis_E2.R

@@ -18,7 +18,7 @@ source("data-analysis/outlier_removal.R")
 load("data-analysis/raw_data_E2.Rda")
 load("data-analysis/demographics_E2.Rda")
 
-
+theme_set(theme_cowplot())
 # Find subs with < 75% accuracy
 low_acc <- raw_data_E2 %>%
   group_by(Subject,Condition,PC,Congruency) %>%
@@ -167,8 +167,8 @@ ACC.graph <- ggplot(ACC.Diff,aes(x=PC, y=Flanker,fill=PC))+
   theme(       legend.position=c(1,1),
                legend.justification = c(1,1),
                legend.direction = "horizontal",
-               legend.background = element_rect(colour = "black", fill = "white", size=1),
-               legend.box.background = element_rect(colour = "black"),
+               # legend.background = element_rect(colour = "black", fill = "white", size=1),
+               # legend.box.background = element_rect(colour = "black"),
                legend.margin = margin(t = .1, r = .10, b = .05, l = .1, unit = "cm"),
                legend.text = element_text(size = 8),
                legend.title = element_text(size = 8)

### 2019-09-30 data-analysis/analysis_E3.R

@@ -18,6 +18,7 @@ load("data-analysis/raw_data_E3.Rda")
 # load("data-analysis/demographics_E3.Rda")
 # demographics_E3$Subject <- demographics_E3$subnum
 
+theme_set(theme_cowplot())
 
 # Find subs with < 75% accuracy
 low_acc <- raw_data_E3 %>%
@@ -184,7 +185,7 @@ ACC.graph <- ggplot(ACC.Diff,aes(x=Task_Relevant_Context, y=Flanker,fill=Task_Re
   theme(       legend.position=c(1,1),
                legend.justification = c(1,1),
                legend.direction = "vertical",
-               legend.background = element_rect(colour = "black", fill = "white", size=1),
+               # legend.background = element_rect(colour = "black", fill = "white", size=1),
                #legend.box.background = element_rect(colour = "black"),
                legend.margin = margin(t = .1, r = .10, b = .05, l = .1, unit = "cm"),
                legend.text = element_text(size = 8),
@@ -200,7 +201,7 @@ ACC.graph <- ggplot(ACC.Diff,aes(x=Task_Relevant_Context, y=Flanker,fill=Task_Re
 figure4<-plot_grid(RT.graph,NULL,ACC.graph, 
                    nrow = 1, 
                    rel_widths = c(1, 0.05, 1),
-                   labels = c("A", "", "B"))
+                   labels = c("A.", "", "B."))
 
 #title <- ggdraw() + draw_label("Experiment 3", fontface='bold')
 #figure4<-plot_grid(title, figure4, ncol=1, rel_heights=c(0.1, 1)) # rel_heights values control title margins

### 2019-09-30 data-analysis/plot-power-simulation.R

@@ -1,9 +1,13 @@
 load(file="data-analysis/sim_effectSizes.Rda")
 
+theme_set(theme_cowplot())
 
 sim_effectSizes <- sim_effectSizes %>% filter(effect.size < 41)
+levels(sim_effectSizes$effect) <- c("CSPC x\nContext-Type", "CSPC (N = 50)","CSPC (N = 150)")
 
-plot.1 <- ggplot(sim_effectSizes[sim_effectSizes$effect != "CSPC x Condition",], aes(effect.size, prop.sig, color = effect)) + 
+
+
+plot.1 <- ggplot(sim_effectSizes[sim_effectSizes$effect != levels(sim_effectSizes$effect)[1],], aes(effect.size, prop.sig, color = effect)) + 
   geom_smooth( aes(color = effect), se = FALSE, method = "gam", formula = y ~ s(log(x)))+
   geom_point(aes(x = effect.size, y = prop.sig, color=effect, shape = effect), size = 2) +
   geom_vline(xintercept = 20, linetype = "dashed") +
@@ -22,8 +26,7 @@ plot.1 <- ggplot(sim_effectSizes[sim_effectSizes$effect != "CSPC x Condition",],
         legend.title = element_text(size = 8)
   ) 
 
-sim_effectSizes <- sim_effectSizes[sim_effectSizes$effect == "CSPC x Condition",]
-levels(sim_effectSizes$effect) <- c("CSPC x\nCondition", "CSPC (N = 50)","CSPC (N = 150)")
+sim_effectSizes <- sim_effectSizes[sim_effectSizes$effect == levels(sim_effectSizes$effect)[1],]
 
 plot.2 <- ggplot(sim_effectSizes, aes(effect.size, prop.sig, color = effect)) + 
   geom_smooth( aes(color = effect), se = FALSE, method = "gam", formula = y ~ s(log(x)))+
@@ -82,7 +85,7 @@ plot.4 <- ggplot(sim_sampleSizes[sim_sampleSizes$effect != "PC",], aes(sample.si
   geom_smooth(aes(color = effect.size), se = FALSE, method = "gam", formula = y ~ s(log(x)), size = .9) +
   geom_point(aes(color = effect.size, shape = effect.size), size = 2) +
   geom_hline(yintercept = .8, linetype ="dashed") +
-  labs(y = "Proportion p < .05", x = "Sample Size", color = "CSPC x\nCondition Effect", shape =  "CSPC x\nCondition Effect") +
[…]

### 2019-10-01 manuscript_pretty.Rmd
editing

@@
 
-The key finding was that the congruency effects for the frequency unbiased items were significantly larger when the low-conflict context was made task-relevant as compared to when the high-conflict context was made task-relevant.
+The key finding, in Experiment 1, was that congruency effects for the frequency unbiased items were significantly larger when the low-conflict context was made task-relevant as compared to when the high-conflict context was made task-relevant.
 This result is consistent with prior CSPC effects and, like the previous work, suggests that the context cues triggered rapid adjustments to attentional control [@crump_flexibility_2009].
@@
 
-Another key result of this study concerned the different stimuli used as context cues.
+In Experiment 2, we found that participants did not spontaneously learn the associations between proportion congruency and context-cues without the secondary counting task.
+This replicates previous work () and demonstrates further that task-relevance is necessary for establishing associations between contexts and attentional priorities.
+Additionally, in Experiment 3 explicit instructions to make use of the cues also failed to produce context-specific effects.
+This result also tracks well with previous work that found instruction manipulations could successfully produce list-wide proportion congruency effects, but not item-specific () or context-specific () effects.
+
+Another key result of this study concerned the different stimuli used as context cues in Experiment 1.
 Across the three conditions, we varied the type of context image and dimensions.
@@
 Furthermore, CSPC effects were present even when using non-repeating images which suggests that context-dependency did not rely on image-specific associations but higher-order, learned categorical information.
+We should also note an important limitation is that the experimental design, while moderately powered to detect the presence versus absence of the CSPC effect between groups, it was likely under-powered to detect small changes in the CSPC effect (see the Replicability section above).
 

### 2019-10-08 manuscript_pretty.Rmd
so close

@@
 In short, we found that making new contextual information task-relevant caused participants to ignore a previously learned context-attention association and adopt a new context-specific control strategy; all without changing the experimental stimuli.
-This result suggests that task-relevance is a key determinant of context-specific control."
+Furthermore, we found participants did not spontaneously learn about context-specific proportion manipulations and explicit instructions insufficient for producing context-specific effects.
+These results suggests that task-relevance is a key determinant of context-specific control."
 
@@
 source("data-analysis/table1.R")
+source("data-analysis/table2.R")
+source("data-analysis/table3.R")
 source("data-analysis/analysis_E1_Exploratory.R")
@@
 Typically, a high proportion congruent experiment produces large congruency effects, whereas a low proportion congruent experiment produces small congruency effects [@logan_when_1979; @lowe_selective_1982; @west_effects_1998].
-This result is usually  explained as strategic control, where participants increase attentional control under high-conflict demands and relax attentional control under low-conflict demands [@logan_attention_1980; @logan_strategies_1984; @logan_when_1979; @lowe_selective_1982].
+This result is usually  explained as strategic control, where participants increase attentional control under high conflict demands and relax attentional control under low conflict demands [@logan_attention_1980; @logan_strategies_1984; @logan_when_1979; @lowe_selective_1982].
 Recent work however, has demonstrated that attentional control is not only adjusted by top-down regulation, but can also be triggered automatically by environmental cues [@brosowsky_memory-guided_2018; @bugg_support_2012; @egner_creatures_2014; @fischer_predicting_2015; @king_priming_2012; @mayr_outsourcing_2007].
@@
 The current study addresses two related issues: First, how is attentional control resolved when multiple contextual features could be used as cues?
-And second, what determines the expression of previously learned attentional associations?
+And second, what determines the expression and/or suppression of previously learned attentional associations?
 
-Real-world environments are complex and contain many potential context cues.
-For instance, consider someone writing in a coffee shop.
-The coffee shop is a rich environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which we have different experiences with and afford different learned associations.
-Although a laptop could cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
+Real-world environments are complex and contain many potential cues for directing attention.
+For instance, a coffee shop is a rich environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which someone could have different experiences with and afford different learned associations.
+A laptop for example, could cue attentional processing helpful for writing while other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
 Given that all of these cues are available to set attentional priorities, what determines which associative relationships will be used to guide attention?
 On the one hand, context-based retrieval of attentional priorities might be completely obligatory: the mere presence of learned cues might trigger attention in a ballistic manner [e.g., @schneider_controlled_1977; @shiffrin_controlled_1977].
-A writer's attention in this case would be at the mercy of the environment and attention is guided by the strongest association.
+Attention in this case would be at the mercy of the environment and attention is guided by the strongest association.
 On the other hand, our current task-goals might constrain the expression of previously learned associations.
-The writer's current goals may allow the laptop to take priority over other environmental cues that are irrelevant to the task at hand.
+If someone sits down to write in the coffee shope, their current goals may allow the laptop to take priority over other environmental cues that are irrelevant to the task at hand.
 
-Historically, perspectives of automaticity and attentional control have emphasized the role of practice and likened the learning process to the development of automaticity in skill-learning [@schneider_controlled_1977; @shiffrin_controlled_1977; @logan_toward_1988; @logan_attention_1992].
+Historically, perspectives of automaticity and attentional control have emphasized the role of practice and likened the learning of attentional associations to the development of automaticity in skill-learning [@schneider_controlled_1977; @shiffrin_controlled_1977; @logan_toward_1988; @logan_attention_1992].
 Under this view, forming an association requires many repeated experiences pairing a cue with a set of attentional priorities.
@@
 Learned associations are therefore ballistic, difficult to suppress, and difficult to unlearn [e.g., @schneider_controlled_1977; @shiffrin_controlled_1977; @posner_attention_1975; @posner_facilitation_1975; @treisman_contextual_1960; @treisman_selective_1964; @treisman_strategies_1969].
-This view is reflected in modern work on contextual cuing where it is assumed that learned associations require practice [e.g., @lehle_fly_2008; @crump_learning_2016], form without awareness or intention, and are triggered automatically by the mere presence of the cue [@crump_context-specific_2006; @crump_contextual_2010; @crump_context-specific_2008; @king_priming_2012; @reuss_unconscious_2014; though, see @brosowsky_context-specific_2016].
+This view is often referenced in modern work on contextual cuing where it is assumed that learned associations require practice [e.g., @lehle_fly_2008; @crump_learning_2016], form without awareness or intention, and are triggered automatically by the mere presence of the cue [@crump_context-specific_2006; @crump_contextual_2010; @crump_context-specific_2008; @king_priming_2012; @reuss_unconscious_2014; though, see @brosowsky_context-specific_2016].
 
-Memory-based perspectives however, take a more nuanced view [@norman_memory_1969; @norman_memory_1976; @abrahamse_grounding_2016; @brosowsky_memory-guided_2018; @crump_learning_2016; @egner_creatures_2014].
-Here, practice is only important to the extent that it improves memory retrieval.
-Learning an association is the process of encoding experiences where attentional priorities and cues co-occur.
+An alternative view---the memory-based perspective---takes a more nuanced view [@norman_memory_1969; @norman_memory_1976; @abrahamse_grounding_2016; @brosowsky_memory-guided_2018; @crump_learning_2016; @egner_creatures_2014].
+Here, practice is only important to the extent that it improves memory encoding and retrieval.
+Learning an association can be thought of as the process of encoding experiences where attentional priorities and cues co-occur.
 The expression of previously learned associations however, is dictated by memory retrieval---a similarity-based, cue-driven process [e.g., @jacoby_interpreting_1978; @hintzman_minerva_1984; @hintzman_schema_1986; @hintzman_judgments_1988].
@@
 If this is the case, then a previously learned association should be easily ignored if that feature was made irrelevant to the task because that feature would no longer contribute to memory-retrieval.
-Furthermore, it would suggest that the mere presence of a cue is not sufficient for automatically directing attention, but instead requires some task-integration.
+Furthermore, it would suggest that the mere presence of a cue is not sufficient for automatically directing attention, but instead requires task-integration.
 
-Recent work lends some credence to the possibility that task-relevance is necessary for establishing new context-attention associations.
+Recent work on contextual cueing suggests that task-relevance is important for establishing new context-attention associations.
 Crump, Vaquero, & Milliken [-@crump_context-specific_2008] used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe.
@@
 
+```{r figure1, echo=FALSE, fig.width=6.7,fig.height=4.51, fig.cap='(ref:figure1)'}
+#, out.width="\\textwidth", fig.env="figure*"
+knitr::include_graphics("images/Task.jpg")
+```
+
+(ref:figure1) Illustration of the stimuli and trial construction.
+Figure 1A shows the feature dimensions for each of the conditions.
+Figure 1B shows an example trial stimulus containing both the context and flanker images.
+Figure 1C shows an example of how feature dimensions could have been assigned to each proportion congruency (PC) condition, and an example of the secondary task assignments.
+The secondary task order, as well as the feature and congruency assignments were all randomized for each participant.
+
 Prior work suggests that the task-relevance of contextual information could be important for establishing new associations between context cues and attentional priorities.
 Simply put, CSPC effects tend to emerge when context cues are somehow made relevant to the task, but do not when made irrelevant [@canadas_social_2013; @crump_context-specific_2006; @crump_context-specific_2008].
-However, what determines the learning and expression of context-attention associations remains unclear.
+However, what determines the  expression of previously learned context-attention associations remains unclear.
 In the current study, we examined whether manipulating task-relevance would allow participants to ignore a previously learned association and adopt a new context-specific control strategy.
@@
 The critical measure of interest is the congruency effect produced in the frequency unbiased context.
-If, on the one hand, task-relevance has no impact on the use of context-attention associations we would expect no differences between the congruency effects when the high-conflict context dimension is made task-relevant or the low-conflict context dimension is made task-relevant.
+If, on the one hand, task-relevance has no impact on the use of context-attention associations we would expect no differences between the congruency effects when the high conflict context dimension is made task-relevant or the low conflict context dimension is made task-relevant.
 This could occur because all three contexts are treated as individual contexts throughout the whole experiment [e.g., @canadas_social_2013].
@@
 On other hand, task-relevance may dictate the expression of previously learned associations.
-In this case, we would expect smaller congruency effects when the high-conflict context dimension is made task-relevant as compared to when the low-conflict context dimension is made task-relevant.
+In this case, we would expect smaller congruency effects when the high conflict context dimension is made task-relevant as compared to when the low conflict context dimension is made task-relevant.
 This would demonstrate that participants were able to ignore a previously learned association and adopt a new context-specific control strategy.
@@
 # Methods
-```{r figure1, echo=FALSE, fig.width=6.7,fig.height=4.51, fig.cap='(ref:figure1)'}
-#, out.width="\\textwidth", fig.env="figure*"
-knitr::include_graphics("images/Task.jpg")
-```
-
-(ref:figure1) Illustration of the stimuli and trial construction.
-Figure 1A shows the feature dimensions for each of the conditions.
-Figure 1B shows an example trial stimulus containing both the context and flanker images.
-Figure 1C shows an example of how feature dimensions could have been assigned to each proportion congruency (PC) condition, and an example of the secondary task assignments.
-The secondary task order, as well as the feature and congruency assignments were all randomized for each participant.
 
@@
 ## Design 
-Experiment 1 used a 2x2x3 mixed design with task-relevant context (0% and 100%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+Experiment 1 used a 2x2x3 mixed design with task-relevant context (high conflict and low conflict) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
 
@@
 ## Data Analysis
+
 All analyses in this and the following experiments were performed in R [@r_software_2019] using a variety of R packages and resources [@r_wickham_ggplot2_2016; @r_wickham_dplyr_2019; @r_papaja_2018; @r_cowplot_2019].
@@
 # Results
+
 Participants with mean error rates greater than 25% were excluded from the analyses, eliminating `r N_subjects_removed` participants.
@@
 
+```{r echo=FALSE, results='asis'}
+#, fig.align="center", fig.cap="" ,out.width="\\textwidth", fig.env="figure*"
+cat(TR_Table)
+
+#knitr::include_graphics("images/table1.pdf")
+```
+
 ## Exploratory analyses: Order effects
@@
 ```
-
-(ref:figure2b) Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent) and phase order (100% to 0% PC versus 0% to 100% PC).
-Figure A shows a summary of the data containing all trials, whereas Figure B shows a summary of the data restricted to the 24 trials immediately before and 24 trials immediately after the transition.
-In both cases, the interaction was non-significant ($p > .05$) and Bayesian analyses resulted in moderate evidence in favor of the null hypothesis ($\mathrm{BF}_{\textrm{01}} > 3$).
 
@@
 
-```{r echo=FALSE, results='asis'}
-#, fig.align="center", fig.cap="" ,out.width="\\textwidth", fig.env="figure*"
-cat(TR_Table)
-
-#knitr::include_graphics("images/table1.pdf")
-```
-
-<!-- ```{r echo=FALSE, echo = FALSE, warning = FALSE, message=FALSE, results='asis', out.width="\\textwidth"} -->
-<!-- #print latex table -->
-<!-- cat(TR_Table) -->
-<!-- ``` -->
-
 # Experiment 2
 
-In Experiment 1, we found that manipulating the task-relevance of a shared contextual feature was associated in predictable changes in context-specific proportion congruency effects for frequency unbiased context items; Namely, larger congruency effects when the context was associated with low conflict than when the context was associated with high conflict.
-This suggests that participants learned the association between context and conflict-level in the first block (despite multiple, competing cues), and subsequently ignored that association in the second block to learn a new association.
+In Experiment 1, we found that manipulating the task-relevance of a shared contextual feature was associated in predictable changes in context-specific proportion congruency effects for frequency unbiased context items.
+Namely, we found larger congruency effects when the context was associated with low conflict than when the context was associated with high conflict.
+This suggests that participants learned the association between context and conflict-level in the first block (despite multiple conetxt cues), and subsequently ignored that association in the second block to learn a new association.
 Task-relevance then, may not just be important for establishing new associations [e.g.,@crump_flexibility_2009] but also important for determining which learned associations are expressed in the present moment.
@@
 Experiment 2, therefore, serves as a control experiment to test these two assumptions directly.
-Experiment 2 is identical to Experiment 1 with two important changes: First, we removed the counting task, giving no explicit instructions about how to use the context cues; We only informed participants that images would be present throughout the task.
+Experiment 2 is identical to Experiment 1 with two important changes: First, we removed the counting task, giving no explicit instructions about how to use the context cues.
+We only informed participants that images would be present throughout the task.
 This allowed us to determine if there was any systematic effect of biased items on the unbiased items absent the counting task.
@@
 
+```{r figure3, echo=FALSE, fig.width=3.25, fig.height=4, fig.cap='(ref:figure3)'}
+#print figure 3
+#source: data-analysis/analysis_E2.R
+figure3
+```
+
+(ref:figure3) Results from Experiment 2 showing congruency effects (incongruent - congruent) across proportion congruency (25%, 75%, and 100% PC) in reaction times (left) and error rates (right).
+
 # Results
@@
 
-```{r figure3, echo=FALSE, fig.width=3.25, fig.height=4, fig.cap='(ref:figure3)'}
-#print figure 3
-#source: data-analysis/analysis_E2.R
-figure3
+```{r echo=FALSE, results='asis'}
+#, fig.align="center", fig.cap="" ,out.width="\\textwidth", fig.env="figure*"
+cat(TR_Table_2)
+
+#knitr::include_graphics("images/table1.pdf")
 ```
-
-(ref:figure3) Results from Experiment 2 showing congruency effects (incongruent - congruent) across proportion congruency (25%, 75%, and 100% PC) in reaction times (left) and error rates (right).
 
@@
 
-In the current study, we have been examining the importance of task-relevance for the contextual recruitment of selective attention.
+The goal of the current study has been to examine the importance of task-relevance for the contextual recruitment of selective attention.
 In Experiment 1, we found that task-relevance allowed participants to exploit context cues in the presence of a competing, contradictory cue and subsequently ignore a previously learned association in favor of a different context cue.
@@
 The evidence thus far suggests that context-cues, rather than being irrelevant to the task (as their namesake would suggest), need to be integrated into the task-representation to guide attentional control.
-There is some evidence that instructions alone can be sufficient to produce list-wide proportion congruency effects, though not item-specific proportion congruency effects (e.g., Entel et al., 2014; though, see Desender, 2018) and not context-specific proportion congruency effects (e.g., ).
-Explicit instructions however, are another way of making context-cues relevant to the on-going task and could serve the same purpose as the counting task---although, instructions are likely a much weaker manipulation than the counting task.
+There is some evidence that instructions alone can be sufficient to produce list-wide proportion congruency effects, though not item-specific proportion congruency effects [@entel_proportion_2014; @desender_different_2018] and not context-specific proportion congruency effects [@crump_flexibility_2009].
+Explicit instructions however, are another way of making context-cues relevant to the on-going task and could serve the same purpose as the counting task.
 In Experiment 3, we test whether participants are able to explicitly use the context-cues to guide attentional control through an instruction manipulation.
@@
 The primary question of interest was whether the task-relevance of context features (made relevant through explicit task instructions) associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items.
-Mean correct RTs and mean error rates from frequency unbiased trials were submitted to an analysis of variance (ANOVA) with task-relevant context (0% and 100% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors.
+Mean correct RTs and mean error rates from frequency unbiased trials were submitted to an analysis of variance (ANOVA) with task-relevant context (0% and 100% PC) as the within-subject factors.
 
-The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be non-significant, `r RT_ANOVA_E3$Task_Relevant_Context`.
-Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA_E3$Task_Relevant_Context`.
+The results of the RT analysis revealed the effect of task-relevance to be non-significant, `r RT_ANOVA_E3$Task_Relevant_Context`, with moderate evidence in favor of the null, `r RT_BF_E3[[1]]`.
+Similarly, the corresponding error analysis also resulted in a non-significant effect of task-relevance, `r ACC_ANOVA_E3$Task_Relevant_Context`, with moderate evidence in favor of the null, `r ACC_BF_E3[[1]]`.
+
+```{r echo=FALSE, results='asis'}
+#, fig.align="center", fig.cap="" ,out.width="\\textwidth", fig.env="figure*"
+cat(TR_Table_3)
+
+#knitr::include_graphics("images/table1.pdf")
+```
 
@@
 
-```{r figure5, echo=FALSE, fig.cap='(ref:figure5)', fig.width=6.875, fig.height= 5}
+In Experiment 1, we found no evidence for differences in the task-relevance effect across context-type.
+Similarly, Experiments 2 and 3 failed to find CSPC effects.
+To determine the limitations in our ability to draw inferences from these results, we need to assess the extent to which our experiments could have detected effects, if present.
+Although replicability has become an important and salient issue in Psychology at large [e.g., @camerer_evaluating_2018; @open_science_collaboration_estimating_2015], this issue has also arisen in the context-specific proportion congruency literature [@crump_reproducing_2017; @hutcheon_limits_2017; ].
+
+To address this issue in the current study---and to do so transparently---we conducted simulation-based power and sensitivity analyses [] to determine the range effect sizes our experimental design was sensitive to detect and the required sample sizes to detect a range of effects.
+We used a Monte Carlo simulation approach with a statistical model of the distributions that underlie the effect of interest (Maxwell, 2008).
+Rather than estimating power based on observed effect sizes from prior experiments (typically, over-estimates), we instead estimated the properties of the base reaction time distributions from our current data and sampled from these distributions using a Monte Carlo simulation approach to estimate the replication success rate across a range of effect sizes and sample sizes.
+
+We created the conflictPower R-package to conduct the Monte Carlo simulations [@r_conflictpower_2019].
+The conflictPower package samples simulated reaction time data for subjects at the trial-level using base reaction time distributions for the conflict and no-conflict conditions.
+To generate the base reaction time distributions, we fitted ex-Gaussian functions to the reaction time data from individual participants and averaged across all three experiments using the retimes R-package [@r_retimes_2013].
+We then used the conflictPower package to simulate the results across a range of effect and sample sizes, calculating the proportion of experiments, across $10 000$ simulations, resulting in a p-value less than $.05$ (see Figure 5; for a more detailed explanation of the sampling procedure see Crump and Brosowsky, 2019).
+
+First, the results of these analyses show that our experimental design was reasonably powered to detect CSPC effects.
+In particular, with 150 participants, we estimated 89% power to detect effects as small 10 ms; With only 50 participants, we were still reasonably powered to detect CSPC effects as small as 15 ms at an estimated 78%.
+Understandably, our design was not as sensitive to detecting changes in the CSPC effect between groups (Experiment 1, for example).
+We estimated only 75% power to detect the difference between a 20 ms and 0 ms CSPC effect with 50 participants per group.
+That is, the experimental design could detect the presence/absence of the CSPC effect moderately well, but likely does not reliably detect small changes in the CSPC effect across conditions.
+To reliably detect a 15 ms change in the CSPC effect at roughly 80% power, for example, we estimate would require 100 participants per group.
+
+```{r figure5, echo=FALSE, fig.cap='(ref:figure5)', fig.width=6.875, fig.height= 5, out.width = "\\textwidth", fig.pos = "!h"}
 #print figure 3
@@
 
-In Experiment 1, we found no evidence for differences in the task-relevance effect across context-type.
-Similarly, Experiments 2 and 3 failed to find CSPC effects.
-To effectively draw inferences from these results, we need to assess the extent to which our experiments could have detected effects, if present.
-Although replicability has become an important and salient issue in Psychology at large (e.g., ), this issue has also arisen in the context-specific proportion congruency literature (e.g., Brosowsky Crump, Hutcheon speiler, TiCS).
-
-To address this issue in the current study---and to do so transparently---we conducted simulation-based power and sensitivity analyses (Maxwell, Kelley, and Raush, 2008; Brosowsky and Crump) to determine the range effect sizes our experimental design was sensitive to detect and the required sample sizes to detect them.
-We used a Monte Carlo simulation approach with a statistical model of the distributions that underlie the effect of interest (Maxwell, 2008).
-Rather than estimating power based on observed effect sizes from prior experiments (typically, over-estimates), we instead estimated the properties of the base reaction time distributions from our current data and sampled from these distributions using a Monte Carlo simulation approach to estimate the replication success rate across a range of effect sizes and sample sizes.
-
-We created the conflictPower R-package to conduct the Monte Carlo simulations (Crump and Brosowsky; Tics).
-The conflictPower package samples simulated reaction time data for subjects at the trial-level, given base reaction time distributions for the conflict and no-conflict conditions.
-To generate the base reaction time distributions, we fitted ex-Gaussian functions to the reaction time data from individual participants and averaged across all three experiments using the retimes R-package (XXXX).
-We then used the conflictPower package to simulate the results across a range of effect and sample sizes, calculating the proportion of experiments, across $10 000$ simulations, resulting in a p-value less than $.05$ (see Figure 5; for a more detailed explanation of the sampling procedure see Crump and Brosowsky, 2019).
-
-First, the results of these analyses show that our experimental design was reasonably powered to detect CSPC effects.
-In particular, with 150 participants, we estimated 89% power to detect effects as small 10 ms; With only 50 participants, we were still reasonably powered to detect CSPC effects as small as 15 ms at an estimated 78%.
-Understandably, our design was not as sensitive to detecting changes the in the CSPC effect across conditions (in Experiment 1, for example).
-We estimated only 75% power to detect the difference between a 20 ms and 0 ms CSPC effect with 50 participants per group.
-That is, the experimental design could detect the presence/absence of the CSPC effect moderately well, but likely does not reliably detect small changes in the CSPC effect across conditions.
-To reliably detect a 15 ms change in the CSPC effect at roughly 80% power, for example, we estimate would require 100 participants per group.
-
 # General Discussion
@@
 
-The key finding, in Experiment 1, was that congruency effects for the frequency unbiased items were significantly larger when the low-conflict context was made task-relevant as compared to when the high-conflict context was made task-relevant.
+The key finding was that congruency effects for the frequency unbiased items were significantly larger when the low conflict context was made task-relevant as compared to when the high conflict context was made task-relevant.
 This result is consistent with prior CSPC effects and, like the previous work, suggests that the context cues triggered rapid adjustments to attentional control [@crump_flexibility_2009].
@@
 Similarly, @canadas_social_2013 eliminated the CSPC effect by making the contextual cue effectively unrelated to the task.
-These studies suggest that task-relevance plays an important role in establishing associations between contextual information and attentional priorities to produce CSPC effects.
+These studies suggest that task-relevance plays an important role in establishing new associations between contextual information and attentional priorities to produce CSPC effects.
 Our finding extends this work in two important ways.
@@
 
-In light of prior work, we take this as evidence that the contextual recruitment of selective attention, although likely implicit, is not obligatory [e.g., @brosowsky_context-specific_2016], requiring that environmental information be incorporated into the task representation.
-Similarly, there appears to be flexibility in which environmental features are selected and used to guide attention, which can be rapidly updated depending on the task-relevance of those features.
+In Experiment 2, we found that participants did not spontaneously learn the associations between proportion congruency and context-cues without the secondary counting task.
+This replicates previous work [@crump_context-specific_2008] and demonstrates further that task-relevance is necessary for establishing associations between contexts and attentional priorities.
+Moreover, this should serve as a cautionary tale for future work using the context-specific proportion congruent design.
+Prior studies have had difficulty replicating CSPC effects using the typical location-based CSPC design.
+The inconsistency of participants to learn associations between attentional priorities and location cues might arise because location is a poor cue in terms of task-relevance.
+Additionally, in Experiment 3 explicit instructions to make use of the cues also failed to produce context-specific effects.
+This result also tracks well with previous work that found instruction manipulations could successfully produce list-wide proportion congruency effects, but not item-specific [@entel_proportion_2014] or context-specific [@crump_context-specific_2008] effects.
+Explicit instructions are another method for inducing task-relevance further illustrating that weak task-relevance manipulations are not sufficient for producing CSPC effects.
+
+In light of prior work, we take these results as evidence that the contextual recruitment of selective attention, although likely implicit, is not obligatory [e.g., @brosowsky_context-specific_2016], requiring that environmental information be incorporated into the task representation.
+Similarly, there appears to be flexibility in which environmental features are selected and used to guide attention, which can be rapidly updated depending on the task-relevance of those features (for a similar perspective, see @hommel_event_2004; @hommel_theory_2019).
 Such a result lends some insight into how context-specific control might operate in more complex, real-world environments, where there is an over-abundance of environmental features that afford many different learned associations.
@@
 
-In Experiment 2, we found that participants did not spontaneously learn the associations between proportion congruency and context-cues without the secondary counting task.
-This replicates previous work () and demonstrates further that task-relevance is necessary for establishing associations between contexts and attentional priorities.
-Additionally, in Experiment 3 explicit instructions to make use of the cues also failed to produce context-specific effects.
-This result also tracks well with previous work that found instruction manipulations could successfully produce list-wide proportion congruency effects, but not item-specific () or context-specific () effects.
-
-Another key result of this study concerned the different stimuli used as context cues in Experiment 1.
+Finally, another key result of this study concerned the different stimuli used as context cues in Experiment 1.
 Across the three conditions, we varied the type of context image and dimensions.
@@
 
+\newpage
+
 # References

### 2019-10-08 manuscript_pretty.tex
so close

@@
 In short, we found that making new contextual information task-relevant caused participants to ignore a previously learned context-attention association and adopt a new context-specific control strategy; all without changing the experimental stimuli.
-This result suggests that task-relevance is a key determinant of context-specific control.
+Furthermore, we found participants did not spontaneously learn about context-specific proportion manipulations and explicit instructions insufficient for producing context-specific effects.
+These results suggests that task-relevance is a key determinant of context-specific control.
 
@@
 Typically, a high proportion congruent experiment produces large congruency effects, whereas a low proportion congruent experiment produces small congruency effects (Logan \& Zbrodoff, 1979; Lowe \& Mitterer, 1982; West \& Baylis, 1998).
-This result is usually explained as strategic control, where participants increase attentional control under high-conflict demands and relax attentional control under low-conflict demands (Logan, 1980; Logan \& Zbrodoff, 1979; Logan, Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer, 1982).
+This result is usually explained as strategic control, where participants increase attentional control under high conflict demands and relax attentional control under low conflict demands (Logan, 1980; Logan \& Zbrodoff, 1979; Logan, Zbrodoff, \& Williamson, 1984; Lowe \& Mitterer, 1982).
 Recent work however, has demonstrated that attentional control is not only adjusted by top-down regulation, but can also be triggered automatically by environmental cues (Brosowsky \& Crump, 2018; Bugg \& Crump, 2012; Egner, 2014; Fischer \& Dreisbach, 2015; King, Korb, \& Egner, 2012; Mayr \& Bryck, 2007).
@@
 The current study addresses two related issues: First, how is attentional control resolved when multiple contextual features could be used as cues?
-And second, what determines the expression of previously learned attentional associations?
-
-Real-world environments are complex and contain many potential context cues.
-For instance, consider someone writing in a coffee shop.
-The coffee shop is a rich environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which we have different experiences with and afford different learned associations.
-Although a laptop could cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
+And second, what determines the expression and/or suppression of previously learned attentional associations?
+
+Real-world environments are complex and contain many potential cues for directing attention.
+For instance, a coffee shop is a rich environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which someone could have different experiences with and afford different learned associations.
+A laptop for example, could cue attentional processing helpful for writing while other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
 Given that all of these cues are available to set attentional priorities, what determines which associative relationships will be used to guide attention?
 On the one hand, context-based retrieval of attentional priorities might be completely obligatory: the mere presence of learned cues might trigger attention in a ballistic manner (e.g., Schneider \& Shiffrin, 1977; Shiffrin \& Schneider, 1977).
-A writer's attention in this case would be at the mercy of the environment and attention is guided by the strongest association.
+Attention in this case would be at the mercy of the environment and attention is guided by the strongest association.
 On the other hand, our current task-goals might constrain the expression of previously learned associations.
-The writer's current goals may allow the laptop to take priority over other environmental cues that are irrelevant to the task at hand.
-
-Historically, perspectives of automaticity and attentional control have emphasized the role of practice and likened the learning process to the development of automaticity in skill-learning (Logan, 1988, 1992; Schneider \& Shiffrin, 1977; Shiffrin \& Schneider, 1977).
+If someone sits down to write in the coffee shope, their current goals may allow the laptop to take priority over other environmental cues that are irrelevant to the task at hand.
+
+Historically, perspectives of automaticity and attentional control have emphasized the role of practice and likened the learning of attentional associations to the development of automaticity in skill-learning (Logan, 1988, 1992; Schneider \& Shiffrin, 1977; Shiffrin \& Schneider, 1977).
 Under this view, forming an association requires many repeated experiences pairing a cue with a set of attentional priorities.
@@
 Learned associations are therefore ballistic, difficult to suppress, and difficult to unlearn (e.g., Schneider \& Shiffrin, 1977; Posner \& Snyder, 1975a, 1975b; Shiffrin \& Schneider, 1977; Treisman, 1960, 1964, 1969).
-This view is reflected in modern work on contextual cuing where it is assumed that learned associations require practice (e.g., Lehle \& Hübner, 2008; Crump, 2016), form without awareness or intention, and are triggered automatically by the mere presence of the cue (Crump et al., 2006; Crump \& Logan, 2010; Crump, Vaquero, \& Milliken, 2008; King et al., 2012; Reuss, Desender, Kiesel, \& Kunde, 2014; though, see Brosowsky \& Crump, 2016).
-
-Memory-based perspectives however, take a more nuanced view (Abrahamse et al., 2016; Brosowsky \& Crump, 2018; Crump, 2016; Egner, 2014; Norman, 1969, 1976).
-Here, practice is only important to the extent that it improves memory retrieval.
-Learning an association is the process of encoding experiences where attentional priorities and cues co-occur.
+This view is often referenced in modern work on contextual cuing where it is assumed that learned associations require practice (e.g., Lehle \& Hübner, 2008; Crump, 2016), form without awareness or intention, and are triggered automatically by the mere presence of the cue (Crump et al., 2006; Crump \& Logan, 2010; Crump, Vaquero, \& Milliken, 2008; King et al., 2012; Reuss, Desender, Kiesel, \& Kunde, 2014; though, see Brosowsky \& Crump, 2016).
+
+An alternative view---the memory-based perspective---takes a more nuanced view (Abrahamse et al., 2016; Brosowsky \& Crump, 2018; Crump, 2016; Egner, 2014; Norman, 1969, 1976).
+Here, practice is only important to the extent that it improves memory encoding and retrieval.
+Learning an association can be thought of as the process of encoding experiences where attentional priorities and cues co-occur.
 The expression of previously learned associations however, is dictated by memory retrieval---a similarity-based, cue-driven process (e.g., Jacoby, 1978; Hintzman, 1984, 1986, 1988).
@@
 If this is the case, then a previously learned association should be easily ignored if that feature was made irrelevant to the task because that feature would no longer contribute to memory-retrieval.
-Furthermore, it would suggest that the mere presence of a cue is not sufficient for automatically directing attention, but instead requires some task-integration.
-
-Recent work lends some credence to the possibility that task-relevance is necessary for establishing new context-attention associations.
+Furthermore, it would suggest that the mere presence of a cue is not sufficient for automatically directing attention, but instead requires task-integration.
+
+Recent work on contextual cueing suggests that task-relevance is important for establishing new context-attention associations.
 Crump, Vaquero, \& Milliken (2008) used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe.
@@
 
+\begin{figure}
+\centering
+\includegraphics{images/Task.jpg}
+\caption{\label{fig:figure1}Illustration of the stimuli and trial construction.
+Figure 1A shows the feature dimensions for each of the conditions.
+Figure 1B shows an example trial stimulus containing both the context and flanker images.
+Figure 1C shows an example of how feature dimensions could have been assigned to each proportion congruency (PC) condition, and an example of the secondary task assignments.
+The secondary task order, as well as the feature and congruency assignments were all randomized for each participant.}
+\end{figure}
+
 Prior work suggests that the task-relevance of contextual information could be important for establishing new associations between context cues and attentional priorities.
 Simply put, CSPC effects tend to emerge when context cues are somehow made relevant to the task, but do not when made irrelevant (Cañadas et al., 2013; Crump et al., 2006, 2008).
-However, what determines the learning and expression of context-attention associations remains unclear.
+However, what determines the expression of previously learned context-attention associations remains unclear.
 In the current study, we examined whether manipulating task-relevance would allow participants to ignore a previously learned association and adopt a new context-specific control strategy.
@@
 The critical measure of interest is the congruency effect produced in the frequency unbiased context.
-If, on the one hand, task-relevance has no impact on the use of context-attention associations we would expect no differences between the congruency effects when the high-conflict context dimension is made task-relevant or the low-conflict context dimension is made task-relevant.
+If, on the one hand, task-relevance has no impact on the use of context-attention associations we would expect no differences between the congruency effects when the high conflict context dimension is made task-relevant or the low conflict context dimension is made task-relevant.
 This could occur because all three contexts are treated as individual contexts throughout the whole experiment (e.g., Cañadas et al., 2013).
@@
 
-\begin{figure}
-\centering
-\includegraphics{images/Task.jpg}
-\caption{\label{fig:figure1}Illustration of the stimuli and trial construction.
-Figure 1A shows the feature dimensions for each of the conditions.
-Figure 1B shows an example trial stimulus containing both the context and flanker images.
-Figure 1C shows an example of how feature dimensions could have been assigned to each proportion congruency (PC) condition, and an example of the secondary task assignments.
-The secondary task order, as well as the feature and congruency assignments were all randomized for each participant.}
-\end{figure}
-
 \hypertarget{participants}{%
@@
 
-Experiment 1 used a 2x2x3 mixed design with task-relevant context (0\% and 100\%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+Experiment 1 used a 2x2x3 mixed design with task-relevant context (high conflict and low conflict) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
 
@@
 Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant and effects did not vary across context-type, corroborating the results of the reaction time analysis.
-
-\hypertarget{exploratory-analyses-order-effects}{%
-\subsection{Exploratory analyses: Order effects}\label{exploratory-analyses-order-effects}}
-
-Previous work has shown that shifting between list-wide proportion congruent phases produced asymmetrical effects.
-Abrahamse, Duthoo, Notebaert, and Risko (2013) found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects.
-The authors posited a learned attentional modulation in the mostly-incongruent block had carried over into the mostly-congruent block reducing what, typically, would be a large congruency effect.
-In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from the use of one context cue to another.
-We therefore randomized the order across participants to control for the effects of order.
-However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was asymmetrical.
-
-To address this question, we collapsed over context-type and categorized participants according to the order of the counting task: 100\% congruent to 0\% congruent (100\%-0\%) or 0\% congruent to 100\% congruent (0\%-100\%).
-We again removed participants with error rates greater than 25\% and adopted the same outlier removal procedure as described above.
-We submitted congruency effects for frequency unbiased items to a 2x2 mixed ANOVA with task-relevant context (0\% and 100\% PC) as within-subject factors and phase order (100\%-0\% and 0\%-100\%) as the between-subjects factor, and supplemented each test with a corresponding Bayesian analysis.
-
-Consistent with the original analysis, the effect of task-relevant context was significant,\(F(1, 129) = 8.92\), \(\mathit{MSE} = 3,255.69\), \(p = .003\), \(\hat{\eta}^2_p = .065\), 90\% CI \([0.01\), \(0.14]\), with moderate evidence in favor of the alternative, \(\mathrm{BF}_{\textrm{10}} = 8.11\) \([\pm 0.83\%]\).
-However, the two-way interaction between task-relevant context and phase order was non-significant, \(F(1, 129) = 2.56\), \(\mathit{MSE} = 3,255.69\), \(p = .112\), \(\hat{\eta}^2_p = .019\), 90\% CI \([0\), \(0.07]\), with moderate evidence in favor of the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 4.92\) \([\pm 2.95\%]\).
-Therefore, we did not find statistical support for a list-shift asymmetry.
-Additionally, the (non-significant) asymmetrical effects we do see in this sample is in the opposite direction than would be predicted given the prior research (e.g., Abrahamse et al., 2013).
-
-We also conduncted an additional, more severe, test of the list-shift hypothesis.
-Given that the asymmetry is interpreted as resulting from a carry-over of learned attentional modulation across phases, we might expect that any asymmetry would be exaggerated near the point of transition.
-We therefore repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.
-
-Again, the interaction between task-relevant context and phase order was non-significant, \(F(1, 129) = 0.02\), \(\mathit{MSE} = 5,732.31\), \(p = .902\), \(\hat{\eta}^2_p < .001\), 90\% CI \([0\), \(0.01]\), with moderate to strong evidence in favor of the null \(\mathrm{BF}_{\textrm{01}} = 8.88\) \([\pm 2.88\%]\).
-Interestingly, the main effect of task-relevant context was still significant, \(F(1, 129) = 6.65\), \(\mathit{MSE} = 5,732.31\), \(p = .011\), \(\hat{\eta}^2_p = .049\), 90\% CI \([0.01\), \(0.12]\), with moderate evidence in favor of the alternative, \(\mathrm{BF}_{\textrm{10}} = 3.22\) \([\pm 2.16\%]\).
-This result supports the conclusion that there was no asymmetry.
-Additionally, the the shift in context-dependent effects appears to have taken place almost immediately after the transition.
 
@@
 \midrule
-\multirow{9}{*}{100\% PC} & \multirow{3}{*}{Object} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{693 (26)} & \multicolumn{1}{l}{4.17 (0.73)} \\
+\multirow{9}{*}{Low Conflict} & \multirow{3}{*}{Object} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{693 (26)} & \multicolumn{1}{l}{4.17 (0.73)} \\
 & & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{585 (23)} & \multicolumn{1}{l}{0.74 (0.27)} & \multicolumn{1}{l}{675 (28)} & \multicolumn{1}{l}{4.81 (0.82)} \\
@@
 \midrule
-\multirow{9}{*}{0\% PC} & \multirow{3}{*}{Object} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{649 (16)} & \multicolumn{1}{l}{3.84 (0.6)} \\
+\multirow{9}{*}{High Conflict} & \multirow{3}{*}{Object} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{649 (16)} & \multicolumn{1}{l}{3.84 (0.6)} \\
 & & \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{587 (17)} & \multicolumn{1}{l}{0.56 (0.21)} & \multicolumn{1}{l}{657 (17)} & \multicolumn{1}{l}{4.17 (1.02)} \\
@@
 
+\hypertarget{exploratory-analyses-order-effects}{%
+\subsection{Exploratory analyses: Order effects}\label{exploratory-analyses-order-effects}}
+
+Previous work has shown that shifting between list-wide proportion congruent phases produced asymmetrical effects.
+Abrahamse, Duthoo, Notebaert, and Risko (2013) found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects.
+The authors posited a learned attentional modulation in the mostly-incongruent block had carried over into the mostly-congruent block reducing what, typically, would be a large congruency effect.
+In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from the use of one context cue to another.
+We therefore randomized the order across participants to control for the effects of order.
+However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was asymmetrical.
+
+To address this question, we collapsed over context-type and categorized participants according to the order of the counting task: 100\% congruent to 0\% congruent (100\%-0\%) or 0\% congruent to 100\% congruent (0\%-100\%).
+We again removed participants with error rates greater than 25\% and adopted the same outlier removal procedure as described above.
+We submitted congruency effects for frequency unbiased items to a 2x2 mixed ANOVA with task-relevant context (0\% and 100\% PC) as within-subject factors and phase order (100\%-0\% and 0\%-100\%) as the between-subjects factor, and supplemented each test with a corresponding Bayesian analysis.
+
+Consistent with the original analysis, the effect of task-relevant context was significant,\(F(1, 129) = 8.92\), \(\mathit{MSE} = 3,255.69\), \(p = .003\), \(\hat{\eta}^2_p = .065\), 90\% CI \([0.01\), \(0.14]\), with moderate evidence in favor of the alternative, \(\mathrm{BF}_{\textrm{10}} = 8.11\) \([\pm 0.83\%]\).
+However, the two-way interaction between task-relevant context and phase order was non-significant, \(F(1, 129) = 2.56\), \(\mathit{MSE} = 3,255.69\), \(p = .112\), \(\hat{\eta}^2_p = .019\), 90\% CI \([0\), \(0.07]\), with moderate evidence in favor of the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 4.92\) \([\pm 2.95\%]\).
+Therefore, we did not find statistical support for a list-shift asymmetry.
+Additionally, the (non-significant) asymmetrical effects we do see in this sample is in the opposite direction than would be predicted given the prior research (e.g., Abrahamse et al., 2013).
+
+We also conduncted an additional, more severe, test of the list-shift hypothesis.
+Given that the asymmetry is interpreted as resulting from a carry-over of learned attentional modulation across phases, we might expect that any asymmetry would be exaggerated near the point of transition.
+We therefore repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.
+
+Again, the interaction between task-relevant context and phase order was non-significant, \(F(1, 129) = 0.02\), \(\mathit{MSE} = 5,732.31\), \(p = .902\), \(\hat{\eta}^2_p < .001\), 90\% CI \([0\), \(0.01]\), with moderate to strong evidence in favor of the null \(\mathrm{BF}_{\textrm{01}} = 8.88\) \([\pm 2.88\%]\).
+Interestingly, the main effect of task-relevant context was still significant, \(F(1, 129) = 6.65\), \(\mathit{MSE} = 5,732.31\), \(p = .011\), \(\hat{\eta}^2_p = .049\), 90\% CI \([0.01\), \(0.12]\), with moderate evidence in favor of the alternative, \(\mathrm{BF}_{\textrm{10}} = 3.22\) \([\pm 2.16\%]\).
+This result supports the conclusion that there was no asymmetry.
+Additionally, the the shift in context-dependent effects appears to have taken place almost immediately after the transition.
+
 \hypertarget{experiment-2}{%
@@
 
-In Experiment 1, we found that manipulating the task-relevance of a shared contextual feature was associated in predictable changes in context-specific proportion congruency effects for frequency unbiased context items; Namely, larger congruency effects when the context was associated with low conflict than when the context was associated with high conflict.
-This suggests that participants learned the association between context and conflict-level in the first block (despite multiple, competing cues), and subsequently ignored that association in the second block to learn a new association.
+In Experiment 1, we found that manipulating the task-relevance of a shared contextual feature was associated in predictable changes in context-specific proportion congruency effects for frequency unbiased context items.
+Namely, we found larger congruency effects when the context was associated with low conflict than when the context was associated with high conflict.
+This suggests that participants learned the association between context and conflict-level in the first block (despite multiple conetxt cues), and subsequently ignored that association in the second block to learn a new association.
 Task-relevance then, may not just be important for establishing new associations (e.g., Crump \& Milliken, 2009) but also important for determining which learned associations are expressed in the present moment.
@@
 
-\hypertarget{results-1}{%
-\section{Results}\label{results-1}}
-
-Participants with mean error rates greater than 25\% were excluded from the analyses, eliminating 3 participants.
-For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure.
-The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms (Van Selst \& Jolicoeur, 1994).
-This procedure removed 3.14\% of the total observations.
-
-The questions of interest were whether participants would learn the associations between the context cues without the task-relevance manipulation (i.e., the counting task) and whether responding to the unbiased cues would be influenced by the presence of the biased cues.
-To that end, congruency effects (incongruent minus congruent performance) for RTs and error rates were submitted to an analysis of variance (ANOVA) with proportion congruency (25\%, 50\%, and 75\%) as the sole within-subject factor.
-
-The results of the RT analysis revealed the effect of proportion congruency to be non-significant, \(F(2, 92) = 0.85\), \(\mathit{MSE} = 997.11\), \(p = .431\), \(\hat{\eta}^2_p = .018\), 90\% CI \([0\), \(0.07]\), with moderate evidence in favor of the null, \(\mathrm{BF}_{\textrm{01}} = 6.91\) \([\pm 0.9\%]\).
-Similarly, the corresponding error analysis also resulted in a non-significant effect of proportion congruency, \(F(2, 92) = 0.45\), \(\mathit{MSE} = 9.23\), \(p = .641\), \(\hat{\eta}^2_p = .010\), 90\% CI \([0\), \(0.05]\), with strong evidence in favor of the null, \(\mathrm{BF}_{\textrm{01}} = 9.93\) \([\pm 1.03\%]\).
-Therefore, there was no evidence that the context cues, absent the counting task, systematically influenced the congruency effects in any way.
-
 \begin{figure}
@@
 
+\hypertarget{results-1}{%
+\section{Results}\label{results-1}}
+
+Participants with mean error rates greater than 25\% were excluded from the analyses, eliminating 3 participants.
+For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure.
+The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms (Van Selst \& Jolicoeur, 1994).
+This procedure removed 3.14\% of the total observations.
+
+The questions of interest were whether participants would learn the associations between the context cues without the task-relevance manipulation (i.e., the counting task) and whether responding to the unbiased cues would be influenced by the presence of the biased cues.
+To that end, congruency effects (incongruent minus congruent performance) for RTs and error rates were submitted to an analysis of variance (ANOVA) with proportion congruency (25\%, 50\%, and 75\%) as the sole within-subject factor.
+
+The results of the RT analysis revealed the effect of proportion congruency to be non-significant, \(F(2, 92) = 0.85\), \(\mathit{MSE} = 997.11\), \(p = .431\), \(\hat{\eta}^2_p = .018\), 90\% CI \([0\), \(0.07]\), with moderate evidence in favor of the null, \(\mathrm{BF}_{\textrm{01}} = 6.91\) \([\pm 0.9\%]\).
+Similarly, the corresponding error analysis also resulted in a non-significant effect of proportion congruency, \(F(2, 92) = 0.45\), \(\mathit{MSE} = 9.23\), \(p = .641\), \(\hat{\eta}^2_p = .010\), 90\% CI \([0\), \(0.05]\), with strong evidence in favor of the null, \(\mathrm{BF}_{\textrm{01}} = 9.93\) \([\pm 1.03\%]\).
+Therefore, there was no evidence that the context cues, absent the counting task, systematically influenced the congruency effects in any way.
+
+\begin{table}[htbp]
+\caption{Reaction times and error rates from Experiment 2.}
+\label{TR_table_2}
+\centering
+\begin{tabular}{lcccc}
+\toprule
+& \multicolumn{2}{c}{Congruent} & \multicolumn{2}{c}{Incongruent} \\
+\cmidrule(rl){2-3}
+\cmidrule(rl){4-5}
+\multicolumn{1}{c}{PC} & \multicolumn{1}{c}{RT} & \multicolumn{1}{c}{ER} & \multicolumn{1}{c}{RT} & \multicolumn{1}{c}{ER}  \\
+\midrule
+\multicolumn{1}{l}{25\%} & \multicolumn{1}{l}{518 (16)} & \multicolumn{1}{l}{0.35 (0.17)} & \multicolumn{1}{l}{598 (17)} & \multicolumn{1}{l}{3.78 (0.71)} \\
+\multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{515 (15)} & \multicolumn{1}{l}{0.27 (0.1)} & \multicolumn{1}{l}{603 (17)} & \multicolumn{1}{l}{4.26 (0.7)} \\
+\multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{523 (18)} & \multicolumn{1}{l}{0.18 (0.07)} & \multicolumn{1}{l}{603 (19)} & \multicolumn{1}{l}{3.72 (0.61)} \\
+\bottomrule
+\multicolumn{5}{l}{\textit{Note}: RT = Reaction Time (ms);  ER = Error Rates (\%);} \\
+\multicolumn{5}{l}{PC = Proportion Congruent; Standard Errors} \\
+\multicolumn{5}{l}{are presented in parantheses.} \\
+\end{tabular}%
+\end{table}
+
 \hypertarget{experiment-3}{%
@@
 The evidence thus far suggests that context-cues, rather than being irrelevant to the task (as their namesake would suggest), need to be integrated into the task-representation to guide attentional control.
-There is some evidence that instructions alone can be sufficient to produce list-wide proportion congruency effects, though not item-specific proportion congruency effects (e.g., Entel et al., 2014; though, see Desender, 2018) and not context-specific proportion congruency effects (e.g., ).
-Explicit instructions however, are another way of making context-cues relevant to the on-going task and could serve the same purpose as the counting task---although, instructions are likely a much weaker manipulation than the counting task.
+There is some evidence that instructions alone can be sufficient to produce list-wide proportion congruency effects, though not item-specific proportion congruency effects (Desender, 2018; Entel, Tzelgov, \& Bereby-Meyer, 2014) and not context-specific proportion congruency effects (Crump \& Milliken, 2009).
+Explicit instructions however, are another way of making context-cues relevant to the on-going task and could serve the same purpose as the counting task.
 In Experiment 3, we test whether participants are able to explicitly use the context-cues to guide attentional control through an instruction manipulation.
@@
 The primary question of interest was whether the task-relevance of context features (made relevant through explicit task instructions) associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items.
-Mean correct RTs and mean error rates from frequency unbiased trials were submitted to an analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors.
-
-The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be non-significant, \(F(1, 45) = 0.02\), \(\mathit{MSE} = 4,030.54\), \(p = .876\), \(\hat{\eta}^2_p = .001\), 90\% CI \([0\), \(0.04]\).
-Similarly, the corresponding error analysis also resulted in a non-significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 45) = 0.66\), \(\mathit{MSE} = 28.52\), \(p = .420\), \(\hat{\eta}^2_p = .014\), 90\% CI \([0\), \(0.11]\).
+Mean correct RTs and mean error rates from frequency unbiased trials were submitted to an analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) as the within-subject factors.
+
+The results of the RT analysis revealed the effect of task-relevance to be non-significant, \(F(1, 45) = 0.02\), \(\mathit{MSE} = 4,030.54\), \(p = .876\), \(\hat{\eta}^2_p = .001\), 90\% CI \([0\), \(0.04]\), with moderate evidence in favor of the null, \(\mathrm{BF}_{\textrm{01}} = 4.48\) \([\pm 2.17\%]\).
+Similarly, the corresponding error analysis also resulted in a non-significant effect of task-relevance, \(F(1, 45) = 0.66\), \(\mathit{MSE} = 28.52\), \(p = .420\), \(\hat{\eta}^2_p = .014\), 90\% CI \([0\), \(0.11]\), with moderate evidence in favor of the null, \(\mathrm{BF}_{\textrm{01}} = 3.39\) \([\pm 1.19\%]\).
+
+\begin{table}[htbp]
+\caption{Reaction times and error rates from Experiment 3.}
+\label{TR_table_3}
+\centering
+\begin{tabular}{llcccc}
+\toprule
+& & \multicolumn{2}{c}{Congruent} & \multicolumn{2}{c}{Incongruent} \\
+\cmidrule(rl){3-4}
+\cmidrule(rl){5-6}
+\multicolumn{1}{c}{Task-Relevant Context} & \multicolumn{1}{c}{PC} & \multicolumn{1}{c}{RT} & \multicolumn{1}{c}{ER} & \multicolumn{1}{c}{RT} & \multicolumn{1}{c}{ER}  \\
+\midrule
+\multirow{3}{*}{Low Conflict} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{658 (28)} & \multicolumn{1}{l}{5.66 (0.94)} \\
+& \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{579 (32)} & \multicolumn{1}{l}{0.54 (0.31)} & \multicolumn{1}{l}{664 (29)} & \multicolumn{1}{l}{5.25 (1.03)} \\
+& \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{571 (26)} & \multicolumn{1}{l}{0.45 (0.24)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
+\midrule
+\multirow{3}{*}{High Conflict} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{643 (26)} & \multicolumn{1}{l}{6.43 (0.87)} \\
+& \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{550 (21)} & \multicolumn{1}{l}{0.36 (0.28)} & \multicolumn{1}{l}{637 (23)} & \multicolumn{1}{l}{5.98 (0.99)} \\
+& \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{547 (22)} & \multicolumn{1}{l}{0.45 (0.17)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
+ & & & & & \\
+\bottomrule
+\multicolumn{6}{l}{\textit{Note}: RT = Reaction Time (ms);  ER = Error Rates (\%);} \\
+\multicolumn{6}{l}{PC = Proportion Congruent; Standard Errors are presented in parantheses.} \\
+\end{tabular}%
+\end{table}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{manuscript_pretty_files/figure-latex/figure5-1.pdf}
-\caption{\label{fig:figure5}Results from the simulation-based sensitivity and power-analyses.
+In Experiment 1, we found no evidence for differences in the task-relevance effect across context-type.
+Similarly, Experiments 2 and 3 failed to find CSPC effects.
+To determine the limitations in our ability to draw inferences from these results, we need to assess the extent to which our experiments could have detected effects, if present.
+Although replicability has become an important and salient issue in Psychology at large (e.g., Camerer et al., 2018; Collaboration, 2015), this issue has also arisen in the context-specific proportion congruency literature {[}Crump et al.
+(2017); Hutcheon and Spieler (2017); {]}.
+
+To address this issue in the current study---and to do so transparently---we conducted simulation-based power and sensitivity analyses {[}{]} to determine the range effect sizes our experimental design was sensitive to detect and the required sample sizes to detect a range of effects.
+We used a Monte Carlo simulation approach with a statistical model of the distributions that underlie the effect of interest (Maxwell, 2008).
+Rather than estimating power based on observed effect sizes from prior experiments (typically, over-estimates), we instead estimated the properties of the base reaction time distributions from our current data and sampled from these distributions using a Monte Carlo simulation approach to estimate the replication success rate across a range of effect sizes and sample sizes.
+
+We created the conflictPower R-package to conduct the Monte Carlo simulations ({\textbf{???}}).
+The conflictPower package samples simulated reaction time data for subjects at the trial-level using base reaction time distributions for the conflict and no-conflict conditions.
+To generate the base reaction time distributions, we fitted ex-Gaussian functions to the reaction time data from individual participants and averaged across all three experiments using the retimes R-package (Massidda, 2013).
+We then used the conflictPower package to simulate the results across a range of effect and sample sizes, calculating the proportion of experiments, across \(10 000\) simulations, resulting in a p-value less than \(.05\) (see Figure 5; for a more detailed explanation of the sampling procedure see Crump and Brosowsky, 2019).
+
+First, the results of these analyses show that our experimental design was reasonably powered to detect CSPC effects.
+In particular, with 150 participants, we estimated 89\% power to detect effects as small 10 ms; With only 50 participants, we were still reasonably powered to detect CSPC effects as small as 15 ms at an estimated 78\%.
+Understandably, our design was not as sensitive to detecting changes in the CSPC effect between groups (Experiment 1, for example).
+We estimated only 75\% power to detect the difference between a 20 ms and 0 ms CSPC effect with 50 participants per group.
+That is, the experimental design could detect the presence/absence of the CSPC effect moderately well, but likely does not reliably detect small changes in the CSPC effect across conditions.
+To reliably detect a 15 ms change in the CSPC effect at roughly 80\% power, for example, we estimate would require 100 participants per group.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{manuscript_pretty_files/figure-latex/figure5-1} \caption{Results from the simulation-based sensitivity and power-analyses.
 Figure A shows the sensitivity of our experimental design to detect a range of effect sizes for the context-specific proportion congruency (CSPC) effect with 50 (e.g., Experiments 2 and 3) and 150 (e.g., Experiment 1) participants.
 Figure B shows the sensitivity to detect the CSPC by context-type interaction with 50 participants per group (e.g., Experiment 1).
-Figures C and D show the corresponding power curves for the CSPC and CSPC by context-type effects across sample sizes.}
+Figures C and D show the estimated power curves for the CSPC and CSPC by context-type effects across sample sizes.
+Each data point represents the proportion of p-values less than .05 from 10,000 simulations.}\label{fig:figure5}
 \end{figure}
-
-In Experiment 1, we found no evidence for differences in the task-relevance effect across context-type.
-Similarly, Experiments 2 and 3 failed to find CSPC effects.
-To effectively draw inferences from these results, we need to assess the extent to which our experiments could have detected effects, if present.
-Although replicability has become an important and salient issue in Psychology at large (e.g., ), this issue has also arisen in the context-specific proportion congruency literature (e.g., Brosowsky Crump, Hutcheon speiler, TiCS).
-
-To address this issue in the current study---and to do so transparently---we conducted simulation-based power and sensitivity analyses (Maxwell, Kelley, and Raush, 2008; Brosowsky and Crump) to determine the range effect sizes our experimental design was sensitive to detect and the required sample sizes to detect them.
-We used a Monte Carlo simulation approach with a statistical model of the distributions that underlie the effect of interest (Maxwell, 2008).
-Rather than estimating power based on observed effect sizes from prior experiments (typically, over-estimates), we instead estimated the properties of the base reaction time distributions from our current data and sampled from these distributions using a Monte Carlo simulation approach to estimate the replication success rate across a range of effect sizes and sample sizes.
-
-We created the conflictPower R-package to conduct the Monte Carlo simulations (Crump and Brosowsky; Tics).
-The conflictPower package samples simulated reaction time data for subjects at the trial-level, given base reaction time distributions for the conflict and no-conflict conditions.
-To generate the base reaction time distributions, we fitted ex-Gaussian functions to the reaction time data from individual participants and averaged across all three experiments using the retimes R-package (XXXX).
-Using the extimated ex-Gaussian parameters, we used the conflictPower package to simulate the results across a range of effect and sample sizes, calculating the proportion of experiments (across \(10 000\) simulations) resulting in a p-value less than \(.05\) (see Figure 5; for a more detailed explanation of the sampling procedure see Crump and Brosowsky, 2019).
-
-First, the results of these analyses show that our experimental design was reasonably powered to detect CSPC effects.
-In particular, with 150 participants, we estimated 89\% power to detect effects as small 10 ms; With only 50 participants, we were still reasonably powered to detect CSPC effects as small as 15 ms at an estimated 78\%.
-Understandably, our design was not as sensitive to detecting changes the in the CSPC effect across conditions (in Experiment 1, for example).
-For instance, we estimated only 75\% power to detect the difference between a 20 ms and 0 ms CSPC effect with 50 participants per group.
-That is, the experimental design could detect the presence/absence of the CSPC effect moderately well, but likely does not reliably detect small changes in the CSPC effect across conditions.
-To reliably detect a 15 ms change in the CSPC effect, for example, we estimate would require 100 participants per group.
 
@@
 
-The key finding was that the congruency effects for the frequency unbiased items were significantly larger when the low-conflict context was made task-relevant as compared to when the high-conflict context was made task-relevant.
+The key finding was that congruency effects for the frequency unbiased items were significantly larger when the low conflict context was made task-relevant as compared to when the high conflict context was made task-relevant.
 This result is consistent with prior CSPC effects and, like the previous work, suggests that the context cues triggered rapid adjustments to attentional control (Crump \& Milliken, 2009).
@@
 (2013) eliminated the CSPC effect by making the contextual cue effectively unrelated to the task.
-These studies suggest that task-relevance plays an important role in establishing associations between contextual information and attentional priorities to produce CSPC effects.
+These studies suggest that task-relevance plays an important role in establishing new associations between contextual information and attentional priorities to produce CSPC effects.
 Our finding extends this work in two important ways.
@@
 
-In light of prior work, we take this as evidence that the contextual recruitment of selective attention, although likely implicit, is not obligatory (e.g., Brosowsky \& Crump, 2016), requiring that environmental information be incorporated into the task representation.
-Similarly, there appears to be flexibility in which environmental features are selected and used to guide attention, which can be rapidly updated depending on the task-relevance of those features.
+In Experiment 2, we found that participants did not spontaneously learn the associations between proportion congruency and context-cues without the secondary counting task.
+This replicates previous work (Crump et al., 2008) and demonstrates further that task-relevance is necessary for establishing associations between contexts and attentional priorities.
+Moreover, this should serve as a cautionary tale for future work using the context-specific proportion congruent design.
+Prior studies have had difficulty replicating CSPC effects using the typical location-based CSPC design.
+The inconsistency of participants to learn associations between attentional priorities and location cues might arise because location is a poor cue in terms of task-relevance.
+Additionally, in Experiment 3 explicit instructions to make use of the cues also failed to produce context-specific effects.
+This result also tracks well with previous work that found instruction manipulations could successfully produce list-wide proportion congruency effects, but not item-specific (Entel et al., 2014) or context-specific (Crump et al., 2008) effects.
+Explicit instructions are another method for inducing task-relevance further illustrating that weak task-relevance manipulations are not sufficient for producing CSPC effects.
+
+In light of prior work, we take these results as evidence that the contextual recruitment of selective attention, although likely implicit, is not obligatory (e.g., Brosowsky \& Crump, 2016), requiring that environmental information be incorporated into the task representation.
+Similarly, there appears to be flexibility in which environmental features are selected and used to guide attention, which can be rapidly updated depending on the task-relevance of those features (for a similar perspective, see Hommel (2004); Hommel (2019)).
 Such a result lends some insight into how context-specific control might operate in more complex, real-world environments, where there is an over-abundance of environmental features that afford many different learned associations.
@@
 
-Another key result of this study concerned the different stimuli used as context cues.
+Finally, another key result of this study concerned the different stimuli used as context cues in Experiment 1.
 Across the three conditions, we varied the type of context image and dimensions.
@@
 These effects were found to be generalizable across two different kinds of stimuli and occurred even when using non-repeating images, and implicate an important role for task-relevance in producing context-dependency and are consistent with memory-based accounts of CSPC phenomena.
+
+\newpage
 
@@
 J.
+C.
 (2016).
@@
 \leavevmode\hypertarget{ref-bugg_conflict-triggered_2014}{}%
-Bugg, J. (2014). Conflict-triggered top-down control: Default mode, last resort, or no such thing? \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}(2), 567.
+Bugg, J. M. (2014). Conflict-triggered top-down control: Default mode, last resort, or no such thing? \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{40}(2), 567.
 
 \leavevmode\hypertarget{ref-bugg_support_2012}{}%
-Bugg, J., \& Crump, M.
+Bugg, J.
+M., \& Crump, M.
 J.
+C.
 (2012).
@@
 \leavevmode\hypertarget{ref-bugg_converging_2013}{}%
-Bugg, J., \& Hutchison, K.
+Bugg, J.
+M., \& Hutchison, K.
 A.
@@
 \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{39}(2), 433.
+
+\leavevmode\hypertarget{ref-camerer_evaluating_2018}{}%
+Camerer, C.
+F., Dreber, A., Holzmeister, F., Ho, T.-H., Huber, J., Johannesson, M., \ldots{} Wu, H.
+(2018).
+Evaluating the replicability of social science experiments in Nature and Science between 2010 and 2015.
+\emph{Nature Human Behaviour}, \emph{2}(9), 637--644.
+doi:\href{https://doi.org/10.1038/s41562-018-0399-z}{10.1038/s41562-018-0399-z}
 
@@
 doi:\href{https://doi.org/10.1037/a0029794}{10.1037/a0029794}
+
+\leavevmode\hypertarget{ref-open_science_collaboration_estimating_2015}{}%
+Collaboration, O.
+S.
+(2015).
+Estimating the reproducibility of psychological science.
+\emph{Science}, \emph{349}(6251), aac4716.
+doi:\href{https://doi.org/10.1126/science.aac4716}{10.1126/science.aac4716}
 
@@
 
+\leavevmode\hypertarget{ref-r_conflictPower_2019}{}%
+Crump, M. J. C., \& Brosowsky, N. P. (2019). \emph{ConflictPower: Simulation based power analysis for adaptive control designs}. Retrieved from \url{https://github.com/CrumpLab/conflictPower}
+
 \leavevmode\hypertarget{ref-crump_reproducing_2017}{}%
 Crump, M.
-J., Brosowsky, N.
+J.
+C., Brosowsky, N.
 P., \& Milliken, B.
@@
 
-\leavevmode\hypertarget{ref-r_conflictPower_2019}{}%
-Crump, M. J. C., \& Brosowsky, N. P. (2019). \emph{ConflictPower: Simulation based power analysis for adaptive control designs}. Retrieved from \url{https://github.com/CrumpLab/conflictPower}
+\leavevmode\hypertarget{ref-crump_context-specific_2006}{}%
+Crump, M.
+J.
+C., Gong, Z., \& Milliken, B.
+(2006).
+The context-specific proportion congruent Stroop effect: Location as a contextual cue.
+\emph{Psychonomic Bulletin \& Review}, \emph{13}, 316--321.
+doi:\href{https://doi.org/10.3758/BF03193850}{10.3758/BF03193850}
+
+\leavevmode\hypertarget{ref-crump_contextual_2010}{}%
+Crump, M.
+J.
+C., \& Logan, G.
+D.
+(2010).
+Contextual control over task-set retrieval.
+\emph{Attention, Perception, \& Psychophysics}, \emph{72}, 2047--2053.
+Retrieved from \url{http://link.springer.com/article/10.3758/BF03196681}
 
@@
 
-\leavevmode\hypertarget{ref-crump_context-specific_2006}{}%
-Crump, M.
-J., Gong, Z., \& Milliken, B.
-(2006).
-The context-specific proportion congruent Stroop effect: Location as a contextual cue.
-\emph{Psychonomic Bulletin \& Review}, \emph{13}, 316--321.
-doi:\href{https://doi.org/10.3758/BF03193850}{10.3758/BF03193850}
-
-\leavevmode\hypertarget{ref-crump_contextual_2010}{}%
-Crump, M.
-J., \& Logan, G.
-D.
-(2010).
-Contextual control over task-set retrieval.
-\emph{Attention, Perception, \& Psychophysics}, \emph{72}, 2047--2053.
-Retrieved from \url{http://link.springer.com/article/10.3758/BF03196681}
-
 \leavevmode\hypertarget{ref-crump_context-specific_2008}{}%
 Crump, M.
-J., Vaquero, J.
+J.
+C., Vaquero, J.
+M.
 M., \& Milliken, B.
@@
 doi:\href{https://doi.org/10.1016/j.concog.2007.01.004}{10.1016/j.concog.2007.01.004}
+
+\leavevmode\hypertarget{ref-desender_different_2018}{}%
+Desender, K.
+(2018).
+Different mechanisms can account for the instruction induced proportion congruency effect.
+\emph{Acta Psychologica}, \emph{184}, 39--45.
+doi:\href{https://doi.org/10.1016/j.actpsy.2017.03.011}{10.1016/j.actpsy.2017.03.011}
 
@@
 doi:\href{https://doi.org/10.3389/fpsyg.2014.01247}{10.3389/fpsyg.2014.01247}
+
+\leavevmode\hypertarget{ref-entel_proportion_2014}{}%
+Entel, O., Tzelgov, J., \& Bereby-Meyer, Y.
+(2014).
+Proportion congruency effects: Instructions may be enough.
+\emph{Frontiers in Psychology}, \emph{5}.
+doi:\href{https://doi.org/10.3389/fpsyg.2014.01108}{10.3389/fpsyg.2014.01108}
 
@@
 
+\leavevmode\hypertarget{ref-hommel_event_2004}{}%
+Hommel, B.
+(2004).
+Event files: Feature binding in and across perception and action.
+\emph{Trends in Cognitive Sciences}, \emph{8}, 494--500.
+doi:\href{https://doi.org/10.1016/j.tics.2004.08.007}{10.1016/j.tics.2004.08.007}
+
+\leavevmode\hypertarget{ref-hommel_theory_2019}{}%
+Hommel, B.
+(2019).
+Theory of Event Coding (TEC) V2.0: Representing and controlling perception and action.
+\emph{Attention, Perception, \& Psychophysics}.
+doi:\href{https://doi.org/10.3758/s13414-019-01779-4}{10.3758/s13414-019-01779-4}
+
 \leavevmode\hypertarget{ref-hutcheon_limits_2017}{}%
@@
 Macrae, C. N., \& Bodenhausen, G. V. (2001). Social cognition: Categorical person perception. \emph{British Journal of Psychology}, \emph{92}, 239--255.
+
+\leavevmode\hypertarget{ref-r_retimes_2013}{}%
+Massidda, D. (2013). \emph{Retimes: Reaction time analysis}. Retrieved from \url{https://CRAN.R-project.org/package=retimes}
 
@@
 J., \& Bugg, J.
+M.
 (2016).
@@
 \leavevmode\hypertarget{ref-weidler_attentional_2018}{}%
-Weidler, B. J., Dey, A., \& Bugg, J. (2018). Attentional control transfers beyond the reference frame. \emph{Psychological Research}, 1--14.
+Weidler, B. J., Dey, A., \& Bugg, J. M. (2018). Attentional control transfers beyond the reference frame. \emph{Psychological Research}, 1--14.
 

### 2019-10-08 data-analysis/analysis_E1.R

@@ -126,7 +126,7 @@ RT.Diff<-RT.DF %>%
   ) 
 
 #names(RT.Diff)[names(RT.Diff) == "Task_Relevant_Context"] <- 'Task Relevant\nContext'
-levels(RT.Diff$Task_Relevant_Context) <- c("100% PC", "0% PC")
+levels(RT.Diff$Task_Relevant_Context) <- c("Low Conflict", "High Conflict")
 levels(RT.Diff$Condition) <- c("Object", "Social", "Social (NR)")
 
 
@@ -197,7 +197,7 @@ ACC.Diff <- raw_data %>%
     SE = sd/sqrt(N)
   ) 
 
-levels(ACC.Diff$Task_Relevant_Context) <- c("100% PC", "0% PC")
+levels(ACC.Diff$Task_Relevant_Context) <- c("Low Conflict", "High Conflict")
 levels(ACC.Diff$Condition) <- c("Object", "Social", "Social (NR)")
 
 limits <- aes(ymax = Flanker + SE, ymin = Flanker - SE)

### 2019-10-08 data-analysis/analysis_E3.R

@@ -110,6 +110,7 @@ RT.Diff<- RT.Analysis %>%
   ) 
 
 RT.Diff$Task_Relevant_Context <- factor(RT.Diff$Task_Relevant_Context,levels(RT.Diff$Task_Relevant_Context)[c(2,1)])
+levels(RT.Diff$Task_Relevant_Context) <- c("Low Conflict", "High Conflict")
 
 limits <- aes(ymax = Flanker + SE, ymin = Flanker - SE)
 RT.graph <- ggplot(RT.Diff,aes(x=Task_Relevant_Context, y=Flanker,fill=Task_Relevant_Context))+
@@ -165,7 +166,7 @@ ACC.Diff <- raw_data_E3 %>%
   ) 
 
 
-#levels(ACC.Diff$Task_Relevant_Context) <- c("100% PC", "0% PC")
+levels(ACC.Diff$Task_Relevant_Context) <- c("Low Conflict", "High Conflict")
 #levels(ACC.Diff$Condition) <- c("Object", "Social", "Social (NR)")
 ACC.Diff$Task_Relevant_Context <- factor(ACC.Diff$Task_Relevant_Context,levels(ACC.Diff$Task_Relevant_Context)[c(2,1)])
 

### 2019-10-08 data-analysis/demographics.R

@@ -1,0 +1,55 @@
+library(dplyr)
+library(tidyr)
+library(afex)
+library(ggplot2)
+library(cowplot)
+library(BayesFactor)
+#As of 2018/12/07 apa_print() requires development version of Papaja
+#devtools::install_github("crsh/papaja")
+library(papaja)
+library(kableExtra)
+
+load("data-analysis/demographics_E1.Rda")
+load("data-analysis/demographics_E2.Rda")
+load("data-analysis/demographics_E3.Rda")
+demographics$Exp <- "E1"
+
+df <- rbind(demographics, demographics_E2)
+df <- rbind(df, demographics_E3[,1:16])
+df$Exp <- as.factor(df$Exp)
+
+age <- df %>%
+  filter(age != "undefined",
+         age != "") %>%
+  select(Exp, gender, age, handedness, vision, english) %>%
+  mutate(age = as.character(age)) %>%
+  filter(age != "male") %>%
+  mutate(age = as.numeric(age)) %>%
+  group_by(Exp) %>%
+  summarize(
+    mean = mean(age),
+    median = median(age),
+    sd = sd (age)
+  )
+
+age <- left_join(age, df %>% 
+  filter(age == "undefined" | age == "" | age == "male" | is.na(age)) %>%
+  group_by(Exp) %>%
+  summarize(
+    `No Response` = n()
+  ), by = c("Exp"))
+
+age[is.na(age$`No Response`),]$`No Response` <- 0
+
+gender <- df %>%
+  group_by(Exp) %>%
+  summarize(Male = table(gender)[[1]],
+            Female = table(gender)[[2]],
+            `No Response` = table(gender)[[3]])
+
+handedness <- df %>%
+  group_by(Exp) %>%
+  summarize(Right = table(handedness)[[1]],
+            Left = table(handedness)[[2]],
+            `No Response` = table(handedness)[[3]],
+            Both = table(handedness)[[4]])

### 2019-10-08 data-analysis/table.R

@@ -178,7 +178,7 @@ TR_Table<-paste(
     "\\cmidrule(rl){6-7}",
     "\\multicolumn{1}{c}{Task-Relevant Context} & \\multicolumn{1}{c}{Condition} & \\multicolumn{1}{c}{PC} & \\multicolumn{1}{c}{RT} & \\multicolumn{1}{c}{ER} & \\multicolumn{1}{c}{RT} & \\multicolumn{1}{c}{ER}  \\\\",
     "\\midrule", 
-    paste0("\\multirow{9}{*}{Low Conflict} & \\multirow{3}{*}{Object} & \\multicolumn{1}{l}{0\\%} & \\multicolumn{1}{l}{", paste(forTable[1,],collapse="} & \\multicolumn{1}{l}{"), "} \\\\"),
+    paste0("\\multirow{9}{*}{100\\% PC} & \\multirow{3}{*}{Object} & \\multicolumn{1}{l}{0\\%} & \\multicolumn{1}{l}{", paste(forTable[1,],collapse="} & \\multicolumn{1}{l}{"), "} \\\\"),
     paste0("& & \\multicolumn{1}{l}{50\\%} & \\multicolumn{1}{l}{", paste(forTable[2,],collapse="} & \\multicolumn{1}{l}{"), "} \\\\"),
     paste0("& & \\multicolumn{1}{l}{100\\%} & \\multicolumn{1}{l}{", paste(forTable[3,],collapse="} & \\multicolumn{1}{l}{"), "} \\\\"),
     "\\cmidrule(rl){2-7}",
@@ -191,7 +191,7 @@ TR_Table<-paste(
     paste0("& & \\multicolumn{1}{l}{100\\%} & \\multicolumn{1}{l}{", paste(forTable[9,],collapse="} & \\multicolumn{1}{l}{"), "} \\\\"),
     "\\midrule", 
     
-    paste0("\\multirow{9}{*}{High Conflict} & \\multirow{3}{*}{Object} & \\multicolumn{1}{l}{0\\%} & \\multicolumn{1}{l}{", paste(forTable[10,],collapse="} & \\multicolumn{1}{l}{"), "} \\\\"),
+    paste0("\\multirow{9}{*}{0\\% PC} & \\multirow{3}{*}{Object} & \\multicolumn{1}{l}{0\\%} & \\multicolumn{1}{l}{", paste(forTable[10,],collapse="} & \\multicolumn{1}{l}{"), "} \\\\"),
[…]

### 2019-10-08 data-analysis/table2.R

@@ -1,0 +1,138 @@
+
+library(dplyr)
+library(tidyr)
+library(afex)
+library(ggplot2)
+library(cowplot)
+library(BayesFactor)
+#As of 2018/12/07 apa_print() requires development version of Papaja
+#devtools::install_github("crsh/papaja")
+library(papaja)
+library(kableExtra)
+
+# Load functions
+source("data-analysis/print_apa_ci.R")
+source("data-analysis/print_bf.R")
+source("data-analysis/outlier_removal.R")
+
+# Load data
+load("data-analysis/raw_data_E2.Rda")
+load("data-analysis/demographics_E2.Rda")
+
+theme_set(theme_cowplot())
+# Find subs with < 75% accuracy
+low_acc <- raw_data_E2 %>%
+  group_by(Subject,Condition,PC,Congruency) %>%
+  summarise(meanAccuracy = mean(ACC)) %>%
+  filter(meanAccuracy < .75) %>%
+  .$Subject
+
+N_subjects_removed_E2 <-length(unique(low_acc))
+
+## summarise by subject
+RT.DF <- raw_data_E2 %>%
+  filter(
+    RT < 3000,
+    RT > 0,
+    ACC == TRUE,
+    Subject%in%low_acc == FALSE
+  ) %>%
+  group_by(Subject,PC,Congruency)%>%
+  summarise(vjoutRT = vjoutNR(RT,1))
+
+## Find percentage of trials removed 
+percent_removed_E2 <- raw_data_E2 %>%
+  filter(
+    RT < 3000,
+    RT > 0,
+    ACC == TRUE,
+    Subject%in%low_acc == FALSE
+  ) %>%
+  group_by(Subject,PC,Congruency)%>%
+  summarise(percent_removed = vjoutNR(RT,2)) %>%
+  ungroup() %>%
+  summarise(avg_removed = mean(percent_removed)) %>%
+  .$avg_removed
+
+## Analyze RTs 
+RT.DF <- RT.DF %>%
+  ungroup() %>%
+  mutate(Subject = factor(Subject),
+         PC = factor(PC)) %>%
+  group_by(Subject,PC,Congruency) %>%
+  summarise(meanRT = mean(vjoutRT)) %>%
+  group_by(PC,Congruency) %>%
+  summarise(N = n_distinct(Subject),
+            RT = mean(meanRT),
[…]

### 2019-10-08 data-analysis/table3.R

@@ -1,0 +1,184 @@
+library(dplyr)
+library(tidyr)
+library(afex)
+library(ggplot2)
+library(cowplot)
+#As of 2018/12/07 apa_print() requires development version of Papaja
+#devtools::install_github("crsh/papaja")
+library(papaja)
+
+
+folderName <- function(){
+  wd<-getwd()
+  wd<-strsplit(wd,"/")
+  wd<-wd[[1]][length(wd[[1]])]
+  
+  return(wd)
+}
+
+
+vjoutNR <- function(x,n) {
+  xm <- mean(x)
+  xsize <- c(3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 20, 
+             25, 30, 35, 50, 80)
+  stds <- c(1.3, 1.458, 1.68, 1.841, 1.961, 2.05, 2.12, 2.173, 
+            2.22, 2.246, 2.274, 2.31, 2.326, 2.391, 2.41, 2.4305, 
+            2.45, 2.48, 2.5)
+  stdindex <- length(xsize[xsize <= length(x)])
+  removed <- x[x < xm+sd(x)*stds[stdindex]]
+  removed <- removed[removed > xm - (sd(x)*stds[stdindex])]
+  proportionRemoved <- length(removed)/length(x)
+  finaldata<-c(mean(removed),1-proportionRemoved)
+  return(finaldata[[n]])
+}
+
+# Load data
+load("data-analysis/raw_data_E3.Rda")
+
+
+# Find subs with < 75% accuracy
+low_acc <- raw_data_E3 %>%
+  group_by(Subject,Condition,Task_Relevant_Context,Frequency,Congruency) %>%
+  summarise(meanAccuracy = mean(ACC)) %>%
+  filter(meanAccuracy < .75) %>%
+  .$Subject
+
+N_subjects_removed_E3 <-length(unique(low_acc))
+## summarise by subject
+RT.DF <- raw_data_E3 %>%
+  filter(
+    RT < 3000,
+    RT > 0,
+    ACC == TRUE,
+    Subject%in%low_acc == FALSE
+  ) %>%
+  group_by(Condition,Subject,Frequency,Order,Phase,Block,Frequency,Task_Relevant_Context,Congruency)%>%
+  summarise(vjoutRT = vjoutNR(RT,1)) %>%
+  group_by(Condition,Subject,Frequency,Task_Relevant_Context,Congruency) %>%
[…]

### 2019-10-17 bWFudXNjcmlwdF9wcmV0dHkuUm1k.Rmd
draft complete

--- 2019-10-08 manuscript_pretty.Rmd
@@
 Using a secondary counting task, context dimensions associated with differing levels of conflict were made task-relevant or -irrelevant across the experiment.
-In short, we found that making new contextual information task-relevant caused participants to ignore a previously learned context-attention association and adopt a new context-specific control strategy; all without changing the experimental stimuli.
-Furthermore, we found participants did not spontaneously learn about context-specific proportion manipulations and explicit instructions insufficient for producing context-specific effects.
+In short, we found that making new contextual information task-relevant caused participants to suppress a previously learned context-attention association and adopt a new context-specific control strategy; all without changing the experimental stimuli.
+Furthermore, we found participants did not spontaneously learn about context-specific proportion manipulations and explicit instructions were insufficient for producing context-specific effects.
 These results suggests that task-relevance is a key determinant of context-specific control."
@@
 bibliography      : ["task-relevance-cspc.bib"]
+appendix          : "appendix_a.rmd"
 
@@
 header-includes:
+  - \usepackage{threeparttable}
   - \usepackage{setspace}\singlespacing 
@@
 One location was associated with a high frequency of conflict (25% congruent trials) and the other with a low frequency of conflict (75% congruent trials).
-Overall, the proportion of congruent trials was 50% and randomized such that the upcoming location could not be predicted.
+Overall, the proportion of congruent trials was 50% and trials were randomized such that the upcoming location could not be predicted.
 Even so, congruency effects were shown to be smaller for trials where the stimulus appeared in the high conflict location as compared to the low conflict location.
@@
 On the other hand, our current task-goals might constrain the expression of previously learned associations.
-If someone sits down to write in the coffee shope, their current goals may allow the laptop to take priority over other environmental cues that are irrelevant to the task at hand.
+If someone sits down to write in the coffee shop, their current goals may allow the laptop to take priority over other environmental cues that are irrelevant to the task at hand.
 
@@
 The expression of previously learned associations however, is dictated by memory retrieval---a similarity-based, cue-driven process [e.g., @jacoby_interpreting_1978; @hintzman_minerva_1984; @hintzman_schema_1986; @hintzman_judgments_1988].
-Presumably, the features of our immediate environment automatically cue memory and reinstate the retrieved attentional priorites [@logan_toward_1988; @logan_attention_1992].
+Presumably, the features of our immediate environment automatically cue memory and reinstate the retrieved attentional priorities [@logan_toward_1988; @logan_attention_1992].
 If a few prior experiences are easily retrievable (i.e., memories are distinct or very similar to the retrieval cue), they could support the reinstatement of a learned attentional association despite very little practice [e.g., @brosowsky_memory-guided_2018].
 Conversely, if prior experiences are difficult to retrieve (i.e., memories are indistinct or low in similarity to the retrieval cue), then learned associations may not be expressed, even after much practice.
-To the extent that you could manipulate memory retrieval, you should als be able manipulate the expression of learned associations.
+To the extent that you could manipulate memory retrieval, you should also be able manipulate the expression of learned associations.
 
@@
 We hypothesized that the cue-driven, memory-retrieval process might be constrained to the features of our environment that are relevant to our on-going task and goals.
-If this is the case, then a previously learned association should be easily ignored if that feature was made irrelevant to the task because that feature would no longer contribute to memory-retrieval.
-Furthermore, it would suggest that the mere presence of a cue is not sufficient for automatically directing attention, but instead requires task-integration.
+If this is the case, then a previously learned association should be easily suppressed if that feature was made irrelevant to the task because that feature would no longer contribute to memory-retrieval.
+Furthermore, it would suggest that the mere presence of a cue is not sufficient for automatically directing attention, but instead requires task-integration (for a similar perspective, see @hommel_event_2004; @hommel_theory_2019).
 
@@
 However, what determines the  expression of previously learned context-attention associations remains unclear.
-In the current study, we examined whether manipulating task-relevance would allow participants to ignore a previously learned association and adopt a new context-specific control strategy.
+In the current study, we examined whether manipulating task-relevance would allow participants to suppress a previously learned association and adopt a new context-specific control strategy.
 
@@
 In this case, we would expect smaller congruency effects when the high conflict context dimension is made task-relevant as compared to when the low conflict context dimension is made task-relevant.
-This would demonstrate that participants were able to ignore a previously learned association and adopt a new context-specific control strategy.
+This would demonstrate that participants were able to suppress a previously learned association and adopt a new context-specific control strategy.
 
@@
 
-We also conduncted an additional, more severe, test of the list-shift hypothesis.
+We also conducted an additional, more severe, test of the list-shift hypothesis.
 Given that the asymmetry is interpreted as resulting from a carry-over of learned attentional modulation across phases, we might expect that any asymmetry would be exaggerated near the point of transition.
@@
 Namely, we found larger congruency effects when the context was associated with low conflict than when the context was associated with high conflict.
-This suggests that participants learned the association between context and conflict-level in the first block (despite multiple conetxt cues), and subsequently ignored that association in the second block to learn a new association.
+This suggests that participants learned the association between context and conflict-level in the first block (despite multiple context cues), and subsequently suppressed in the second block, allowing participants to learn a new association.
 Task-relevance then, may not just be important for establishing new associations [e.g.,@crump_flexibility_2009] but also important for determining which learned associations are expressed in the present moment.
@@
 Second, we assumed that the biased proportion congruency manipulations would have no systematic effect on the unbiased items without the counting task.
-Although we randomized all aspects of the task across participants to control for potential confounds, it still remains unclear whether the biased items would influence how paricipants responded to the unbiased items.
+Although we randomized all aspects of the task across participants to control for potential confounds, it still remains unclear whether the biased items would influence how participants responded to the unbiased items.
 
@@
 The goal of the current study has been to examine the importance of task-relevance for the contextual recruitment of selective attention.
-In Experiment 1, we found that task-relevance allowed participants to exploit context cues in the presence of a competing, contradictory cue and subsequently ignore a previously learned association in favor of a different context cue.
+In Experiment 1, we found that task-relevance allowed participants to exploit context cues in the presence of a competing, contradictory cue and subsequently suppress a previously learned association in favor of a different context cue.
 In Experiment 2, we conceptually replicated previous work showing that task-relevance was necessary for participants to learn about the biased proportion congruency associations [e.g., @crump_flexibility_2009] and ruled out possible confounding effects of the biased items.
@@
 The aim of the current study was to determine whether task-relevance plays a role in the contextual recruitment of selective attention.
-In Experiment 1, we tested whether manipulating the relative task-relevance of context cues could cause participants to ignore a previously learned context-association and apply a new association.
+In Experiment 1, we tested whether manipulating the relative task-relevance of context cues could cause participants to suppress a previously learned context-association and apply a new association.
 We created a frequency unbiased context cue that shared features with two frequency biased contexts and used a feature-counting task to manipulate the task-relevance of context dimensions across two blocks of trials.
@@
 However, unlike prior studies, we were able to experimentally manipulate the CSPC effect across blocks of trials without changing any of the physical properties of the stimuli.
-This novel finding demonstrates that participants were able to learn and apply one context-attention association in the first phase, and subsequently ignore that association to learn a new association in the second phase.
+This novel finding demonstrates that participants were able to learn and apply one context-attention association in the first phase, and subsequently suppress that association to learn a new association in the second phase.
 
@@
 First, we show that changing the task-relevance of the presented cues corresponded with a change in attentional control in the predicted direction.
-This demonstrates that task-relevance is also a key determinant of whether a previously learned attention-context association will be used or ignored in favor of a new association.
+This demonstrates that task-relevance is also a key determinant the previously learned attention-context association is expressed or suppressed.
 Second, we show that task-relevance allowed participants resolve competition between two competing contextual cues, responding on the basis of one at the expense of the other.
@@
 Under this view, a memory process encodes attentional priorities in the representation of individual experiences and, as a result, become associated with the environment where they were used.
-The subsequent reoccurrence of a prior context triggers the retrieval and reinstatement of those attentional priorities.
+The subsequent re-occurrence of a prior context triggers the retrieval and reinstatement of those attentional priorities.
 Our results show however, that all the features of the environment may not be treated equally and that only task-relevant features are used to probe memory and guide attention.

### 2019-10-17 manuscript.tex
draft complete

@@
 \newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-\usepackage{setspace}\doublespacing
-\newenvironment{zeroindent} {\par\setlength{\parindent}{0pt}} {\par}
+\usepackage{threeparttable}
+\usepackage{setspace}
+
+\singlespacing
 \setlength{\parskip}{0pt}
@@
 Using a secondary counting task, context dimensions associated with differing levels of conflict were made task-relevant or -irrelevant across the experiment.
-In short, we found that making new contextual information task-relevant caused participants to ignore a previously learned context-attention association and adopt a new context-specific control strategy; all without changing the experimental stimuli.
-This result suggests that task-relevance is a key determinant of context-specific control.
+In short, we found that making new contextual information task-relevant caused participants to suppress a previously learned context-attention association and adopt a new context-specific control strategy; all without changing the experimental stimuli.
+Furthermore, we found participants did not spontaneously learn about context-specific proportion manipulations and explicit instructions were insufficient for producing context-specific effects.
+These results suggests that task-relevance is a key determinant of context-specific control.
 
@@
 One location was associated with a high frequency of conflict (25\% congruent trials) and the other with a low frequency of conflict (75\% congruent trials).
-Overall, the proportion of congruent trials was 50\% and randomized such that the upcoming location could not be predicted.
+Overall, the proportion of congruent trials was 50\% and trials were randomized such that the upcoming location could not be predicted.
 Even so, congruency effects were shown to be smaller for trials where the stimulus appeared in the high conflict location as compared to the low conflict location.
@@
 As a result, automatic memory-based retrieval allows attentional priorities to be rapidly adjusted in a context-appropriate fashion.
-However, the obligatory nature of memory-based attentional control remains unclear, in particular in situations when multiple contextual features could be used as cues for retrieval.
+How the learning and reinstatement process works however, remains largely unclear.
 
-For example, real-world environments offer a plethora of context cues.
-Consider writing an article in a coffee shop.
-The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), and associated attentional priorities.
-Although a laptop might cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
+The current study addresses two related issues: First, how is attentional control resolved when multiple contextual features could be used as cues?
+And second, what determines the expression and/or suppression of previously learned attentional associations?
+
+Real-world environments are complex and contain many potential cues for directing attention.
+For instance, a coffee shop is a rich environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which someone could have different experiences with and afford different learned associations.
+A laptop for example, could cue attentional processing helpful for writing while other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching.
 Given that all of these cues are available to set attentional priorities, what determines which associative relationships will be used to guide attention?
-On the one hand, context-based retrieval of attentional priorities might be completely obligatory and a writer's attention would be at the mercy of the environment.
-On the other hand, there is some evidence that contextual cuing of attention is not entirely obligatory and can be constrained by task goals, allowing the laptop to take priority as a contextual cue over other contextual cues that are irrelevant to the task at hand.
+On the one hand, context-based retrieval of attentional priorities might be completely obligatory: the mere presence of learned cues might trigger attention in a ballistic manner (e.g., Schneider \& Shiffrin, 1977; Shiffrin \& Schneider, 1977).
+Attention in this case would be at the mercy of the environment and attention is guided by the strongest association.
+On the other hand, our current task-goals might constrain the expression of previously learned associations.
+If someone sits down to write in the coffee shop, their current goals may allow the laptop to take priority over other environmental cues that are irrelevant to the task at hand.
 
-Prior work shows that task-relevance is necessary for establishing and using context-attention associations.
-First, the most commonly used context cue is location (Brosowsky \& Crump, 2016; Corballis \& Gratton, 2003; Crump, 2016; Crump et al., 2006; Crump, Vaquero, \& Milliken, 2008; Weidler \& Bugg, 2016; Weidler et al., 2018).
-Although in some sense, the location is irrelevant for identifying the color of a word, it seems disingenuous to consider it completely task-irrelevant.
-In order to identify the target, the participant must first identify and orient to its location on the screen.
-In this is sense, it is relevant to their ability to complete the task and furthermore, location information may receive priority during encoding (Logan, 1998; Mayr, 1996).
-Similar arguments could be made about other context features that are inherent to processing the target stimulus, like font-type (Bugg, Jacoby, \& Toth, 2008) and color (Vietze \& Wendt, 2009).
+Historically, perspectives of automaticity and attentional control have emphasized the role of practice and likened the learning of attentional associations to the development of automaticity in skill-learning (Logan, 1988, 1992; Schneider \& Shiffrin, 1977; Shiffrin \& Schneider, 1977).
+Under this view, forming an association requires many repeated experiences pairing a cue with a set of attentional priorities.
+Once formed however, it becomes habitual or hard-wired and the mere presence of the cue is sufficient to automatically adjust attention.
+Learned associations are therefore ballistic, difficult to suppress, and difficult to unlearn (e.g., Schneider \& Shiffrin, 1977; Posner \& Snyder, 1975a, 1975b; Shiffrin \& Schneider, 1977; Treisman, 1960, 1964, 1969).
+This view is often referenced in modern work on contextual cuing where it is assumed that learned associations require practice (e.g., Lehle \& Hübner, 2008; Crump, 2016), form without awareness or intention, and are triggered automatically by the mere presence of the cue (Crump et al., 2006; Crump \& Logan, 2010; Crump, Vaquero, \& Milliken, 2008; King et al., 2012; Reuss, Desender, Kiesel, \& Kunde, 2014; though, see Brosowsky \& Crump, 2016).
 
-Second, we are aware of only one study that has looked at task-relevance within the CSPC literature.
+An alternative view---the memory-based perspective---takes a more nuanced view (Abrahamse et al., 2016; Brosowsky \& Crump, 2018; Crump, 2016; Egner, 2014; Norman, 1969, 1976).
+Here, practice is only important to the extent that it improves memory encoding and retrieval.
+Learning an association can be thought of as the process of encoding experiences where attentional priorities and cues co-occur.
+The expression of previously learned associations however, is dictated by memory retrieval---a similarity-based, cue-driven process (e.g., Jacoby, 1978; Hintzman, 1984, 1986, 1988).
+Presumably, the features of our immediate environment automatically cue memory and reinstate the retrieved attentional priorities (Logan, 1988, 1992).
+If a few prior experiences are easily retrievable (i.e., memories are distinct or very similar to the retrieval cue), they could support the reinstatement of a learned attentional association despite very little practice (e.g., Brosowsky \& Crump, 2018).
+Conversely, if prior experiences are difficult to retrieve (i.e., memories are indistinct or low in similarity to the retrieval cue), then learned associations may not be expressed, even after much practice.
+To the extent that you could manipulate memory retrieval, you should also be able manipulate the expression of learned associations.
+
+Here, we examine whether task-relevance influences the retrieval of previously used attentional priorities.
+We hypothesized that the cue-driven, memory-retrieval process might be constrained to the features of our environment that are relevant to our on-going task and goals.
+If this is the case, then a previously learned association should be easily suppressed if that feature was made irrelevant to the task because that feature would no longer contribute to memory-retrieval.
+Furthermore, it would suggest that the mere presence of a cue is not sufficient for automatically directing attention, but instead requires task-integration (for a similar perspective, see Hommel (2004); Hommel (2019)).
+
+Recent work on contextual cueing suggests that task-relevance is important for establishing new context-attention associations.
 Crump, Vaquero, \& Milliken (2008) used a Stroop prime-probe task where the distractor word is presented first followed by a color patch probe.
@@
 The first experiment failed to find evidence for context-specificity, whereas the second did.
-Although not testing task-relevance directly, Cañadas, Rodríguez-Bailón, Milliken, and Lupiáñez (2013){]} found similar effects.
+Although not testing task-relevance directly, Cañadas, Rodríguez-Bailón, Milliken, and Lupiáñez (2013) found similar effects.
 In this study they used images of male and female faces as context cues in a flanker task.
 When given instructions to think of the faces as members of the gender categories they found CSPC effects, but when given instructions to think of the faces as individuals they did not.
-These results suggest that making a context dimension relevant to the on-going task is important for producing CSPC effects.
+These results suggest that making a context dimension relevant to the on-going task is important for establishing new associations and producing CSPC effects.
+However, the extent to which task-relevance influences the expression of previously learned associations is still unknown.
 
-\hypertarget{the-current-study}{%
-\section{The Current Study}\label{the-current-study}}
+\hypertarget{experiment-1}{%
+\section{Experiment 1}\label{experiment-1}}
 
-Prior work suggests that the task-relevance of contextual information is important for establishing new associations between context cues and attentional priorities.
-Simply put, CSPC effects emerge when context cues are somehow made relevant to the task, but do not when made irrelevant (Cañadas et al., 2013; Crump et al., 2006, 2008).
-However, it still remains unclear how task-relevance may or may not inform the use of previously learned associations.
-In the current study, we examined whether manipulating task-relevance would cause participants to ignore a previously learned association and adopt a new context-specific control strategy.
+\begin{figure}
+\centering
+\includegraphics{images/Task.jpg}
+\caption{\label{fig:figure1}Illustration of the stimuli and trial construction.
+Figure 1A shows the feature dimensions for each of the conditions.
+Figure 1B shows an example trial stimulus containing both the context and flanker images.
+Figure 1C shows an example of how feature dimensions could have been assigned to each proportion congruency (PC) condition, and an example of the secondary task assignments.
+The secondary task order, as well as the feature and congruency assignments were all randomized for each participant.}
+\end{figure}
+
+Prior work suggests that the task-relevance of contextual information could be important for establishing new associations between context cues and attentional priorities.
+Simply put, CSPC effects tend to emerge when context cues are somehow made relevant to the task, but do not when made irrelevant (Cañadas et al., 2013; Crump et al., 2006, 2008).
+However, what determines the expression of previously learned context-attention associations remains unclear.
+In the current study, we examined whether manipulating task-relevance would allow participants to suppress a previously learned association and adopt a new context-specific control strategy.
 
@@
 The critical measure of interest is the congruency effect produced in the frequency unbiased context.
-If, on the one hand, task-relevance has no impact on the use of context-attention associations we would expect no differences between the congruency effects when the high-conflict context dimension is made task-relevant or the low-conflict context dimension is made task-relevant.
+If, on the one hand, task-relevance has no impact on the use of context-attention associations we would expect no differences between the congruency effects when the high conflict context dimension is made task-relevant or the low conflict context dimension is made task-relevant.
 This could occur because all three contexts are treated as individual contexts throughout the whole experiment (e.g., Cañadas et al., 2013).
 Or it could occur because associations formed in the first block interfere with learning new associations in the second (e.g., Brosowsky \& Crump, 2016).
-On other hand, task-relevance might not only dictate how associations are formed, but also whether learned associations are used.
-In this case, we would expect smaller congruency effects when the high-conflict context dimension is made task-relevant as compared to when the low-conflict context dimension is made task-relevant.
-This would demonstrate that participants were able to ignore a previously learned association and adopt a new context-specific control strategy.
+On other hand, task-relevance may dictate the expression of previously learned associations.
+In this case, we would expect smaller congruency effects when the high conflict context dimension is made task-relevant as compared to when the low conflict context dimension is made task-relevant.
+This would demonstrate that participants were able to suppress a previously learned association and adopt a new context-specific control strategy.
 
@@
 \section{Methods}\label{methods}}
-
-\begin{figure}
-\centering
-\includegraphics{images/Task.jpg}
-\caption{\label{fig:figure1}Illustration of the stimuli and trial construction.
-Figure 1A shows the feature dimensions for each of the conditions.
-Figure 1B shows an example trial stimulus containing both the context and flanker images.
-Figure 1C shows an example of how feature dimensions could have been assigned to each proportion congruency (PC) condition, and an example of the secondary task assignments.
-The secondary task order, as well as the feature and congruency assignments were all randomized for each participant.}
-\end{figure}
 
@@
 
-Experiment 1 used a 2x2x3 mixed design with task-relevant context (0\% and 100\%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+Experiment 1 used a 2x2x3 mixed design with task-relevant context (high conflict and low conflict) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+
 All three conditions were constructed using the same general method.
@@
 \includegraphics{manuscript_files/figure-latex/figure2-1.pdf}
-\caption{\label{fig:figure2}Results from experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent).}
+\caption{\label{fig:figure2}Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent).
+Task-relevance was manipulated by the secondary feature-counting task.}
 \end{figure}
+
+\hypertarget{data-analysis}{%
+\subsection{Data Analysis}\label{data-analysis}}
+
+All analyses in this and the following experiments were performed in R (R Core Team, 2019) using a variety of R packages and resources (Aust \& Barth, 2018; Wickham, 2016; Wickham, François, Henry, \& Müller, 2019; Wilke, 2019).
+Of particular note: we used the afex and car packages to perform all the Null Hypothesis Significance Tests (Fox \& Weisberg, 2019; Singmann, Bolker, Westfall, \& Aust, 2019), the BayesFactor package to perform Bayesian analyses (Morey \& Rouder, 2018), and the conflictPower package to perform the simulation-based sensitivity and power analyses (Crump \& Brosowsky, 2019).
+All data and scripts can be found on the Open Science Framework (\url{https://osf.io/ztcyb/}).
+
+We supplemented each Null Hypothesis Significance Test with a Bayes Factor analysis (Rouder, Speckman, Sun, Morey, \& Iverson, 2009).
+Using conventional frequentist testing it is not possible to quantify the evidence for a null effect.
+A Bayes Factor, however, is a continuous measure of the relative strength of evidence and can quantify the degree to which the data are compatible with the null over the alternative hypothesis (Dienes, 2014; Rouder et al., 2009).
+All Bayesian analyses were performed using the R package BayesFactor and Bayes Factors (\(\mathrm{BFs}\)) were calculated using its default settings (Morey \& Rouder, 2018).
+\(\mathrm{BF}_{\textrm{10}}\) indicates evidence in favor of the alternative hypothesis whereas \(\mathrm{BF}_{\textrm{01}}\) indicates evidence in favor of the null hypothesis.
+To simplify the interpretation, we report the Bayes Factor in the direction the data supports (e.g., \(\mathrm{BF}_{\textrm{01}}\) when there is more evidence in favor of the null over alternative hypothesis).
+As per previous recommendations, we refer to a \(\mathrm{BF > 3}\) as \enquote{moderate} and \(\mathrm{BF > 10}\) as \enquote{strong} evidence (Jeffreys, 1961; Rouder et al., 2009).
 
@@
 The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1).
-To that end, mean correct RTs and mean error rates from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+To that end, congruency effects (incongruent minus congruent performance) from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) as the within-subjects factor and context-type (object, social, and social/non-repeating) as the between-subjects factor.
+We supplement each Null Hypothesis Significance Test with a corresponding Bayesian analysis.
 
-The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 1,608.54\), \(p = .005\), \(\hat{\eta}^2_p = .061\), demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant.
-Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, \(F(2, 128) = 0.00\), \(\mathit{MSE} = 1,608.54\), \(p = .996\), \(\hat{\eta}^2_p = .000\), showing no evidence for differences between the CSPC effects across context-type manipulations.
+The results of the reaction time analysis revealed a significant effect of the task-relevant context, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 3,217.08\), \(p = .005\), \(\hat{\eta}^2_p = .061\), 90\% CI \([0.01\), \(0.14]\), with moderate evidence in favor of the alternative, \(\mathrm{BF}_{\textrm{10}} = 6.87\) \([\pm 1.41\%]\).
+Specifically, we found smaller congruency effects when the context dimension associated with high conflict was made task-relevant as compared to when the low conflict dimension was made task-relevant.
+The main effect of context-type, however, was non-significant, \(F(2, 128) = 1.51\), \(\mathit{MSE} = 6,368.18\), \(p = .225\), \(\hat{\eta}^2_p = .023\), 90\% CI \([0\), \(0.07]\), with moderate evidence in favor of the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 3.96\) \([\pm 1.52\%]\).
+The two-way interaction between the task-relevant context and context-type was also non-significant, \(F(2, 128) < 0.01\), \(\mathit{MSE} = 3,217.08\), \(p = .996\), \(\hat{\eta}^2_p < .001\), 90\% CI \([0\), \(1]\), with moderate evidence in favor of the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 7.9\) \([\pm 1.49\%]\).
+Finally, the preferred model containing only the task-relevant context was preferred over the model containing the both factors and the interaction by a factor of \(54.25\) \([\pm 2.05\%]\).
+Therefore, congruency effects did not vary across context-types and, more importantly, the effect of task-relevance did not vary across context-types.
 
-Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 128) = 6.72\), \(\mathit{MSE} = 13.93\), \(p = .011\), \(\hat{\eta}^2_p = .050\), and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, \(F(2, 128) = 0.92\), \(\mathit{MSE} = 13.93\), \(p = .400\), \(\hat{\eta}^2_p = .014\).
-Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.
+Similarly, the corresponding error analysis also resulted a significant effect of the task-relevant context, \(F(1, 128) = 6.72\), \(\mathit{MSE} = 27.87\), \(p = .011\), \(\hat{\eta}^2_p = .050\), 90\% CI \([0.01\), \(0.12]\), with moderate evidence in favor of the alternative evidence \(\mathrm{BF}_{\textrm{10}} = 3.13\) \([\pm 5.2\%]\); A non-significant effect of context-type, \(F(2, 128) = 0.81\), \(\mathit{MSE} = 51.40\), \(p = .449\), \(\hat{\eta}^2_p = .012\), 90\% CI \([0\), \(0.05]\), with moderate evidence for the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 7.54\) \([\pm 1.22\%]\); And a non-significant interaction between task-relevant context and context-type,\(F(2, 128) = 0.92\), \(\mathit{MSE} = 27.87\), \(p = .400\), \(\hat{\eta}^2_p = .014\), 90\% CI \([0\), \(0.05]\), with strong evidence in favor of the null hypothesis,\(\mathrm{BF}_{\textrm{01}} = 15.04\) \([\pm 2.57\%]\).
+Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant and effects did not vary across context-type, corroborating the results of the reaction time analysis.
 
@@
 
+\hypertarget{exploratory-analyses-order-effects}{%
+\subsection{Exploratory analyses: Order effects}\label{exploratory-analyses-order-effects}}
+
+Previous work has shown that shifting between list-wide proportion congruent phases produced asymmetrical effects.
+Abrahamse, Duthoo, Notebaert, and Risko (2013) found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects.
+The authors posited a learned attentional modulation in the mostly-incongruent block had carried over into the mostly-congruent block reducing what, typically, would be a large congruency effect.
+In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from the use of one context cue to another.
+We therefore randomized the order across participants to control for the effects of order.
+However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was asymmetrical.
+
+To address this question, we collapsed over context-type and categorized participants according to the order of the counting task: 100\% congruent to 0\% congruent (100\%-0\%) or 0\% congruent to 100\% congruent (0\%-100\%).
+We again removed participants with error rates greater than 25\% and adopted the same outlier removal procedure as described above.
+We submitted congruency effects for frequency unbiased items to a 2x2 mixed ANOVA with task-relevant context (0\% and 100\% PC) as within-subject factors and phase order (100\%-0\% and 0\%-100\%) as the between-subjects factor, and supplemented each test with a corresponding Bayesian analysis.
+
+Consistent with the original analysis, the effect of task-relevant context was significant,\(F(1, 129) = 8.92\), \(\mathit{MSE} = 3,255.69\), \(p = .003\), \(\hat{\eta}^2_p = .065\), 90\% CI \([0.01\), \(0.14]\), with moderate evidence in favor of the alternative, \(\mathrm{BF}_{\textrm{10}} = 8.11\) \([\pm 0.83\%]\).
+However, the two-way interaction between task-relevant context and phase order was non-significant, \(F(1, 129) = 2.56\), \(\mathit{MSE} = 3,255.69\), \(p = .112\), \(\hat{\eta}^2_p = .019\), 90\% CI \([0\), \(0.07]\), with moderate evidence in favor of the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 4.92\) \([\pm 2.95\%]\).
+Therefore, we did not find statistical support for a list-shift asymmetry.
+Additionally, the (non-significant) asymmetrical effects we do see in this sample is in the opposite direction than would be predicted given the prior research (e.g., Abrahamse et al., 2013).
+
+We also conducted an additional, more severe, test of the list-shift hypothesis.
+Given that the asymmetry is interpreted as resulting from a carry-over of learned attentional modulation across phases, we might expect that any asymmetry would be exaggerated near the point of transition.
+We therefore repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.
+
+Again, the interaction between task-relevant context and phase order was non-significant, \(F(1, 129) = 0.02\), \(\mathit{MSE} = 5,732.31\), \(p = .902\), \(\hat{\eta}^2_p < .001\), 90\% CI \([0\), \(0.01]\), with moderate to strong evidence in favor of the null \(\mathrm{BF}_{\textrm{01}} = 8.88\) \([\pm 2.88\%]\).
+Interestingly, the main effect of task-relevant context was still significant, \(F(1, 129) = 6.65\), \(\mathit{MSE} = 5,732.31\), \(p = .011\), \(\hat{\eta}^2_p = .049\), 90\% CI \([0.01\), \(0.12]\), with moderate evidence in favor of the alternative, \(\mathrm{BF}_{\textrm{10}} = 3.22\) \([\pm 2.16\%]\).
+This result supports the conclusion that there was no asymmetry.
+Additionally, the the shift in context-dependent effects appears to have taken place almost immediately after the transition.
+
+\hypertarget{experiment-2}{%
+\section{Experiment 2}\label{experiment-2}}
+
+In Experiment 1, we found that manipulating the task-relevance of a shared contextual feature was associated in predictable changes in context-specific proportion congruency effects for frequency unbiased context items.
+Namely, we found larger congruency effects when the context was associated with low conflict than when the context was associated with high conflict.
+This suggests that participants learned the association between context and conflict-level in the first block (despite multiple context cues), and subsequently suppressed in the second block, allowing participants to learn a new association.
+Task-relevance then, may not just be important for establishing new associations (e.g., Crump \& Milliken, 2009) but also important for determining which learned associations are expressed in the present moment.
+
+We made two assumptions in the design of Experiment 1: First, we assumed that task-relevance was required for participants to learn about the associations between context cues and the biased proportion congruency manipulations.
+Our task was inspired by Crump and Milliken (2009) who failed find context-specific effects using a task-irrelevant shape cue until they used a counting task to make the shapes relevant.
+However, location is the most-often used context cue in these kinds of paradigms (e.g., ).
+In these cases, no task-relevance manipulation is necessary to produce CSPC effects, though, it is arguable whether location is truly task-irrelevant when localizing the target is necessary for responding.
+Regardless, it is unclear in our paradigm whether participants required the counting task to learn about the biased proportion congruency manipulations.
+
+Second, we assumed that the biased proportion congruency manipulations would have no systematic effect on the unbiased items without the counting task.
+Although we randomized all aspects of the task across participants to control for potential confounds, it still remains unclear whether the biased items would influence how participants responded to the unbiased items.
+
+Experiment 2, therefore, serves as a control experiment to test these two assumptions directly.
+Experiment 2 is identical to Experiment 1 with two important changes: First, we removed the counting task, giving no explicit instructions about how to use the context cues.
+We only informed participants that images would be present throughout the task.
+This allowed us to determine if there was any systematic effect of biased items on the unbiased items absent the counting task.
+Second, we altered the proportion congruency of the biased item sets from 100\%/0\% to 75\%/25\%.
+This allowed us to measure the congruency effect for the biased item sets to determine whether participants learned about the associations between proportion congruency and the context cues without the counting task (e.g., Crump \& Milliken, 2009).
+If this were the case, we would expect larger congruency effects for the 75\% proportion congruent items as compared to the 25\% proportion congruent items.
+
+\hypertarget{methods-1}{%
+\section{Methods}\label{methods-1}}
+
+\hypertarget{participants-1}{%
+\subsection{Participants}\label{participants-1}}
+
+All participants were recruited from Amazon Mechanical Turk (AMT) and compensated \$2.00 for participating.
+The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by \$6.00 per hour.
+For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study.
+Participants were included in the study if they completed all trials.
+We posted 50 HITs and 50 participants completed all trials.
+
+\hypertarget{apparatus-stimuli-1}{%
+\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli-1}}
+
+The apparatus and stimuli were identical to Experiment 1. The context stimuli were identical to those used for the object condition in Experiment 1.
+
+\hypertarget{design-1}{%
+\subsection{Design}\label{design-1}}
+
+Experiment 2 used a 2x3 within-subjects design with proportion congruent (25\%, 50\%, and 75\%) and congruency (congruent and incongruent) as factors.
+The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials or instructions informing participants about the proportion manipulations.
+The design in every other respect was identical to Experiment 1.
+
+\hypertarget{procedure-1}{%
+\subsection{Procedure}\label{procedure-1}}
+
+All participants were AMT workers who found the experiment using the AMT system.
+The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board.
+Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form.
+Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window.
+Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing \enquote{z} if the arrow pointed left, and \enquote{m} if the arrow pointed right.
+
+Each trial began with a blank inter-stimulus interval (ISI) of 400 ms, followed by a fixation cross presented in the center of the screen for 200 ms, then a second blank ISI of 400 ms.
+Next, the flanker and context stimuli appeared in the center of screen (the flanker above the context image; see Figure 1B) and remained on screen until a response was made.
+Following a response, accuracy feedback was presented for 1000 ms.
+A response automatically triggered the next trial.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/figure3-1.pdf}
+\caption{\label{fig:figure3}Results from Experiment 2 showing congruency effects (incongruent - congruent) across proportion congruency (25\%, 75\%, and 100\% PC) in reaction times (left) and error rates (right).}
+\end{figure}
+
+\hypertarget{results-1}{%
+\section{Results}\label{results-1}}
+
+Participants with mean error rates greater than 25\% were excluded from the analyses, eliminating 3 participants.
+For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure.
+The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms (Van Selst \& Jolicoeur, 1994).
+This procedure removed 3.14\% of the total observations.
+
+The questions of interest were whether participants would learn the associations between the context cues without the task-relevance manipulation (i.e., the counting task) and whether responding to the unbiased cues would be influenced by the presence of the biased cues.
+To that end, congruency effects (incongruent minus congruent performance) for RTs and error rates were submitted to an analysis of variance (ANOVA) with proportion congruency (25\%, 50\%, and 75\%) as the sole within-subject factor.
+
+The results of the RT analysis revealed the effect of proportion congruency to be non-significant, \(F(2, 92) = 0.85\), \(\mathit{MSE} = 997.11\), \(p = .431\), \(\hat{\eta}^2_p = .018\), 90\% CI \([0\), \(0.07]\), with moderate evidence in favor of the null, \(\mathrm{BF}_{\textrm{01}} = 6.91\) \([\pm 0.9\%]\).
+Similarly, the corresponding error analysis also resulted in a non-significant effect of proportion congruency, \(F(2, 92) = 0.45\), \(\mathit{MSE} = 9.23\), \(p = .641\), \(\hat{\eta}^2_p = .010\), 90\% CI \([0\), \(0.05]\), with strong evidence in favor of the null, \(\mathrm{BF}_{\textrm{01}} = 9.93\) \([\pm 1.03\%]\).
+Therefore, there was no evidence that the context cues, absent the counting task, systematically influenced the congruency effects in any way.
+
+\begin{table}[htbp]
+\centering
+\begin{threeparttable}
+\caption{Reaction times and error rates from Experiment 2.}
+\label{TR_table_2}
+\centering
+\begin{tabular}{lcccc}
+\toprule
+& \multicolumn{2}{c}{Congruent} & \multicolumn{2}{c}{Incongruent} \\
+\cmidrule(rl){2-3}
+\cmidrule(rl){4-5}
+\multicolumn{1}{c}{PC} & \multicolumn{1}{c}{RT} & \multicolumn{1}{c}{ER} & \multicolumn{1}{c}{RT} & \multicolumn{1}{c}{ER}  \\
+\midrule
+\multicolumn{1}{l}{25\%} & \multicolumn{1}{l}{518 (16)} & \multicolumn{1}{l}{0.35 (0.17)} & \multicolumn{1}{l}{598 (17)} & \multicolumn{1}{l}{3.78 (0.71)} \\
+\multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{515 (15)} & \multicolumn{1}{l}{0.27 (0.1)} & \multicolumn{1}{l}{603 (17)} & \multicolumn{1}{l}{4.26 (0.7)} \\
+\multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{523 (18)} & \multicolumn{1}{l}{0.18 (0.07)} & \multicolumn{1}{l}{603 (19)} & \multicolumn{1}{l}{3.72 (0.61)} \\
+& & & & \\
+\bottomrule
+\multicolumn{5}{l}{\textit{Note}: RT = Reaction Time (ms);  ER = Error} \\
+\multicolumn{5}{l}{Rates (\%); PC = Proportion Congruent; Standard} \\
+\multicolumn{5}{l}{Errors are presented in parantheses.} \\
+\end{tabular}%
+\end{threeparttable}
+\end{table}
+
+\hypertarget{experiment-3}{%
+\section{Experiment 3}\label{experiment-3}}
+
+The goal of the current study has been to examine the importance of task-relevance for the contextual recruitment of selective attention.
+In Experiment 1, we found that task-relevance allowed participants to exploit context cues in the presence of a competing, contradictory cue and subsequently suppress a previously learned association in favor of a different context cue.
+In Experiment 2, we conceptually replicated previous work showing that task-relevance was necessary for participants to learn about the biased proportion congruency associations (e.g., Crump \& Milliken, 2009) and ruled out possible confounding effects of the biased items.
+
+Experiment 3 tests the boundaries of the task-relevance effect found in Experiment 1.
+The evidence thus far suggests that context-cues, rather than being irrelevant to the task (as their namesake would suggest), need to be integrated into the task-representation to guide attentional control.
+There is some evidence that instructions alone can be sufficient to produce list-wide proportion congruency effects, though not item-specific proportion congruency effects (Desender, 2018; Entel, Tzelgov, \& Bereby-Meyer, 2014) and not context-specific proportion congruency effects (Crump \& Milliken, 2009).
+Explicit instructions however, are another way of making context-cues relevant to the on-going task and could serve the same purpose as the counting task.
+In Experiment 3, we test whether participants are able to explicitly use the context-cues to guide attentional control through an instruction manipulation.
+
+\hypertarget{methods-2}{%
+\section{Methods}\label{methods-2}}
+
+\hypertarget{participants-2}{%
+\subsection{Participants}\label{participants-2}}
+
+All participants were recruited from Amazon Mechanical Turk (AMT) and compensated \$2.00 for participating.
+The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by \$6.00 per hour.
+For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study.
+Participants were included in the study if they completed all trials.
+We posted 50 HITs and 50 participants completed all trials.
+
+\hypertarget{apparatus-stimuli-2}{%
+\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli-2}}
+
+The apparatus and stimuli were identical to Experiment 1. The context stimuli were identical to those used for the object condition in Experiment 1.
+
+\hypertarget{design-2}{%
+\subsection{Design}\label{design-2}}
+
+Experiment 3 used a 2x3 mixed design with task-relevant context (0\% and 100\%) and unbiased-item congruency (congruent and incongruent) as the within-subject factors.
+The experiment consisted of 288 flanker trials (96 per proportion congruent condition) and did not include any counting trials.
+However, participants were explicitly informed about the proportion congruency manipulations and instructed to make used of the context cues (see the Procedure section below for more details).
+Therefore, unlike Experiment 1, context images were made task-relevant through explicit instructions rather than the counting task.
+The design in every other respect was identical to Experiment 1.
+
+\hypertarget{procedure-2}{%
+\subsection{Procedure}\label{procedure-2}}
+
+All participants were AMT workers who found the experiment using the AMT system.
+The participant recruitment procedure and tasks were approved by the Brooklyn College Institutional Review Board.
+Each participant read a short description of the task and gave consent by pressing a button acknowledging they had read the displayed consent form.
+Participants then completed a short demographic survey, and proceeded to the main task, which was displayed as a pop-up window.
+Participants were instructed to identify the direction of the center arrow on each trial as quickly and accurately as possible by pressing \enquote{z} if the arrow pointed left, and \enquote{m} if the arrow pointed right.
+
+Importantly, participants were given further instructions to exploit the proportion congruency associated with context cues.
+Halfway through the experiment, participants received new instructions about which context features were relevant and associated with high/low conflict.
+For example:
+
+\begin{quote}
+\emph{"On every trial you'll see five arrows (pointed left or right) paired with an image.}
+\end{quote}
+
+\begin{quote}
+\emph{The images will help you perform this task.}
+\end{quote}
+
+\begin{quote}
+\emph{The arrows will either be congruent (the center arrow is the same as the flanking arrows) or incongruent (the center arrow is different from the flanking arrows).
+Incongruent trials are typically harder because you need to ignore the flanking arrows, while the congruent trials are easier, because you do not need to ignore the flanking arrows.}
+\end{quote}
+
+\begin{quote}
+\emph{In the first block of the experiment, trials that include a chair (regardless of whether it is blue or green) will be mostly incongruent.
+That is, most of the trials that include a chair will be hard.}
+\end{quote}
+
+\begin{quote}
+\emph{This will be helpful to perform the task, so try to proactively use this information when you perform the task."}
+\end{quote}
+
+Each trial began with a blank inter-stimulus interval (ISI) of 400 ms, followed by a fixation cross presented in the center of the screen for 200 ms, then a second blank ISI of 400 ms.
+Next, the flanker and context stimuli appeared in the center of screen (the flanker above the context image; see Figure 1B) and remained on screen until a response was made.
+Following a response, accuracy feedback was presented for 1000 ms.
+A response automatically triggered the next trial.
+
+\begin{figure}
+\centering
+\includegraphics{manuscript_files/figure-latex/figure4-1.pdf}
+\caption{\label{fig:figure4}Results from Experiment 3 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent).
+Task-relevance was manipulated through explicit instructions.}
+\end{figure}
+
+\hypertarget{results-2}{%
+\section{Results}\label{results-2}}
+
+Participants with mean error rates greater than 25\% were excluded from the analyses, eliminating 4 participants.
+For all remaining participants, the correct RTs from frequency unbiased trials in each condition were submitted to an outlier removal procedure.
+The non-recursive Van Selst and Jolicoeur outlier removal procedure was applied after removing response times greater than 3000 ms (Van Selst \& Jolicoeur, 1994).
+This procedure removed 3.42\% of the total observations.
+
+The primary question of interest was whether the task-relevance of context features (made relevant through explicit task instructions) associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items.
+Mean correct RTs and mean error rates from frequency unbiased trials were submitted to an analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) as the within-subject factors.
+
+The results of the RT analysis revealed the effect of task-relevance to be non-significant, \(F(1, 45) = 0.02\), \(\mathit{MSE} = 4,030.54\), \(p = .876\), \(\hat{\eta}^2_p = .001\), 90\% CI \([0\), \(0.04]\), with moderate evidence in favor of the null, \(\mathrm{BF}_{\textrm{01}} = 4.48\) \([\pm 2.17\%]\).
+Similarly, the corresponding error analysis also resulted in a non-significant effect of task-relevance, \(F(1, 45) = 0.66\), \(\mathit{MSE} = 28.52\), \(p = .420\), \(\hat{\eta}^2_p = .014\), 90\% CI \([0\), \(0.11]\), with moderate evidence in favor of the null, \(\mathrm{BF}_{\textrm{01}} = 3.39\) \([\pm 1.19\%]\).
+
+\begin{table}[htbp]
+\centering
+\begin{threeparttable}
+\caption{Reaction times and error rates from Experiment 3.}
+\label{TR_table_3}
+\centering
+\begin{tabular}{llcccc}
+\toprule
+& & \multicolumn{2}{c}{Congruent} & \multicolumn{2}{c}{Incongruent} \\
+\cmidrule(rl){3-4}
+\cmidrule(rl){5-6}
+\multicolumn{1}{c}{Task-Relevant Context} & \multicolumn{1}{c}{PC} & \multicolumn{1}{c}{RT} & \multicolumn{1}{c}{ER} & \multicolumn{1}{c}{RT} & \multicolumn{1}{c}{ER}  \\
+\midrule
+\multirow{3}{*}{Low Conflict} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{658 (28)} & \multicolumn{1}{l}{5.66 (0.94)} \\
+& \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{579 (32)} & \multicolumn{1}{l}{0.54 (0.31)} & \multicolumn{1}{l}{664 (29)} & \multicolumn{1}{l}{5.25 (1.03)} \\
+& \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{571 (26)} & \multicolumn{1}{l}{0.45 (0.24)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
+\midrule
+\multirow{3}{*}{High Conflict} & \multicolumn{1}{l}{0\%} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{643 (26)} & \multicolumn{1}{l}{6.43 (0.87)} \\
+& \multicolumn{1}{l}{50\%} & \multicolumn{1}{l}{550 (21)} & \multicolumn{1}{l}{0.36 (0.28)} & \multicolumn{1}{l}{637 (23)} & \multicolumn{1}{l}{5.98 (0.99)} \\
+& \multicolumn{1}{l}{100\%} & \multicolumn{1}{l}{547 (22)} & \multicolumn{1}{l}{0.45 (0.17)} & \multicolumn{1}{l}{-} & \multicolumn{1}{l}{-} \\
+ & & & & & \\
+\bottomrule
+\multicolumn{6}{l}{\textit{Note}: RT = Reaction Time (ms);  ER = Error Rates (\%);} \\
+\multicolumn{6}{l}{PC = Proportion Congruent; Standard Errors are presented in parantheses.} \\
+\end{tabular}%
+\end{threeparttable}
+\end{table}
+
+\hypertarget{estimating-replicability-by-simulation-based-sensitivity--and-power-analyses}{%
+\section{Estimating replicability by simulation-based sensitivity- and power-analyses}\label{estimating-replicability-by-simulation-based-sensitivity--and-power-analyses}}
+
+In Experiment 1, we found no evidence for differences in the task-relevance effect across context-type.
+Similarly, Experiments 2 and 3 failed to find CSPC effects.
+To determine the limitations in our ability to draw inferences from these results, we need to assess the extent to which our experiments could have detected effects, if present.
+Although replicability has become an important and salient issue in Psychology at large (e.g., Camerer et al., 2018; Collaboration, 2015), this issue has also arisen in the context-specific proportion congruency literature {[}Crump et al.
+(2017); Hutcheon and Spieler (2017); {]}.
+
+To address this issue in the current study---and to do so transparently---we conducted simulation-based power and sensitivity analyses {[}{]} to determine the range effect sizes our experimental design was sensitive to detect and the required sample sizes to detect a range of effects.
+We used a Monte Carlo simulation approach with a statistical model of the distributions that underlie the effect of interest (Maxwell, 2008).
+Rather than estimating power based on observed effect sizes from prior experiments (typically, over-estimates), we instead estimated the properties of the base reaction time distributions from our current data and sampled from these distributions using a Monte Carlo simulation approach to estimate the replication success rate across a range of effect sizes and sample sizes.
+
+We created the conflictPower R-package to conduct the Monte Carlo simulations ({\textbf{???}}).
+The conflictPower package samples simulated reaction time data for subjects at the trial-level using base reaction time distributions for the conflict and no-conflict conditions.
+To generate the base reaction time distributions, we fitted ex-Gaussian functions to the reaction time data from individual participants and averaged across all three experiments using the retimes R-package (Massidda, 2013).
+We then used the conflictPower package to simulate the results across a range of effect and sample sizes, calculating the proportion of experiments, across \(10 000\) simulations, resulting in a p-value less than \(.05\) (see Figure 5; for a more detailed explanation of the sampling procedure see Crump and Brosowsky, 2019).
+
+First, the results of these analyses show that our experimental design was reasonably powered to detect CSPC effects.
+In particular, with 150 participants, we estimated 89\% power to detect effects as small 10 ms; With only 50 participants, we were still reasonably powered to detect CSPC effects as small as 15 ms at an estimated 78\%.
+Understandably, our design was not as sensitive to detecting changes in the CSPC effect between groups (Experiment 1, for example).
+We estimated only 75\% power to detect the difference between a 20 ms and 0 ms CSPC effect with 50 participants per group.
+That is, the experimental design could detect the presence/absence of the CSPC effect moderately well, but likely does not reliably detect small changes in the CSPC effect across conditions.
+To reliably detect a 15 ms change in the CSPC effect at roughly 80\% power, for example, we estimate would require 100 participants per group.
+
+\begin{figure}[!h]
+\includegraphics[width=\textwidth]{manuscript_files/figure-latex/figure5-1} \caption{Results from the simulation-based sensitivity and power-analyses.
+Figure A shows the sensitivity of our experimental design to detect a range of effect sizes for the context-specific proportion congruency (CSPC) effect with 50 (e.g., Experiments 2 and 3) and 150 (e.g., Experiment 1) participants.
+Figure B shows the sensitivity to detect the CSPC by context-type interaction with 50 participants per group (e.g., Experiment 1).
+Figures C and D show the estimated power curves for the CSPC and CSPC by context-type effects across sample sizes.
+Each data point represents the proportion of p-values less than .05 from 10,000 simulations.}\label{fig:figure5}
+\end{figure}
+
 \hypertarget{general-discussion}{%
@@
 The aim of the current study was to determine whether task-relevance plays a role in the contextual recruitment of selective attention.
-Specifically, we tested whether manipulating the relative task-relevance of context cues could cause participants to ignore a previously learned context-association and apply a new association.
+In Experiment 1, we tested whether manipulating the relative task-relevance of context cues could cause participants to suppress a previously learned context-association and apply a new association.
 We created a frequency unbiased context cue that shared features with two frequency biased contexts and used a feature-counting task to manipulate the task-relevance of context dimensions across two blocks of trials.
@@
 
-The key finding was that the congruency effects for the frequency unbiased items were significantly larger when the low-conflict context was made task-relevant as compared to when the high-conflict context was made task-relevant.
+The key finding was that congruency effects for the frequency unbiased items were significantly larger when the low conflict context was made task-relevant as compared to when the high conflict context was made task-relevant.
 This result is consistent with prior CSPC effects and, like the previous work, suggests that the context cues triggered rapid adjustments to attentional control (Crump \& Milliken, 2009).
 However, unlike prior studies, we were able to experimentally manipulate the CSPC effect across blocks of trials without changing any of the physical properties of the stimuli.
-This novel finding demonstrates that participants were able to learn and apply one context-attention association in the first phase, and subsequently ignore that association to learn a new association in the second phase.
+This novel finding demonstrates that participants were able to learn and apply one context-attention association in the first phase, and subsequently suppress that association to learn a new association in the second phase.
 
@@
 (2013) eliminated the CSPC effect by making the contextual cue effectively unrelated to the task.
-These studies suggest that task-relevance plays an important role in establishing associations between contextual information and attentional priorities to produce CSPC effects.
+These studies suggest that task-relevance plays an important role in establishing new associations between contextual information and attentional priorities to produce CSPC effects.
 Our finding extends this work in two important ways.
 First, we show that changing the task-relevance of the presented cues corresponded with a change in attentional control in the predicted direction.
-This demonstrates that task-relevance is also a key determinant of whether a previously learned attention-context association will be used or ignored in favor of a new association.
+This demonstrates that task-relevance is also a key determinant the previously learned attention-context association is expressed or suppressed.
 Second, we show that task-relevance allowed participants resolve competition between two competing contextual cues, responding on the basis of one at the expense of the other.
@@
 Under this view, a memory process encodes attentional priorities in the representation of individual experiences and, as a result, become associated with the environment where they were used.
-The subsequent reoccurrence of a prior context triggers the retrieval and reinstatement of those attentional priorities.
+The subsequent re-occurrence of a prior context triggers the retrieval and reinstatement of those attentional priorities.
 Our results show however, that all the features of the environment may not be treated equally and that only task-relevant features are used to probe memory and guide attention.
 
-Another key result of this study concerned the different stimuli used as context cues.
+Finally, another key result of this study concerned the different stimuli used as context cues in Experiment 1.
 Across the three conditions, we varied the type of context image and dimensions.
@@
 
-\leavevmode\hypertarget{ref-bugg_multiple_2008}{}%
-Bugg, J., Jacoby, L.
-L., \& Toth, J.
-P.
-(2008).
-Multiple levels of control in the Stroop task.
-\emph{Memory \& Cognition}, \emph{36}, 1484--1494.
-doi:\href{https://doi.org/10.3758/MC.36.8.1484}{10.3758/MC.36.8.1484}
+\leavevmode\hypertarget{ref-camerer_evaluating_2018}{}%
+Camerer, C.
+F., Dreber, A., Holzmeister, F., Ho, T.-H., Huber, J., Johannesson, M., \ldots{} Wu, H.
+(2018).
+Evaluating the replicability of social science experiments in Nature and Science between 2010 and 2015.
+\emph{Nature Human Behaviour}, \emph{2}(9), 637--644.
+doi:\href{https://doi.org/10.1038/s41562-018-0399-z}{10.1038/s41562-018-0399-z}
 
@@
 doi:\href{https://doi.org/10.1080/17470218.2016.1206130}{10.1080/17470218.2016.1206130}
+
+\leavevmode\hypertarget{ref-crump_context-specific_2006}{}%
+Crump, M.
+J.
+C., Gong, Z., \& Milliken, B.
+(2006).
+The context-specific proportion congruent Stroop effect: Location as a contextual cue.
+\emph{Psychonomic Bulletin \& Review}, \emph{13}, 316--321.
+doi:\href{https://doi.org/10.3758/BF03193850}{10.3758/BF03193850}
+
+\leavevmode\hypertarget{ref-crump_contextual_2010}{}%
+Crump, M.
+J.
+C., \& Logan, G.
+D.
+(2010).
+Contextual control over task-set retrieval.
+\emph{Attention, Perception, \& Psychophysics}, \emph{72}, 2047--2053.
+Retrieved from \url{http://link.springer.com/article/10.3758/BF03196681}
 
@@
 
-\leavevmode\hypertarget{ref-crump_context-specific_2006}{}%
-Crump, M.
-J., Gong, Z., \& Milliken, B.
-(2006).
-The context-specific proportion congruent Stroop effect: Location as a contextual cue.
-\emph{Psychonomic Bulletin \& Review}, \emph{13}, 316--321.
-doi:\href{https://doi.org/10.3758/BF03193850}{10.3758/BF03193850}
-
 \leavevmode\hypertarget{ref-crump_context-specific_2008}{}%
 Crump, M.
-J., Vaquero, J.
+J.
+C., Vaquero, J.
+M.
 M., \& Milliken, B.
@@
 
+\leavevmode\hypertarget{ref-desender_different_2018}{}%
+Desender, K.
+(2018).
+Different mechanisms can account for the instruction induced proportion congruency effect.
+\emph{Acta Psychologica}, \emph{184}, 39--45.
+doi:\href{https://doi.org/10.1016/j.actpsy.2017.03.011}{10.1016/j.actpsy.2017.03.011}
+
 \leavevmode\hypertarget{ref-devine_stereotypes_1989}{}%
 Devine, P. G. (1989). Stereotypes and prejudice: Their automatic and controlled components. \emph{Journal of Personality and Social Psychology}, \emph{56}(1), 5.
+
+\leavevmode\hypertarget{ref-dienes_using_2014}{}%
+Dienes, Z. (2014). Using Bayes to get the most out of non-significant results. \emph{Frontiers in Psychology}, \emph{5}. doi:\href{https://doi.org/10.3389/fpsyg.2014.00781}{10.3389/fpsyg.2014.00781}
 
@@
 
+\leavevmode\hypertarget{ref-r_car_2019}{}%
+Fox, J., \& Weisberg, S. (2019). \emph{An R companion to applied regression} (Third.). Thousand Oaks CA: Sage. Retrieved from \url{https://socialsciences.mcmaster.ca/jfox/Books/Companion/}
+
+\leavevmode\hypertarget{ref-hintzman_minerva_1984}{}%
+Hintzman, D.
+L.
+(1984).
+MINERVA 2: A simulation model of human memory.
+\emph{Behavior Research Methods, Instruments, \& Computers}, \emph{16}(2), 96--101.
+Retrieved from \url{http://link.springer.com/article/10.3758/BF03202365}
+
+\leavevmode\hypertarget{ref-hintzman_schema_1986}{}%
+Hintzman, D. L. (1986). Schema abstraction in a multiple-trace memory model. \emph{Psychological Review}, \emph{93}, 411--428.
+
+\leavevmode\hypertarget{ref-hintzman_judgments_1988}{}%
+Hintzman, D. L. (1988). Judgments of frequency and recognition memory in a multiple-trace memory model. \emph{Psychological Review}, \emph{95}(4), 528.
+
+\leavevmode\hypertarget{ref-hommel_event_2004}{}%
+Hommel, B.
+(2004).
+Event files: Feature binding in and across perception and action.
+\emph{Trends in Cognitive Sciences}, \emph{8}, 494--500.
+doi:\href{https://doi.org/10.1016/j.tics.2004.08.007}{10.1016/j.tics.2004.08.007}
+
+\leavevmode\hypertarget{ref-hommel_theory_2019}{}%
+Hommel, B.
+(2019).
+Theory of Event Coding (TEC) V2.0: Representing and controlling perception and action.
+\emph{Attention, Perception, \& Psychophysics}.
+doi:\href{https://doi.org/10.3758/s13414-019-01779-4}{10.3758/s13414-019-01779-4}
+
 \leavevmode\hypertarget{ref-hutcheon_limits_2017}{}%
@@
 
+\leavevmode\hypertarget{ref-jacoby_interpreting_1978}{}%
+Jacoby, L. L. (1978). On interpreting the effects of repetition: Solving a problem versus remembering a solution. \emph{Journal of Verbal Learning and Verbal Behavior}, \emph{17}(6), 649--667.
+
+\leavevmode\hypertarget{ref-jeffreys1961theory}{}%
+Jeffreys, H. (1961). \emph{Theory of probability, clarendon}. Oxford: Oxford University Press, Clarendon Press.
+
 \leavevmode\hypertarget{ref-king_priming_2012}{}%
@@
 
+\leavevmode\hypertarget{ref-lehle_fly_2008}{}%
+Lehle, C., \& Hübner, R.
+(2008).
+On-the-fly adaptation of selectivity in the flanker task.
+\emph{Psychonomic Bulletin \& Review}, \emph{15}(4), 814--818.
+Retrieved from \url{http://link.springer.com/article/10.3758/PBR.15.4.814}
+
 \leavevmode\hypertarget{ref-logan_attention_1980}{}%
@@
 
-\leavevmode\hypertarget{ref-logan_what_1998}{}%
-Logan, G. D. (1998). What is learned during automatization? II. Obligatory encoding of spatial location. \emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{24}, 1720.
+\leavevmode\hypertarget{ref-logan_toward_1988}{}%
+Logan, G. D. (1988). Toward an instance theory of automatization. \emph{Psychological Review}, \emph{95}, 492--527. doi:\href{https://doi.org/10.1037/0033-295X.95.4.492}{10.1037/0033-295X.95.4.492}
+
+\leavevmode\hypertarget{ref-logan_attention_1992}{}%
+Logan, G. D. (1992). Attention and preattention in theories of automaticity. \emph{The American Journal of Psychology}, 317--339.
 
@@
 
-\leavevmode\hypertarget{ref-mayr_spatial_1996}{}%
-Mayr, U.
-(1996).
-Spatial attention and implicit sequence learning: Evidence for independent learning of spatial and nonspatial sequences.
-\emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{22}, 350.
+\leavevmode\hypertarget{ref-r_retimes_2013}{}%
+Massidda, D. (2013). \emph{Retimes: Reaction time analysis}. Retrieved from \url{https://CRAN.R-project.org/package=retimes}
 
@@
 
+\leavevmode\hypertarget{ref-r_bayesfactor_2018}{}%
+Morey, R. D., \& Rouder, J. N. (2018). \emph{BayesFactor: Computation of bayes factors for common designs}. Retrieved from \url{https://CRAN.R-project.org/package=BayesFactor}
+
+\leavevmode\hypertarget{ref-norman_memory_1969}{}%
+Norman, D. A. (1969). Memory while shadowing. \emph{Quarterly Journal of Experimental Psychology}, \emph{21}(1), 85--93.
+
+\leavevmode\hypertarget{ref-norman_memory_1976}{}%
+Norman, D. A. (1976). Memory and attention: An introduction to human information processing.
+
+\leavevmode\hypertarget{ref-posner_attention_1975}{}%
+Posner, M.
+I., \& Snyder, C.
+R.
+R.
+(1975a).
+Attention and cognitive control.
+In R.
+L.
+Solso (Ed.), \emph{Information processing and cognition: The Loyola symposium} (pp.
+153--175).
+Hillsdale, NJ: Erlbaum.
+
+\leavevmode\hypertarget{ref-posner_facilitation_1975}{}%
+Posner, M.
+I., \& Snyder, C.
+R.
+R.
+(1975b).
+Facilitation and inhibition in the processing of signals.
+In P.
+M.
+A.
+Rabbit \& S.
+Dornic (Eds.), \emph{Attention and performance V} (pp.
+669--682).
+New York, NY: Academic Press.
+
+\leavevmode\hypertarget{ref-r_software_2019}{}%
+R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-reuss_unconscious_2014}{}%
+Reuss, H., Desender, K., Kiesel, A., \& Kunde, W.
+(2014).
+Unconscious conflicts in unconscious contexts: The role of awareness and timing in flexible conflict adaptation.
+\emph{Journal of Experimental Psychology: General}, \emph{143}, 1701--1718.
+doi:\href{https://doi.org/10.1037/a0036437}{10.1037/a0036437}
+
+\leavevmode\hypertarget{ref-rouder_bayesian_2009}{}%
+Rouder, J.
+N., Speckman, P.
+L., Sun, D., Morey, R.
+D., \& Iverson, G.
+(2009).
+Bayesian t tests for accepting and rejecting the null hypothesis.
+\emph{Psychonomic Bulletin \& Review}, \emph{16}, 225--237.
+doi:\href{https://doi.org/10.3758/PBR.16.2.225}{10.3758/PBR.16.2.225}
+
 \leavevmode\hypertarget{ref-schmidt_stroop_2008}{}%
@@
 doi:\href{https://doi.org/10.1037/0278-7393.34.3.514}{10.1037/0278-7393.34.3.514}
+
+\leavevmode\hypertarget{ref-schneider_controlled_1977}{}%
+Schneider, W., \& Shiffrin, R. M. (1977). Controlled and automatic human information processing: I. Detection, search, and attention. \emph{Psychological Review}, \emph{84}(1), 1.
+
+\leavevmode\hypertarget{ref-shiffrin_controlled_1977}{}%
+Shiffrin, R.
+M., \& Schneider, W.
+(1977).
+Controlled and automatic human information processing: II.
+Perceptual learning, automatic attending and a general theory.
+\emph{Psychological Review}, \emph{84}, 127--190.
+doi:\href{https://doi.org/10.1037/0033-295X.84.2.127}{10.1037/0033-295X.84.2.127}
+
+\leavevmode\hypertarget{ref-r_afex_2019}{}%
+Singmann, H., Bolker, B., Westfall, J., \& Aust, F. (2019). \emph{Afex: Analysis of factorial experiments}. Retrieved from \url{https://CRAN.R-project.org/package=afex}
 
@@
 
+\leavevmode\hypertarget{ref-r_wickham_ggplot2_2016}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-r_wickham_dplyr_2019}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\hypertarget{ref-r_cowplot_2019}{}%
+Wilke, C. O. (2019). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
+
 \endgroup
 
+\clearpage
+\makeatletter
+\efloat@restorefloats
+\makeatother
+
+\begin{appendix}
+\section{}
+\begin{table}[htbp]
+\centering
+\begin{threeparttable}
+\caption{Demographics from Experiments 1 to 3}
+\label{TR_table_4}
+\begin{tabular}{llccccccc}
+\toprule
+& \multicolumn{2}{c}{Exp. 1} & \multicolumn{2}{c}{Exp. 2} & \multicolumn{2}{c}{Exp. 3} & \\
+\cmidrule(rl){2-3}
+\cmidrule(rl){4-5}
+\cmidrule(rl){6-7}
+\multicolumn{1}{c}{Age} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{\%}  \\
+\midrule
+\multicolumn{1}{l}{> 59} & \multicolumn{1}{l}{10} & \multicolumn{1}{l}{ 6.99} & \multicolumn{1}{l}{3} & \multicolumn{1}{l}{ 6.00} & \multicolumn{1}{l}{2} & \multicolumn{1}{l}{ 4.00} \\
+\multicolumn{1}{l}{50-59} & \multicolumn{1}{l}{21} & \multicolumn{1}{l}{14.69} & \multicolumn{1}{l}{7} & \multicolumn{1}{l}{14.00} & \multicolumn{1}{l}{8} & \multicolumn{1}{l}{16.00} \\
+\multicolumn{1}{l}{40-49} & \multicolumn{1}{l}{16} & \multicolumn{1}{l}{11.19} & \multicolumn{1}{l}{8} & \multicolumn{1}{l}{16.00} & \multicolumn{1}{l}{5} & \multicolumn{1}{l}{10.00} \\
+\multicolumn{1}{l}{30-39} & \multicolumn{1}{l}{55} & \multicolumn{1}{l}{38.46} & \multicolumn{1}{l}{18} & \multicolumn{1}{l}{36.00} & \multicolumn{1}{l}{23} & \multicolumn{1}{l}{46.00} \\
+\multicolumn{1}{l}{18-29} & \multicolumn{1}{l}{40} & \multicolumn{1}{l}{27.97} & \multicolumn{1}{l}{14} & \multicolumn{1}{l}{28.00} & \multicolumn{1}{l}{12} & \multicolumn{1}{l}{24.00} \\
+\multicolumn{1}{l}{No Response} & \multicolumn{1}{l}{1} & \multicolumn{1}{l}{ 0.70} & \multicolumn{1}{l}{0} & \multicolumn{1}{l}{ 0.00} & \multicolumn{1}{l}{0} & \multicolumn{1}{l}{ 0.00} \\
+& & & & & & & \\
+\multicolumn{1}{c}{Gender} & & & & & & \\
+\midrule
+\multicolumn{1}{l}{Female} & \multicolumn{1}{l}{66} & \multicolumn{1}{l}{45.83} & \multicolumn{1}{l}{20} & \multicolumn{1}{l}{40.00} & \multicolumn{1}{l}{18} & \multicolumn{1}{l}{36.00} \\
+\multicolumn{1}{l}{Male} & \multicolumn{1}{l}{76} & \multicolumn{1}{l}{52.78} & \multicolumn{1}{l}{29} & \multicolumn{1}{l}{58.00} & \multicolumn{1}{l}{32} & \multicolumn{1}{l}{64.00} \\
+\multicolumn{1}{l}{No Response} & \multicolumn{1}{l}{2} & \multicolumn{1}{l}{ 1.39} & \multicolumn{1}{l}{1} & \multicolumn{1}{l}{ 2.00} & \multicolumn{1}{l}{0} & \multicolumn{1}{l}{ 0.00} \\
+& & & & & & & \\
+\multicolumn{1}{c}{Handedness} & & & & & & \\
+\midrule
+\multicolumn{1}{l}{Left} & \multicolumn{1}{l}{21} & \multicolumn{1}{l}{14.58} & \multicolumn{1}{l}{5} & \multicolumn{1}{l}{10.00} & \multicolumn{1}{l}{11} & \multicolumn{1}{l}{22.00} \\
+\multicolumn{1}{l}{Right} & \multicolumn{1}{l}{118} & \multicolumn{1}{l}{81.94} & \multicolumn{1}{l}{44} & \multicolumn{1}{l}{88.00} & \multicolumn{1}{l}{38} & \multicolumn{1}{l}{76.00} \\
+\multicolumn{1}{l}{Both} & \multicolumn{1}{l}{3} & \multicolumn{1}{l}{ 2.08} & \multicolumn{1}{l}{1} & \multicolumn{1}{l}{ 2.00} & \multicolumn{1}{l}{1} & \multicolumn{1}{l}{ 2.00} \\
+\multicolumn{1}{l}{No Response} & \multicolumn{1}{l}{2} & \multicolumn{1}{l}{ 1.39} & \multicolumn{1}{l}{0} & \multicolumn{1}{l}{ 0.00} & \multicolumn{1}{l}{0} & \multicolumn{1}{l}{ 0.00} \\
+& & & & & \\
+\bottomrule
+\end{tabular}%
+\end{threeparttable}
+\end{table}
+\end{appendix}
+
 \end{document}

### 2019-10-17 manuscript_pretty.Rmd
draft complete

@@
 bibliography      : ["task-relevance-cspc.bib"]
+appendix          : "appendix_a.Rmd"
 
@@
 \endgroup
+
+```{r echo = FALSE, results = 'asis'}
+render_appendix('appendix_a.rmd')
+```

### 2019-10-17 data-analysis/demographics.R

@@ -19,37 +19,97 @@ df <- rbind(df, demographics_E3[,1:16])
 df$Exp <- as.factor(df$Exp)
 
 age <- df %>%
-  filter(age != "undefined",
-         age != "") %>%
   select(Exp, gender, age, handedness, vision, english) %>%
   mutate(age = as.character(age)) %>%
   filter(age != "male") %>%
   mutate(age = as.numeric(age)) %>%
   group_by(Exp) %>%
-  summarize(
-    mean = mean(age),
-    median = median(age),
-    sd = sd (age)
-  )
+  mutate(bin = case_when(age < 30 ~ "18-29",
+                         age > 29 & age < 40 ~ "30-39",
+                         age > 39 & age < 50 ~ "40-49",
+                         age > 49 & age < 60 ~ "50-59",
+                         age > 59  ~ "> 59",
+                         TRUE ~ "No Response")) %>%
+  ungroup() %>%
+  mutate(bin = as.factor(bin)) %>%
+  group_by(Exp, bin)%>%
+  summarise(n = n()) %>%
+  mutate(freq = round((n / sum(n)*100), digits = 2)) %>%
+  complete(bin, fill = list(n = 0, freq = 0)) %>%
+  arrange(Exp, factor(bin, levels = c("> 59", "50-59", "40-49", "30-39", "18-29", "No Response"))) %>%
+  mutate(bin = as.character(bin))  %>%
+  mutate(freq = format(freq, digits = 2, nsmall = 2))
 
-age <- left_join(age, df %>% 
-  filter(age == "undefined" | age == "" | age == "male" | is.na(age)) %>%
-  group_by(Exp) %>%
-  summarize(
-    `No Response` = n()
-  ), by = c("Exp"))
-
-age[is.na(age$`No Response`),]$`No Response` <- 0
+age <- cbind(age[age$Exp == "E1",2:4],age[age$Exp == "E2",3:4],age[age$Exp == "E3",3:4])
 
 gender <- df %>%
   group_by(Exp) %>%
   summarize(Male = table(gender)[[1]],
             Female = table(gender)[[2]],
-            `No Response` = table(gender)[[3]])
+            `No Response` = table(gender)[[3]]) %>%
[…]

### 2019-10-17 data-analysis/table2.R

@@ -115,6 +115,8 @@ forTable<-as.matrix(table[,2:5])
 
 TR_Table_2 <-paste(
   "\\begin{table}[htbp]",
+  "\\centering",
+  "\\begin{threeparttable}",
   "\\caption{Reaction times and error rates from Experiment 2.}",
   "\\label{TR_table_2}",
   "\\centering",
@@ -128,11 +130,13 @@ TR_Table_2 <-paste(
   paste0("\\multicolumn{1}{l}{25\\%} & \\multicolumn{1}{l}{", paste(forTable[1,],collapse="} & \\multicolumn{1}{l}{"), "} \\\\"),
   paste0("\\multicolumn{1}{l}{50\\%} & \\multicolumn{1}{l}{", paste(forTable[2,],collapse="} & \\multicolumn{1}{l}{"), "} \\\\"),
   paste0("\\multicolumn{1}{l}{100\\%} & \\multicolumn{1}{l}{", paste(forTable[3,],collapse="} & \\multicolumn{1}{l}{"), "} \\\\"),
+  "& & & & \\\\",
   "\\bottomrule",
-  "\\multicolumn{5}{l}{\\textit{Note}: RT = Reaction Time (ms);  ER = Error Rates (\\%);} \\\\",
-  "\\multicolumn{5}{l}{PC = Proportion Congruent; Standard Errors} \\\\",
-  "\\multicolumn{5}{l}{are presented in parantheses.} \\\\",
+  "\\multicolumn{5}{l}{\\textit{Note}: RT = Reaction Time (ms);  ER = Error} \\\\",
+  "\\multicolumn{5}{l}{Rates (\\%); PC = Proportion Congruent; Standard} \\\\",
+  "\\multicolumn{5}{l}{Errors are presented in parantheses.} \\\\",
   "\\end{tabular}%",
+  "\\end{threeparttable}",
   "\\end{table}",
   sep = "\n"
 )

### 2019-10-17 data-analysis/table3.R

@@ -157,6 +157,8 @@ forTable<-as.matrix(table[,3:6])
 
 TR_Table_3 <-paste(
     "\\begin{table}[htbp]",
+    "\\centering",
+    "\\begin{threeparttable}",
     "\\caption{Reaction times and error rates from Experiment 3.}",
     "\\label{TR_table_3}",
     "\\centering",
@@ -179,6 +181,7 @@ TR_Table_3 <-paste(
     "\\multicolumn{6}{l}{\\textit{Note}: RT = Reaction Time (ms);  ER = Error Rates (\\%);} \\\\",
     "\\multicolumn{6}{l}{PC = Proportion Congruent; Standard Errors are presented in parantheses.} \\\\",
     "\\end{tabular}%",
+    "\\end{threeparttable}",
     "\\end{table}",
     sep = "\n"
 )
